### 2019-11-13 article-modif-A&E.tex
initial commit

%% Copernicus Publications Manuscript Preparation Template for LaTeX Submissions
%% ---------------------------------
%% This template should be used for copernicus.cls
%% The class file and some style files are bundled in the Copernicus Latex Package, which can be downloaded from the different journal webpages.
%% For further assistance please contact Copernicus Publications at: production@copernicus.org
%% https://publications.copernicus.org/for_authors/manuscript_preparation.html

%% Please use the following documentclass and journal abbreviations for discussion papers and final revised papers.

%% 2-column papers and discussion papers
\documentclass[npg, manuscript]{copernicus}

%% Journal abbreviations (please use the same for discussion papers and final revised papers)

% Advances in Geosciences (adgeo)
% Advances in Radio Science (ars)
% Advances in Science and Research (asr)
% Advances in Statistical Climatology, Meteorology and Oceanography (ascmo)
% Annales Geophysicae (angeo)
% Archives Animal Breeding (aab)
% ASTRA Proceedings (ap)
% Atmospheric Chemistry and Physics (acp)
% Atmospheric Measurement Techniques (amt)
% Biogeosciences (bg)
% Climate of the Past (cp)
% DEUQUA Special Publications (deuquasp)
% Drinking Water Engineering and Science (dwes)
% Earth Surface Dynamics (esurf)
% Earth System Dynamics (esd)
% Earth System Science Data (essd)
% E&G Quaternary Science Journal (egqsj)
% Fossil Record (fr)
% Geographica Helvetica (gh)
% Geoscientific Instrumentation, Methods and Data Systems (gi)
% Geoscientific Model Development (gmd)
% History of Geo- and Space Sciences (hgss)
% Hydrology and Earth System Sciences (hess)
% Journal of Micropalaeontology (jm)
% Journal of Sensors and Sensor Systems (jsss)
% Mechanical Sciences (ms)
% Natural Hazards and Earth System Sciences (nhess)
% Nonlinear Processes in Geophysics (npg)
% Ocean Science (os)
% Primate Biology (pb)
% Proceedings of the International Association of Hydrological Sciences (piahs)
% Scientific Drilling (sd)
% SOIL (soil)
% Solid Earth (se)
% The Cryosphere (tc)
% Web Ecology (we)
% Wind Energy Science (wes)

%% \usepackage commands included in the copernicus.cls:
%\usepackage[german, english]{babel}
%\usepackage{tabularx}
%\usepackage{cancel}
%\usepackage{multirow}
%\usepackage{supertabular}
%\usepackage{algorithmic}
%\usepackage{algorithm}
%\usepackage{amsthm}
%\usepackage{float}
%\usepackage{subfig}
%\usepackage{rotating}
\usepackage{easy-todo}
\usepackage{graphicx}

% À changer
\newcommand{\yobs}{\mathbf{y}^o}
\DeclareMathOperator*{\argmin}{arg\,min \,}
\DeclareMathOperator*{\argmax}{arg\,max \,}
\newcommand{\Var}{\mathbb{V}\textrm{ar}}
\newcommand{\Ex}{\mathbb{E}}
\newcommand{\Prob}{\mathbb{P}}
\newcommand{\Cov}{\textsf{Cov}}
\newcommand{\tra}{\mathrm{tr}}
\newcommand{\kmean}{{\mathbf{k}}_{\mathrm{mean}}}
\newcommand{\hatkmean}{\hat{\mathbf{k}}_{\mathrm{mean}}}
\newcommand{\kvar}{{\mathbf{k}}_{\mathrm{var}}}
\newcommand{\hatkvar}{\hat{\mathbf{k}}_{\mathrm{var}}}
\newcommand{\kmpe}{{\mathbf{k}}_{\mathrm{MPE}}}
\newcommand{\hatkmpe}{\hat{\mathbf{k}}_{\mathrm{MPE}}}
\newcommand{\kest}{\hat{\mathbf{k}}}

\newcommand{\checkap}{{\alpha}_p}
\newcommand{\checka}{{\alpha}}
\newcommand{\checkk}{\mathbf{k}}
\newcommand{\checkkp}{{\mathbf{k}}_p}
\newcommand{\Kspace}{\mathbb{K}}
\newcommand{\Uspace}{\mathbb{U}}

\newcommand{\arthur}[1]{{\itshape \color{cyan} ({#1})}}
\newcommand{\elise}[1]{{\itshape \color{red} ({#1})}}
\newcommand{\victor}[1]{{\itshape \color{green} ({#1})}}

\begin{document}

\title{Title-- \today{}}%TEXT}

% \Author[affil]{given_name}{surname}

\Author[]{Victor}{Trappler}
\Author[]{Élise}{Arnaud}
\Author[]{Laurent}{Debreu}
\Author[]{Arthur}{Vidard}

\affil[]{Univ. Grenoble Alpes, CNRS, Inria, Grenoble INP*, LJK, 38000 Grenoble, France}
% \affil[]{ADDRESS}

%% The [] brackets identify the author with the corresponding affiliation. 1, 2, 3, etc. should be inserted.

\runningtitle{Title}

\runningauthor{Trappler V.}

\correspondence{Victor Trappler (victor.trappler@univ-grenoble-alpes.fr)}

\received{}
\pubdiscuss{} %% only important for two-stage journals
\revised{}
\accepted{}
\published{}

%% These dates will be inserted by Copernicus Publications during the typesetting process.

\firstpage{1}

\maketitle

% \listoftodos\

\begin{abstract}
Classical methods of parameter estimation usually imply the minimisation of an objective function, that measures the error between some observations and the results obtained by a numerical model. In the presence of random inputs, the objective function becomes a random variable, and notions of robustness have to be introduced.

In this paper, we are going to present how to take into account those uncertainties by defining a notion of robustness based on the distribution of the conditional minimisers and compare it with the minimum in the mean sense, and the minimum of variance.
\victor{Pour le nom: Il y a l'idée que l'on veut avoir un regret $J(\mathbf{k},\mathbf{u}) - \alpha J^*(\mathbf{u})$ controlé à l'aide de $\alpha$: Relative regret ?}
\end{abstract}

\copyrightstatement{TEXT}

%----------------------------------------------------------------------------
% \listoftodos{}

%\arthur{Revoir les notations ($\hat{\bf k}$, ${\bf k}^*$ c'est la meme chose ou pas ? les u, U je ne suis pas sûr que c'est bon non plus)}
%\victor{Pour moi, ce qui est en majuscule, c'est des v.a., et tous les inputs sont en gras (mais on peut laisser tomber le gras)}
\introduction%% \introduction[modified heading if necessary]
%\subsection{Motivation}

Numerical models are widely used to study or forecast natural phenomenon and improve industrial processes. However, by essence models only partially represents reality and sources of uncertainties are ubiquitous (discretisation errors, missing physical processes, poorly known boundary conditions).
%Many physical phenomena are modelled numerically in order to better understand and/or to predict their behaviour. Because of the complexity and or ignorance of the underlying physics, numerical models are imperfect representations of the reality. 
%
%Various sources of uncertainties can corrupt the model quality, such as the discretisation of the domain, or presence of  small scale phenomena that can not be fully represented. 
Moreover, such uncertainties may be of different nature. 
 \cite{walker_defining_2003} propose two to consider two categories of uncertainties. On the one hand aleatoric uncertainties,  coming from the inherent variability of a phenomenon, e.g. intrinsic randomness of some environmental variables. On the other hand, epistemic uncertainties coming from a lack of knowledge about the properties and conditions of the phenomena underlying the behaviour of the system under study.
The latter can be accounted for through the introduction of ad-hoc correcting terms in the numerical model, that need to be properly estimated. Thus, reducing the epistemic uncertainty can be done through parameters estimation approaches. 
%when one is having observations of the reality. 
This is usually done using optimal control techniques, leading to an optimisation of a well chosen cost function which is typically built as a comparison with reference observations.
%
An application of such an approach, in the context of ocean circulation modeling, is the estimation of ocean bottom friction parameters in \cite{das_estimation_1991} and \cite{boutet_estimation_2015}.

If parameters to be estimated are not the only source of uncertainties, their optimal control 
%However, in the presence of other sources of uncertainties, parameter estimation 
is doomed to overfit the data, \emph{e.g} to artificially introduce errors in the controlled parameter to compensate for other sources. If such uncertainties are of aleatoric nature, then the parameter estimation is only optimal for the observed situation, and may be very poor in other configurations, phenomenon coined as \textit{localized optimization} in~\cite{huyse_free-form_2001}.
%A methodology based on the Hessian matrix has been described in~\cite{ribaud_krigeage_2018-1}.
%\arthur{L\`A AUSSI UNE REF SERAIT BIENVENUE}. 
Taking into account aleatoric uncertainties in optimisation problems takes several names, including \textit{robust optimisation}, \textit{robust design} in~\cite{lelievre_consideration_2016}, or \textit{optimization under uncertainties} \citep{petrone_robustness_2011, seshadri_density-matching_2014,cook_horsetail_2018}.

%In this paper we adopt the \textit{robust} terminology.

%Taking into account aleatoric uncertainties while calibrating the model (reducing epistemic uncertainties) is often referred as {\it robust control problem} in the literature (see for instance, \arthur{REFs}), or optimization under uncertainties \citep{petrone_robustness_2011, seshadri_density-matching_2014,cook_horsetail_2018}.

Let's denote $\mathbf{k} \in \Kspace$ the parameter set to be estimated, to reduce epistemic errors. The aleatoric uncertainties are modelled as a random vector $\mathbf{U}$ whose sample space is $\Uspace$. The probability measure of $\mathbf{U}$ is $\Prob_{\mathbf{U}}$, and its density, if it exists, is $p_{\mathbf{U}}$. %Furthermore, $\mathbf{u}^t$ (used to generate $\mathbf{y}^{\mathrm{obs}}$) is sampled from $\mathbf{U}$.
%
The cost function $J(\mathbf{k}, \mathbf{U})$ is a random variable in this context. %, quantity of interest summarising what we aim to represent with our numerical system $J(\mathbf{k}, \mathbf{U})$ is a random variable that will be further designed as the cost function. 
It is most often defined as the squared norm of a given function $\mathcal{G}(\mathbf{k}, \mathbf{U})$% involving the numerical model. 
\begin{align}
  \label{eq:def_cost_fun}
  J(\mathbf{k},\mathbf{U}) & = \frac12\|\mathcal{G}(\mathbf{k}, \mathbf{U})\|^2
  \end{align}
%$J$ is possibly complemented by a regularisation function that is omitted here for the sake of clarity. 
For instance, in data assimilation, $J$ describes a distance between the output of the numerical model and given observed data, plus generally some regularization terms.
%Calibrating the numerical models consists in the computation of $\kest$ verifying
%\begin{equation}
%  \label{eq:khat_def}
%  \kest = \argmin_{\mathbf{k} \in \Kspace} J(\mathbf{k}, \mathbf{u})
%\end{equation}
%\elise{la il y a un soucis car J(k,U) est une variable aleatoire donc on sait pas ce que ca veut dire de prendre le min} \victor{ici ça serait mieux de mettre un $\mathbf{u}^b$}
%
%where $J$ is then an objective function to minimise,
 %
%For a given $\mathbf{k}$, $J(\mathbf{k},\mathbf{U})$ is a random variable. The main point is to be able to compute a value $\mathbf{k}$ that ``minimises'' in a certain sense the random variable $J(\mathbf{k},\mathbf{U})$. \elise{a revoir. un v.a. ne se minimise pas} 
%
For a practical purpose, we assume that $\forall~ \mathbf{u}$ a realisation of $\mathbf{U}$, finding ${\mathbf{k}}_{\mathbf{u}}$ that minimises the cost function $J(\mathbf{k}, \mathbf{U}=\mathbf{u})$ is a well-posed problem, and that the optimum is unique.
Additionally, the following assumption are made: the cost function is strictly positive, and $\forall~  \mathbf{k} \in \Kspace$, the random variable $J(\mathbf{k},\mathbf{U})$ has finite first- and second-order moments.

In this paper, we aim at finding $\kest$ a {\it robust} estimator of $\mathbf{k}$.
The definition of robustness differs depending on the context in which it is used. Indeed, one definition of the robustness of an estimate is a measure of the sensibility of said estimate to outliers~\citep{huber_robust_2011}. This lead to the introduction of robust norms in data assimilation \citep{rao_robust_2015}. %The point of this norm is to assume Gaussian distribution for small errors (the usual $L_2$ norm), while the large errors are assumed to be Laplace distributed (so the $L_1$ norm).
In a Bayesian framework, robustness may refer to the sensitivity to a wrong specification of the priors~\citep{berger_overview_1994}.
%
Throughout this paper, 
%we define robustness as the ability of $\kest$ to perform reasonably well under different operating conditions (i.e.\ different $\mathbf{u}$).
robust has to be understood as satisfactory for a broad range of $\mathbf{u}$, and/or as insensitive as possible to uncertainties encompassed in $\mathbf{U}$.

The usual practice consists in neglecting the variability of $\mathbf{U}$ by setting it to an {\it a priori} value $\mathbf{u}^b$.
 In this case, $\kest$ is set to the optimum ${\mathbf{k}}_{\mathbf{u}^{b}} $ of $J(\mathbf{k}, \mathbf{U}=\mathbf{u}^b)$.  There is no guarantee on the performance of $\kest$ if the calibrated model is used for predictions, as the estimated value will compensate the error made by a possibly wrong specification of $\mathbf{u}^b$.
In a data assimilation context, this situation appears if $\mathbf{u}^b$ does not properly represent the conditions on which the observations have been obtained.
Another strategy, that consists in minimising $J$ over the joint space $\Kspace\times\Uspace$, is not always possible or relevant. The complexity of the optimisation is increased, and the computed estimation of $\kest$ has no reason to be robust in the end: this kind of method does not take into consideration the variability of the uncertain variable. 
%
The worst-case approach \citep{marzat_worst-case_2013} is another popular method, and is based on the minimisation with respect to $\mathbf{k}$ of the maximum of the cost function for $\mathbf{u}\in\Uspace$: $\min_{\mathbf{k}} \max_{\mathbf{u}} J(\mathbf{k}, \mathbf{U} = \mathbf{u})$. This approach may yield over-conservative solutions, and does not take into account the random nature of $\mathbf{U}$.% when the support of $\mathbf{U}$ is unbounded.

Accounting for the probabilistic nature of  $\mathbf{U}$ leads to study the distribution of the random variable $J(\mathbf{k},\mathbf{U})$, or the distribution of its minimisers ${\mathbf{k}}_{\mathbf{U}}$. The latter is referred as 
the distribution of the conditional minimisers, notion that appeared notably in~\cite{villemonteix_informational_2006} and in~\cite{hennig_entropy_2011} for a global optimisation purpose. Both approaches and related robust estimates are described in section \ref{robust formulations}. Section \ref{sec:relax_constraint} introduces a new class of estimators, by relaxing the constraint of optimality and defining regions of acceptability, similarly as~\cite{buhmann_robust_2013} in discrete combinatorial problems.  The intention is that a robust estimate provides values of the cost function close enough to the attainable minimum for each configuration induced by $\mathbf{u}\in\Uspace$. Illustration of the various discribed methods are given on a numerical exemple in section \ref{sec:SWE_application}.

% ----------------------------------------------------------------------------

\section{Classical robust estimators}
\label{robust formulations}

As mentioned before, robustness can be understood as satisfactory for a broad range of $\mathbf{u}$, and/or as insensitive as possible to uncertainties encompassed in $\mathbf{U}$. Under this definition, one may design classical robust estimators, either by optimising the moments of the cost function ; or based on the distribution of its minimisers.

%
%When robustness is defined as the ability of $\kest$ to perform reasonably well under different operating conditions (i.e.\ different $\mathbf{u}$), two classical  approaches can be used to define robust estimators:
%\begin{itemize} 
%\item Optimisation of the statistical moments of the random variable $J(\mathbf{k}, \mathbf{U})$: usually minimisation of the expected value, of the variance or a combination of them
%\item Estimate based on the distribution of the minimisers $\mathbf{k}_{\mathbf{u}}$, assuming the inverse problem is well-posed to ensure the existence and the unicity of the minimiser for each $\mathbf{u}$. 
%\end{itemize}

%\subsection{simple/classical estimators \arthur{TITRE \`A REVOIR}}

%Broadly speaking, two different aspects can be used to define robust estimators:
%\begin{itemize} 
%\item Optimisation of the statistical moments of the random variable: usually minimisation of the expected value, of the variance or a combination of them
%\item Estimate based on the distribution of the minimisers, assuming the inverse problem is well-posed to ensure the existence and the unicity of the minimiser for each $\mathbf{u}$. 
%\end{itemize}

% ----------------------------------------------------------------------------
\subsection{Optimisation of the moments}

%Statistical moments, especially  expectation and variance, are common tools used to describe and summarise a random variable. %A case in point are the Gaussian random variables, that are uniquely defined by their expected value and their variance. 
%It then makes sense that the statistical moments have a central role in robust optimisation. In practice, such ideas relies on the expected value as seen in \cite{shapiro_lectures_2009}, while looking at the same time mean and variance is the basis of Markowitz's portfolio selection theory in \cite{markowitz_portfolio_1952}. 
%

{\color{red} kmean ou kexpectation ?}

Let us define $\mu(\mathbf{k})$ and $\sigma^2(\mathbf{k})$, the expected value and the variance of the cost variable  for a given $\mathbf{k}$ as 
\begin{align}
  \label{eq:def_mu}
  \mu(\mathbf{k}) &= \Ex_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U})\right] = %\int_{\Uspace} J(\mathbf{k},\mathbf{u}) \, \mathrm{d}\Prob_{\mathbf{U}}(\mathbf{u}) 
   \int_{\Uspace} J(\mathbf{k},\mathbf{u})p_{\mathbf{U}}(\mathbf{u}) \, \mathrm{d}\mathbf{u} \\
  \label{eq:def_sigma2}
  \sigma^2(\mathbf{k}) &= \Var_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U})\right] 
  % \int_{\Uspace} \left(J(\mathbf{k},\mathbf{u}) - \mu(\mathbf{k})\right)^2 \, \mathrm{d}\Prob_{\mathbf{U}}(\mathbf{u})
   =\int_{\Uspace} \left(J(\mathbf{k},\mathbf{u}) - \mu(\mathbf{k})\right)^2 p_{\mathbf{U}}(\mathbf{u})\, \mathrm{d}\mathbf{u}
\end{align} 
%
Minimising the expectation leads to the estimate $\kmean$ defined by:
\begin{equation}
  \label{eq:stoch_opt_def_mean}
  \kmean = \argmin_{\mathbf{k}\in\Kspace} \mu(\mathbf{k})
\end{equation}
In order to take into account the spread around the mean value, one can choose to minimise the variance, leading to $\kvar$:
\begin{equation}
  \label{eq:stoch_opt_def_var}
  \kvar = \argmin_{\mathbf{k} \in \Kspace} \sigma^2(\mathbf{k})
\end{equation}

A lot of different methods are readily available to solve these minimisation problems. For instance, stochastic Sample Approximation \citep{juditsky_stochastic_2009,kim_guide_2015} is based on a finite and fixed set of samples $\{ \mathbf{u}^{i}\}_{i=1 \dots N}$  of $\mathbf{U}$.
%the sampling of a certain amount of $\mathbf{U}$ 
The estimations are computed using the following expressions {\color{red} plus subtil qu'un calcul empririque ? si oui, expliciter}:
\begin{equation}
\hatkmean = \argmin_{\mathbf{k} \in \Kspace} \sum_{i=1}^N  J(\mathbf{k},\mathbf{u}^i)
\end{equation}
\begin{equation}
\hatkvar = \argmin_{\mathbf{k} \in \Kspace} \sum_{i=1}^N  \left( J(\mathbf{k},\mathbf{u}^i) -  \sum_{j=1}^N  J(\mathbf{k},\mathbf{u}^j) \right )^2
\end{equation}
%In the following, the hat notation will indicate an estimator. 
If computationally affordable, one can perform these estimations on a regular grid on $\Kspace \times \Uspace$. In case of expensive computer code, one can build a meta model to ease the minimisation, such as Gaussian processes \citep{janusevskis_simultaneous_2010}.
Even though $\kmean$ is a reasonable choice, there is no guarantee that $J(\kmean, \mathbf{U}=\mathbf{u})$ will not reach catastrophic level for some  $\mathbf{u}$. On the other hand, using $\kvar$ will ensure stability of the cost function, but whithout any control of its level of quality.
%
%For a single $\mathbf{k}$, the value of the cost function is controlled in a probabilistic sense by the mean and variance.
%Chebyshev's inequality gives an upper bound on the probability of being more than $\lambda>0$ units from the mean:
%\begin{equation}
%  \label{eq:cheby_ineq}
%  \Prob_{\mathbf{U}}\left[|J(\mathbf{k}% _{\mathrm{mean}}
%    ,\mathbf{U}) - \mu(\mathbf{k}% _{\mathrm{mean}}
%    )|> \lambda\right] \leq \frac{\sigma^2(\mathbf{k}% _{\mathrm{mean}}
%    )}{\lambda^2}
%\end{equation}
%
Ideally, one would want to have a small mean value, and a small variance as well. Multi-objective optimisation is a proper tool to deal with these simultaneous and sometimes concurrent objectives, for exemple by computing the Pareto front of $\left(\mu(\mathbf{k}),\sigma^2(\mathbf{k})\right)$ as done in~\cite{baudoui_optimisation_2012}.

As the computation of this Pareto front is usually hard and expensive, alternative strategies based on the minimisation of a scalarized version of the vector of objectives are often considered. Some are based on a weighted sum of the objectives, as presented in~\cite{grodzevich_normalization_2006} and in \cite{marler_weighted_2010}, while some others are based on the minimisation of one of the objectives under constraints on the others, as performed in~\cite{lehman_designing_2004}. Both of these methods are based on an \textit{delicate} choice of weights or of constraints before any computation. This choice relies heavily on a knowledge of the properties of the cost function.

To summarise, even though the notions of mean and variance are quite easily understood, getting a satisfactory estimator is not that straightforward. One could instead consider how often a particular value $\mathbf{k}$ is a minimiser of the cost function, leading to the notion of most probable estimate, as explained in the next subsection.

{\color{red} mean ou expectation ?}

% ----------------------------------------------------------------------------
\subsection{Most probable estimate}
Let us consider the minimal attainable cost in each configuration brought by $\mathbf{u}$.
The resulting conditional minimum is denoted as $J^*$:
\begin{equation}
\label{eq:def_Jstar}
J^*: \mathbf{u} \in\Uspace \longmapsto J^*(\mathbf{u}) = \min_{\mathbf{k}\in \Kspace} J(\mathbf{k},\mathbf{U}=\mathbf{u})
\end{equation}
Similarly, the function of conditional minimisers can then defined by:
  \begin{equation}
  \label{eq:conditional_minimiser}
   \mathbf{k}^*: \mathbf{u}\in\Uspace \longmapsto \mathbf{k}^*(\mathbf{u}) = \mathbf{k}_{\mathbf{u}}=  \argmin_{{\mathbf{k}}\in\Kspace} J({\mathbf{k}},\mathbf{U}=\mathbf{u})
  \end{equation}
Using this function, we can define the corresponding random variable $\mathbf{K}^*$ as
  \begin{equation}
    \label{eq:def_study_minimisers}
    \mathbf{K}^*= \mathbf{k}^*(\mathbf{U}),
  \end{equation}
and its associated density function $p_{\mathbf{K}^*}(\mathbf{k})$, that will be further referred as the density of minimisers.
The mode of this density is called the Most Probable Estimate (MPE) and is noted  $\kmpe$:
\begin{equation}
  \label{eq:MPE}
  \kmpe = \argmax_{\mathbf{k} \in\Kspace} p_{\mathbf{K}^*}(\mathbf{k}) 
\end{equation}
To give some intuition on this estimate, let us imagine that the distribution of minimisers is a dirac centered on $\kmpe$. Then it would mean that this estimate is the minimiser of the cost function whatever the realisation of the uncertain variable, therefore optimal in all conditions. 
If the distribution $p_{\mathbf{K}^*}$ is heavily dominated by a single value, the MPE may be a good candidate for robust control. This is not so obvious in case of a multimodal distribution. 
In general, an analytical form of $p_{\mathbf{K}^*}$ is usually impossible to obtain, so an estimation $\hat{p}_{\mathbf{K}^*}$ must be used, and its maximum computed to get the MPE.

Once again, a set of samples  $\{\mathbf{u}^i\}_{i=1\dots N}$ can be used to compute the set $\{\mathbf{k}_{\mathbf{u}^i}\}_{i=1\dots N}$, from which one can 
approximate  $p_{\mathbf{K}^*}$. The resulting approximation and therefore its mode, is sensitive to the density estimation method. Main methods are KDE  (Kernel Density Estimation) \cite{elise}, and  EM (Expectation-Maximisation)~\citep{dempster_maximum_1977}.

%Two widely used methods to estimate the density are the KDE (Kernel Density Estimation), and the EM~\citep{dempster_maximum_1977} algorithm to fit a mixture of Gaussian random variable to the observations.

KDE is a non-parametric estimation technique based on the use of a kernel function $f$. Assuming an isotropic kernel, the estimation has the following form:
\begin{equation}
\hat{p}_{\mathbf{K}^*}(\mathbf{k}) = \frac{1}{Nh^{\dim \Kspace}} \sum_{i=1}^N f\left(\frac{\mathbf{k} - \mathbf{k}_{\mathbf{u}^i}}{h}\right)
\end{equation}
where $h$ is the bandwidth. In a multidimensional setting, one usually consider a kernel based on the product of 1D kernels, applied independently to all components: $f(\mathbf{k}) = \prod_{j=1}^{\dim \Kspace} f_{\mathrm{1D}} (k^{(j)})$
where $k^{(j)}$ is the $j$-th component of $\mathbf{k}$. There is wide choice of available $f_{\mathrm{1D}}$, such as a rectangle function, $f_{\mathrm{1D}}(x) = 1 \text{ if } |x|< \frac{1}{2}$ and  $0$ elsewhere, or a Gaussian kernel $f_{\mathrm{1D}}(x)= \frac{1}{\sqrt{2\pi}}\exp(-x^2 / 2)$. One can notice that the rectangle function as a kernel yields non-smooth densities, very similar to the histogram of the minimisers.

The EM algorithm can also be used to estimate the density, by minimising the statistical distance between the empirical distribution and a mixture of $\nu$ Gaussian densities. The estimation has then the following form:
\begin{equation}
\hat{p}_{\mathbf{K}^*}(\mathbf{k}) = \sum_{i=1}^{\nu} \pi_i \phi(\mathbf{k}; \mathbf{m}_i, \mathbf{\Sigma}_i)
\end{equation}
where $\phi( \cdot; \mathbf{m}, \mathbf{\Sigma})$ is the probability density function of the normal distribution of mean $\mathbf{m}$ and covariance matrix $\mathbf{\Sigma}$, and $\{\pi_i \}_{i=1 \dots \nu}$ are the mixing coefficients.

%\elise{Ici parle de l'estimation de kMPE. se referer au cas precedent ou on utilise une ensemble fini de ui. et dire que ca nous génere des kui avec lesquels on fait une approximation de la densite de pK*. Le choix de la methode d'approximation aura une grosse influence sur l'estimation de kMPE. 
%Soit on fait une approximation par noyau (eventuellement noyau créneau d'ou histogramme), ou on peut faire approcher le truc par un melange de gaussienne. Eventuellement reutiliser des phrases du paragraphe suivant (en commentaire) ? }

%The computation of the MPE is more problematic. Indeed, an analytical form of the distribution of the minimisers $p_{\mathbf{K}^*}$ is usually impossible to obtain, so an approximation must be used, and its maximum computed to get the MPE.
%Computationally speaking, to compute a realisation of $\mathbf{K}^*$, a value $\mathbf{u}$ is sampled from $\mathbf{U}$, and a minimisation problem is solved to get $\mathbf{k}^*(\mathbf{u})$. Using the grid mentioned before, 1000 realisations of $\mathbf{K}^*$ have been obtained by direct search on grid.

Despite the fact that those methods are well established, using them in a plug-in approach has some flaws. One of the basic assumption of density estimation is to assume that $\mathbf{K}^*$ is a continuous random variable, hypothesis that may be violated. Worse, the notion of mode is not well defined when the distribution of the minimisers is a discrete-continuous mixture. This may result in inconsistent 
estimations of $\hatkmpe$ when using different methods as illustrated in next subsection.

%The quantities introduced here try to include the random nature of the environmental variables, but the control variable is considered still very locally: some of the values of $\mathbf{k}$, when changed slightly, produce still a very acceptable cost

%Beside the fact that one would like a value that encompasses the robustness capacity of the estimate $\kmpe$, its estimation is sensitive to the required density approximation procedure, 
%\victor{j'ai enlevé la "robustness capacity"}
%However, if the value of this maximum is not high, it may not be considered robust: this formulation does not provide information on the performance of the estimator for the configuration where it is not optimal, situation that happens with probability $1-p_{\mathbf{K}^*}(\kmpe)$.

%In the case where $\mathbf{K}^*$ is continuous, $p_{\mathbf{K}^*}$ is now its probability density function, and $\kmpe$ is defined in the same fashion. 
%However, the MPE is sensitive to the method used to estimate the density as illustrated in Section~\ref{ssec:num_illu}. 
%The introduction of a relaxation of the equality constraint will also allow us to get rid of these issues altogether in Section~\ref{ssec:relax_constraint}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Numerical illustration}
\label{ssec:num_illu}
Before going further in the explanation of our approach, let us illustrate the nature of the 3 previously detailled estimator, $\hatkmean, \hatkvar$ and $\hatkmpe$ on two analytical cost functions. These functions are based on the Branin-Hoo's function, slightly modified to ensure strict positivity:
\begin{align}
  \label{eq:branin_hoo}
 \mathrm{BH}(x_1,x_2) = \frac{1}{51.95}\left[\left(\bar{x}_2 - \frac{5.1 \bar{x}_1^2}{4\pi^2} + \frac{5\bar{x}_1}{\pi} -6 \right)^2 + \left(10 - \frac{10}{8\pi}\right)\cos(\bar{x}_1)-44.81\right]+2\\
\text{with } \bar{x}_1 = 3x_1-5,\quad \bar{x}_2 = 3x_2
\end{align}
%
Using Eq.~\eqref{eq:branin_hoo}, we define the two cost functions on $\Kspace \times \Uspace = [0,5] \times [0,5]$ as:
\begin{align*} J_{\mathrm{BH}} : (\mathbf{k},\mathbf{u}) \mapsto \mathrm{BH}(\mathbf{k},\mathbf{u}) \\
J_{\mathrm{BHswap}} : (\mathbf{k},\mathbf{u}) \mapsto \mathrm{BH}(\mathbf{u},\mathbf{k})
\end{align*}
%We will continue to use $J$ as a generic notation for the cost function, when its use is not specific to the Branin-Hoo function.
Even though the functions are quite similar, the asymmetric roles of $\mathbf{k}$ and $\mathbf{u}$ cause different behaviour.

\begin{figure*}[!ht]
  \includegraphics[width=12cm]{Figures/branin_side_moments_noscale.pdf}
  \caption{Left: Contour of the $J_{\mathrm{BH}}$ function, conditional mean and variance. The estimates $\hatkmean$ and $\hatkvar$ are plotted with the dashed line. Right: $J_{\mathrm{BHswap}}$ function. The scale of the bottom plots have not been represented.} %TODO revoir
\label{fig:branin_moments}
\end{figure*}
%\clearpage % Pour lisibilité dans le preview

The random variable $\mathbf{U}$ is assumed to be uniformly distributed over $\Uspace$.
%The definition and the estimation of $\kmean$ and $\kvar$ is pretty standard.  
The estimations are %$\mathbf{k}\mapsto \mu(\mathbf{k})$ and $\mathbf{k}\mapsto\sigma(\mathbf{k})$ 
based on a $1000 \times 1000$ regular grid over $\Kspace\times\Uspace$. Both cost functions are shown in  Figure~\ref{fig:branin_moments}, top row.

 The left, respectively right, column stands for $J_{\mathrm{BH}}$, respectively $J_{\mathrm{BHswap}}$ function. Functions $\mu(\mathbf{k})$ and $\sigma(\mathbf{k})$ are drawn on the bottom row, respectively in purple and green. The corresponding minimizers $\hatkmean$ and $\hatkvar$ are also plotted.
On this figure, we can observe that $\hatkmean$ and $\hatkvar$ are close for the $J_{\mathrm{BH}}$ function, while have significant different value for the $J_{\mathrm{BHswap}}$ function.
%\clearpage

Illustrations related to $\hatkmpe$ are depicted on Figure \ref{fig:contours}. As before, the set of $\mathbf{u}^i$ is taken from a regular grid. Top row shows the contour plot of both functions as well as the set of conditional minimisers $\{\mathbf{k}_{\mathbf{u}^i}\}_{1\leq i \leq N}$ in red, as defined in Eq.~\eqref{eq:conditional_minimiser}.
The left, respectively right, column stands for $J_{\mathrm{BH}}$, respectively $J_{\mathrm{BHswap}}$ function. The bottom rows presents three approximations of the density of minimisers: the histogram in grey (bin size selected using Freedman-Diaconis from \cite{freedman_histogram_1981}), the result of a kernel density estimation (KDE) with Gaussian kernels in red (using Scott's rule from \cite{scott_optimal_1979} for bandwidth selection), and the estimation by a Gaussian mixture. The latter has been calculated with the EM algorithm. The number of Gaussians has been fixed to 3, a guess based on the general shape of the histogram. Respective estimations of $\hatkmpe$ are also depicted using dashed lines.

%The computation of the MPE is more problematic. Indeed, an analytical form of the distribution of the minimisers $p_{\mathbf{K}^*}$ is usually impossible to obtain, so an approximation must be used, and its maximum computed to get the MPE.
%Computationally speaking, to compute a realisation of $\mathbf{K}^*$, a value $\mathbf{u}$ is sampled from $\mathbf{U}$, and a minimisation problem is solved to get $\mathbf{k}^*(\mathbf{u})$. Using the grid mentioned before, 1000 realisations of $\mathbf{K}^*$ have been obtained by direct search on grid.

%In this paper, we used two different methods to estimate the distribution of the minimisers: KDE (kernel density estimation)~\citep{parzen_estimation_1962,bishop_pattern_2006} and the EM algorithm~\citep{dempster_maximum_1977,borman_expectation_2004} to fit a mixture of Gaussian distributions. This algorithm needing the number of densities to fit, we chose to fit three Gaussian, a guess based on the general shape of the histograms.
%Figure~\ref{fig:contours} shows the contour plot, conditional mean and conditional minimisers of the $J_{\mathrm{BH}}$ function (left) and the $J_{\mathrm{BHswap}}$ function (right).

\begin{figure*}
  \includegraphics[width=12cm]{Figures/branin_side_66.pdf}
  \caption{Top Left:  $J_{\mathrm{BH}}$ function along with conditional minimisers in red. Bottom left: Estimated density using KDE and EM algorithm and conditional mean. The dashed lines indicate the MPE found using those methods. Right: Same quantities with $J_{\mathrm{BHswap}}$. The estimation of the MPE is consistent between the methods for $J_{\mathrm{BHswap}}$, but not for  $J_{\mathrm{BH}}$}
\label{fig:contours}
\end{figure*}

For the $J_{\mathrm{BHswap}}$ function, we can observe that those three methods give coherent results, as $\hatkmpe {}_{,\mathrm{KDE}} =\hatkmpe {}_{,\mathrm{EM}}=\hatkmpe {}_{,\mathrm{histogram}}\approx 0.8$. This is not the case for the  $J_{\mathrm{BH}}$ function however. Using Kernel density estimation (Gaussian), the estimation of $\kmpe$ is $\hatkmpe {}_{,\mathrm{KDE}} \approx 1.5$, while using the histogram and Gaussian mixture, $\hatkmpe {}_{,\mathrm{histogram}}=\hatkmpe {}_{,\mathrm{EM}}=3.8$.
This difference is explained by the accumulation of minimisers at this point: this challenges the assumption that $\mathbf{K}^*$ is continuous. As the density estimation techniques traditionally assume this continuity, the EM algorithm fits this using a normal distribution with a very small variance, while the KDE considers a sum of Gaussian kernels of constant bandwidth, located at the same point. This particular problem highlights the issue with $\kmpe$, as its estimation is highly sensitive to the density approximation procedure.

Alternatively, we can consider the mixing coefficients of the EM density estimation. The Gaussian centered at $1.5$ has been attributed a weight of $0.608$, while the one centered at $3.8$ has a mixing weight of $0.226$. Ultimately, an optimiser would be more likely to be close to $1.5$, but we do not have information on its performance in this region around this value.

% as we can argue that both values may be a sensible choice for the MPE. This comes from the fact that the hypothesis that $\mathbf{K}^*$ is a continuous r.v.\ is violated. 
\victor{Réécrit}
A way to avoid this issue is to introduce a bit of leeway for a value to be optimal, or at least ``acceptably not optimal''. This slackness takes the form of a relaxation coefficient, whose choice leads to a new family of robust estimators, along with a measure of their robustness via the coefficient.
%This leads us to the definition of a new family of estimators, for which one can attribute a {\it level of robustness} \elise{je me rend bien compte que cette phrase est un peu bizarre ...mais bon c'est l'idee}

%, by transforming the equality of Eq.~\eqref{eq:def_R1} into a inequality.

% ----------------------------------------------------------------------------

\section{A new family of robust estimators \elise{titre a revoir}}
\label{sec:relax_constraint}
\subsection{Taking the neighborhood into consideration}
The density of minimisers has been estimated by optimising $\mathbf{k}\mapsto J(\mathbf{k},\mathbf{u})$ over $\Kspace$ for different realisations of $\mathbf{u}$. Instead of only considering  optimal values, we propose to consider their {\it acceptable} neighbourhood in terms of performance of the cost function as well, as illustrated in Figure~\ref{fig:relax_tuto}. 
To do so, for each $\mathbf{u}$, we define as acceptable values of the cost function, the values that are below $\alpha J^*(\mathbf{u})$, with $\alpha > 1$.

For each $\mathbf{u}$, we construct a region around the optimiser that produces acceptable values of the cost function, as seen on the bottom left plot. Looking at it the other way around, for a given $\mathbf{k}$, the set $R_{\alpha}(\mathbf{k}) \subset \Uspace$ is defined as the set of $\mathbf{u}$ verifying the condition of acceptability:
\begin{equation}
\label{eq:def_Ralpha}
R_{\alpha}(\mathbf{k}) = \left\{ \mathbf{u} \in \Uspace \mid J(\mathbf{k},\mathbf{u}) \leq \alpha J^*(\mathbf{u}) \right\}
\end{equation}
% This notion of acceptability will be introduced later.
Finally, for each $\mathbf{k}$, we will measure (with respect to $\Prob_{\mathbf{U}}$) the set of $\mathbf{u}$ within this acceptable neighbourhood, as illustrated in the bottom right plot.

\begin{figure*}[!t]
\includegraphics[width=12cm]{Figures/relaxation_tuto.pdf}
\caption{Principle of the relaxation of the constraint on $J_{\mathrm{BHswap}}$, and illustration of $R_\alpha(\mathbf{k})$}
\label{fig:relax_tuto}
\end{figure*}

%In order to construct this region, we introduce a factor $\alpha \geq 1$, that will be multiplied to $J^*$:
%for a given $\mathbf{u}$, $\mathbf{k}$ is deemed acceptable if $J(\mathbf{k},\mathbf{u}) \leq \alpha J^*( \mathbf{u})$.
Introducing the random nature of $\mathbf{U}$, $\Gamma_\alpha(\mathbf{k})$ is defined as the probability that $\mathbf{k}$ is acceptable given $\alpha$:
\begin{equation}
  \label{eq:def_Gamma}
  \Gamma_\alpha(\mathbf{k}) = \Prob_{\mathbf{U}}\left[\mathbf{U} \in R_\alpha(\mathbf{k})\right] = \Prob_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U}) \leq 
    \alpha J^*(\mathbf{U}) \right]
\end{equation}
In other words, $\Gamma_{\alpha}(\mathbf{k})$ is then the probability that $J(\mathbf{k},\mathbf{U})$ is between 
$J^*(\mathbf{U})$ and 
$\alpha J^*(\mathbf{U})$. Without relaxation, i.e.\ when $\alpha$ is set to $1$, $\Gamma_1$ is non-zero if the set $\{\mathbf{u}\in\Uspace \mid J(\mathbf{k},\mathbf{u}) = J^*(\mathbf{u})\}$ has non-zero measure with respect to $\Prob_{\mathbf{U}}$. Still, this can be related to the definition of the MPE from Eq.~\eqref{eq:MPE}

The motivation behind this relaxation is to take into account the local behaviour of the function around the conditional minimisers.
For a given set of environmental conditions $\mathbf{u}$, if the function $\mathbf{k} \mapsto J(\mathbf{k},\mathbf{u})$ is flat around its minimum $\mathbf{k}^*(\mathbf{u})$, then choosing  $\mathbf{k}^*(\mathbf{u}) + \epsilon$ (for a small $\epsilon$) will produce a value closer to the minimum than when the function has a high curvature.
In addition to that, relaxing the constraint using a multiplicative constant puts more weight (i.e.\ a slower increase of the acceptable region) on the values of $\mathbf{k}^*(\mathbf{u})$ when $J^*(\mathbf{u})$ is close to zero.

Given that $J>0$, $\Gamma_{\alpha}(\mathbf{k})$ is increasing with respect to $\alpha$ for any $\mathbf{k}\in\Kspace$. We can then focus on the smallest value of $\alpha$ such that $\Gamma_\alpha$ reaches a certain level of confidence $p\in[0,1]$. This leads to the definition of $\checkap$
\begin{align}
  \checkap &= \inf\left\{ \alpha\geq 1 \mid \exists \checkkp \in \Kspace,\, \Gamma_{\alpha}(\checkkp) \geq p \right\} \nonumber \\
   &= \inf \left\{ \alpha \geq 1 \mid \max_{\mathbf{k}\in\Kspace} \Gamma_{\alpha}(\mathbf{k}) \geq p \right\}   \label{eq:def_alpha_check}
\end{align}
that is the smallest $\alpha$, such that there exists a particular $\checkkp \in \Kspace$ for which $J(\checkkp,\mathbf{U}) \leq \checkap J^*(\mathbf{U})$ with probability $p$. This formulation can be linked to the Value-at-Risk of the random variable $\max_{\mathbf{k}} \{ \frac{J(\mathbf{k},\mathbf{U})}{J^*(\mathbf{U})}\}$, that is a measure of risk usually applied in the financial sector (see \cite{rockafellar_deviation_2002}). For different levels $p$, and thus different $\alpha_p$, Figure~\ref{fig:illu_alpha_p} shows examples of $\Gamma_{\alpha_p}$. The associated $\mathbf{k}_p$ is then the first value for which $\Gamma_{\alpha_p}$ reaches $p$.

\begin{figure}[!ht]
\centering
\includegraphics[width = 8.3cm]{Figures/illu_alpha_p.pdf}
\caption{Illustration of the influence of different levels $p$ on $\Gamma_{\alpha_p}$ and on $\mathbf{k}_p$ \victor{Est-ce que tu pensais à ce genre de figure ?}}
\label{fig:illu_alpha_p}
\end{figure}

% For computational purpose, we can propose a loose upper bound on relevant values of $\alpha$ from Eq.~\eqref{eq:def_Ralpha}, provided that the maximum and minimum of $J$ is attained on $\Kspace\times\Uspace$. We have that for all $\mathbf{k}$, $\Prob_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U}) \leq \max_{\mathbf{k},\mathbf{u}} J\right]=1$, so
% \begin{equation}
%   \label{eq:upper_bound_alpha}
%   \alpha \geq \frac{\max_{(\mathbf{k},\mathbf{u})} J(\mathbf{k},\mathbf{u})}{\min_{(\mathbf{k},\mathbf{u})} J(\mathbf{k},\mathbf{u}) } \iff R_\alpha(\mathbf{k}) = 1 \quad \forall \mathbf{k}\in\Kspace
% \end{equation}

% In other words, this definition can be seen as the construction of the smallest confidence interval of level $p$:
% \begin{equation}
%  \label{eq:def_CI}
%  \Prob_{\mathbf{U}}\left[ \frac{J(\checkkp,\mathbf{U})}{J^*(\mathbf{U})}\in [1, \checka_p]\right] = p
%\end{equation}

By considering the particular case where $p=1$, a relation between $\checkk_1$ and $\checka_1$ can be derived, by using Eq.~\eqref{eq:def_alpha_check} and the strict positivity of the cost function:
\begin{equation}
  \label{eq:def_alpha1}
  \Prob_{\mathbf{U}}\left[\frac{J(\mathbf{k}_1,\mathbf{U})}{ J^*(\mathbf{U}) } \leq \checka_1\right]=1
\end{equation}
it follows then that 
\begin{equation}
  \label{eq:upper_bound_alpha_check}
  \checka_1 = \sup_{\mathbf{u}\in\Uspace} \frac{J(\mathbf{k}_1,\mathbf{u})}{J^*(\mathbf{u})} =  \inf_{\mathbf{k}\in\Kspace} \left\{ \sup_{\mathbf{u}\in\Uspace} \frac{J(\mathbf{k},\mathbf{u})}{J^*(\mathbf{u})} \right\} 
\end{equation}

This alternative definition of $\checka_1$ is useful to estimate quickly $\hat{\checka}_1$ whenever a grid over $\mathbb{K}\times\mathbb{U}$ has already been evaluated, thus avoiding multiple computations of $\Gamma_{\alpha}(\mathbf{k})$ until its maximum reaches $1$. By Eq.\eqref{eq:upper_bound_alpha_check}, choosing a level of confidence equal to $1$ is then equivalent to looking for the worst-case scenario of the ratio $\frac{J(\mathbf{k},\mathbf{u})}{J^*(\mathbf{u})}$, and therefore suffers from the same pitfall of the worst-case approach. As mentioned in the introduction, this returns over-conservative solution, and is not suited for random variable with unbounded support.

A high value of $\checka_1$ corresponds to a high ratio $\frac{J(\mathbf{k},\mathbf{u})}{J^*(\mathbf{u})}$ for at least one particular $\mathbf{u}$. In that sense, $J(\checkk_1,\mathbf{u})$ may be possibly very high.
More generally, for a level of confidence $p$ fixed, $\checkap$ is the slackness needed to be able to reach the probability $p$. So, in addition to the value of the estimate $\checkkp$, we have an indicator of the robustness associated. We can then see that it is sensible to study jointly $p$, $\checkap$ and $\checkkp$ in order to make a final decision.

\subsection{Concurrence between $p$ and $\alpha$}%Finding a balance between $p$ and $\checkap$}%Selection of a level of confidence}
\label{ssec:balance}
For a practical purpose, we suppose that we have sampled $N$ values of $\mathbf{U}$, namely $\{\mathbf{u}^i\}_{1\leq i \leq N}$.
In order to estimate the quantities introduced above, there are two starting points: either fixing $p$ or fixing the maximal threshold $\alpha$. 
The most trivial way is to set $\alpha$, to find the couples of points $(\mathbf{k},\mathbf{u})$ verifying $J(\mathbf{k},\mathbf{u}) \leq \alpha J^*(\mathbf{u})$, and then to estimate the probability $\Gamma_{\alpha}(\mathbf{k})$ defined in Eq.~\eqref{eq:def_Ralpha} as 
\begin{equation}
\hat{\Gamma}_{\alpha}(\mathbf{k}) = \frac{\# \left\{\mathbf{u}^i \mid J(\mathbf{k},\mathbf{u}^i) \leq \alpha J^*(\mathbf{u}^i)\right\}}{N}
\end{equation}
If $\alpha$ is chosen too small, the resulting $\hat{p}=\max_{\mathbf{k}} \hat{\Gamma}_{\alpha}(\mathbf{k})$ will be also too small, meaning that the cost function will overshoot the value $\alpha J^*(\mathbf{U})$ with high probability.

Similarly, if $p$ is fixed, the corresponding $\hat{\checka}_p$ is computed by searching for the smallest $\alpha$ such that $\max_{\mathbf{k}} \hat{\Gamma}_{\alpha}(\mathbf{k})$ is equal to the level $p$ fixed beforehand. In the end, if the value $\hat{\checka}_p$ is too large, the relaxation needed to get acceptable values with probability $p$ is very high, so the resulting estimation $\hat{\checkk}_p$ may not be relevant for the future application.
\victor{chapeau car ici je parle de l'estimation en pratique}

Without posing any constraints on $p$ nor on $\alpha$, a compromise between $p$ and $\alpha$ would be preferable, and a rough idea of this balance can be obtained by studying $p \mapsto \checkap$, and particularly its slope.
If this curve presents a steep increase, the multiplicative constant $\checkap$ must be increased by a large amount in order to increase the probability $p$ by a small amount. Interesting couples $(p,\checkap)$ would then be the ones located before an abrupt increase of the slope of $p \mapsto \checkap$.

Another possibility is to combine directly $p$ and $\checkap$ in order to find a compromise. We opted to model this compromise by the ratio $(p/\checkap)$, as it increases with respect to $p$ and decreases with respect to $\checka_p$. The level of confidence $p_{\mathrm{maxratio}}$ is then defined as the maximiser of $p\mapsto p / \checka_p$.

The different estimators introduced in this paper are summarised in Table~\ref{tab:RO_recap}.

\begin{table*}[t]
  \caption{Robust estimators, based on a cost function $J$}
  \label{tab:RO_recap}
\begin{tabular}{lrr}
  \tophline
  Definition & Related quantities & Interpretation \\
  \middlehline
   $\argmin_{\mathbf{k}\in\Kspace} \Ex_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U})\right]$& $\kmean$ & Long run performances\\
   $\argmin_{\mathbf{k}\in\Kspace} \Var_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U})\right]$& $\kvar$  & Steady performances\\
   $\argmax_{\mathbf{k}\in\Kspace} p_{\mathbf{K}^*}(\mathbf{k})$ & $\kmpe$ & Most probable minimiser\\
    $\inf\left\{ \alpha \mid \exists \checkkp \in \Kspace,\, \Gamma_{\alpha}(\checkkp) \geq p \right\}$ & $(p, \checkkp,\checkap)$ & Acceptable values with fixed probability $p$ \\
    $p_{\mathrm{maxratio}} = \argmax p/\checkap$ & $(p_{\mathrm{maxratio}}, \checkk_{\mathrm{maxratio}}, \checka_{\mathrm{maxratio}})$ & Maximal ratio of $p$ and $\checkap$ \\
  \bottomhline
\end{tabular}
\end{table*}

%We are now going to compute and compare those estimators on the $J_{\mathrm{BH}}$and $J_{\mathrm{BHswap}}$ function.

% ----------------------------------------------------------------------------
\subsection{Estimation of $\checkkp$ and $\checkap$ for the $J_{\mathrm{BH}}$ and $J_{\mathrm{BHswap}}$ functions}
%Numerical application}
As stated before, we chose to model the uncertainties as a random variable uniformly distributed on $\Uspace$. The bounded nature of $\Uspace$ allow us to consider the estimate introduced before up to a level of confidence $p=1$.
From now on, $\hatkmpe$ is estimated using KDE with Gaussian kernels.
The smallest relaxation $\hat{\checka}_1$ and the corresponding $\hat{\checkk}_1$ has been computed for the $J_{\mathrm{BH}}$ and $J_{\mathrm{BHswap}}$ functions, using a regular grid of $1000 \times 1000$ points on $\Kspace\times\Uspace$. The contour plots of those functions can be seen in the top plots of Figure~\ref{fig:contour_alpha}. The frontier corresponding to the couples of points $(\mathbf{k},\mathbf{u})$ verifying $\{J(\mathbf{k},\mathbf{u}) = \hat{\checka}_1 J^*(\mathbf{u})\}$ has been drawn on top of these contour plots. 
On the bottom plots, the curve $\mathbf{k}\mapsto \hat{\Gamma}_{\alpha}(\mathbf{k})$ for $\alpha=\hat{\checka}_1$ and $\alpha=1.5$ along with the histogram of the minimisers have been represented.

\begin{figure*}[!ht]
\includegraphics[width=12cm]{Figures/branin_side_66_relax_gamma_both.pdf}
\caption{Top: $J_{\mathrm{BH}}$ and $J_{\mathrm{BHswap}}$ contours. The thick yellow lines are the boundaries of the acceptable region defined for $\hat{\checka}_1$, the thick orange are for $\alpha=1.5$. The red dashed line is the estimation $\hat{\checkk}_1$. Bottom: $\hat{\Gamma}_{\alpha}$ for $\alpha = 1.5$ and $\alpha=\hat{\checka}_1$, and estimated density of the minimisers.}
\label{fig:contour_alpha}
\end{figure*}

% For the $J_{\mathrm{BH}}$ function (left), the $\hat{\checka}_1$, $\hatkmean$ and $\hatkvar$ are quite close, so naturally we would expect a robust estimate to be significantly close to those values. $\hat{\checkk}_1$ supports this intuition, and appears to be very close to $\hatkmean$. 
%Concerning the $J_{\mathrm{BHswap}}$ function (right), $\hat{\checkk}_1$ appears to be closer to $\hatkvar$ this time.

In order to choose a satisfying level of confidence $p$, we are going to study $p\mapsto \hat{\checka}_p$ and $p\mapsto p/\hat{\checka}_p$, as described in~\ref{ssec:balance}.

 The plot of $p\mapsto \hat{\checka}_p$ for the $J_{\mathrm{BH}}$ function on Figure~\ref{fig:ratio_BH} shows what seems to be a piecewise linear behaviour. The last change of slope, i.e.\ for $p\approx 0.9$ corresponds to a local maximum of the ratio, while the first change of slope corresponds to the global maximum of the ratio.

\begin{figure}[!ht]
\includegraphics[width=12cm]{Figures/alpha_p_BH.pdf}
\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for the $J_{\mathrm{BH}}$ function. The dashed line indicates the level $p$ associated with the highest ratio}
\label{fig:ratio_BH}
\end{figure}

 For the $J_{\mathrm{BH}}$ function, the numerical values can be found in Table~\ref{tab:recap_estimates_branin}. One can notice that the different estimates are close to each other for this problem.

\begin{table*}[!ht]
\centering
\caption{Estimation performed for $J_{\mathrm{BH}}$, sorted by value}
\label{tab:recap_estimates_branin}
\begin{tabular}{lr}
\tophline
Estimate & Value \\ \middlehline
$\hatkvar$ & 1.371 \\ 
$\kest_p,~p=1$ & 1.557 \\ 
$\hatkmean$ & 1.587 \\ 
$\hatkmpe$ & 1.628 \\ 
$\kest_p,~p=0.95$ & 1.672 \\ 
$\kest_{\mathrm{maxratio}},~\hat{p}_{\mathrm{maxratio}}=0.654$ & 1.637 \\ \bottomhline
\end{tabular}
\end{table*}

Practically speaking, in order to compare the effective values taken by the objective function given an estimate $\kest$ we are going to consider the functions of the form $\mathbf{u} \mapsto J(\kest,\mathbf{u})$, that we will call "profile of $\kest$". Those profiles are well suited for the representation of the cost function for an estimate $\kest$ fixed as the uncertain variable is modelled with a 1D uniform random variable.

For the $J_{\mathrm{BH}}$ function, the curves are plotted in Figure~\ref{fig:profiles_branin}. Based on its definition, the profile of $\hat{\checkk}_1$ is always within the shaded region, corresponding to $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$. The profile of $\hatkmean$ in contrast, exceeds $\hat{\checka}_1 J^*(\mathbf{u})$ for $\mathbf{u}$ close to $5$, while the profile of $\hatkvar$ does for $\mathbf{u}$ close to $0$.

\begin{figure*}[t]
\includegraphics[width=12cm]{Figures/profile_BH_all_estimates_noku.pdf}
\caption{Profiles of the different estimates for the $J_{\mathrm{BH}}$ function, corresponding to the vertical cross sections of the contour. The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$. The red dashed line, corresponding to the values taken by the cost function when the control variable is set to $\mathbf{k}_1$, is always between $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$ per design.}
\label{fig:profiles_branin}
\end{figure*}

We are now going to shift our focus on the $J_{\mathrm{BHswap}}$ function, as Figure~\ref{fig:ratio_BHs} provides the plots of $p\mapsto \hat{\checka}_p$ and $p\mapsto p/\hat{\checka}_p$.
\begin{figure}[ht]
\includegraphics[width=12cm]{Figures/alpha_p_BHs.pdf}
\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for the $J_{\mathrm{BHswap}}$ function. The dashed line indicates the level $p$ associated with the highest ratio}
\label{fig:ratio_BHs}
\end{figure}

Compared to the plots for $J_{\mathrm{BH}}$ in Figure~\ref{fig:ratio_BH}, $\hat{\checka}_p$ exhibits a smoother behaviour for the $J_{\mathrm{BHswap}}$ function as no change of slope is easily discernable. The computation of the ratio advocates for a level of confidence $p_{\mathrm{maxratio}}$ close to $0.75$. The numerical values of the estimations $\hat{k}$ presented in Table~\ref{tab:recap_estimates_BHs} show that contrary to the $J_{\mathrm{BH}}$ function, the objective are concurrent.

\begin{table*}[!h]
\centering
\caption{Estimations performed for $J_{\mathrm{BHswap}}$, sorted by value}
\label{tab:recap_estimates_BHs}
\begin{tabular}{lr} \tophline
Estimate & Value \\ \middlehline
$\kest_{\mathrm{MPE}}$ & 0.606 \\ 
$\kest_{\mathrm{maxratio}},~ \hat{p}_{\mathrm{maxratio}}=0.766$ & 1.537 \\ 
$\kest_{\mathrm{mean}}$ & 1.752 \\ 
$\kest_p,~p=0.90$ & 2.112 \\ 
$\kest_p,~p=0.95$ & 2.457 \\ 
$\kest_{\mathrm{var}}$ & 2.638 \\ 
$\kest_1,~p=1$ & 2.798   \\ \bottomhline
\end{tabular}
\end{table*}

In a similar fashion, the profiles of the different estimates for the $J_{\mathrm{BHswap}}$ function are shown in Figure~\ref{fig:profiles_branin_switch}.

In this case, $\hatkmpe$, $\hatkmean$ and $\hat{\checkk}_{\mathrm{maxratio}}$ present a similar behaviour. They perform very well for $\mathbf{u}>2$, especially for $\hatkmpe$ which is very close to the minimal value; for $\mathbf{u}<2$, it produces high values of the function. 
The performances of $\hat{\checkk}_1$ are closer to the performances of $\hatkvar$ for this function, but it performs worse than $\hatkmean$ and $\hatkvar$ for $\mathbf{u}>2$, even though its range is designed to stay within the interval $[J^*(\mathbf{u}); \hat{\checka}_1 J^*(\mathbf{u})]$.

\begin{figure*}[t]
\includegraphics[width=12cm]{Figures/profile_BHs_all_estimates_noku.pdf}
\caption{Profiles of the different estimates for the $J_{\mathrm{BHswap}}$ function. Those profiles are the vertical cross sections of the contours above. The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$. The red dashed line, corresponding to the values taken by the cost function when the control variable is set to $\mathbf{k}_1$, is always between $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$ per design.}
\label{fig:profiles_branin_switch}
\end{figure*}

% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------
\clearpage

% ----------------------------------------------------------------------------
\section{Robust calibration of a numerical model}
\label{sec:SWE_application}
% ----------------------------------------------------------------------------

\subsection{Calibration of a toy numerical model}
 We will follow \citeauthor{kennedy_bayesian_2001}'s approach in order to establish the function $\mathcal{G}$ described in the first section in Eq.~\eqref{eq:def_cost_fun}, and the resulting cost function $J$.

 Calibration of a numerical model is usually based on the comparison between the numerical model and some observations in a fixed time interval $[0, T]$ called assimilation window.
The physical system at stake is based on an input $\mathbf{u} \in \mathcal{U}$, that represents some operating conditions. This system can then be seen as a map from $\mathcal{U}$ to $\mathcal{Y}$, denoted as $\mathcal{M}^o : \mathbf{u}\mapsto \mathcal{M}^o(\mathbf{u})$.

In addition to the operating conditions $\mathbf{u}$, the numerical model is also dependent on some other input $\mathbf{k}\in\mathcal{K}$. This additional parametrization comes usually from the successive simplifications needed to implement a numerical model of the physical system observed, and from some unobserved physical parameters. These parameters need to be calibrated accordingly, so that the numerical model can be used to predict the behaviour of the physical system under different operating conditions.

The true value taken by the physical system during this window is denoted by $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) \in \mathcal{Y}$, where $\mathbf{u}^{\mathrm{true}} \in \mathcal{U}$ is unknown. The misfit $\mathcal{G}$ and the cost function $J$ defined Eq.\eqref{eq:def_cost_fun} can then be defined as
\begin{equation}
J(\mathbf{k},\mathbf{u}) = \frac12 \| \mathcal{G}(\mathbf{k},\mathbf{u}) \|^2 = \frac12 \|\mathcal{M}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}(\mathbf{u}^{\mathrm{true}}) \|^2
\end{equation}
\subsection{The Shallow Water equations}

The model we wish to calibrate is based on the Shallow Water equations, described Eq.~\eqref{eq:SWE_equations}. $h$ is the height of the water column, $q$ is the discharge, and $z$ is the bathymetry, while $g$ is the usual gravitation constant. The parameter to calibrate, $\mathbf{k}$, is the quadratic friction term, proportional to the square of the inverse of Manning-Strickler coefficient. The environmental parameter $\mathbf{u}$ is the amplitude of a sine wave of period $1$. The domain of those two parameters are $\mathcal{K} = [0.0, 1.3]$ and $\mathcal{U} = [0.5, 0.7]$.

\begin{align}
  \label{eq:SWE_equations}
  \left\{
    \begin{array}{rl}
      \partial_t h + \partial_x q &= 0 \\
      \partial_t q + \partial_x \left(\frac{q^2}{h} + \frac{g}{2}h^2\right) &= - gh\partial_x z - \mathbf{k}q |q|h^{-7/3} \\
      h(0, t) &= 20.0 + 3\cdot \sin \left(\frac{2\pi t}{2}\right) + 1.5\cdot \mathbf{u} \cdot \sin\left(2 \pi t\right)\\
      \partial_x q(0, t) &= 0
      \end{array}
  \right.
\end{align}
These equations are integrated using a finite-volume scheme on a discretized domain $[0, L]$, up to a time $T$. The output of the computer code is the sea surface height $h$, on the center of all the volumes and at all the time-steps, that will be denoted $\mathcal{M}(\mathbf{k},\mathbf{u})$.
In this setting, the variable input is uniformly distributed on $\mathcal{U}$.
To generate the observations, we choose $\mathbf{u}^{\mathrm{true}}=2/3$, and define $\mathcal{M}^o$ based on the computer model $\mathcal{M}$, such that $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) = \mathcal{M}(\mathbf{k}^{\mathrm{true}}, \mathbf{u}^{\mathrm{true}})$. 
This true value $\mathbf{k}^{\mathrm{true}} = (k_1^{\mathrm{true}}, k_2^{\mathrm{true}},\dots, k_{N_\mathrm{vol}}^{\mathrm{true}})$ is not constant over the whole domain, and is defined as
\begin{equation*}
{k}^{\mathrm{true}}_i = 0.2\cdot \left(1 + \sin\left(\frac{2 \pi x_i}{L}\right)\right)
\end{equation*}
where $x_i$ is the center of the $i$-th volume.
\subsection{Estimation}

\begin{figure}[!h]
\centering
\includegraphics[width=12cm]{Figures/RobustSWEmis_plots.pdf}
\caption{Procedure of robust calibration for the shallow water problem. Top: contours of $J$, conditional minimisers and $\{(\mathbf{k},\mathbf{u}) | J(\mathbf{k},\mathbf{u}) = \hat{\alpha}_1 J^*(\mathbf{u})\}$. Middle: Conditional moments and histogram and KDE of the conditional minimisers. Bottom: $\hat{\Gamma}_{\alpha_p}$ for different levels $p$}
\label{fig:my_label}
\end{figure}
\begin{table*}[!h]
\centering
\begin{tabular}{lr}
Estimator & Value \\ \hline
$\hat{\mathbf{k}}_{p},~p=1$ & 0.423 \\ 
$\hat{\mathbf{k}}_p,~p=0.90$ & 0.458 \\ 
$\hat{\mathbf{k}}_{\mathrm{mean}}$ & 0.501 \\ 
$\hat{\mathbf{k}}_p,~p=0.80$ & 0.505 \\ 
$\hat{\mathbf{k}}_p,~p=0.70$ & 0.560 \\ 
$\hat{\mathbf{k}}_{\mathrm{var}}$ & 0.990 \\
\end{tabular}
\caption{Estimation of $\mathbf{k}$ according to different criterion}
\label{tab:recap_estimates_metaSWE}
\end{table*}

\subsection{Assessing the quality of the forecast of the calibrated model}
The calibration of the model has been performed on the time-period $[0, T]$, called assimilation window. 
We now want to compare the quality of the different forecasts depending on the criterion used to calibrate the bottom friction.
To define those forecasts, the models will be integrated from $T$ to $T_{\mathrm{pred}}$.

Given the probabilistic nature $\mathbf{U}$, the forecasts will also be probabilistic. We will then compare $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{U})$, for a calibrated $\mathbf{k}$.

\subsubsection{Squared forecast error}
Let us assume that the observations result from the parameter $\mathbf{u}'$, while the computer simulation is run using $\mathbf{u}$.
The squared forecast error given $\mathbf{u}$ and $\mathbf{u}'$ is
\begin{equation}
\label{eq:squared_forecast_error}
S_{\mathrm{pred}}(\mathbf{k},\mathbf{u},\mathbf{u}') = \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}')\right)^2
\end{equation}
We can then get an estimation of the mean squared forecast per volume per time step:

\begin{equation}
  \label{eq:squared_forecast_error_averaged}
  S(\mathbf{k}) = \frac{1}{N_{\mathbf{u}} N_{\mathbf{u}'}}\sum_{\mathbf{u},\mathbf{u}'} S_{\mathrm{pred}}(\mathbf{k},\mathbf{u},\mathbf{u}') = \frac{1}{N_{\mathbf{u}} N_{\mathbf{u}'}}\sum_{\mathbf{u},\mathbf{u}'}\left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}')\right)^2
\end{equation}

\subsubsection{Averaged Quantile score}
A first approach is to compare the quantiles obtained by the prediction $\mathcal{M}_{\mathrm{pred}}(\kest,\mathbf{U})$, with the quantiles observed of $\mathcal{M}^o_{\mathrm{pred}}(\mathbf{U})$.
We are first going to introduce the pinball loss, or checkloss function:
\begin{equation}
\label{eq:checkloss}
\rho_{\tau}(x) = \begin{cases}
    \tau |x| \quad \text{ if } x \geq 0 \\
    (1- \tau) |x| \quad \text{ if } x < 0
\end{cases}
\end{equation}

Given the time index $j$, and the volume indexed by $i$, the quantile of order $\tau\in [0, 1]$ of $\mathcal{M}(\kest, \mathbf{U})_{(i,j)}$ is $q_{(i,j)}(\tau)$.
Given an obse
\begin{figure*}[t]
\includegraphics[width=12cm]{Figures/forecast_metric.pdf}
\caption{Quality of forecast, depending on the calibrated parameter. The left figures show the metric averaged over time, while the right figures show}
\label{fig:forecast_metric}
\end{figure*}

% \subsection{The Lorenz-63 model}
% A classical toy problem in data assimilation is the Lorenz-63 model, introduced in \cite{lorenz_deterministic_1963}. 
% % xb
% The evolution of the state vector $(x,y,z)$ is described by the non-linear differential system of Eq.~\eqref{eq:lorenz_equations}
% \begin{align}
%   \label{eq:lorenz_equations}
%   \left\{
%     \begin{array}{l}
%       \dot{x} = \sigma\left(y-x \right) \\
%       \dot{y} = \rho x - y - xz \\
%       \dot{z} = xy - \beta z
%       \end{array}
%   \right.
% \end{align}
% Despite its apparent simplicity, this system is known to show chaotic behaviour for $(\sigma,\rho,\beta) = (10, 28, 8/3)$. 
% This differential system is solved numerically using a Runge-Kutta scheme, over $N=100$ time-steps of length $\Delta t = 0.05$. In that time-period, the chaotic behaviour is not yet too apparent.

% The inputs of the computer code are the initial conditions $\left(x_0,y_0,z_0\right)$ and $(\sigma, \beta, \rho)$. The parameter to calibrate is $\mathbf{k}=x_0-1$ with $\mathbf{k}\in[-0.05,0.05]$, and the uncertain parameter is $\mathbf{u}=\beta - 8/3$ with $\mathbf{u} \in \Uspace=[-0.05, 0.05]$. Finally, we suppose that the random variable $\mathbf{U}$ follows an uniform distribution on $\Uspace$. Solving numerically the differential system using those settings yields $x_{i}(\mathbf{k},\mathbf{u})$ for $i$ between $1$ and $N$.

% This problem of calibration will be studied in a twin experiments framework: the target state $x^{o}_i$ for $1\leq i \leq N$ has been generated by the computer code, where the parameters used to generate it are detailed in Table~\ref{tab:lorenz_modelling}. One can notice the discrepancy of $\rho$ between the observations and the model, introduced to ensure that no perfect fit can be achieved, for any set of parameters. 
% \begin{table*}[h]
%   \caption{Choice of modelling of the Lorenz-63 system}
%   \label{tab:lorenz_modelling}
% \begin{tabular}{crrl}
%   \tophline
%   Parameter & Observation: $x_{1:N}^o$ & Modelling: $\mathcal{G}(\mathbf{k},\mathbf{u})$ & Type \\
%   \middlehline
%  $\sigma$ & $10$ & $10$ & Fixed\\
%   $\rho$ & $29$ & $28$ & A priori chosen and fixed \\
%   $\beta$ & ${8}/{3}$ & ${8}/{3} + \mathbf{u}$ & A priori chosen and uncertain \\
%  $x_0$ & $1$ & $1 + \mathbf{k}$ & Calibrated \\
%   $y_0$ & $0$ & $0$ & Fixed \\
%  $z_0$ & $0$ & $0$ & Fixed \\
%   \bottomhline
% \end{tabular}
% \end{table*}

% The misfit between the observations and the output of the numerical model is quantified using the cost function:
% \begin{equation}
% \label{eq:cost_fun_lorenz}
% J(\mathbf{k},\mathbf{u}) = \frac{1}{2}\|\mathcal{G}(\mathbf{k},\mathbf{u}) \|^2 = \frac{1}{2} \|x_{1:N}(\mathbf{k},\mathbf{u}) - x^o_{1:N} \|^2 = \frac{1}{2}\sum_{i=1}^N (x_i(\mathbf{k},\mathbf{u}) - x_i^o)^2
% \end{equation}

% This toy model is cheap to evaluate, so the global minimum can be computed using numerical methods, at different starting points to avoid local minimums.
% \begin{equation}
% \label{eq:min_global_lorenz}
% \min_{(\mathbf{k},\mathbf{u}) \in \Kspace\times\Uspace} J(\mathbf{k},\mathbf{u}) = 38.886712815 \quad \argmin_{(\mathbf{k},\mathbf{u}) \in \Kspace\times\Uspace} J(\mathbf{k},\mathbf{u}) = (0.02414384, -0.00551042)
% \end{equation}

% \subsubsection{MPE and conditional moments}
% Figure~\ref{fig:lorenz_kde_moments} shows the cost function $J$, computed on a regular grid over $\Kspace\times\Uspace$. Using this grid, the conditional mean and standard deviation have been computed, while the MPE has been estimated by KDE. For a single $\mathbf{u}$, it may appear that there are multiple $\mathbf{k}^*(\mathbf{u})$. This is due to the fact that the conditional minimiser jumps back and forth between the two curves.

% \begin{figure}[!h]
% \includegraphics[width=12cm]{Figures/lorenz_kde_moments.pdf}
% \caption{Cost function, locus of conditional minimisers, MPE estimated with KDE, conditional moments and their associated estimates}
% \label{fig:lorenz_kde_moments}
% \end{figure}

% \subsubsection{Relaxation of the constraint}
% Based on the computations described before, the coefficient $\checkap$ have been computed for $p=0.9$, $0.95$ and $p=1$, and reported in Table~\ref{tab:recap_estimates_lorenz}. The curve $R_{\checka_1}$ is plotted in Figure~\ref{fig:lorenz_relax}, where the acceptable region for $\checka_1$ is filled in yellow.

% \begin{figure}[!h]
% \includegraphics[width=12cm]{Figures/lorenz_f3.pdf}
% \caption{Relaxation of the constraint for the Lorenz model. Acceptable region in yellow}
% \label{fig:lorenz_relax}
% \end{figure}

% We can see that for $\mathbf{k}$ being approximately between $0$ and $0.01$, the probability $R_{\checka_1}$ is very close to $1$. Indeed, the cost function seems to be relatively flat on this region, as $\checkk_{0.9} \approx \kmpe$.

% \begin{table*}[!h]
%   \caption{Estimates computed numerically on the Lorenz-63 model}
%   \label{tab:recap_estimates_lorenz}
%   \begin{tabular}{*{3}{r}}\tophline
%     Estimate & Value & Related quantities\\
%     \middlehline
%     $\hatkmean$        & $ 0.008779$ &$\left(\mu(\kmean),\sigma(\kmean)\right) = (42.965, 4.921)$\\
%     $\hatkvar$         & $-0.025338$ &$\left(\mu(\kvar),\sigma(\kvar)\right)= (50.704, 2.024)$\\
%     $\hatkmpe$         & $ 0.008779$ & $\Gamma_1(\kmpe) = 0.053$ \\
%     $\hat{\checkk}_{0.9}$ & $ 0.008729$ & $\hat{\checka}_{0.9}  = 1.202788$ \\
%     $\hat{\checkk}_{0.95}$& $ 0.006078$ & $\hat{\checka}_{0.95} = 1.226050$ \\
%     $\hat{\checkk}_{1}$   & $ 0.000275$ & $\hat{\checka}_{1}    = 1.311002$ \\
%     \bottomhline
%     \end{tabular}
% \end{table*}

% \subsubsection{Selection of the couple $(p,\checkap)$}
% The evolution of $\checkap$ with respect to $p$ is shown on the left plot of Figure~\ref{fig:evolution_p_lorenz}. We can see that $\checkap$ presents two abrupt positive change of slope, for $p$ set to $0.85$ and just before $1$. Those confidence levels corresponds to the local maxima of the ratio $p/\checkap$, that is shown on the right plot of Figure~\ref{fig:evolution_p_lorenz}. The profile of $\checkk_{0.85}$ corresponding to the local maximum of the ratio, has not been plotted as it corresponds to the same profile of $\kmean$.

% \begin{figure*}[!h]
% \includegraphics[width=12cm]{Figures/evol_p_lorenz.pdf}
% \caption{Evolution of $p$ and $\checkap$}
% \label{fig:evolution_p_lorenz}
% \end{figure*}
% In order to compare the values taken by the objective function, the profiles have been represented on Figure~\ref{fig:lorenz_profiles}.
% \begin{figure}[!h]
% % \includegraphics[width=12cm]{Figures/lorenz_cdf_profile.pdf}
% \includegraphics[width=12cm]{Figures/profile_lorenz_all_estimates.pdf}
% \caption{Profiles of different $\mathbf{k}$ for the Lorenz model}
% \label{fig:lorenz_profiles}
% \end{figure}
% The profile of $\kmean$ presents a good insight on the performances of this estimate: for most values of the uncertain variables, the objective is low. In contrast, for $\mathbf{u}$ close to $0.05$, a maximum is reached. 
%\begin{figure}[!h]
%\includegraphics[width=8.3cm]{Figures/cdf_lorenz_with_ratio.pdf}
%\caption{CDF corresponding to different $\mathbf{k}$ for the Lorenz model}
%\label{fig:lorenz_cdf}
%\end{figure}

% \clearpage
% \subsection{Context: Shallow water equations and bottom friction}

% The quality of water circulation modelling in coastal areas is largely dependent on the boundary conditions, (e.g.\ the tide), the bathymetry and the friction induced by the rugosity of the ocean bed \citep{boutet_estimation_2015}. The latter will then be estimated in a robust manner, by applying the criteria introduced above.

% The model studied is based on the one-dimensional shallow water equations, described Eq.~\eqref{eq:SWE_equations}, solved numerically on a domain $D$. $h$ is the height of the water column, $q$ is the discharge, and $z$ is the bathymetry, while $g$ is the usual gravitation constant. $\mathbf{k}$ is a quadratic friction term, proportional to the square of the inverse of Manning-Strickler coefficient.
% \begin{align}
%   \label{eq:SWE_equations}
%   \left\{
%     \begin{array}{l}
%       \partial_t h + \partial_x q = 0 \\
%       \partial_t q + \partial_x \left(\frac{q^2}{h} + \frac{g}{2}h^2\right) = - gh\partial_x z - \mathbf{k}q |q|h^{-7/3} \\
%       h(0, t) = 20.0 + \mathrm{Amplitude} \cdot \sin \left(\frac{2\pi}{\mathbf{u}}t\right) \\
%       q(0, t) = 0
%       \end{array}
%   \right.
% \end{align}

% The estimation of the bottom friction and/or topography has been treated in a deterministic setting, % in Section~\ref{sec:deterministic}
% using tools from variational data assimilation~\cite[e.g.][]{das_estimation_1991,das_variational_1992,honnorat_identification_2010}.
% If the boundary conditions are not well-known, the estimation will then compensate this misspecification. The resulting estimate will then be optimal for this particular configuration, but will not acknowledge the uncertainty upon the boundary conditions. Instead, we are looking for an estimate that is robust considering the variability of the uncertain boundary conditions.

% The problem of the estimation of the bottom friction will be studied using twin experiments. For this purpose, a few references simulations have been performed in order to produce different observations $\mathbf{y}^o$. Those scenarios are detailed Table~\ref{tab:optim_scenar}. The true bottom friction $\mathbf{k}^t$ is the same for all simulations, and is a non-constant function of the spatial domain $D = [0, L]$ defined as:
% \begin{equation}
%   \label{eq:defnition_kt}
%   \mathbf{k}^t= \mathbf{k}^t(x) = 0.2\cdot (1 + \sin(2\pi x/L))
% \end{equation}
% However, the space $\Kspace$ in which we wish to estimate the bottom friction is one-dimensional. This leads to the strict positivity of the cost function, as no perfect fit can be achieved.

% As presented on Table~\ref{tab:RO_modelling}, we consider two a priori chosen variable: $\mathbf{u} \in \Uspace$ that is the period of the sine wave on the left boundary. The aleatoric uncertainty on this variable is modelled by a random variable distributed uniformly on $\Uspace$.
% The amplitude of the sine wave is also chosen a priori and set to an arbitrary value, that may be different from the true amplitude used to generate $\mathbf{y}^o$.

% \begin{table*}[t]
%   \caption{Modelling of the estimation problem}
%   \label{tab:RO_modelling}
% \begin{tabular}{rrr}
%   \tophline
%   Parameter & Modelling & Type of parameter \\
%   \middlehline
%   Bottom friction: $\mathbf{k}$  &$\Kspace=[0, 1]$ & Calibrated parameter \\
%   Period: $\mathbf{U}$ & $\mathrm{Unif}\left([14.7, 15.3]\right)$ & A priori chosen and uncertain\\
%   Amplitude &  5.0 & A priori chosen and fixed\\
%   \bottomhline
% \end{tabular}
% \end{table*}

% % ----------------------------------------------------------------------------
% \section{Deterministic optimisation}
% \label{ssec:deterministic_optimisation}
% The problem has first been studied in a deterministic setting. The following optimisation problem has been performed numerically:
% \begin{equation}
%   \label{eq:opt_deter}
%   \text{Minimise } \mathbf{k}\in\Kspace \mapsto J(\mathbf{k},\mathbf{u}^b)\quad \text{for }\mathbf{u}^b= \Ex_{\mathbf{U}}[\mathbf{U}] = 15.0
% \end{equation}
% At the same time, the background value of the amplitude is fixed and set to $5.0$.
% Different scenario have been established (i.e.\ different $\mathbf{u}^t$ and amplitude producing different $\mathbf{y}^o$), and are detailed in Table~\ref{tab:optim_scenar}. The configurations correspond to different values of the amplitude (letter~``A'') and the period (letter~``P''). If the truth value is greater (resp.\ smaller) than the background value, the lowercase letter ``p'' follows (resp.\ ``m'').

% On the same table, are shown the result $\kest$ of the optimisation defined in Eq.~\eqref{eq:opt_deter} for each one of the different operating conditions.

% \begin{table*}[t]
%   \caption{Settings for reference simulations, and optimisation results}
%   \label{tab:optim_scenar}
% \begin{tabular}{rrrrrrrr} \tophline
% Scenario for $\mathbf{u}^t$: &$\Ex_{\mathbf{U}}[\mathbf{U}]$  & Pm & ApPm & AmPm & Pp & ApPp & AmPp \\ \middlehline
%   $\mathbf{u}^t- \mathbf{u}^b$ & 0.0            & -0.1  & -0.2 & -0.1 & +0.2 & +0.1 & +0.2 \\
%   $\mathrm{Amplitude}- 5.0$   & 0.0             &  0.0  & +0.1 & -0.2 &  0.0 & +0.2 & -0.1 \\ \middlehline
%   $\kest$      & 0.1043          & 0.2028 & 0.2709 & 0.2427 & 0.0  & 0.0 & 0.0015 \\\bottomhline
% \end{tabular}
% \end{table*}

% Optimising without uncertainties (meaning that the $\mathbf{u}^b=\mathbf{u}^t$) yields an optimal value $\kest$ close to $0.10$, that we define to be $\kest_{\mathrm{opt}}$
% We can observe two different regimes, depending on the sign of $\mathbf{u}^t-\Ex_{\mathbf{U}}[\mathbf{U}]$. If this quantity is positive, optimisation will produce an estimation close to $0$. If it is negative, the estimate is larger than $0.20$.

% % ----------------------------------------------------------------------------
% \subsection{Robust estimates}
% In order to compute the robust estimates, the cost function has been evaluated on a regular grid of $150\times150$ points over $\Kspace\times\Uspace$. $\kmean$, $\kvar$, $\checkk_{.9}$, $\checkk_{.95}$ and $\checkk_{1}$ (along with their corresponding factors $\checka_p$) have been evaluated for the different configurations, detailed in Table~\ref{tab:optim_scenar}. As shown on Table~\ref{tab:res_robust}, $\checkkp$ does not vary significantly when the level of confidence $p$ increases.

% \begin{table*}[t]
%   \caption{Mean and variance optimisers, and $\checkkp$ for different levels of confidence $p$}
%   \label{tab:res_robust}
%   \begin{tabular}{rrrrrrrr} \tophline
%     Scenario&$\Ex_{\mathbf{U}}[\mathbf{U}]$ & Pm & ApPm & AmPm & Pp & ApPp & AmPp \\  \middlehline
%   $\kmean$ & 0.1678    & 0.2214  & 0.2617 & 0.2685 & 0.0872 & 0.0738 & 0.1275 \\
%   $\kvar$  & 1.0      &  1.0  & 1.0 & 1.0 &  1.0 & 1.0 & 1.0 \\ \middlehline
%   $\checkk_{.90}$ & 0.1074 & 0.1074 & 0.0872 & 0.1678 & 0.1074  & 0.0738 & 0.1275 \\
%   $\checka_{.90}$    & 1.1754  & 1.1718 & 1.1779 & 1.1293 & 1.1768  & 1.1807 & 1.1406 \\\middlehline

%   $\checkk_{.95}$ & 0.1074 & 0.1074 & 0.0872 & 0.1611 & 0.1074  & 0.0671 & 0.1275 \\
%   $\checka_{.95}$ & 1.1802 & 1.1806 & 1.1868 & 1.1320 & 1.1861  & 1.2027 & 1.1525 \\\middlehline
%     $\checkk_{1}$& 0.1074 & 0.1074 & 0.0872 & 0.1611 & 0.1074  & 0.0671 & 0.1275 \\
%   $\checka_{1}$ & 1.1944    & 1.1922 & 1.1961 & 1.1321 & 1.1976  & 1.2035 & 1.1682 \\\middlehline
% \end{tabular}
% \end{table*}

% In that case, the minimiser of the variance $\kvar$ is the right boundary of $\Kspace$, regardless of the value of $\mathbf{u}^t$. This is due to the fact that at this point, the cost function produces bad, yet steady performances. From a physical point of view, increasing the bottom friction will decrease the momentum. The movement of the water surface will be damped, and the operating conditions will have less effects.

% Looking at $\kmean$, we can see that the estimates obtained are larger than $0.22$ when $\mathbf{u}^t< \Ex_{\mathbf{U}}[\mathbf{U}]$ (that is for Pm, ApPm, and AmPm). Those results are similar to the one obtained in the deterministic setting of Table~\ref{tab:optim_scenar}. However, for $\mathbf{u}^t> \Ex_{\mathbf{U}}[\mathbf{U}]$ (Pp, ApPp, and AmPp), $\kmean$ is much closer to $\kest_{\mathrm{opt}}$, the optimal value without uncertainties.

% Now for $\checkk_1$, while the estimates for scenarios Pp, ApPp and AmPp are similar to $\kmean$, the obtained values for the other scenarios are close to $\kest$.
% Figures~\ref{fig:SWE_checkalpha} and~\ref{fig:SWE_profiles} show the contour plot and profiles of the cost function in centered conditions ($\Ex_{\mathbf{U}}[\mathbf{U}]$ scenario). Figures~\ref{fig:SWE_checkalphaApPp} and \ref{fig:SWE_profilesApPp} (resp. Figures~\ref{fig:SWE_checkalphaAmPm} and~\ref{fig:SWE_profilesAmPm}) show the contour plot and profiles of the cost function for the ApPp scenario (resp. AmPm scenario).

% The concentration of $\checkkp$ close to $\kest_{\mathrm{opt}}$ is caused by the very small value of the cost function at its minimum over $\Kspace\times \Uspace$. Close to this minimum, the region of acceptable $\mathbf{k}$ will be growing slowly as $\alpha$ increases, weighing the estimation toward $\kest_{\mathrm{opt}}$.

% The fact that we retrieved values close to the optimal one should not overlook that a robust estimate is not necessarily $\kest_{\mathrm{opt}}$, and that this result is specific to this problem.

% \clearpage
% \begin{figure*}[!h]
% \includegraphics[width=8cm]{Figures/SWE_big3.pdf}
% \caption{Top: Cost function of the SWE problem ($\Ex_{\mathbf{U}}[\mathbf{U}]$ scenario) and its conditional minimisers. The thick yellow lines represent the boundary of the region where $\phi_\alpha<0$. The red dashed line is the estimate $\checkk_{1}$. Bottom: $R_{\checka}$}
% \label{fig:SWE_checkalpha}
% \end{figure*}

% \begin{figure*}[!h]
%   \centering
%   \includegraphics[width=8cm]{Figures/profile_swe.pdf}
%   \caption{Profiles of different estimates of $\mathbf{k}$ for the $\Ex_{\mathbf{U}}[\mathbf{U}]$ scenario}
%   \label{fig:SWE_profiles}
% \end{figure*}

% \begin{figure*}[!h]
% \includegraphics[width=8cm]{Figures/SWE_ApPp3.pdf}
% \caption{Top: Cost function of the SWE problem (ApPp scenario) and its conditional minimisers. The thick yellow lines represent the boundary of the region where $\phi_\alpha<0$. The red dashed line is the estimate $\checkk_{1}$. Bottom: $R_{\checka}$}
% \label{fig:SWE_checkalphaApPp}
% \end{figure*}

% \begin{figure*}[!h]
%   \centering
%   \includegraphics[width=7cm]{Figures/SWE_ApPp_profile.pdf}
%   \caption{Profiles of different estimates of $\mathbf{k}$ for the ApPp scenario}
%   \label{fig:SWE_profilesApPp}
% \end{figure*}

% \begin{figure*}[!h]
% \includegraphics[width=8cm]{Figures/SWE_AmPm3.pdf}
% \caption{Top: Cost function of the SWE problem (AmPm scenario) and its conditional minimisers. The thick yellow lines represent the boundary of the region where $\phi_\alpha<0$. The red dashed line is the estimate $\checkk_{1}$. Bottom: $R_{\checka}$}
% \label{fig:SWE_checkalphaAmPm}
% \end{figure*}

% \begin{figure*}[!h]
%   \centering
%   \includegraphics[width=8cm]{Figures/SWE_AmPm_profile.pdf}
%   \caption{Profiles of different estimates of $\mathbf{k}$ for the AmPm scenario}
%   \label{fig:SWE_profilesAmPm}
% \end{figure*}

\clearpage
\conclusions  %% \conclusions[modified heading if necessary]
This paper deals with the problem of robust calibration of a computer code in the presence of uncertain inputs.

Our contribution consists in introducing a new criterion of robustness, based on the distribution of the minimisers. More specifically, this estimate is bounding the ratio between the cost function and its conditional minimum.
Experimental results show that this new estimate is able to make a compromise between the minimum of the expected value and the minimum of the variance, will also giving the range of the ratio evoked above.

From a practical perspective, this estimation is very expensive: each evaluation of $\mathbf{k}^*$ requires an optimisation procedure. The distribution of the conditional minimisers is then very complicated to compute.
In addition to that, in order to relax the constraint, the cost function must also be evaluated in the vicinity of the conditional minimisers. Computing precisely this estimate is then intractable if each run of the underlying model is expensive (longer than a couple of seconds).

A solution to explore is the use of surrogate models. Based on an initial design of experiment, the (expensive) cost function is replaced by a function, that is cheap to evaluate.
For instance, \cite{ginsbourger_bayesian_2014}
uses Gaussian Process regression and sequential methods to explore the conditional minimisers.

Finally, the adaptibility of this method has to be studied in a higher dimensional setting. High-dimensional density estimation is a challenge in itself, but is necessary in order to tackle more realistic applications.
%% The following commands are for the statements about the availability of data sets and/or software code corresponding to the manuscript.
%% It is strongly recommended to make use of these sections in case data sets and/or software code have been part of your research the article is based on.

\codeavailability{TEXT} %% use this section when having only software code available

% \dataavailability{TEXT} %% use this section when having only data sets available

\codedataavailability{TEXT} %% use this section when having data sets and software code available

% \sampleavailability{TEXT} %% use this section when having geoscientific samples available

% \appendix
% \section{}    %% Appendix A

% \subsection{}     %% Appendix A1, A2, etc.

% \noappendix       %% use this to mark the end of the appendix section

%% Regarding figures and tables in appendices, the following two options are possible depending on your general handling of figures and tables in the manuscript environment:

%% Option 1: If you sorted all figures and tables into the sections of the text, please also sort the appendix figures and appendix tables into the respective appendix sections.
%% They will be correctly named automatically.

%% Option 2: If you put all figures after the reference list, please insert appendix tables and figures after the normal tables and figures.
%% To rename them correctly to A1, A2, etc., please add the following commands in front of them:

\appendixfigures  %% needs to be added in front of appendix figures

\appendixtables   %% needs to be added in front of appendix tables

%% Please add \clearpage between each table and/or figure. Further guidelines on figures and tables can be found below.

\authorcontribution{TEXT} %% it is strongly recommended to make use of this section

\competinginterests{TEXT} %% this section is mandatory even if you declare that no competing interests are present

\disclaimer{TEXT} %% optional section

\begin{acknowledgements}
TEXT
\end{acknowledgements}

%% REFERENCES

%% The reference list is compiled as follows:

% \begin{thebibliography}{}

% \bibitem[AUTHOR(YEAR)]{LABEL1}
% REFERENCE 1

% \bibitem[AUTHOR(YEAR)]{LABEL2}
% REFERENCE 2

% \end{thebibliography}

%% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
%% authors experienced with BibTeX only have to include the following two lines:
%%

\bibliographystyle{copernicus}
\bibliography{bibzotero}

%%
%% URLs and DOIs can be entered in your BibTeX file as:
%%
%% URL = {http://www.xyz.org/~jones/idx_g.htm}
%% DOI = {10.5194/xyz}

%% LITERATURE CITATIONS
%%
%% command                        & example result
%% \citet{jones90}|               & Jones et al. (1990)
%% \citep{jones90}|               & (Jones et al., 1990)
%% \citep{jones90,jones93}|       & (Jones et al., 1990, 1993)
%% \citep[p.~32]{jones90}|        & (Jones et al., 1990, p.~32)
%% \citep[e.g.,][]{jones90}|      & (e.g., Jones et al., 1990)
%% \citep[e.g.,][p.~32]{jones90}| & (e.g., Jones et al., 1990, p.~32)
%% \citeauthor{jones90}|          & Jones et al.
%% \citeyear{jones90}|            & 1990

%% FIGURES

%% When figures and tables are placed at the end of the MS (article in one-column style), please add \clearpage
%% between bibliography and first table and/or figure as well as between each table and/or figure.

%% ONE-COLUMN FIGURES

%%f
%\begin{figure}[t]
%\includegraphics[width=8.3cm]{FILE NAME}
%\caption{TEXT}
%\end{figure}
%
%%% TWO-COLUMN FIGURES
%
%%f
%\begin{figure*}[t]
%\includegraphics[width=12cm]{FILE NAME}
%\caption{TEXT}
%\end{figure*}
%
%
%%% TABLES
%%%
%%% The different columns must be seperated with a & command and should
%%% end with \\ to identify the column brake.
%
%%% ONE-COLUMN TABLE
%
%%t
%\begin{table}[t]
%\caption{TEXT}
%\begin{tabular}{column = lcr}
%\tophline
%
%\middlehline
%
%\bottomhline
%\end{tabular}
%\belowtable{} % Table Footnotes
%\end{table}
%
%%% TWO-COLUMN TABLE
%
%%t
%\begin{table*}[t]
%\caption{TEXT}
%\begin{tabular}{column = lcr}
%\tophline
%
%\middlehline
%
%\bottomhline
%\end{tabular}
%\belowtable{} % Table Footnotes
%\end{table*}
%
%%% LANDSCAPE TABLE
%
%%t
%\begin{sidewaystable*}[t]
%\caption{TEXT}
%\begin{tabular}{column = lcr}
%\tophline
%
%\middlehline
%
%\bottomhline
%\end{tabular}
%\belowtable{} % Table Footnotes
%\end{sidewaystable*}
%
%
%%% MATHEMATICAL EXPRESSIONS
%
%%% All papers typeset by Copernicus Publications follow the math typesetting regulations
%%% given by the IUPAC Green Book (IUPAC: Quantities, Units and Symbols in Physical Chemistry,
%%% 2nd Edn., Blackwell Science, available at: http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf, 1993).
%%%
%%% Physical quantities/variables are typeset in italic font (t for time, T for Temperature)
%%% Indices which are not defined are typeset in italic font (x, y, z, a, b, c)
%%% Items/objects which are defined are typeset in roman font (Car A, Car B)
%%% Descriptions/specifications which are defined by itself are typeset in roman font (abs, rel, ref, tot, net, ice)
%%% Abbreviations from 2 letters are typeset in roman font (RH, LAI)
%%% Vectors are identified in bold italic font using \vec{x}
%%% Matrices are identified in bold roman font
%%% Multiplication signs are typeset using the LaTeX commands \times (for vector products, grids, and exponential notations) or \cdot
%%% The character * should not be applied as mutliplication sign
%
%
%%% EQUATIONS
%
%%% Single-row equation
%
%\begin{equation}
%
%\end{equation}
%
%%% Multiline equation
%
%\begin{align}
%& 3 + 5 = 8\\
%& 3 + 5 = 8\\
%& 3 + 5 = 8
%\end{align}
%
%
%%% MATRICES
%
%\begin{matrix}
%x & y & z\\
%x & y & z\\
%x & y & z\\
%\end{matrix}
%
%
%%% ALGORITHM
%
%\begin{algorithm}
%\caption{...}
%\label{a1}
%\begin{algorithmic}
%...
%\end{algorithmic}
%\end{algorithm}
%
%
%%% CHEMICAL FORMULAS AND REACTIONS
%
%%% For formulas embedded in the text, please use \chem{}
%
%%% The reaction environment creates labels including the letter R, i.e. (R1), (R2), etc.
%
%\begin{reaction}
%%% \rightarrow should be used for normal (one-way) chemical reactions
%%% \rightleftharpoons should be used for equilibria
%%% \leftrightarrow should be used for resonance structures
%\end{reaction}
%
%
%%% PHYSICAL UNITS
%%%
%%% Please use \unit{} and apply the exponential notation

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2019-11-13 article-modif-A&E.tex
use JCP template

@@
-%% Copernicus Publications Manuscript Preparation Template for LaTeX Submissions
-%% ---------------------------------
-%% This template should be used for copernicus.cls
-%% The class file and some style files are bundled in the Copernicus Latex Package, which can be downloaded from the different journal webpages.
-%% For further assistance please contact Copernicus Publications at: production@copernicus.org
-%% https://publications.copernicus.org/for_authors/manuscript_preparation.html
-
-%% Please use the following documentclass and journal abbreviations for discussion papers and final revised papers.
-
-%% 2-column papers and discussion papers
-\documentclass[npg, manuscript]{copernicus}
-
-%% Journal abbreviations (please use the same for discussion papers and final revised papers)
-
-% Advances in Geosciences (adgeo)
-% Advances in Radio Science (ars)
-% Advances in Science and Research (asr)
-% Advances in Statistical Climatology, Meteorology and Oceanography (ascmo)
-% Annales Geophysicae (angeo)
-% Archives Animal Breeding (aab)
-% ASTRA Proceedings (ap)
-% Atmospheric Chemistry and Physics (acp)
-% Atmospheric Measurement Techniques (amt)
-% Biogeosciences (bg)
-% Climate of the Past (cp)
-% DEUQUA Special Publications (deuquasp)
-% Drinking Water Engineering and Science (dwes)
-% Earth Surface Dynamics (esurf)
-% Earth System Dynamics (esd)
-% Earth System Science Data (essd)
-% E&G Quaternary Science Journal (egqsj)
-% Fossil Record (fr)
-% Geographica Helvetica (gh)
-% Geoscientific Instrumentation, Methods and Data Systems (gi)
-% Geoscientific Model Development (gmd)
-% History of Geo- and Space Sciences (hgss)
-% Hydrology and Earth System Sciences (hess)
-% Journal of Micropalaeontology (jm)
-% Journal of Sensors and Sensor Systems (jsss)
-% Mechanical Sciences (ms)
-% Natural Hazards and Earth System Sciences (nhess)
-% Nonlinear Processes in Geophysics (npg)
-% Ocean Science (os)
-% Primate Biology (pb)
-% Proceedings of the International Association of Hydrological Sciences (piahs)
-% Scientific Drilling (sd)
-% SOIL (soil)
-% Solid Earth (se)
-% The Cryosphere (tc)
-% Web Ecology (we)
-% Wind Energy Science (wes)
-
-%% \usepackage commands included in the copernicus.cls:
-%\usepackage[german, english]{babel}
-%\usepackage{tabularx}
-%\usepackage{cancel}
-%\usepackage{multirow}
-%\usepackage{supertabular}
-%\usepackage{algorithmic}
-%\usepackage{algorithm}
-%\usepackage{amsthm}
-%\usepackage{float}
-%\usepackage{subfig}
-%\usepackage{rotating}
+%% 
+%% Copyright 2007-2019 Elsevier Ltd
+%% 
+%% This file is part of the 'Elsarticle Bundle'.
+%% ---------------------------------------------
+%% l
+%% It may be distributed under the conditions of the LaTeX Project Public
+%% License, either version 1.2 of this license or (at your option) any
+%% later version.  The latest version of this license is in
+%%    http://www.latex-project.org/lppl.txt
+%% and version 1.2 or later is part of all distributions of LaTeX
+%% version 1999/12/01 or later.
+%% 
+%% The list of all files belonging to the 'Elsarticle Bundle' is
+%% given in the file `manifest.txt'.
+%% 
+%% Template article for Elsevier's document class `elsarticle'
+%% with harvard style bibliographic references
+
+\documentclass[preprint, 1p]{elsarticle}
+
+%% Use the option review to obtain double line spacing
+%% \documentclass[preprint,review,12pt]{elsarticle}
+
+%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
+%% for a journal layout:
+% \documentclass[final,1p,times]{elsarticle}
+%% \documentclass[final,1p,times,twocolumn]{elsarticle}
+%% \documentclass[final,3p,times]{elsarticle}
+%% \documentclass[final,3p,times,twocolumn]{elsarticle}
+%% \documentclass[final,5p,times]{elsarticle}
+%% \documentclass[final,5p,times,twocolumn]{elsarticle}
+
+%% For including figures, graphicx.sty has been loaded in
+%% elsarticle.cls. If you prefer to use the old commands
+%% please give \usepackage{epsfig}
+
+%% The amssymb package provides various useful mathematical symbols
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+%% The amsthm package provides extended theorem environments
+%% \usepackage{amsthm}
+
+%% The lineno packages adds line numbers. Start line numbering with
+%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
+%% for the whole article with \linenumbers.
+%% \usepackage{lineno}
 \usepackage{easy-todo}
@@
 
+\journal{Journal of Computational Physics}
+
 \begin{document}
 
-\title{Title-- \today{}}%TEXT}
-
-% \Author[affil]{given_name}{surname}
-
-\Author[]{Victor}{Trappler}
-\Author[]{Élise}{Arnaud}
-\Author[]{Laurent}{Debreu}
-\Author[]{Arthur}{Vidard}
-
-\affil[]{Univ. Grenoble Alpes, CNRS, Inria, Grenoble INP*, LJK, 38000 Grenoble, France}
-% \affil[]{ADDRESS}
-
-%% The [] brackets identify the author with the corresponding affiliation. 1, 2, 3, etc. should be inserted.
-
-\runningtitle{Title}
-
-\runningauthor{Trappler V.}
-
-\correspondence{Victor Trappler (victor.trappler@univ-grenoble-alpes.fr)}
-
-\received{}
-\pubdiscuss{} %% only important for two-stage journals
-\revised{}
-\accepted{}
-\published{}
-
-%% These dates will be inserted by Copernicus Publications during the typesetting process.
-
-\firstpage{1}
-
-\maketitle
-
-% \listoftodos\
+\begin{frontmatter}
+
+%% Title, authors and addresses
+
+%% use the tnoteref command within \title for footnotes;
+%% use the tnotetext command for theassociated footnote;
+%% use the fnref command within \author or \address for footnotes;
+%% use the fntext command for theassociated footnote;
+%% use the corref command within \author for corresponding author footnotes;
+%% use the cortext command for theassociated footnote;
+%% use the ead command for the email address,
+%% and the form \ead[url] for the home page:
+
+\title{Robust calibration of numerical models based on relative regret}
+
+%% use optional labels to link authors explicitly to addresses:
+%% \author[label1,label2]{}
+%% \address[label1]{}
+%% \address[label2]{}
+
+\author[vt]{Victor Trappler}
+\ead{victor.trappler@univ-grenoble-alpes.fr}
+\author[ea]{Élise Arnaud}
+\author[av]{Arthur Vidard}
+\author[ld]{Laurent Debreu}
+
+\address[vt]{Univ. Grenoble Alpes, CNRS, Inria, Grenoble INP*, LJK, 38000 Grenoble, France}
 
 \begin{abstract}
+%% Text of abstract
 Classical methods of parameter estimation usually imply the minimisation of an objective function, that measures the error between some observations and the results obtained by a numerical model.
@@
 In this paper, we are going to present how to take into account those uncertainties by defining a notion of robustness based on the distribution of the conditional minimisers and compare it with the minimum in the mean sense, and the minimum of variance.
-\victor{Pour le nom: Il y a l'idée que l'on veut avoir un regret $J(\mathbf{k},\mathbf{u}) - \alpha J^*(\mathbf{u})$ controlé à l'aide de $\alpha$: Relative regret ?}
 \end{abstract}
 
-\copyrightstatement{TEXT}
+% %%Graphical abstract
+% \begin{graphicalabstract}
+% %\includegraphics{grabs}
+% \end{graphicalabstract}
+
+%%Research highlights
+% \begin{highlights}
+% \item Research highlight 1
+% \item Research highlight 2
+% \end{highlights}
+
+\begin{keyword}
+%% keywords here, in the form: keyword \sep keyword
+
+%% PACS codes here, in the form: \PACS code \sep code
+
+%% MSC codes here, in the form: \MSC code \sep code
+%% or \MSC[2008] code \sep code (2000 is the default)
+
+\end{keyword}
+
+\end{frontmatter}
+
+%% \linenumbers
+
+%% main text
+\section*{Introduction}
+\label{}
 
@@
 \begin{tabular}{lrr}
-  \tophline
+  \hline
   Definition & Related quantities & Interpretation \\
-  \middlehline
+  \hline
    $\argmin_{\mathbf{k}\in\Kspace} \Ex_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U})\right]$& $\kmean$ & Long run performances\\
@@
     $p_{\mathrm{maxratio}} = \argmax p/\checkap$ & $(p_{\mathrm{maxratio}}, \checkk_{\mathrm{maxratio}}, \checka_{\mathrm{maxratio}})$ & Maximal ratio of $p$ and $\checkap$ \\
-  \bottomhline
+  \hline
 \end{tabular}
@@
 \begin{tabular}{lr}
-\tophline
-Estimate & Value \\ \middlehline
+\hline
+Estimate & Value \\ \hline
 $\hatkvar$ & 1.371 \\ 
@@
 $\kest_p,~p=0.95$ & 1.672 \\ 
-$\kest_{\mathrm{maxratio}},~\hat{p}_{\mathrm{maxratio}}=0.654$ & 1.637 \\ \bottomhline
+$\kest_{\mathrm{maxratio}},~\hat{p}_{\mathrm{maxratio}}=0.654$ & 1.637 \\ \hline
 \end{tabular}
@@
 \label{tab:recap_estimates_BHs}
-\begin{tabular}{lr} \tophline
-Estimate & Value \\ \middlehline
+\begin{tabular}{lr} \hline
+Estimate & Value \\ \hline
 $\kest_{\mathrm{MPE}}$ & 0.606 \\ 
@@
 $\kest_{\mathrm{var}}$ & 2.638 \\ 
-$\kest_1,~p=1$ & 2.798   \\ \bottomhline
+$\kest_1,~p=1$ & 2.798   \\ \hline
 \end{tabular}
@@
 The parameter to calibrate, $\mathbf{k}$, is the quadratic friction term, proportional to the square of the inverse of Manning-Strickler coefficient.
-The environmental parameter $\mathbf{u}$ is the amplitude of a sine wave of period $1$.
+The environmental parameter $\mathbf{u}$ is the amplitude of a sine wave of period $1/\omega_0$.
 The domain of those two parameters are $\mathcal{K} = [0.0, 1.3]$ and $\mathcal{U} = [0.5, 0.7]$.
@@
       \partial_t q + \partial_x \left(\frac{q^2}{h} + \frac{g}{2}h^2\right) &= - gh\partial_x z - \mathbf{k}q |q|h^{-7/3} \\
-      h(0, t) &= 20.0 + 3\cdot \sin \left(\frac{2\pi t}{2}\right) + 1.5\cdot \mathbf{u} \cdot \sin\left(2 \pi t\right)\\
+      h(0, t) &= 20.0 + 3\cdot \sin \left(\frac{2\pi t}{2}\right) + 1.5\cdot \mathbf{u} \cdot \sin\left(\frac{2 \pi t}{\omega_0}\right)\\
       \partial_x q(0, t) &= 0
@@
 These equations are integrated using a finite-volume scheme on a discretized domain $[0, L]$, up to a time $T$.
-The output of the computer code is the sea surface height $h$, on the center of all the volumes and at all the time-steps, that will be denoted $\mathcal{M}(\mathbf{k},\mathbf{u})$.
+The output of the computer code is the sea surface height $h$, on the center of all the volumes and at all the time-steps, that will be denoted $\mathcal{M}(\mathbf{k},\mathbf{u};\, \omega_0=1.0)$.
 In this setting, the variable input is uniformly distributed on $\mathcal{U}$.
-To generate the observations, we choose $\mathbf{u}^{\mathrm{true}}=2/3$, and define $\mathcal{M}^o$ based on the computer model $\mathcal{M}$, such that $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) = \mathcal{M}(\mathbf{k}^{\mathrm{true}}, \mathbf{u}^{\mathrm{true}})$.
-This true value $\mathbf{k}^{\mathrm{true}} = (k_1^{\mathrm{true}}, k_2^{\mathrm{true}},\dots, k_{N_\mathrm{vol}}^{\mathrm{true}})$ is not constant over the whole domain, and is defined as
+To generate the observations, we choose $\mathbf{u}^{\mathrm{true}}=2/3$, and define $\mathcal{M}^o$ based on the computer model $\mathcal{M}$, such that $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) = \mathcal{M}(\mathbf{k}^{\mathrm{true}}, \mathbf{u}^{\mathrm{true}}; \, \omega_0 = 0.999)$.
+$\omega_0$
+represents here the uncontrollable error between the observations and the numerical model and will now be omitted systematically in the notation.
+The true value of the bottom friction $\mathbf{k}^{\mathrm{true}} = (k_1^{\mathrm{true}}, k_2^{\mathrm{true}},\dots, k_{N_\mathrm{vol}}^{\mathrm{true}})$ is not constant over the whole domain, and is defined as
 \begin{equation*}
@@
 where $x_i$ is the center of the $i$-th volume.
+The two sources of representativity errors are $\omega_0$, and the fact that we are looking to estimate $\mathbf{k}$ in a 1-dimensional space $\Kspace$.
 \subsection{Estimation}
+Given that the numerical model is expensive to evaluate, it has first been evaluated on a relatively small regular grid.
+A metamodel based on Gaussian process is constructed and the PEI criterion \citep{ginsbourger_bayesian_2014,bossek_learning_2015} allow us to add point to evaluate and to better capture the locus of the conditional minimisers $\{(\mathbf{k}^*(\mathbf{u}), \mathbf{u}) \mid \mathbf{u} \in \Uspace \}$.
+A bigger regular grid is evaluated by the metamodel once the design space has been sufficiently explored.
+The different steps of the estimation are illustrated Figure~\ref{fig:estimation_swe}.
+We can see that the estimation for this problem seems less problematic than the analytical examples shown above, as all derived quantites are unimodal.
+The different estimates however take a wide range of values, as seen on Table~\ref{tab:recap_estimates_metaSWE}.: there is a unique global minimiser on the whole space $\Kspace \times \Uspace$, noted $\kest_{\mathrm{global}}$.
+As discussed earlier, the estimation of the MPE is dependent on the method used, and then its estimation using KDE in the middle plot of Figure~\ref{fig:estimation_swe} is here only for illustrative purposes.
 
@@
 Bottom: $\hat{\Gamma}_{\alpha_p}$ for different levels $p$}
-\label{fig:my_label}
+\label{fig:estimation_swe}
 \end{figure}
@@
 \centering
-\begin{tabular}{lr}
+\caption{Calibrated values of $\mathbf{k}$ according to different criteria}
+\begin{tabular}{lr} \hline
 Estimator & Value \\ \hline
+$\hatkmpe$ & 0.249 \\
+$\kest_{\mathrm{global}}$ & 0.290 \\
 $\hat{\mathbf{k}}_{p},~p=1$ & 0.423 \\ 
 $\hat{\mathbf{k}}_p,~p=0.90$ & 0.458 \\ 
-$\hat{\mathbf{k}}_{\mathrm{mean}}$ & 0.501 \\ 
+$\hatkmean$ & 0.501 \\ 
 $\hat{\mathbf{k}}_p,~p=0.80$ & 0.505 \\ 
 $\hat{\mathbf{k}}_p,~p=0.70$ & 0.560 \\ 
-$\hat{\mathbf{k}}_{\mathrm{var}}$ & 0.990 \\
+$\hatkvar$ & 0.990\\ \hline
 \end{tabular}
-\caption{Estimation of $\mathbf{k}$ according to different criterion}
 \label{tab:recap_estimates_metaSWE}
@@
 \subsection{Assessing the quality of the forecast of the calibrated model}
-The calibration of the model has been performed on the time-period $[0, T]$, called assimilation window. 
-We now want to compare the quality of the different forecasts depending on the criterion used to calibrate the bottom friction.
-To define those forecasts, the models will be integrated from $T$ to $T_{\mathrm{pred}}$.
-
-Given the probabilistic nature $\mathbf{U}$, the forecasts will also be probabilistic.
+The calibration of the model has been performed using by integrating the model on a time-period $[0, T]$, called assimilation window. 
+We now want to compare the quality of the different forecasts, from different calibrated bottom friction.
+Those forecasts result from the integration of the numerical model between the time $T$ and a time $T_{\mathrm{pred}}$.
+
+Given the probabilistic nature of the environmental conditions $\mathbf{U}$, the forecasts will also be probabilistic.
 We will then compare $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{U})$, for a calibrated $\mathbf{k}$.
@@
 \subsubsection{Squared forecast error}
-Let us assume that the observations result from the parameter $\mathbf{u}'$, while the computer simulation is run using $\mathbf{u}$.
-The squared forecast error given $\mathbf{u}$ and $\mathbf{u}'$ is
+Given two environmental conditions $\mathbf{u}$, used to run the computer simulation and $\mathbf{u}'$, used to generate the observations, the squared forecast error for the parameter $\mathbf{k}$ is
 \begin{equation}
@@
 \end{equation}
-We can then get an estimation of the mean squared forecast per volume per time step:
-
+By averaging over $\mathbf{u}$ and $\mathbf{u}'$ using a Monte-Carlo approximation, we can define the mean squared forecast error, defined on every point of the spatial domain, and at every time-steps.
 \begin{equation}
   \label{eq:squared_forecast_error_averaged}
-  S(\mathbf{k}) = \frac{1}{N_{\mathbf{u}} N_{\mathbf{u}'}}\sum_{\mathbf{u},\mathbf{u}'} S_{\mathrm{pred}}(\mathbf{k},\mathbf{u},\mathbf{u}') = \frac{1}{N_{\mathbf{u}} N_{\mathbf{u}'}}\sum_{\mathbf{u},\mathbf{u}'}\left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}')\right)^2
-\end{equation}
-
-\subsubsection{Averaged Quantile score}
-A first approach is to compare the quantiles obtained by the prediction $\mathcal{M}_{\mathrm{pred}}(\kest,\mathbf{U})$, with the quantiles observed of $\mathcal{M}^o_{\mathrm{pred}}(\mathbf{U})$.
-We are first going to introduce the pinball loss, or checkloss function:
-\begin{equation}
-\label{eq:checkloss}
-\rho_{\tau}(x) = \begin{cases}
-    \tau |x| \quad \text{ if } x \geq 0 \\
-    (1- \tau) |x| \quad \text{ if } x < 0
-\end{cases}
-\end{equation}
-
-Given the time index $j$, and the volume indexed by $i$, the quantile of order $\tau\in [0, 1]$ of $\mathcal{M}(\kest, \mathbf{U})_{(i,j)}$ is $q_{(i,j)}(\tau)$.
-Given an obse
-\begin{figure*}[t]
-\includegraphics[width=12cm]{Figures/forecast_metric.pdf}
-\caption{Quality of forecast, depending on the calibrated parameter. The left figures show the metric averaged over time, while the right figures show}
-\label{fig:forecast_metric}
+  S(\mathbf{k}) = \frac{1}{N_{\mathbf{u}} N_{\mathbf{u}'}}\sum_{\mathbf{u},\mathbf{u}'\sim \mathbf{U}} S_{\mathrm{pred}}(\mathbf{k},\mathbf{u},\mathbf{u}') = \frac{1}{N_{\mathbf{u}} N_{\mathbf{u}'}}\sum_{\mathbf{u},\mathbf{u}'\sim \mathbf{U}} \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}')\right)^2
+\end{equation}
+The mean squared forecast error is then averaged over all time-steps between $T$ and $T_{\mathrm{pred}}$, indicating on which point of the domain the forecast error is greater as seen on the left plot of Figure~\ref{fig:forecast_squared_error}.
+\begin{figure*}[!h]
+\centering
+\includegraphics[width=12cm]{Figures/forecast_error.pdf}
+\caption{Quality of forecast, depending on the calibrated parameter.
+The left figures show the metric averaged over time, while the right figure show the mean forecast error, averaged over time and space}
+\label{fig:forecast_squared_error}
 \end{figure*}
-
-% \subsection{The Lorenz-63 model}
-% A classical toy problem in data assimilation is the Lorenz-63 model, introduced in \cite{lorenz_deterministic_1963}. 
-% % xb
-% The evolution of the state vector $(x,y,z)$ is described by the non-linear differential system of Eq.~\eqref{eq:lorenz_equations}
-% \begin{align}
-%   \label{eq:lorenz_equations}
-%   \left\{
-%     \begin{array}{l}
-%       \dot{x} = \sigma\left(y-x \right) \\
-%       \dot{y} = \rho x - y - xz \\
-%       \dot{z} = xy - \beta z
-%       \end{array}
-%   \right.
-% \end{align}
-% Despite its apparent simplicity, this system is known to show chaotic behaviour for $(\sigma,\rho,\beta) = (10, 28, 8/3)$. 
-% This differential system is solved numerically using a Runge-Kutta scheme, over $N=100$ time-steps of length $\Delta t = 0.05$. In that time-period, the chaotic behaviour is not yet too apparent.
-
-% The inputs of the computer code are the initial conditions $\left(x_0,y_0,z_0\right)$ and $(\sigma, \beta, \rho)$.
-The parameter to calibrate is $\mathbf{k}=x_0-1$ with $\mathbf{k}\in[-0.05,0.05]$, and the uncertain parameter is $\mathbf{u}=\beta - 8/3$ with $\mathbf{u} \in \Uspace=[-0.05, 0.05]$.
-Finally, we suppose that the random variable $\mathbf{U}$ follows an uniform distribution on $\Uspace$.
-Solving numerically the differential system using those settings yields $x_{i}(\mathbf{k},\mathbf{u})$ for $i$ between $1$ and $N$.
-
-% This problem of calibration will be studied in a twin experiments framework: the target state $x^{o}_i$ for $1\leq i \leq N$ has been generated by the computer code, where the parameters used to generate it are detailed in Table~\ref{tab:lorenz_modelling}.
-One can notice the discrepancy of $\rho$ between the observations and the model, introduced to ensure that no perfect fit can be achieved, for any set of parameters.
-% \begin{table*}[h]
-%   \caption{Choice of modelling of the Lorenz-63 system}
-%   \label{tab:lorenz_modelling}
-% \begin{tabular}{crrl}
-%   \tophline
-%   Parameter & Observation: $x_{1:N}^o$ & Modelling: $\mathcal{G}(\mathbf{k},\mathbf{u})$ & Type \\
-%   \middlehline
-%  $\sigma$ & $10$ & $10$ & Fixed\\
-%   $\rho$ & $29$ & $28$ & A priori chosen and fixed \\
-%   $\beta$ & ${8}/{3}$ & ${8}/{3} + \mathbf{u}$ & A priori chosen and uncertain \\
-%  $x_0$ & $1$ & $1 + \mathbf{k}$ & Calibrated \\
-%   $y_0$ & $0$ & $0$ & Fixed \\
-%  $z_0$ & $0$ & $0$ & Fixed \\
-%   \bottomhline
-% \end{tabular}
-% \end{table*}
-
-% The misfit between the observations and the output of the numerical model is quantified using the cost function:
-% \begin{equation}
-% \label{eq:cost_fun_lorenz}
-% J(\mathbf{k},\mathbf{u}) = \frac{1}{2}\|\mathcal{G}(\mathbf{k},\mathbf{u}) \|^2 = \frac{1}{2} \|x_{1:N}(\mathbf{k},\mathbf{u}) - x^o_{1:N} \|^2 = \frac{1}{2}\sum_{i=1}^N (x_i(\mathbf{k},\mathbf{u}) - x_i^o)^2
-% \end{equation}
-
-% This toy model is cheap to evaluate, so the global minimum can be computed using numerical methods, at different starting points to avoid local minimums.
-% \begin{equation}
-% \label{eq:min_global_lorenz}
-% \min_{(\mathbf{k},\mathbf{u}) \in \Kspace\times\Uspace} J(\mathbf{k},\mathbf{u}) = 38.886712815 \quad \argmin_{(\mathbf{k},\mathbf{u}) \in \Kspace\times\Uspace} J(\mathbf{k},\mathbf{u}) = (0.02414384, -0.00551042)
-% \end{equation}
-
-% \subsubsection{MPE and conditional moments}
-% Figure~\ref{fig:lorenz_kde_moments} shows the cost function $J$, computed on a regular grid over $\Kspace\times\Uspace$.
-Using this grid, the conditional mean and standard deviation have been computed, while the MPE has been estimated by KDE.
-For a single $\mathbf{u}$, it may appear that there are multiple $\mathbf{k}^*(\mathbf{u})$.
-This is due to the fact that the conditional minimiser jumps back and forth between the two curves.
-
-% \begin{figure}[!h]
-% \includegraphics[width=12cm]{Figures/lorenz_kde_moments.pdf}
-% \caption{Cost function, locus of conditional minimisers, MPE estimated with KDE, conditional moments and their associated estimates}
-% \label{fig:lorenz_kde_moments}
-% \end{figure}
-
-% \subsubsection{Relaxation of the constraint}
-% Based on the computations described before, the coefficient $\checkap$ have been computed for $p=0.9$, $0.95$ and $p=1$, and reported in Table~\ref{tab:recap_estimates_lorenz}.
-The curve $R_{\checka_1}$ is plotted in Figure~\ref{fig:lorenz_relax}, where the acceptable region for $\checka_1$ is filled in yellow.
-
-% \begin{figure}[!h]
-% \includegraphics[width=12cm]{Figures/lorenz_f3.pdf}
-% \caption{Relaxation of the constraint for the Lorenz model. Acceptable region in yellow}
-% \label{fig:lorenz_relax}
-% \end{figure}
-
-% We can see that for $\mathbf{k}$ being approximately between $0$ and $0.01$, the probability $R_{\checka_1}$ is very close to $1$.
-Indeed, the cost function seems to be relatively flat on this region, as $\checkk_{0.9} \approx \kmpe$.
-
-% \begin{table*}[!h]
-%   \caption{Estimates computed numerically on the Lorenz-63 model}
-%   \label{tab:recap_estimates_lorenz}
-%   \begin{tabular}{*{3}{r}}\tophline
-%     Estimate & Value & Related quantities\\
-%     \middlehline
-%     $\hatkmean$        & $ 0.008779$ &$\left(\mu(\kmean),\sigma(\kmean)\right) = (42.965, 4.921)$\\
-%     $\hatkvar$         & $-0.025338$ &$\left(\mu(\kvar),\sigma(\kvar)\right)= (50.704, 2.024)$\\
-%     $\hatkmpe$         & $ 0.008779$ & $\Gamma_1(\kmpe) = 0.053$ \\
-%     $\hat{\checkk}_{0.9}$ & $ 0.008729$ & $\hat{\checka}_{0.9}  = 1.202788$ \\
-%     $\hat{\checkk}_{0.95}$& $ 0.006078$ & $\hat{\checka}_{0.95} = 1.226050$ \\
-%     $\hat{\checkk}_{1}$   & $ 0.000275$ & $\hat{\checka}_{1}    = 1.311002$ \\
-%     \bottomhline
-%     \end{tabular}
-% \end{table*}
-
-% \subsubsection{Selection of the couple $(p,\checkap)$}
-% The evolution of $\checkap$ with respect to $p$ is shown on the left plot of Figure~\ref{fig:evolution_p_lorenz}.
-We can see that $\checkap$ presents two abrupt positive change of slope, for $p$ set to $0.85$ and just before $1$.
-Those confidence levels corresponds to the local maxima of the ratio $p/\checkap$, that is shown on the right plot of Figure~\ref{fig:evolution_p_lorenz}.
-The profile of $\checkk_{0.85}$ corresponding to the local maximum of the ratio, has not been plotted as it corresponds to the same profile of $\kmean$.
-
-% \begin{figure*}[!h]
-% \includegraphics[width=12cm]{Figures/evol_p_lorenz.pdf}
-% \caption{Evolution of $p$ and $\checkap$}
-% \label{fig:evolution_p_lorenz}
-% \end{figure*}
-% In order to compare the values taken by the objective function, the profiles have been represented on Figure~\ref{fig:lorenz_profiles}.
-% \begin{figure}[!h]
-% % \includegraphics[width=12cm]{Figures/lorenz_cdf_profile.pdf}
-% \includegraphics[width=12cm]{Figures/profile_lorenz_all_estimates.pdf}
-% \caption{Profiles of different $\mathbf{k}$ for the Lorenz model}
-% \label{fig:lorenz_profiles}
-% \end{figure}
-% The profile of $\kmean$ presents a good insight on the performances of this estimate: for most values of the uncertain variables, the objective is low.
-In contrast, for $\mathbf{u}$ close to $0.05$, a maximum is reached.
-%\begin{figure}[!h]
-%\includegraphics[width=8.3cm]{Figures/cdf_lorenz_with_ratio.pdf}
-%\caption{CDF corresponding to different $\mathbf{k}$ for the Lorenz model}
-%\label{fig:lorenz_cdf}
-%\end{figure}
-
-% \clearpage
-% \subsection{Context: Shallow water equations and bottom friction}
-
-% The quality of water circulation modelling in coastal areas is largely dependent on the boundary conditions, (e.g.\ the tide), the bathymetry and the friction induced by the rugosity of the ocean bed \citep{boutet_estimation_2015}.
-The latter will then be estimated in a robust manner, by applying the criteria introduced above.
-
-% The model studied is based on the one-dimensional shallow water equations, described Eq.~\eqref{eq:SWE_equations}, solved numerically on a domain $D$.
-$h$ is the height of the water column, $q$ is the discharge, and $z$ is the bathymetry, while $g$ is the usual gravitation constant.
-$\mathbf{k}$ is a quadratic friction term, proportional to the square of the inverse of Manning-Strickler coefficient.
-% \begin{align}
-%   \label{eq:SWE_equations}
-%   \left\{
-%     \begin{array}{l}
-%       \partial_t h + \partial_x q = 0 \\
-%       \partial_t q + \partial_x \left(\frac{q^2}{h} + \frac{g}{2}h^2\right) = - gh\partial_x z - \mathbf{k}q |q|h^{-7/3} \\
-%       h(0, t) = 20.0 + \mathrm{Amplitude} \cdot \sin \left(\frac{2\pi}{\mathbf{u}}t\right) \\
-%       q(0, t) = 0
-%       \end{array}
-%   \right.
-% \end{align}
-
-% The estimation of the bottom friction and/or topography has been treated in a deterministic setting, % in Section~\ref{sec:deterministic}
-% using tools from variational data assimilation~\cite[e.g.][]{das_estimation_1991,das_variational_1992,honnorat_identification_2010}.
-% If the boundary conditions are not well-known, the estimation will then compensate this misspecification.
-The resulting estimate will then be optimal for this particular configuration, but will not acknowledge the uncertainty upon the boundary conditions.
-Instead, we are looking for an estimate that is robust considering the variability of the uncertain boundary conditions.
-
-% The problem of the estimation of the bottom friction will be studied using twin experiments.
-For this purpose, a few references simulations have been performed in order to produce different observations $\mathbf{y}^o$.
-Those scenarios are detailed Table~\ref{tab:optim_scenar}.
-The true bottom friction $\mathbf{k}^t$ is the same for all simulations, and is a non-constant function of the spatial domain $D = [0, L]$ defined as:
-% \begin{equation}
-%   \label{eq:defnition_kt}
-%   \mathbf{k}^t= \mathbf{k}^t(x) = 0.2\cdot (1 + \sin(2\pi x/L))
-% \end{equation}
-% However, the space $\Kspace$ in which we wish to estimate the bottom friction is one-dimensional. This leads to the strict positivity of the cost function, as no perfect fit can be achieved.
-
-% As presented on Table~\ref{tab:RO_modelling}, we consider two a priori chosen variable: $\mathbf{u} \in \Uspace$ that is the period of the sine wave on the left boundary.
-The aleatoric uncertainty on this variable is modelled by a random variable distributed uniformly on $\Uspace$.
-% The amplitude of the sine wave is also chosen a priori and set to an arbitrary value, that may be different from the true amplitude used to generate $\mathbf{y}^o$.
-
-% \begin{table*}[t]
-%   \caption{Modelling of the estimation problem}
-%   \label{tab:RO_modelling}
-% \begin{tabular}{rrr}
-%   \tophline
-%   Parameter & Modelling & Type of parameter \\
-%   \middlehline
-%   Bottom friction: $\mathbf{k}$  &$\Kspace=[0, 1]$ & Calibrated parameter \\
-%   Period: $\mathbf{U}$ & $\mathrm{Unif}\left([14.7, 15.3]\right)$ & A priori chosen and uncertain\\
-%   Amplitude &  5.0 & A priori chosen and fixed\\
-%   \bottomhline
-% \end{tabular}
-% \end{table*}
-
-% % ----------------------------------------------------------------------------
-% \section{Deterministic optimisation}
-% \label{ssec:deterministic_optimisation}
-% The problem has first been studied in a deterministic setting. The following optimisation problem has been performed numerically:
-% \begin{equation}
-%   \label{eq:opt_deter}
-%   \text{Minimise } \mathbf{k}\in\Kspace \mapsto J(\mathbf{k},\mathbf{u}^b)\quad \text{for }\mathbf{u}^b= \Ex_{\mathbf{U}}[\mathbf{U}] = 15.0
-% \end{equation}
-% At the same time, the background value of the amplitude is fixed and set to $5.0$.
-% Different scenario have been established (i.e.\ different $\mathbf{u}^t$ and amplitude producing different $\mathbf{y}^o$), and are detailed in Table~\ref{tab:optim_scenar}.
-The configurations correspond to different values of the amplitude (letter~``A'') and the period (letter~``P'').
-If the truth value is greater (resp.\ smaller) than the background value, the lowercase letter ``p'' follows (resp.\ ``m'').
-
-% On the same table, are shown the result $\kest$ of the optimisation defined in Eq.~\eqref{eq:opt_deter} for each one of the different operating conditions.
-
-% \begin{table*}[t]
-%   \caption{Settings for reference simulations, and optimisation results}
-%   \label{tab:optim_scenar}
-% \begin{tabular}{rrrrrrrr} \tophline
-% Scenario for $\mathbf{u}^t$: &$\Ex_{\mathbf{U}}[\mathbf{U}]$  & Pm & ApPm & AmPm & Pp & ApPp & AmPp \\ \middlehline
-%   $\mathbf{u}^t- \mathbf{u}^b$ & 0.0            & -0.1  & -0.2 & -0.1 & +0.2 & +0.1 & +0.2 \\
-%   $\mathrm{Amplitude}- 5.0$   & 0.0             &  0.0  & +0.1 & -0.2 &  0.0 & +0.2 & -0.1 \\ \middlehline
-%   $\kest$      & 0.1043          & 0.2028 & 0.2709 & 0.2427 & 0.0  & 0.0 & 0.0015 \\\bottomhline
-% \end{tabular}
-% \end{table*}
-
-% Optimising without uncertainties (meaning that the $\mathbf{u}^b=\mathbf{u}^t$) yields an optimal value $\kest$ close to $0.10$, that we define to be $\kest_{\mathrm{opt}}$
-% We can observe two different regimes, depending on the sign of $\mathbf{u}^t-\Ex_{\mathbf{U}}[\mathbf{U}]$.
-If this quantity is positive, optimisation will produce an estimation close to $0$.
-If it is negative, the estimate is larger than $0.20$.
-
-% % ----------------------------------------------------------------------------
-% \subsection{Robust estimates}
-% In order to compute the robust estimates, the cost function has been evaluated on a regular grid of $150\times150$ points over $\Kspace\times\Uspace$.
-$\kmean$, $\kvar$, $\checkk_{.9}$, $\checkk_{.95}$ and $\checkk_{1}$ (along with their corresponding factors $\checka_p$) have been evaluated for the different configurations, detailed in Table~\ref{tab:optim_scenar}.
-As shown on Table~\ref{tab:res_robust}, $\checkkp$ does not vary significantly when the level of confidence $p$ increases.
-
-% \begin{table*}[t]
-%   \caption{Mean and variance optimisers, and $\checkkp$ for different levels of confidence $p$}
-%   \label{tab:res_robust}
-%   \begin{tabular}{rrrrrrrr} \tophline
-%     Scenario&$\Ex_{\mathbf{U}}[\mathbf{U}]$ & Pm & ApPm & AmPm & Pp & ApPp & AmPp \\  \middlehline
-%   $\kmean$ & 0.1678    & 0.2214  & 0.2617 & 0.2685 & 0.0872 & 0.0738 & 0.1275 \\
-%   $\kvar$  & 1.0      &  1.0  & 1.0 & 1.0 &  1.0 & 1.0 & 1.0 \\ \middlehline
-%   $\checkk_{.90}$ & 0.1074 & 0.1074 & 0.0872 & 0.1678 & 0.1074  & 0.0738 & 0.1275 \\
-%   $\checka_{.90}$    & 1.1754  & 1.1718 & 1.1779 & 1.1293 & 1.1768  & 1.1807 & 1.1406 \\\middlehline
-
-%   $\checkk_{.95}$ & 0.1074 & 0.1074 & 0.0872 & 0.1611 & 0.1074  & 0.0671 & 0.1275 \\
-%   $\checka_{.95}$ & 1.1802 & 1.1806 & 1.1868 & 1.1320 & 1.1861  & 1.2027 & 1.1525 \\\middlehline
-%     $\checkk_{1}$& 0.1074 & 0.1074 & 0.0872 & 0.1611 & 0.1074  & 0.0671 & 0.1275 \\
-%   $\checka_{1}$ & 1.1944    & 1.1922 & 1.1961 & 1.1321 & 1.1976  & 1.2035 & 1.1682 \\\middlehline
-% \end{tabular}
-% \end{table*}
-
-% In that case, the minimiser of the variance $\kvar$ is the right boundary of $\Kspace$, regardless of the value of $\mathbf{u}^t$.
-This is due to the fact that at this point, the cost function produces bad, yet steady performances.
-From a physical point of view, increasing the bottom friction will decrease the momentum.
-The movement of the water surface will be damped, and the operating conditions will have less effects.
-
-% Looking at $\kmean$, we can see that the estimates obtained are larger than $0.22$ when $\mathbf{u}^t< \Ex_{\mathbf{U}}[\mathbf{U}]$ (that is for Pm, ApPm, and AmPm).
-Those results are similar to the one obtained in the deterministic setting of Table~\ref{tab:optim_scenar}.
-However, for $\mathbf{u}^t> \Ex_{\mathbf{U}}[\mathbf{U}]$ (Pp, ApPp, and AmPp), $\kmean$ is much closer to $\kest_{\mathrm{opt}}$, the optimal value without uncertainties.
-
-% Now for $\checkk_1$, while the estimates for scenarios Pp, ApPp and AmPp are similar to $\kmean$, the obtained values for the other scenarios are close to $\kest$.
-% Figures~\ref{fig:SWE_checkalpha} and~\ref{fig:SWE_profiles} show the contour plot and profiles of the cost function in centered conditions ($\Ex_{\mathbf{U}}[\mathbf{U}]$ scenario).
-Figures~\ref{fig:SWE_checkalphaApPp} and \ref{fig:SWE_profilesApPp} (resp.
-Figures~\ref{fig:SWE_checkalphaAmPm} and~\ref{fig:SWE_profilesAmPm}) show the contour plot and profiles of the cost function for the ApPp scenario (resp.
-AmPm scenario).
-
-% The concentration of $\checkkp$ close to $\kest_{\mathrm{opt}}$ is caused by the very small value of the cost function at its minimum over $\Kspace\times \Uspace$.
-Close to this minimum, the region of acceptable $\mathbf{k}$ will be growing slowly as $\alpha$ increases, weighing the estimation toward $\kest_{\mathrm{opt}}$.
-
-% The fact that we retrieved values close to the optimal one should not overlook that a robust estimate is not necessarily $\kest_{\mathrm{opt}}$, and that this result is specific to this problem.
-
-% \clearpage
-% \begin{figure*}[!h]
-% \includegraphics[width=8cm]{Figures/SWE_big3.pdf}
-% \caption{Top: Cost function of the SWE problem ($\Ex_{\mathbf{U}}[\mathbf{U}]$ scenario) and its conditional minimisers.
-The thick yellow lines represent the boundary of the region where $\phi_\alpha<0$.
-The red dashed line is the estimate $\checkk_{1}$.
-Bottom: $R_{\checka}$}
-% \label{fig:SWE_checkalpha}
-% \end{figure*}
-
-% \begin{figure*}[!h]
-%   \centering
-%   \includegraphics[width=8cm]{Figures/profile_swe.pdf}
-%   \caption{Profiles of different estimates of $\mathbf{k}$ for the $\Ex_{\mathbf{U}}[\mathbf{U}]$ scenario}
-%   \label{fig:SWE_profiles}
-% \end{figure*}
-
-% \begin{figure*}[!h]
-% \includegraphics[width=8cm]{Figures/SWE_ApPp3.pdf}
-% \caption{Top: Cost function of the SWE problem (ApPp scenario) and its conditional minimisers.
-The thick yellow lines represent the boundary of the region where $\phi_\alpha<0$.
-The red dashed line is the estimate $\checkk_{1}$.
-Bottom: $R_{\checka}$}
-% \label{fig:SWE_checkalphaApPp}
-% \end{figure*}
-
-% \begin{figure*}[!h]
-%   \centering
-%   \includegraphics[width=7cm]{Figures/SWE_ApPp_profile.pdf}
-%   \caption{Profiles of different estimates of $\mathbf{k}$ for the ApPp scenario}
-%   \label{fig:SWE_profilesApPp}
-% \end{figure*}
-
-% \begin{figure*}[!h]
-% \includegraphics[width=8cm]{Figures/SWE_AmPm3.pdf}
-% \caption{Top: Cost function of the SWE problem (AmPm scenario) and its conditional minimisers.
-The thick yellow lines represent the boundary of the region where $\phi_\alpha<0$.
-The red dashed line is the estimate $\checkk_{1}$.
-Bottom: $R_{\checka}$}
-% \label{fig:SWE_checkalphaAmPm}
-% \end{figure*}
-
-% \begin{figure*}[!h]
-%   \centering
-%   \includegraphics[width=8cm]{Figures/SWE_AmPm_profile.pdf}
-%   \caption{Profiles of different estimates of $\mathbf{k}$ for the AmPm scenario}
-%   \label{fig:SWE_profilesAmPm}
-% \end{figure*}
+We can see that the mean forecast error squared, on the right side, averaged over time and space is the smallest for $\kest_{\mathrm{global}}$, while $\kest_{1.0}$ performs slightly better $\hatkmean$.
+
+Figure~\ref{fig:forecast_squared_error_distrib} shows the distribution of the mean squared error. 
+\begin{figure*}[!h]
+\centering
+\includegraphics[width=10cm]{Figures/forecast_error_distrib_2.pdf}
+\caption{Distribution of the forecast squared error, averaged over the different values of the uncertain parameter in the numerical simulations \victor{doublon avec fig.\ref{fig:forecast_squared_error} ?}}
+\label{fig:forecast_squared_error_distrib}
+\end{figure*}
+
+\subsubsection{Continuous Ranked Probability Score}
+The Continuous ranked probability score (CRPS) measure the squared difference between the predicted CDF $F_{\mathrm{pred}}$ using a calibrated value, and the CDF of the observation $F_{\mathrm{pred}}^o$.
+\begin{equation}
+\label{eq:def_crps}
+\mathrm{CRPS}(\mathbf{k}) = \int_{\mathbb{R}} (F_{\mathrm{pred}}(x,\mathbf{k}) - F^o_{\mathrm{pred}}(x))^2 \,\mathrm{d}x
+\end{equation}
 
 \clearpage
-\conclusions  %% \conclusions[modified heading if necessary]
+\section*{Conclusion}  %% \conclusions[modified heading if necessary]
 This paper deals with the problem of robust calibration of a computer code in the presence of uncertain inputs.
@@
 
-\codeavailability{TEXT} %% use this section when having only software code available
-
-% \dataavailability{TEXT} %% use this section when having only data sets available
-
-\codedataavailability{TEXT} %% use this section when having data sets and software code available
-
 % \sampleavailability{TEXT} %% use this section when having geoscientific samples available
@@
 
-% \subsection{}     %% Appendix A1, A2, etc.
-
-% \noappendix       %% use this to mark the end of the appendix section
-
-%% Regarding figures and tables in appendices, the following two options are possible depending on your general handling of figures and tables in the manuscript environment:
-
-%% Option 1: If you sorted all figures and tables into the sections of the text, please also sort the appendix figures and appendix tables into the respective appendix sections.
-%% They will be correctly named automatically.
-
-%% Option 2: If you put all figures after the reference list, please insert appendix tables and figures after the normal tables and figures.
-%% To rename them correctly to A1, A2, etc., please add the following commands in front of them:
-
-\appendixfigures  %% needs to be added in front of appendix figures
-
-\appendixtables   %% needs to be added in front of appendix tables
-
-%% Please add \clearpage between each table and/or figure. Further guidelines on figures and tables can be found below.
-
-\authorcontribution{TEXT} %% it is strongly recommended to make use of this section
-
-\competinginterests{TEXT} %% this section is mandatory even if you declare that no competing interests are present
-
-\disclaimer{TEXT} %% optional section
-
-\begin{acknowledgements}
-TEXT
-\end{acknowledgements}
-
-%% REFERENCES
-
-%% The reference list is compiled as follows:
-
-% \begin{thebibliography}{}
-
-% \bibitem[AUTHOR(YEAR)]{LABEL1}
-% REFERENCE 1
-
-% \bibitem[AUTHOR(YEAR)]{LABEL2}
-% REFERENCE 2
-
-% \end{thebibliography}
-
-%% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
-%% authors experienced with BibTeX only have to include the following two lines:
+%% If you have bibdatabase file and want bibtex to generate the
+%% bibitems, please use
 %%
-
-\bibliographystyle{copernicus}
+%%  \bibliographystyle{elsarticle-num-names} 
+%%  \bibliography{<your bibdatabase>}
+
+%% else use the following coding to input the bibitems directly in the
+%% TeX file.
+\bibliographystyle{elsarticle-num-names} 
 \bibliography{bibzotero}
 
+\end{document}
+
+\endinput
 %%
-%% URLs and DOIs can be entered in your BibTeX file as:
-%%
-%% URL = {http://www.xyz.org/~jones/idx_g.htm}
-%% DOI = {10.5194/xyz}
-
-%% LITERATURE CITATIONS
-%%
-%% command                        & example result
-%% \citet{jones90}|               & Jones et al. (1990)
-%% \citep{jones90}|               & (Jones et al., 1990)
-%% \citep{jones90,jones93}|       & (Jones et al., 1990, 1993)
-%% \citep[p.~32]{jones90}|        & (Jones et al., 1990, p.~32)
-%% \citep[e.g.,][]{jones90}|      & (e.g., Jones et al., 1990)
-%% \citep[e.g.,][p.~32]{jones90}| & (e.g., Jones et al., 1990, p.~32)
-%% \citeauthor{jones90}|          & Jones et al.
-%% \citeyear{jones90}|            & 1990
-
-%% FIGURES
-
-%% When figures and tables are placed at the end of the MS (article in one-column style), please add \clearpage
-%% between bibliography and first table and/or figure as well as between each table and/or figure.
-
-%% ONE-COLUMN FIGURES
-
-%%f
-%\begin{figure}[t]
-%\includegraphics[width=8.3cm]{FILE NAME}
-%\caption{TEXT}
-%\end{figure}
-%
-%%% TWO-COLUMN FIGURES
-%
-%%f
-%\begin{figure*}[t]
-%\includegraphics[width=12cm]{FILE NAME}
-%\caption{TEXT}
-%\end{figure*}
-%
-%
-%%% TABLES
-%%%
-%%% The different columns must be seperated with a & command and should
-%%% end with \\ to identify the column brake.
-%
-%%% ONE-COLUMN TABLE
-%
-%%t
-%\begin{table}[t]
-%\caption{TEXT}
-%\begin{tabular}{column = lcr}
-%\tophline
-%
-%\middlehline
-%
-%\bottomhline
-%\end{tabular}
-%\belowtable{} % Table Footnotes
-%\end{table}
-%
-%%% TWO-COLUMN TABLE
-%
-%%t
-%\begin{table*}[t]
-%\caption{TEXT}
-%\begin{tabular}{column = lcr}
-%\tophline
-%
-%\middlehline
-%
-%\bottomhline
-%\end{tabular}
-%\belowtable{} % Table Footnotes
-%\end{table*}
-%
-%%% LANDSCAPE TABLE
-%
-%%t
-%\begin{sidewaystable*}[t]
-%\caption{TEXT}
-%\begin{tabular}{column = lcr}
-%\tophline
-%
-%\middlehline
-%
-%\bottomhline
-%\end{tabular}
-%\belowtable{} % Table Footnotes
-%\end{sidewaystable*}
-%
-%
-%%% MATHEMATICAL EXPRESSIONS
-%
-%%% All papers typeset by Copernicus Publications follow the math typesetting regulations
-%%% given by the IUPAC Green Book (IUPAC: Quantities, Units and Symbols in Physical Chemistry,
-%%% 2nd Edn., Blackwell Science, available at: http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf, 1993).
-%%%
-%%% Physical quantities/variables are typeset in italic font (t for time, T for Temperature)
-%%% Indices which are not defined are typeset in italic font (x, y, z, a, b, c)
-%%% Items/objects which are defined are typeset in roman font (Car A, Car B)
-%%% Descriptions/specifications which are defined by itself are typeset in roman font (abs, rel, ref, tot, net, ice)
-%%% Abbreviations from 2 letters are typeset in roman font (RH, LAI)
-%%% Vectors are identified in bold italic font using \vec{x}
-%%% Matrices are identified in bold roman font
-%%% Multiplication signs are typeset using the LaTeX commands \times (for vector products, grids, and exponential notations) or \cdot
-%%% The character * should not be applied as mutliplication sign
-%
-%
-%%% EQUATIONS
-%
-%%% Single-row equation
-%
-%\begin{equation}
-%
-%\end{equation}
-%
-%%% Multiline equation
-%
-%\begin{align}
-%& 3 + 5 = 8\\
-%& 3 + 5 = 8\\
-%& 3 + 5 = 8
-%\end{align}
-%
-%
-%%% MATRICES
-%
-%\begin{matrix}
-%x & y & z\\
-%x & y & z\\
-%x & y & z\\
-%\end{matrix}
-%
-%
-%%% ALGORITHM
-%
-%\begin{algorithm}
-%\caption{...}
-%\label{a1}
-%\begin{algorithmic}
-%...
-%\end{algorithmic}
-%\end{algorithm}
-%
-%
-%%% CHEMICAL FORMULAS AND REACTIONS
-%
-%%% For formulas embedded in the text, please use \chem{}
-%
-%%% The reaction environment creates labels including the letter R, i.e. (R1), (R2), etc.
-%
-%\begin{reaction}
-%%% \rightarrow should be used for normal (one-way) chemical reactions
-%%% \rightleftharpoons should be used for equilibria
-%%% \leftrightarrow should be used for resonance structures
-%\end{reaction}
-%
-%
-%%% PHYSICAL UNITS
-%%%
-%%% Please use \unit{} and apply the exponential notation
-
-\end{document}
+%% End of file `elsarticle-template-num-names.tex'.
 

### 2019-11-18 article-modif-A&E.tex
fix remaining pb when switching from npg -> JCP
add title: 'relative regret', centering of the figures

@@
 
-%% For including figures, graphicx.sty has been loaded in
+%% For including figures, graphicx.sty has been loxaded in
 %% elsarticle.cls. If you prefer to use the old commands
@@
 %\victor{Pour moi, ce qui est en majuscule, c'est des v.a., et tous les inputs sont en gras (mais on peut laisser tomber le gras)}
-\introduction%% \introduction[modified heading if necessary]
+%% \introduction[modified heading if necessary]
 %\subsection{Motivation}
@@
 %the sampling of a certain amount of $\mathbf{U}$ 
-The estimations are computed using the following expressions {\color{red} plus subtil qu'un calcul empririque ? si oui, expliciter}:
+The estimations at a given $\mathbf{k}$ are computed using standard Monte Carlo, resulting in the following optimisation problems:
 \begin{equation}
@@
 \end{equation}
+and
 \begin{equation}
@@
   \label{eq:branin_hoo}
- \mathrm{BH}(x_1,x_2) = \frac{1}{51.95}\left[\left(\bar{x}_2 - \frac{5.1 \bar{x}_1^2}{4\pi^2} + \frac{5\bar{x}_1}{\pi} -6 \right)^2 + \left(10 - \frac{10}{8\pi}\right)\cos(\bar{x}_1)-44.81\right]+2\\
-\text{with } \bar{x}_1 = 3x_1-5,\quad \bar{x}_2 = 3x_2
+ \mathrm{BH}(x_1,x_2) &= \frac{1}{51.95}\left[\left(\bar{x}_2 - \frac{5.1 \bar{x}_1^2}{4\pi^2} + \frac{5\bar{x}_1}{\pi} -6 \right)^2 + \left(10 - \frac{10}{8\pi}\right)\cos(\bar{x}_1)-44.81\right]+2\\
+&\text{with } \bar{x}_1 = 3x_1-5,\quad \bar{x}_2 = 3x_2
 \end{align}
@@
 % as we can argue that both values may be a sensible choice for the MPE. This comes from the fact that the hypothesis that $\mathbf{K}^*$ is a continuous r.v.\ is violated. 
-\victor{Réécrit}
 A way to avoid this issue is to introduce a bit of leeway for a value to be optimal, or at least ``acceptably not optimal''.
@@
 
-\section{A new family of robust estimators \elise{titre a revoir}}
+\section{Relative regret-based family of estimators}%A new family of robust estimators \elise{titre a revoir}}
 \label{sec:relax_constraint}
@@
 that is the smallest $\alpha$, such that there exists a particular $\checkkp \in \Kspace$ for which $J(\checkkp,\mathbf{U}) \leq \checkap J^*(\mathbf{U})$ with probability $p$.
-This formulation can be linked to the Value-at-Risk of the random variable $\max_{\mathbf{k}} \{ \frac{J(\mathbf{k},\mathbf{U})}{J^*(\mathbf{U})}\}$, that is a measure of risk usually applied in the financial sector (see \cite{rockafellar_deviation_2002}).
+This formulation can be linked to the quantiles and Value-at-Risk of the random variable $\max_{\mathbf{k}} \{ \frac{J(\mathbf{k},\mathbf{U})}{J^*(\mathbf{U})}\}$, that is a measure of risk usually applied in the financial sector (see \cite{rockafellar_deviation_2002}).
 For different levels $p$, and thus different $\alpha_p$, Figure~\ref{fig:illu_alpha_p} shows examples of $\Gamma_{\alpha_p}$.
@@
 \begin{table*}[t]
+  \centering
   \caption{Robust estimators, based on a cost function $J$}
@@
 \begin{figure*}[!ht]
-\includegraphics[width=12cm]{Figures/branin_side_66_relax_gamma_both.pdf}
+  \centering
+\includegraphics[width=10cm]{Figures/branin_side_66_relax_gamma_both.pdf}
 \caption{Top: $J_{\mathrm{BH}}$ and $J_{\mathrm{BHswap}}$ contours.
@@
  \begin{figure}[!ht]
-\includegraphics[width=12cm]{Figures/alpha_p_BH.pdf}
+   \centering
+\includegraphics[width=10cm]{Figures/alpha_p_BH.pdf}
 \caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for the $J_{\mathrm{BH}}$ function. The dashed line indicates the level $p$ associated with the highest ratio}
@@
   $\hatkmpe$ & 1.628 \\
-$\kest_p,~p=0.95$ & 1.672 \\ 
-$\kest_{\mathrm{maxratio}},~\hat{p}_{\mathrm{maxratio}}=0.654$ & 1.637 \\ \hline
+  $\kest_{\mathrm{maxratio}},~\hat{p}_{\mathrm{maxratio}}=0.654$ & 1.637 \\
+$\kest_p,~p=0.95$ & 1.672 \\ \hline
 \end{tabular}
@@
 \begin{figure*}[t]
-\includegraphics[width=12cm]{Figures/profile_BH_all_estimates_noku.pdf}
+  \centering
+\includegraphics[width=10cm]{Figures/profile_BH_all_estimates_noku.pdf}
 \caption{Profiles of the different estimates for the $J_{\mathrm{BH}}$ function, corresponding to the vertical cross sections of the contour.
@@
 \begin{figure}[ht]
-\includegraphics[width=12cm]{Figures/alpha_p_BHs.pdf}
+  \centering
+\includegraphics[width=10cm]{Figures/alpha_p_BHs.pdf}
 \caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for the $J_{\mathrm{BHswap}}$ function. The dashed line indicates the level $p$ associated with the highest ratio}
@@
 \begin{figure*}[t]
-\includegraphics[width=12cm]{Figures/profile_BHs_all_estimates_noku.pdf}
+  \centering
+\includegraphics[width=10cm]{Figures/profile_BHs_all_estimates_noku.pdf}
 \caption{Profiles of the different estimates for the $J_{\mathrm{BHswap}}$ function.
@@
 \centering
-\includegraphics[width=12cm]{Figures/RobustSWEmis_plots.pdf}
+\includegraphics[width=.7\textwidth]{Figures/RobustSWEmis_plots.pdf}
 \caption{Procedure of robust calibration for the shallow water problem.
@@
 
+\begin{figure}[!h]
+  \centering
+  \includegraphics[width=.8\textwidth]{Figures/profile_swe}
+  \caption{Profiles for the calibration problem}
+  \label{fig:profiles_swe}
+\end{figure}
+
 \subsection{Assessing the quality of the forecast of the calibrated model}
@@
 \centering
-\includegraphics[width=12cm]{Figures/forecast_error.pdf}
+\includegraphics[width=.9\textwidth]{Figures/forecast_error.pdf}
 \caption{Quality of forecast, depending on the calibrated parameter.
@@
 We can see that the mean forecast error squared, on the right side, averaged over time and space is the smallest for $\kest_{\mathrm{global}}$, while $\kest_{1.0}$ performs slightly better $\hatkmean$.
+\begin{figure}[!h]
+  \centering
+  \includegraphics[width=.9\textwidth]{Figures/forecast_CRPS}
+  \caption{CRPS computed for different calibrated parameters}
+  \label{fig:forecast_crps}
+\end{figure}
 
-Figure~\ref{fig:forecast_squared_error_distrib} shows the distribution of the mean squared error. 
-\begin{figure*}[!h]
-\centering
-\includegraphics[width=10cm]{Figures/forecast_error_distrib_2.pdf}
-\caption{Distribution of the forecast squared error, averaged over the different values of the uncertain parameter in the numerical simulations \victor{doublon avec fig.\ref{fig:forecast_squared_error} ?}}
-\label{fig:forecast_squared_error_distrib}
-\end{figure*}
+% \begin{figure*}[!h]
+% \centering
+% \includegraphics[width=10cm]{Figures/distrib_L2norm.pdf}
+% \caption{Distribution of the forecast squared error, averaged over the different values of the uncertain parameter in the numerical simulations \victor{doublon avec fig.\ref{fig:forecast_squared_error} ?}}
+% \label{fig:forecast_squared_error_distrib}
+% \end{figure*}
 

### 2019-11-19 article-modif-A&E.tex
fix space in front of cite, booktabs

@@
 
-%% For including figures, graphicx.sty has been loxaded in
+%% For including figures, graphicx.sty has been loaded in
 %% elsarticle.cls. If you prefer to use the old commands
@@
 \usepackage{graphicx}
-
+\usepackage{booktabs}
 % À changer
@@
 \newcommand{\Uspace}{\mathbb{U}}
+\newcommand{\JBH}{J_{\mathrm{BH}}}
+\newcommand{\JBHS}{J_{\mathrm{BHswap}}}
 
-\newcommand{\arthur}[1]{{\itshape \color{cyan} ({#1})}}
-\newcommand{\elise}[1]{{\itshape \color{red} ({#1})}}
-\newcommand{\victor}[1]{{\itshape \color{green} ({#1})}}
+\newcommand{\arthur}[1]{{\itshape\color{cyan} ({#1})}}
+\newcommand{\elise}[1]{{\itshape\color{red} ({#1})}}
+\newcommand{\victor}[1]{{\itshape\color{green} ({#1})}}
 
@@
 Moreover, such uncertainties may be of different nature. 
- \cite{walker_defining_2003} propose two to consider two categories of uncertainties.
-On the one hand aleatoric uncertainties,  coming from the inherent variability of a phenomenon, e.g.
-intrinsic randomness of some environmental variables.
+~\cite{walker_defining_2003} propose two to consider two categories of uncertainties.
+On the one hand aleatoric uncertainties,  coming from the inherent variability of a phenomenon, e.g.\ intrinsic randomness of some environmental variables.
 On the other hand, epistemic uncertainties coming from a lack of knowledge about the properties and conditions of the phenomena underlying the behaviour of the system under study.
@@
 %
-An application of such an approach, in the context of ocean circulation modeling, is the estimation of ocean bottom friction parameters in \cite{das_estimation_1991} and \cite{boutet_estimation_2015}.
+An application of such an approach, in the context of ocean circulation modeling, is the estimation of ocean bottom friction parameters in~\cite{das_estimation_1991} and~\cite{boutet_estimation_2015}.
 
@@
 the distribution of the conditional minimisers, notion that appeared notably in~\cite{villemonteix_informational_2006} and in~\cite{hennig_entropy_2011} for a global optimisation purpose.
-Both approaches and related robust estimates are described in section \ref{robust formulations}.
-Section \ref{sec:relax_constraint} introduces a new class of estimators, by relaxing the constraint of optimality and defining regions of acceptability, similarly as~\cite{buhmann_robust_2013} in discrete combinatorial problems.
+Both approaches and related robust estimates are described in Section~\ref{robust formulations}.
+Section~\ref{sec:relax_constraint} introduces a new class of estimators, by relaxing the constraint of optimality and defining regions of acceptability, similarly as~\cite{buhmann_robust_2013} in discrete combinatorial problems.
 The intention is that a robust estimate provides values of the cost function close enough to the attainable minimum for each configuration induced by $\mathbf{u}\in\Uspace$.
-Illustration of the various discribed methods are given on a numerical exemple in section \ref{sec:SWE_application}.
+Illustration of the various discribed methods are given on a numerical exemple in Section~\ref{sec:SWE_application}.
 
@@
 As mentioned before, robustness can be understood as satisfactory for a broad range of $\mathbf{u}$, and/or as insensitive as possible to uncertainties encompassed in $\mathbf{U}$.
-Under this definition, one may design classical robust estimators, either by optimising the moments of the cost function ; or based on the distribution of its minimisers.
+Under this definition, one may design classical robust estimators, either by optimising the moments of the cost function; or based on the distribution of its minimisers.
 
@@
 As the computation of this Pareto front is usually hard and expensive, alternative strategies based on the minimisation of a scalarized version of the vector of objectives are often considered.
-Some are based on a weighted sum of the objectives, as presented in~\cite{grodzevich_normalization_2006} and in \cite{marler_weighted_2010}, while some others are based on the minimisation of one of the objectives under constraints on the others, as performed in~\cite{lehman_designing_2004}.
+Some are based on a weighted sum of the objectives, as presented in~\cite{grodzevich_normalization_2006} and in~\cite{marler_weighted_2010}, while some others are based on the minimisation of one of the objectives under constraints on the others, as performed in~\cite{lehman_designing_2004}.
 Both of these methods are based on an \textit{delicate} choice of weights or of constraints before any computation.
@@
 The resulting approximation and therefore its mode, is sensitive to the density estimation method.
-Main methods are KDE  (Kernel Density Estimation) \cite{elise}, and  EM (Expectation-Maximisation)~\citep{dempster_maximum_1977}.
+Main methods are KDE  (Kernel Density Estimation)~\cite{elise}, and  EM (Expectation-Maximisation)~\citep{dempster_maximum_1977}.
 
@@
 \begin{figure*}[!ht]
+  \centering
   \includegraphics[width=12cm]{Figures/branin_side_moments_noscale.pdf}
@@
 
-Illustrations related to $\hatkmpe$ are depicted on Figure \ref{fig:contours}.
+Illustrations related to $\hatkmpe$ are depicted on Figure~\ref{fig:contours}.
 As before, the set of $\mathbf{u}^i$ is taken from a regular grid.
@@
 The left, respectively right, column stands for $J_{\mathrm{BH}}$, respectively $J_{\mathrm{BHswap}}$ function.
-The bottom rows presents three approximations of the density of minimisers: the histogram in grey (bin size selected using Freedman-Diaconis from \cite{freedman_histogram_1981}), the result of a kernel density estimation (KDE) with Gaussian kernels in red (using Scott's rule from \cite{scott_optimal_1979} for bandwidth selection), and the estimation by a Gaussian mixture.
+The bottom rows presents three approximations of the density of minimisers: the histogram in grey (bin size selected using Freedman-Diaconis from~\cite{freedman_histogram_1981}), the result of a kernel density estimation (KDE) with Gaussian kernels in red (using Scott's rule from~\cite{scott_optimal_1979} for bandwidth selection), and the estimation by a Gaussian mixture.
 The latter has been calculated with the EM algorithm.
@@
 \begin{figure*}
+  \centering
   \includegraphics[width=12cm]{Figures/branin_side_66.pdf}
@@
 \begin{figure*}[!t]
+\centering
 \includegraphics[width=12cm]{Figures/relaxation_tuto.pdf}
@@
 $\alpha J^*(\mathbf{U})$.
-Without relaxation, i.e.\ when $\alpha$ is set to $1$, $\Gamma_1$ is non-zero if the set $\{\mathbf{u}\in\Uspace \mid J(\mathbf{k},\mathbf{u}) = J^*(\mathbf{u})\}$ has non-zero measure with respect to $\Prob_{\mathbf{U}}$.
-Still, this can be related to the definition of the MPE from Eq.~\eqref{eq:MPE}
+Without relaxation, i.e.\ when $\alpha$ is set to $1$, $\Gamma_1$ is non-zero if the set $\{\mathbf{u}\in\Uspace \mid J(\mathbf{k},\mathbf{u}) = J^*(\mathbf{u})\}$ has non-zero measure with respect to $\Prob_{\mathbf{U}}$, that is when the distribution of $\mathbf{K}^*$ presents atoms.
+This can be linked to the definition of the MPE from Eq.~\eqref{eq:MPE}.
+In the more general case, the MPE can be seen as the limiting case when $\alpha$ tends to $1$.
 
@@
 that is the smallest $\alpha$, such that there exists a particular $\checkkp \in \Kspace$ for which $J(\checkkp,\mathbf{U}) \leq \checkap J^*(\mathbf{U})$ with probability $p$.
-This formulation can be linked to the quantiles and Value-at-Risk of the random variable $\max_{\mathbf{k}} \{ \frac{J(\mathbf{k},\mathbf{U})}{J^*(\mathbf{U})}\}$, that is a measure of risk usually applied in the financial sector (see \cite{rockafellar_deviation_2002}).
+This formulation can be linked to the quantiles and Value-at-Risk of the random variable $\max_{\mathbf{k}} \{ \frac{J(\mathbf{k},\mathbf{U})}{J^*(\mathbf{U})}\}$, that is a measure of risk usually applied in the financial sector (see~\cite{rockafellar_deviation_2002}).
 For different levels $p$, and thus different $\alpha_p$, Figure~\ref{fig:illu_alpha_p} shows examples of $\Gamma_{\alpha_p}$.
-The associated $\mathbf{k}_p$ is then the first value for which $\Gamma_{\alpha_p}$ reaches $p$.
+By definition, the associated $\mathbf{k}_p$ is then the first value for which $\Gamma_{\alpha_p}$ reaches $p$.
+We can see that changing the level $p$ shifts the maximiser of $\Gamma_{\alpha_p}$.
 
@@
 \includegraphics[width = 8.3cm]{Figures/illu_alpha_p.pdf}
-\caption{Illustration of the influence of different levels $p$ on $\Gamma_{\alpha_p}$ and on $\mathbf{k}_p$ \victor{Est-ce que tu pensais à ce genre de figure ?}}
+\caption{Illustration of the influence of different levels $p$ on $\Gamma_{\alpha_p}$ and on $\mathbf{k}_p$ \victor{Pertinence ?}}
 \label{fig:illu_alpha_p}
@@
   \centering
-  \caption{Robust estimators, based on a cost function $J$}
 \label{tab:RO_recap}
 \begin{tabular}{lrr}
-  \hline
-  Definition & Related quantities & Interpretation \\
-  \hline
+  \toprule
+  Definition & Related quantities & Interpretation \\ \midrule
    $\argmin_{\mathbf{k}\in\Kspace} \Ex_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U})\right]$& $\kmean$ & Long run performances\\
@@
     $p_{\mathrm{maxratio}} = \argmax p/\checkap$ & $(p_{\mathrm{maxratio}}, \checkk_{\mathrm{maxratio}}, \checka_{\mathrm{maxratio}})$ & Maximal ratio of $p$ and $\checkap$ \\
-  \hline
+  \bottomrule
 \end{tabular}
+  \caption{Robust estimators, based on a cost function $J$}
+
 \end{table*}
@@
 The contour plots of those functions can be seen in the top plots of Figure~\ref{fig:contour_alpha}.
-The frontier corresponding to the couples of points $(\mathbf{k},\mathbf{u})$ verifying $\{J(\mathbf{k},\mathbf{u}) = \hat{\checka}_1 J^*(\mathbf{u})\}$ has been drawn on top of these contour plots.
-On the bottom plots, the curve $\mathbf{k}\mapsto \hat{\Gamma}_{\alpha}(\mathbf{k})$ for $\alpha=\hat{\checka}_1$ and $\alpha=1.5$ along with the histogram of the minimisers have been represented.
+The frontier corresponding to the couples of points $(\mathbf{k},\mathbf{u})$ verifying $\{J(\mathbf{k},\mathbf{u}) = \alpha J^*(\mathbf{u})\}$ has been drawn on top of these contour plots, for $\alpha=\hat{\checka}_1$ and an arbitrary $\alpha=1.5<\hat{\checka}_1$, to illustrate the effect of the acceptable region when the relaxation $\alpha$ increases.
+On the bottom plots, the curves $\mathbf{k}\mapsto \hat{\Gamma}_{\alpha}(\mathbf{k})$ for $\alpha=\hat{\checka}_1$ and $\alpha=1.5$ along with the histogram of the minimisers are represented.
+One can notice that the relaxation does not present an issue with the accumulation of the minimisers of $\JBH$ at $3.8$, as opposed to the MPE and its dependence on the estimation procedure of the distribution.
 
@@
 \begin{tabular}{lr}
-\hline
-Estimate & Value \\ \hline
+\toprule
+Estimate & Value \\ \midrule
 $\hatkvar$ & 1.371 \\ 
@@
   $\kest_{\mathrm{maxratio}},~\hat{p}_{\mathrm{maxratio}}=0.654$ & 1.637 \\
-$\kest_p,~p=0.95$ & 1.672 \\ \hline
+$\kest_p,~p=0.95$ & 1.672 \\ \bottomrule
 \end{tabular}
@@
 
-Practically speaking, in order to compare the effective values taken by the objective function given an estimate $\kest$ we are going to consider the functions of the form $\mathbf{u} \mapsto J(\kest,\mathbf{u})$, that we will call "profile of $\kest$".
+Practically speaking, in order to compare the effective values taken by the objective function given an estimate $\kest$ we are going to consider the functions of the form $\mathbf{u} \mapsto J(\kest,\mathbf{u})$, that we will call ``profile of $\kest$''.
 Those profiles are well suited for the representation of the cost function for an estimate $\kest$ fixed as the uncertain variable is modelled with a 1D uniform random variable.
@@
 \label{tab:recap_estimates_BHs}
-\begin{tabular}{lr} \hline
-Estimate & Value \\ \hline
+\begin{tabular}{lr} \toprule
+Estimate & Value \\ \midrule
 $\kest_{\mathrm{MPE}}$ & 0.606 \\ 
@@
 $\kest_{\mathrm{var}}$ & 2.638 \\ 
-$\kest_1,~p=1$ & 2.798   \\ \hline
+$\kest_1,~p=1$ & 2.798   \\ \bottomrule
 \end{tabular}
@@
 \caption{Calibrated values of $\mathbf{k}$ according to different criteria}
-\begin{tabular}{lr} \hline
-Estimator & Value \\ \hline
+\begin{tabular}{lr} \toprule
+Estimator & Value \\ \midrule
 $\hatkmpe$ & 0.249 \\
@@
 $\hat{\mathbf{k}}_p,~p=0.70$ & 0.560 \\ 
-$\hatkvar$ & 0.990\\ \hline
+$\hatkvar$ & 0.990\\ \bottomrule
 \end{tabular}
@@
 \subsubsection{Continuous Ranked Probability Score}
-The Continuous ranked probability score (CRPS) measure the squared difference between the predicted CDF $F_{\mathrm{pred}}$ using a calibrated value, and the CDF of the observation $F_{\mathrm{pred}}^o$.
+Given the random variables $\mathcal{M}_{\mathrm{pred}}(\kest, \mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$, representing the probabilistic forecast and the probabilistic observations, we can define the cumulative distribution functions (CDF) $F_{\mathrm{pred}}(\cdot, \kest)$ and $F^o_{\mathrm{pred}}(\cdot)$
+The Continuous ranked probability score (CRPS) measures the squared difference between the predicted CDF $F_{\mathrm{pred}}$ using a calibrated value, and the CDF of the observations $F_{\mathrm{pred}}^o$.
 \begin{equation}
@@
 A solution to explore is the use of surrogate models. Based on an initial design of experiment, the (expensive) cost function is replaced by a function, that is cheap to evaluate.
-For instance, \cite{ginsbourger_bayesian_2014}
+For instance,~\cite{ginsbourger_bayesian_2014}
 uses Gaussian Process regression and sequential methods to explore the conditional minimisers.

### 2019-11-19 article-modif-A&E.tex
estimation on swe

@@
 By definition, the associated $\mathbf{k}_p$ is then the first value for which $\Gamma_{\alpha_p}$ reaches $p$.
-We can see that changing the level $p$ shifts the maximiser of $\Gamma_{\alpha_p}$.
+We can see that changing the level $p$ shifts the maximiser of $\Gamma_{\alpha_p}$, and that for small $\alpha$, $\Gamma_{\alpha}(\mathbf{k}_1)$ is also very small.
+This indicates that $\mathbf{k}_1$ is located quite far from the conditional minimisers, and thus represents a compromise.
 
@@
 
-\begin{table*}[t]
+\begin{table}[t]
   \centering
-\label{tab:RO_recap}
 \begin{tabular}{lrr}
@@
 \end{tabular}
+\label{tab:RO_recap}
   \caption{Robust estimators, based on a cost function $J$}
-
-\end{table*}
+\end{table}
 
@@
 The profile of $\hatkmean$ in contrast, exceeds $\hat{\checka}_1 J^*(\mathbf{u})$ for $\mathbf{u}$ close to $5$, while the profile of $\hatkvar$ does for $\mathbf{u}$ close to $0$.
+As the different $\kest$ are very close for every criteria introduced in this paper, the profiles are almost undistinguishable.
 
@@
 In this case, $\hatkmpe$, $\hatkmean$ and $\hat{\checkk}_{\mathrm{maxratio}}$ present a similar behaviour.
-They perform very well for $\mathbf{u}>2$, especially for $\hatkmpe$ which is very close to the minimal value; for $\mathbf{u}<2$, it produces high values of the function.
+They perform very well for $\mathbf{u}>2$, especially for $\hatkmpe$ which is very close to the minimal value; However for $\mathbf{u}<2$, they produce high values of the function.
+
 The performances of $\hat{\checkk}_1$ are closer to the performances of $\hatkvar$ for this function, but it performs worse than $\hatkmean$ and $\hatkvar$ for $\mathbf{u}>2$, even though its range is designed to stay within the interval $[J^*(\mathbf{u}); \hat{\checka}_1 J^*(\mathbf{u})]$.
@@
 We can see that the estimation for this problem seems less problematic than the analytical examples shown above, as all derived quantites are unimodal.
-The different estimates however take a wide range of values, as seen on Table~\ref{tab:recap_estimates_metaSWE}.: there is a unique global minimiser on the whole space $\Kspace \times \Uspace$, noted $\kest_{\mathrm{global}}$.
+The different estimates however take a wide range of values, as seen on Table~\ref{tab:recap_estimates_metaSWE}.
+As a basis for comparison, the global minimiser of $J$ over $\Kspace \times \Uspace$ has been computed, and $\kest_{\mathrm{global}}$ is then obtained by discarding the $\mathbf{u}$ value.
+An interesting comparison arises when comparing with $\kest_{\mathrm{global}}$, where $\kest_1$ outperforms the global minimiser for $\mathbf{u} < 0.625$.
+
 As discussed earlier, the estimation of the MPE is dependent on the method used, and then its estimation using KDE in the middle plot of Figure~\ref{fig:estimation_swe} is here only for illustrative purposes.
@@
 \end{table*}
-
+Similarly as for $\JBH$ and $\JBHS$, the profiles are depicted Figure~\ref{fig:profiles_swe}.
 \begin{figure}[!h]
@@
 \end{figure}
-
+We can see that the performances of $\kest_1$ and $\hatkmean$ are very similar, but $\kest_1$ has better performances when $\mathbf{u} > 0.6$.
+\clearpage
 \subsection{Assessing the quality of the forecast of the calibrated model}

### 2019-11-20 article-modif-A&E.tex
autoformatting

@@
 
-In this paper, we aim at finding $\kest$ a {\it robust} estimator of $\mathbf{k}$.
+In this paper, we aim at finding $\kest$ a {\it robust\/} estimator of $\mathbf{k}$.
 The definition of robustness differs depending on the context in which it is used.
@@
 
-A lot of different methods are readily available to solve these minimisation problems.
-For instance, stochastic Sample Approximation \citep{juditsky_stochastic_2009,kim_guide_2015} is based on a finite and fixed set of samples $\{ \mathbf{u}^{i}\}_{i=1 \dots N}$  of $\mathbf{U}$.
+A lot of different methods are readily available to solve these
+minimisation problems. For instance, stochastic Sample Approximation
+\citep{juditsky_stochastic_2009,kim_guide_2015} is based on a finite
+and fixed set of samples $\{ \mathbf{u}^{i}\}_{i=1 \dots N}$ of
+$\mathbf{U}$.
 %the sampling of a certain amount of $\mathbf{U}$ 
@@
 The estimations are %$\mathbf{k}\mapsto \mu(\mathbf{k})$ and $\mathbf{k}\mapsto\sigma(\mathbf{k})$ 
-based on a $1000 \times 1000$ regular grid over $\Kspace\times\Uspace$. Both cost functions are shown in  Figure~\ref{fig:branin_moments}, top row.
+based on a $1000 \times 1000$ regular grid over $\Kspace\times\Uspace$. Both cost functions are shown on~Figure~\ref{fig:branin_moments}, top row.
 
@@
 
-Alternatively, we can consider the mixing coefficients of the EM density estimation.
-The Gaussian centered at $1.5$ has been attributed a weight of $0.608$, while the one centered at $3.8$ has a mixing weight of $0.226$.
-Ultimately, an optimiser would be more likely to be close to $1.5$, but we do not have information on its performance in this region around this value.
+Alternatively, we can consider the mixing coefficients of the EM
+density estimation. The Gaussian centered at $1.5$ has been attributed
+a weight of $0.608$, while the one centered at $3.8$ has a mixing
+weight of $0.226$. Ultimately, an optimiser would be more likely to be
+close to $1.5$, but we do not have information on its performance in
+this region around this value.
 
@@
 We can see that changing the level $p$ shifts the maximiser of $\Gamma_{\alpha_p}$, and that for small $\alpha$, $\Gamma_{\alpha}(\mathbf{k}_1)$ is also very small.
-This indicates that $\mathbf{k}_1$ is located quite far from the conditional minimisers, and thus represents a compromise.
+This indicates that $\mathbf{k}_1$ is located quite far from the conditional minimisers, and arise as a compromise when the relaxation is large enough.
 
@@
 
-%We are now going to compute and compare those estimators on the $J_{\mathrm{BH}}$and $J_{\mathrm{BHswap}}$ function.
+% We are now going to compute and compare those estimators on the $J_{\mathrm{BH}}$and $J_{\mathrm{BHswap}}$ function.
 
@@
 Given that the numerical model is expensive to evaluate, it has first been evaluated on a relatively small regular grid.
-A metamodel based on Gaussian process is constructed and the PEI criterion \citep{ginsbourger_bayesian_2014,bossek_learning_2015} allow us to add point to evaluate and to better capture the locus of the conditional minimisers $\{(\mathbf{k}^*(\mathbf{u}), \mathbf{u}) \mid \mathbf{u} \in \Uspace \}$.
+A metamodel based on Gaussian process is constructed and the PEI criterion~\citep{ginsbourger_bayesian_2014,bossek_learning_2015} allow us to add point to evaluate and to better capture the locus of the conditional minimisers $\{(\mathbf{k}^*(\mathbf{u}), \mathbf{u}) \mid \mathbf{u} \in \Uspace \}$.
 A bigger regular grid is evaluated by the metamodel once the design space has been sufficiently explored.
@@
 As a basis for comparison, the global minimiser of $J$ over $\Kspace \times \Uspace$ has been computed, and $\kest_{\mathrm{global}}$ is then obtained by discarding the $\mathbf{u}$ value.
-An interesting comparison arises when comparing with $\kest_{\mathrm{global}}$, where $\kest_1$ outperforms the global minimiser for $\mathbf{u} < 0.625$.
 

### 2019-11-22 article.tex
modif name .tex, update .gitignore, del pdf

--- 2019-11-20 article-modif-A&E.tex
@@
 where $k^{(j)}$ is the $j$-th component of $\mathbf{k}$.
-There is wide choice of available $f_{\mathrm{1D}}$, such as a rectangle function, $f_{\mathrm{1D}}(x) = 1 \text{ if } |x|< \frac{1}{2}$ and  $0$ elsewhere, or a Gaussian kernel $f_{\mathrm{1D}}(x)= \frac{1}{\sqrt{2\pi}}\exp(-x^2 / 2)$.
-One can notice that the rectangle function as a kernel yields non-smooth densities, very similar to the histogram of the minimisers.
+There is wide choice of available $f_{\mathrm{1D}}$, and a popular choice is  %such as a rectangle function, $f_{\mathrm{1D}}(x) = 1 \text{ if } |x|< \frac{1}{2}$ and  $0$ elsewhere,
+the Gaussian kernel $f_{\mathrm{1D}}(x)= \frac{1}{\sqrt{2\pi}}\exp(-x^2 / 2)$.
+% One can notice that the rectangle function as a kernel yields non-smooth densities, very similar to the histogram of the minimisers.
 
@@
 The computation of the ratio advocates for a level of confidence $p_{\mathrm{maxratio}}$ close to $0.75$.
-The numerical values of the estimations $\hat{k}$ presented in Table~\ref{tab:recap_estimates_BHs} show that contrary to the $J_{\mathrm{BH}}$ function, the objective are concurrent.
+The numerical values of the estimations $\hat{k}$ presented in Table~\ref{tab:recap_estimates_BHs} show that, contrary to the $J_{\mathrm{BH}}$ function, the objective are concurrent.
 
@@
 We can see that the performances of $\kest_1$ and $\hatkmean$ are very similar, but $\kest_1$ has better performances when $\mathbf{u} > 0.6$.
+When comparing with the global optimiser $\kest_{\mathrm{global}}$, $\kest_1$ performs better when $\mathbf{u}<0.625$.
+As $\mathbf{U}$ is uniformly distributed on $\Uspace=[0.5,0.7]$, we can graphically estimate that the probability that $\kest_1$ outperforms $\kest_{\mathrm{global}}$ is greater than $0.5$, that is that $\Prob_\mathbf{U}\left[J(\kest_1,\mathbf{U})<J(\kest_{\mathrm{global}},\mathbf{U})\right] > 0.5$.
+
+The calibration of this numerical model is done in order to get a calibrated value $\kest$, that will be used for forecasts, using the same numerical model.
+We are now going to compare how well three of those values compare in a forecast context: $\kest_1$, $\hatkmean$ and $\kest_{\mathrm{global}}$, as the first two refer quite naturally to the notion of robustness, and the latter is an example of an estimate that does not take into account the uncertainties.
 \clearpage
@@
 \end{equation}
-By averaging over $\mathbf{u}$ and $\mathbf{u}'$ using a Monte-Carlo approximation, we can define the mean squared forecast error, defined on every point of the spatial domain, and at every time-steps.
+Averaging over $\mathbf{u}$, $\mathbf{u}'$ defines the mean squared forecast error, defined on every point of the spatial domain, and at every time-steps.
+This can be done using a Monte-Carlo approximation: as $\mathbf{u}$ and $\mathbf{u}'$ are iid, let us assume that we have a set of samples $\{\mathbf{u}^i\}_{1\leq i \leq N_{\mathbf{u}}}$.
 \begin{equation}
   \label{eq:squared_forecast_error_averaged}
-  S(\mathbf{k}) = \frac{1}{N_{\mathbf{u}} N_{\mathbf{u}'}}\sum_{\mathbf{u},\mathbf{u}'\sim \mathbf{U}} S_{\mathrm{pred}}(\mathbf{k},\mathbf{u},\mathbf{u}') = \frac{1}{N_{\mathbf{u}} N_{\mathbf{u}'}}\sum_{\mathbf{u},\mathbf{u}'\sim \mathbf{U}} \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}')\right)^2
+  S(\mathbf{k}) = \frac{1}{N_{\mathbf{u}}^2 }\sum_{i=1}^{N_{\mathbf{u}}}\sum_{j=1}^{N_{\mathbf{u}}} S_{\mathrm{pred}}(\mathbf{k},\mathbf{u}^i,\mathbf{u}^j) = \frac{1}{N_{\mathbf{u}}^2 }\sum_{i=1}^{N_{\mathbf{u}}}\sum_{j=1}^{N_{\mathbf{u}}}  \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}^i) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}^j)\right)^2
 \end{equation}
-The mean squared forecast error is then averaged over all time-steps between $T$ and $T_{\mathrm{pred}}$, indicating on which point of the domain the forecast error is greater as seen on the left plot of Figure~\ref{fig:forecast_squared_error}.
+The mean squared forecast error averaged over the whole space and over all the time-steps gives an indication on the overall prediction quality of the prediction given this metric, and are represented on the right plot of Figure~\ref{fig:forecast_squared_error}.
+We can see that $\kest_{\mathrm{global}}$ performs slightly better than $\kest_1$, itself performing slightly better than $\hatkmean$.
+Averaging $S(\mathbf{\kest}$ over only the time steps between $T$ and $T_{\mathrm{pred}}$, we have an indication on the quality of the forecast in the squared sense depending on the spatial position, as seen on the left plot of Figure~\ref{fig:forecast_squared_error}.
 \begin{figure*}[!h]
@@
 \clearpage
-\section*{Conclusion}  %% \conclusions[modified heading if necessary]
+\section*{Conclusion}  
+\victor{À faire à la fin}
 This paper deals with the problem of robust calibration of a computer code in the presence of uncertain inputs.

### 2019-11-22 article.tex
change notation k_mean, k_var to k_E , k_V
change notation k_mean, k_var to k_E , k_V, new figs
typos

@@
 \newcommand{\tra}{\mathrm{tr}}
-\newcommand{\kmean}{{\mathbf{k}}_{\mathrm{mean}}}
-\newcommand{\hatkmean}{\hat{\mathbf{k}}_{\mathrm{mean}}}
-\newcommand{\kvar}{{\mathbf{k}}_{\mathrm{var}}}
-\newcommand{\hatkvar}{\hat{\mathbf{k}}_{\mathrm{var}}}
+\newcommand{\kmean}{{\mathbf{k}}_{\Ex}}
+\newcommand{\hatkmean}{\hat{\mathbf{k}}_{\Ex}}
+\newcommand{\kvar}{{\mathbf{k}}_{\mathbb{V}}}
+\newcommand{\hatkvar}{\hat{\mathbf{k}}_{\mathbb{V}}}
 \newcommand{\kmpe}{{\mathbf{k}}_{\mathrm{MPE}}}
@@
 \newcommand{\checkkp}{{\mathbf{k}}_p}
+\newcommand{\hatkp}{\hat{\mathbf{k}}_p}
 \newcommand{\Kspace}{\mathbb{K}}
@@
 %  \label{eq:cheby_ineq}
-%  \Prob_{\mathbf{U}}\left[|J(\mathbf{k}% _{\mathrm{mean}}
-%    ,\mathbf{U}) - \mu(\mathbf{k}% _{\mathrm{mean}}
-%    )|> \lambda\right] \leq \frac{\sigma^2(\mathbf{k}% _{\mathrm{mean}}
+%  \Prob_{\mathbf{U}}\left[|J(\mathbf{k}% _{\Ex}
+%    ,\mathbf{U}) - \mu(\mathbf{k}% _{\Ex}
+%    )|> \lambda\right] \leq \frac{\sigma^2(\mathbf{k}% _{\Ex}
 %    )}{\lambda^2}
@@
 \label{ssec:num_illu}
-Before going further in the explanation of our approach, let us illustrate the nature of the 3 previously detailled estimator, $\hatkmean, \hatkvar$ and $\hatkmpe$ on two analytical cost functions.
+Before going further in the explanation of our approach, let us illustrate the nature of previously detailed estimators, $\hatkmean, \hatkvar$ and $\hatkmpe$ on two analytical cost functions.
 These functions are based on the Branin-Hoo's function, slightly modified to ensure strict positivity:
@@
   \includegraphics[width=12cm]{Figures/branin_side_moments_noscale.pdf}
-  \caption{Left: Contour of the $J_{\mathrm{BH}}$ function, conditional mean and variance.
-The estimates $\hatkmean$ and $\hatkvar$ are plotted with the dashed line.
-Right: $J_{\mathrm{BHswap}}$ function.
-The scale of the bottom plots have not been represented.} %TODO revoir
-\label{fig:branin_moments}
+  \caption{The left column concerns the $J_{\mathrm{BH}}$ function, while the right one deals with $J_{\mathrm{BHswap}}$.
+Contours of both functions are plotted on the top, and curves of  $\mu(\mathbf{k})$ and $\sigma(\mathbf{k})$ are shown on the bottom (respective scales are note represented).
+Estimates $\hatkmean$ and $\hatkvar$ are plotted with the dashed line.
+} \label{fig:branin_moments}
 \end{figure*}
@@
 The corresponding minimizers $\hatkmean$ and $\hatkvar$ are also plotted.
-On this figure, we can observe that $\hatkmean$ and $\hatkvar$ are close for the $J_{\mathrm{BH}}$ function, while have significant different value for the $J_{\mathrm{BHswap}}$ function.
+On this figure, we can observe that $\hatkmean$ and $\hatkvar$ are close for the $J_{\mathrm{BH}}$ function, while being significantly different for the $J_{\mathrm{BHswap}}$ function.
 %\clearpage
 
-Illustrations related to $\hatkmpe$ are depicted on Figure~\ref{fig:contours}.
-As before, the set of $\mathbf{u}^i$ is taken from a regular grid.
+Similarly $\hatkmpe$ estimations are depicted on Figure~\ref{fig:contours}.
 Top row shows the contour plot of both functions as well as the set of conditional minimisers $\{\mathbf{k}_{\mathbf{u}^i}\}_{1\leq i \leq N}$ in red, as defined in Eq.~\eqref{eq:conditional_minimiser}.
-The left, respectively right, column stands for $J_{\mathrm{BH}}$, respectively $J_{\mathrm{BHswap}}$ function.
 The bottom rows presents three approximations of the density of minimisers: the histogram in grey (bin size selected using Freedman-Diaconis from~\cite{freedman_histogram_1981}), the result of a kernel density estimation (KDE) with Gaussian kernels in red (using Scott's rule from~\cite{scott_optimal_1979} for bandwidth selection), and the estimation by a Gaussian mixture.
@@
 The dashed lines indicate the MPE found using those methods.
-Right: Same quantities with $J_{\mathrm{BHswap}}$.
-The estimation of the MPE is consistent between the methods for $J_{\mathrm{BHswap}}$, but not for  $J_{\mathrm{BH}}$}
+Right: Same quantities with $J_{\mathrm{BHswap}}$.}
 \label{fig:contours}
@@
 close to $1.5$, but we do not have information on its performance in
-this region around this value.
+this region around this value. \arthur{je ne comprends pas ce passage}
 
@@
 \label{sec:relax_constraint}
-\subsection{Taking the neighborhood into consideration}
+\subsection{Relaxing the optimality constraint}
 The density of minimisers has been estimated by optimising $\mathbf{k}\mapsto J(\mathbf{k},\mathbf{u})$ over $\Kspace$ for different realisations of $\mathbf{u}$.
@@
 $\kest_{\mathrm{maxratio}},~ \hat{p}_{\mathrm{maxratio}}=0.766$ & 1.537 \\ 
-$\kest_{\mathrm{mean}}$ & 1.752 \\ 
+$\hatkmean$ & 1.752 \\ 
 $\kest_p,~p=0.90$ & 2.112 \\ 
 $\kest_p,~p=0.95$ & 2.457 \\ 
-$\kest_{\mathrm{var}}$ & 2.638 \\ 
+$\hatkvar$ & 2.638 \\ 
 $\kest_1,~p=1$ & 2.798   \\ \bottomrule
@@
 $\kest_{\mathrm{global}}$ & 0.290 \\
-$\hat{\mathbf{k}}_{p},~p=1$ & 0.423 \\ 
-$\hat{\mathbf{k}}_p,~p=0.90$ & 0.458 \\ 
+$\hatkp,~p=1$ & 0.423 \\ 
+$\hatkp,~p=0.90$ & 0.458 \\ 
 $\hatkmean$ & 0.501 \\ 
-$\hat{\mathbf{k}}_p,~p=0.80$ & 0.505 \\ 
-$\hat{\mathbf{k}}_p,~p=0.70$ & 0.560 \\ 
+$\hatkp,~p=0.80$ & 0.505 \\ 
+$\hatkp,~p=0.70$ & 0.560 \\ 
 $\hatkvar$ & 0.990\\ \bottomrule

### 2019-11-25 article.tex

@@
 
-\journal{Journal of Computational Physics}
-
 \begin{document}
 
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-
-\title{Robust calibration of numerical models based on relative regret}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
-
-\author[vt]{Victor Trappler}
-\ead{victor.trappler@univ-grenoble-alpes.fr}
-\author[ea]{Élise Arnaud}
-\author[av]{Arthur Vidard}
-\author[ld]{Laurent Debreu}
-
-\address[vt]{Univ. Grenoble Alpes, CNRS, Inria, Grenoble INP*, LJK, 38000 Grenoble, France}
+\title{Title-- \today{}}%TEXT}
+
+% \Author[affil]{given_name}{surname}
+
+\Author[]{Victor}{Trappler}
+\Author[]{Élise}{Arnaud}
+\Author[]{Laurent}{Debreu}
+\Author[]{Arthur}{Vidard}
+
+\affil[]{Univ. Grenoble Alpes, CNRS, Inria, Grenoble INP*, LJK, 38000 Grenoble, France}
+% \affil[]{ADDRESS}
+
+%% The [] brackets identify the author with the corresponding affiliation. 1, 2, 3, etc. should be inserted.
+
+\runningtitle{Title}
+
+\runningauthor{Trappler V.}
+
+\correspondence{Victor Trappler (victor.trappler@univ-grenoble-alpes.fr)}
+
+\received{}
+\pubdiscuss{} %% only important for two-stage journals
+\revised{}
+\accepted{}
+\published{}
+
+%% These dates will be inserted by Copernicus Publications during the typesetting process.
+
+\firstpage{1}
+
+\maketitle
+
+% \listoftodos\
 
 \begin{abstract}
-%% Text of abstract
 Classical methods of parameter estimation usually imply the minimisation of an objective function, that measures the error between some observations and the results obtained by a numerical model.
@@
 In this paper, we are going to present how to take into account those uncertainties by defining a notion of robustness based on the distribution of the conditional minimisers and compare it with the minimum in the mean sense, and the minimum of variance.
+\victor{Pour le nom: Il y a l'idée que l'on veut avoir un regret $J(\mathbf{k},\mathbf{u}) - \alpha J^*(\mathbf{u})$ controlé à l'aide de $\alpha$: Relative regret ?}
 \end{abstract}
 
-% %%Graphical abstract
-% \begin{graphicalabstract}
-% %\includegraphics{grabs}
-% \end{graphicalabstract}
-
-%%Research highlights
-% \begin{highlights}
-% \item Research highlight 1
-% \item Research highlight 2
-% \end{highlights}
-
-\begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
-
-%% PACS codes here, in the form: \PACS code \sep code
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
-\end{keyword}
-
-\end{frontmatter}
-
-%% \linenumbers
-
-%% main text
-\section*{Introduction}
-\label{}
+\copyrightstatement{TEXT}
 
@@
 The parameter to calibrate, $\mathbf{k}$, is the quadratic friction term, proportional to the square of the inverse of Manning-Strickler coefficient.
-The environmental parameter $\mathbf{u}$ is the amplitude of a sine wave of period $1/\omega_0$.
+The environmental parameter $\mathbf{u}$ is the amplitude of a sine wave of period $1$.
 The domain of those two parameters are $\mathcal{K} = [0.0, 1.3]$ and $\mathcal{U} = [0.5, 0.7]$.
@@
       \partial_t q + \partial_x \left(\frac{q^2}{h} + \frac{g}{2}h^2\right) &= - gh\partial_x z - \mathbf{k}q |q|h^{-7/3} \\
-      h(0, t) &= 20.0 + 3\cdot \sin \left(\frac{2\pi t}{2}\right) + 1.5\cdot \mathbf{u} \cdot \sin\left(\frac{2 \pi t}{\omega_0}\right)\\
+      h(0, t) &= 20.0 + 3\cdot \sin \left(\frac{2\pi t}{2}\right) + 1.5\cdot \mathbf{u} \cdot \sin\left(2 \pi t\right)\\
       \partial_x q(0, t) &= 0
@@
 These equations are integrated using a finite-volume scheme on a discretized domain $[0, L]$, up to a time $T$.
-The output of the computer code is the sea surface height $h$, on the center of all the volumes and at all the time-steps, that will be denoted $\mathcal{M}(\mathbf{k},\mathbf{u};\, \omega_0=1.0)$.
+The output of the computer code is the sea surface height $h$, on the center of all the volumes and at all the time-steps, that will be denoted $\mathcal{M}(\mathbf{k},\mathbf{u})$.
 In this setting, the variable input is uniformly distributed on $\mathcal{U}$.
-To generate the observations, we choose $\mathbf{u}^{\mathrm{true}}=2/3$, and define $\mathcal{M}^o$ based on the computer model $\mathcal{M}$, such that $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) = \mathcal{M}(\mathbf{k}^{\mathrm{true}}, \mathbf{u}^{\mathrm{true}}; \, \omega_0 = 0.999)$.
-$\omega_0$
-represents here the uncontrollable error between the observations and the numerical model and will now be omitted systematically in the notation.
-The true value of the bottom friction $\mathbf{k}^{\mathrm{true}} = (k_1^{\mathrm{true}}, k_2^{\mathrm{true}},\dots, k_{N_\mathrm{vol}}^{\mathrm{true}})$ is not constant over the whole domain, and is defined as
+To generate the observations, we choose $\mathbf{u}^{\mathrm{true}}=2/3$, and define $\mathcal{M}^o$ based on the computer model $\mathcal{M}$, such that $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) = \mathcal{M}(\mathbf{k}^{\mathrm{true}}, \mathbf{u}^{\mathrm{true}})$.
+This true value $\mathbf{k}^{\mathrm{true}} = (k_1^{\mathrm{true}}, k_2^{\mathrm{true}},\dots, k_{N_\mathrm{vol}}^{\mathrm{true}})$ is not constant over the whole domain, and is defined as
 \begin{equation*}
@@
 where $x_i$ is the center of the $i$-th volume.
-The two sources of representativity errors are $\omega_0$, and the fact that we are looking to estimate $\mathbf{k}$ in a 1-dimensional space $\Kspace$.
 \subsection{Estimation}
@@
 Bottom: $\hat{\Gamma}_{\alpha_p}$ for different levels $p$}
-\label{fig:estimation_swe}
+\label{fig:my_label}
 \end{figure}
@@
 \end{tabular}
+\caption{Estimation of $\mathbf{k}$ according to different criterion}
 \label{tab:recap_estimates_metaSWE}
@@
 \subsection{Assessing the quality of the forecast of the calibrated model}
-The calibration of the model has been performed using by integrating the model on a time-period $[0, T]$, called assimilation window. 
-We now want to compare the quality of the different forecasts, from different calibrated bottom friction.
-Those forecasts result from the integration of the numerical model between the time $T$ and a time $T_{\mathrm{pred}}$.
-
-Given the probabilistic nature of the environmental conditions $\mathbf{U}$, the forecasts will also be probabilistic.
+The calibration of the model has been performed on the time-period $[0, T]$, called assimilation window. 
+We now want to compare the quality of the different forecasts depending on the criterion used to calibrate the bottom friction.
+To define those forecasts, the models will be integrated from $T$ to $T_{\mathrm{pred}}$.
+
+Given the probabilistic nature $\mathbf{U}$, the forecasts will also be probabilistic.
 We will then compare $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{U})$, for a calibrated $\mathbf{k}$.
@@
 \subsubsection{Squared forecast error}
-Given two environmental conditions $\mathbf{u}$, used to run the computer simulation and $\mathbf{u}'$, used to generate the observations, the squared forecast error for the parameter $\mathbf{k}$ is
+Let us assume that the observations result from the parameter $\mathbf{u}'$, while the computer simulation is run using $\mathbf{u}$.
+The squared forecast error given $\mathbf{u}$ and $\mathbf{u}'$ is
 \begin{equation}
@@
 \centering
-\includegraphics[width=.9\textwidth]{Figures/forecast_error.pdf}
+\includegraphics[width=.9\textwidth]{Figures/L2_full.pdf}
 \caption{Quality of forecast, depending on the calibrated parameter.
@@
   \centering
-  \includegraphics[width=.9\textwidth]{Figures/forecast_CRPS}
+  \includegraphics[width=.9\textwidth]{Figures/CRPS_full}
   \caption{CRPS computed for different calibrated parameters}
@@
 \begin{equation}
-\label{eq:def_crps}
-\mathrm{CRPS}(\mathbf{k}) = \int_{\mathbb{R}} (F_{\mathrm{pred}}(x,\mathbf{k}) - F^o_{\mathrm{pred}}(x))^2 \,\mathrm{d}x
-\end{equation}
+\label{eq:checkloss}
+\rho_{\tau}(x) = \begin{cases}
+    \tau |x| \quad \text{ if } x \geq 0 \\
+    (1- \tau) |x| \quad \text{ if } x < 0
+\end{cases}
+\end{equation}
+
+Given the time index $j$, and the volume indexed by $i$, the quantile of order $\tau\in [0, 1]$ of $\mathcal{M}(\kest, \mathbf{U})_{(i,j)}$ is $q_{(i,j)}(\tau)$.
+Given an obse
+\begin{figure*}[t]
+\includegraphics[width=12cm]{Figures/forecast_metric.pdf}
+\caption{Quality of forecast, depending on the calibrated parameter. The left figures show the metric averaged over time, while the right figures show}
+\label{fig:forecast_metric}
+\end{figure*}
+
+% \subsection{The Lorenz-63 model}
+% A classical toy problem in data assimilation is the Lorenz-63 model, introduced in \cite{lorenz_deterministic_1963}. 
+% % xb
+% The evolution of the state vector $(x,y,z)$ is described by the non-linear differential system of Eq.~\eqref{eq:lorenz_equations}
+% \begin{align}
+%   \label{eq:lorenz_equations}
+%   \left\{
+%     \begin{array}{l}
+%       \dot{x} = \sigma\left(y-x \right) \\
+%       \dot{y} = \rho x - y - xz \\
+%       \dot{z} = xy - \beta z
+%       \end{array}
+%   \right.
+% \end{align}
+% Despite its apparent simplicity, this system is known to show chaotic behaviour for $(\sigma,\rho,\beta) = (10, 28, 8/3)$. 
+% This differential system is solved numerically using a Runge-Kutta scheme, over $N=100$ time-steps of length $\Delta t = 0.05$. In that time-period, the chaotic behaviour is not yet too apparent.
+
+% The inputs of the computer code are the initial conditions $\left(x_0,y_0,z_0\right)$ and $(\sigma, \beta, \rho)$.
+The parameter to calibrate is $\mathbf{k}=x_0-1$ with $\mathbf{k}\in[-0.05,0.05]$, and the uncertain parameter is $\mathbf{u}=\beta - 8/3$ with $\mathbf{u} \in \Uspace=[-0.05, 0.05]$.
+Finally, we suppose that the random variable $\mathbf{U}$ follows an uniform distribution on $\Uspace$.
+Solving numerically the differential system using those settings yields $x_{i}(\mathbf{k},\mathbf{u})$ for $i$ between $1$ and $N$.
+
+% This problem of calibration will be studied in a twin experiments framework: the target state $x^{o}_i$ for $1\leq i \leq N$ has been generated by the computer code, where the parameters used to generate it are detailed in Table~\ref{tab:lorenz_modelling}.
+One can notice the discrepancy of $\rho$ between the observations and the model, introduced to ensure that no perfect fit can be achieved, for any set of parameters.
+% \begin{table*}[h]
+%   \caption{Choice of modelling of the Lorenz-63 system}
+%   \label{tab:lorenz_modelling}
+% \begin{tabular}{crrl}
+%   \tophline
+%   Parameter & Observation: $x_{1:N}^o$ & Modelling: $\mathcal{G}(\mathbf{k},\mathbf{u})$ & Type \\
+%   \middlehline
+%  $\sigma$ & $10$ & $10$ & Fixed\\
+%   $\rho$ & $29$ & $28$ & A priori chosen and fixed \\
+%   $\beta$ & ${8}/{3}$ & ${8}/{3} + \mathbf{u}$ & A priori chosen and uncertain \\
+%  $x_0$ & $1$ & $1 + \mathbf{k}$ & Calibrated \\
+%   $y_0$ & $0$ & $0$ & Fixed \\
+%  $z_0$ & $0$ & $0$ & Fixed \\
+%   \bottomhline
+% \end{tabular}
+% \end{table*}
+
+% The misfit between the observations and the output of the numerical model is quantified using the cost function:
+% \begin{equation}
+% \label{eq:cost_fun_lorenz}
+% J(\mathbf{k},\mathbf{u}) = \frac{1}{2}\|\mathcal{G}(\mathbf{k},\mathbf{u}) \|^2 = \frac{1}{2} \|x_{1:N}(\mathbf{k},\mathbf{u}) - x^o_{1:N} \|^2 = \frac{1}{2}\sum_{i=1}^N (x_i(\mathbf{k},\mathbf{u}) - x_i^o)^2
+% \end{equation}
+
+% This toy model is cheap to evaluate, so the global minimum can be computed using numerical methods, at different starting points to avoid local minimums.
+% \begin{equation}
+% \label{eq:min_global_lorenz}
+% \min_{(\mathbf{k},\mathbf{u}) \in \Kspace\times\Uspace} J(\mathbf{k},\mathbf{u}) = 38.886712815 \quad \argmin_{(\mathbf{k},\mathbf{u}) \in \Kspace\times\Uspace} J(\mathbf{k},\mathbf{u}) = (0.02414384, -0.00551042)
+% \end{equation}
+
+% \subsubsection{MPE and conditional moments}
+% Figure~\ref{fig:lorenz_kde_moments} shows the cost function $J$, computed on a regular grid over $\Kspace\times\Uspace$.
+Using this grid, the conditional mean and standard deviation have been computed, while the MPE has been estimated by KDE.
+For a single $\mathbf{u}$, it may appear that there are multiple $\mathbf{k}^*(\mathbf{u})$.
+This is due to the fact that the conditional minimiser jumps back and forth between the two curves.
+
+% \begin{figure}[!h]
+% \includegraphics[width=12cm]{Figures/lorenz_kde_moments.pdf}
+% \caption{Cost function, locus of conditional minimisers, MPE estimated with KDE, conditional moments and their associated estimates}
+% \label{fig:lorenz_kde_moments}
+% \end{figure}
+
+% \subsubsection{Relaxation of the constraint}
+% Based on the computations described before, the coefficient $\checkap$ have been computed for $p=0.9$, $0.95$ and $p=1$, and reported in Table~\ref{tab:recap_estimates_lorenz}.
+The curve $R_{\checka_1}$ is plotted in Figure~\ref{fig:lorenz_relax}, where the acceptable region for $\checka_1$ is filled in yellow.
+
+% \begin{figure}[!h]
+% \includegraphics[width=12cm]{Figures/lorenz_f3.pdf}
+% \caption{Relaxation of the constraint for the Lorenz model. Acceptable region in yellow}
+% \label{fig:lorenz_relax}
+% \end{figure}
+
+% We can see that for $\mathbf{k}$ being approximately between $0$ and $0.01$, the probability $R_{\checka_1}$ is very close to $1$.
+Indeed, the cost function seems to be relatively flat on this region, as $\checkk_{0.9} \approx \kmpe$.
+
+% \begin{table*}[!h]
+%   \caption{Estimates computed numerically on the Lorenz-63 model}
+%   \label{tab:recap_estimates_lorenz}
+%   \begin{tabular}{*{3}{r}}\tophline
+%     Estimate & Value & Related quantities\\
+%     \middlehline
+%     $\hatkmean$        & $ 0.008779$ &$\left(\mu(\kmean),\sigma(\kmean)\right) = (42.965, 4.921)$\\
+%     $\hatkvar$         & $-0.025338$ &$\left(\mu(\kvar),\sigma(\kvar)\right)= (50.704, 2.024)$\\
+%     $\hatkmpe$         & $ 0.008779$ & $\Gamma_1(\kmpe) = 0.053$ \\
+%     $\hat{\checkk}_{0.9}$ & $ 0.008729$ & $\hat{\checka}_{0.9}  = 1.202788$ \\
+%     $\hat{\checkk}_{0.95}$& $ 0.006078$ & $\hat{\checka}_{0.95} = 1.226050$ \\
+%     $\hat{\checkk}_{1}$   & $ 0.000275$ & $\hat{\checka}_{1}    = 1.311002$ \\
+%     \bottomhline
+%     \end{tabular}
+% \end{table*}
+
+% \subsubsection{Selection of the couple $(p,\checkap)$}
+% The evolution of $\checkap$ with respect to $p$ is shown on the left plot of Figure~\ref{fig:evolution_p_lorenz}.
+We can see that $\checkap$ presents two abrupt positive change of slope, for $p$ set to $0.85$ and just before $1$.
+Those confidence levels corresponds to the local maxima of the ratio $p/\checkap$, that is shown on the right plot of Figure~\ref{fig:evolution_p_lorenz}.
+The profile of $\checkk_{0.85}$ corresponding to the local maximum of the ratio, has not been plotted as it corresponds to the same profile of $\kmean$.
+
+% \begin{figure*}[!h]
+% \includegraphics[width=12cm]{Figures/evol_p_lorenz.pdf}
+% \caption{Evolution of $p$ and $\checkap$}
+% \label{fig:evolution_p_lorenz}
+% \end{figure*}
+% In order to compare the values taken by the objective function, the profiles have been represented on Figure~\ref{fig:lorenz_profiles}.
+% \begin{figure}[!h]
+% % \includegraphics[width=12cm]{Figures/lorenz_cdf_profile.pdf}
+% \includegraphics[width=12cm]{Figures/profile_lorenz_all_estimates.pdf}
+% \caption{Profiles of different $\mathbf{k}$ for the Lorenz model}
+% \label{fig:lorenz_profiles}
+% \end{figure}
+% The profile of $\kmean$ presents a good insight on the performances of this estimate: for most values of the uncertain variables, the objective is low.
+In contrast, for $\mathbf{u}$ close to $0.05$, a maximum is reached.
+%\begin{figure}[!h]
+%\includegraphics[width=8.3cm]{Figures/cdf_lorenz_with_ratio.pdf}
+%\caption{CDF corresponding to different $\mathbf{k}$ for the Lorenz model}
+%\label{fig:lorenz_cdf}
+%\end{figure}
+
+% \clearpage
+% \subsection{Context: Shallow water equations and bottom friction}
+
+% The quality of water circulation modelling in coastal areas is largely dependent on the boundary conditions, (e.g.\ the tide), the bathymetry and the friction induced by the rugosity of the ocean bed \citep{boutet_estimation_2015}.
+The latter will then be estimated in a robust manner, by applying the criteria introduced above.
+
+% The model studied is based on the one-dimensional shallow water equations, described Eq.~\eqref{eq:SWE_equations}, solved numerically on a domain $D$.
+$h$ is the height of the water column, $q$ is the discharge, and $z$ is the bathymetry, while $g$ is the usual gravitation constant.
+$\mathbf{k}$ is a quadratic friction term, proportional to the square of the inverse of Manning-Strickler coefficient.
+% \begin{align}
+%   \label{eq:SWE_equations}
+%   \left\{
+%     \begin{array}{l}
+%       \partial_t h + \partial_x q = 0 \\
+%       \partial_t q + \partial_x \left(\frac{q^2}{h} + \frac{g}{2}h^2\right) = - gh\partial_x z - \mathbf{k}q |q|h^{-7/3} \\
+%       h(0, t) = 20.0 + \mathrm{Amplitude} \cdot \sin \left(\frac{2\pi}{\mathbf{u}}t\right) \\
+%       q(0, t) = 0
+%       \end{array}
+%   \right.
+% \end{align}
+
+% The estimation of the bottom friction and/or topography has been treated in a deterministic setting, % in Section~\ref{sec:deterministic}
+% using tools from variational data assimilation~\cite[e.g.][]{das_estimation_1991,das_variational_1992,honnorat_identification_2010}.
+% If the boundary conditions are not well-known, the estimation will then compensate this misspecification.
+The resulting estimate will then be optimal for this particular configuration, but will not acknowledge the uncertainty upon the boundary conditions.
+Instead, we are looking for an estimate that is robust considering the variability of the uncertain boundary conditions.
+
+% The problem of the estimation of the bottom friction will be studied using twin experiments.
+For this purpose, a few references simulations have been performed in order to produce different observations $\mathbf{y}^o$.
+Those scenarios are detailed Table~\ref{tab:optim_scenar}.
+The true bottom friction $\mathbf{k}^t$ is the same for all simulations, and is a non-constant function of the spatial domain $D = [0, L]$ defined as:
+% \begin{equation}
+%   \label{eq:defnition_kt}
+%   \mathbf{k}^t= \mathbf{k}^t(x) = 0.2\cdot (1 + \sin(2\pi x/L))
+% \end{equation}
+% However, the space $\Kspace$ in which we wish to estimate the bottom friction is one-dimensional. This leads to the strict positivity of the cost function, as no perfect fit can be achieved.
+
+% As presented on Table~\ref{tab:RO_modelling}, we consider two a priori chosen variable: $\mathbf{u} \in \Uspace$ that is the period of the sine wave on the left boundary.
+The aleatoric uncertainty on this variable is modelled by a random variable distributed uniformly on $\Uspace$.
+% The amplitude of the sine wave is also chosen a priori and set to an arbitrary value, that may be different from the true amplitude used to generate $\mathbf{y}^o$.
+
+% \begin{table*}[t]
+%   \caption{Modelling of the estimation problem}
+%   \label{tab:RO_modelling}
+% \begin{tabular}{rrr}
+%   \tophline
+%   Parameter & Modelling & Type of parameter \\
+%   \middlehline
+%   Bottom friction: $\mathbf{k}$  &$\Kspace=[0, 1]$ & Calibrated parameter \\
+%   Period: $\mathbf{U}$ & $\mathrm{Unif}\left([14.7, 15.3]\right)$ & A priori chosen and uncertain\\
+%   Amplitude &  5.0 & A priori chosen and fixed\\
+%   \bottomhline
+% \end{tabular}
+% \end{table*}
+
+% % ----------------------------------------------------------------------------
+% \section{Deterministic optimisation}
+% \label{ssec:deterministic_optimisation}
+% The problem has first been studied in a deterministic setting. The following optimisation problem has been performed numerically:
+% \begin{equation}
+%   \label{eq:opt_deter}
+%   \text{Minimise } \mathbf{k}\in\Kspace \mapsto J(\mathbf{k},\mathbf{u}^b)\quad \text{for }\mathbf{u}^b= \Ex_{\mathbf{U}}[\mathbf{U}] = 15.0
+% \end{equation}
+% At the same time, the background value of the amplitude is fixed and set to $5.0$.
+% Different scenario have been established (i.e.\ different $\mathbf{u}^t$ and amplitude producing different $\mathbf{y}^o$), and are detailed in Table~\ref{tab:optim_scenar}.
+The configurations correspond to different values of the amplitude (letter~``A'') and the period (letter~``P'').
+If the truth value is greater (resp.\ smaller) than the background value, the lowercase letter ``p'' follows (resp.\ ``m'').
+
+% On the same table, are shown the result $\kest$ of the optimisation defined in Eq.~\eqref{eq:opt_deter} for each one of the different operating conditions.
+
+% \begin{table*}[t]
+%   \caption{Settings for reference simulations, and optimisation results}
+%   \label{tab:optim_scenar}
+% \begin{tabular}{rrrrrrrr} \tophline
+% Scenario for $\mathbf{u}^t$: &$\Ex_{\mathbf{U}}[\mathbf{U}]$  & Pm & ApPm & AmPm & Pp & ApPp & AmPp \\ \middlehline
+%   $\mathbf{u}^t- \mathbf{u}^b$ & 0.0            & -0.1  & -0.2 & -0.1 & +0.2 & +0.1 & +0.2 \\
+%   $\mathrm{Amplitude}- 5.0$   & 0.0             &  0.0  & +0.1 & -0.2 &  0.0 & +0.2 & -0.1 \\ \middlehline
+%   $\kest$      & 0.1043          & 0.2028 & 0.2709 & 0.2427 & 0.0  & 0.0 & 0.0015 \\\bottomhline
+% \end{tabular}
+% \end{table*}
+
+% Optimising without uncertainties (meaning that the $\mathbf{u}^b=\mathbf{u}^t$) yields an optimal value $\kest$ close to $0.10$, that we define to be $\kest_{\mathrm{opt}}$
+% We can observe two different regimes, depending on the sign of $\mathbf{u}^t-\Ex_{\mathbf{U}}[\mathbf{U}]$.
+If this quantity is positive, optimisation will produce an estimation close to $0$.
+If it is negative, the estimate is larger than $0.20$.
+
+% % ----------------------------------------------------------------------------
+% \subsection{Robust estimates}
+% In order to compute the robust estimates, the cost function has been evaluated on a regular grid of $150\times150$ points over $\Kspace\times\Uspace$.
+$\kmean$, $\kvar$, $\checkk_{.9}$, $\checkk_{.95}$ and $\checkk_{1}$ (along with their corresponding factors $\checka_p$) have been evaluated for the different configurations, detailed in Table~\ref{tab:optim_scenar}.
+As shown on Table~\ref{tab:res_robust}, $\checkkp$ does not vary significantly when the level of confidence $p$ increases.
+
+% \begin{table*}[t]
+%   \caption{Mean and variance optimisers, and $\checkkp$ for different levels of confidence $p$}
+%   \label{tab:res_robust}
+%   \begin{tabular}{rrrrrrrr} \tophline
+%     Scenario&$\Ex_{\mathbf{U}}[\mathbf{U}]$ & Pm & ApPm & AmPm & Pp & ApPp & AmPp \\  \middlehline
+%   $\kmean$ & 0.1678    & 0.2214  & 0.2617 & 0.2685 & 0.0872 & 0.0738 & 0.1275 \\
+%   $\kvar$  & 1.0      &  1.0  & 1.0 & 1.0 &  1.0 & 1.0 & 1.0 \\ \middlehline
+%   $\checkk_{.90}$ & 0.1074 & 0.1074 & 0.0872 & 0.1678 & 0.1074  & 0.0738 & 0.1275 \\
+%   $\checka_{.90}$    & 1.1754  & 1.1718 & 1.1779 & 1.1293 & 1.1768  & 1.1807 & 1.1406 \\\middlehline
+
+%   $\checkk_{.95}$ & 0.1074 & 0.1074 & 0.0872 & 0.1611 & 0.1074  & 0.0671 & 0.1275 \\
+%   $\checka_{.95}$ & 1.1802 & 1.1806 & 1.1868 & 1.1320 & 1.1861  & 1.2027 & 1.1525 \\\middlehline
+%     $\checkk_{1}$& 0.1074 & 0.1074 & 0.0872 & 0.1611 & 0.1074  & 0.0671 & 0.1275 \\
+%   $\checka_{1}$ & 1.1944    & 1.1922 & 1.1961 & 1.1321 & 1.1976  & 1.2035 & 1.1682 \\\middlehline
+% \end{tabular}
+% \end{table*}
+
+% In that case, the minimiser of the variance $\kvar$ is the right boundary of $\Kspace$, regardless of the value of $\mathbf{u}^t$.
+This is due to the fact that at this point, the cost function produces bad, yet steady performances.
+From a physical point of view, increasing the bottom friction will decrease the momentum.
+The movement of the water surface will be damped, and the operating conditions will have less effects.
+
+% Looking at $\kmean$, we can see that the estimates obtained are larger than $0.22$ when $\mathbf{u}^t< \Ex_{\mathbf{U}}[\mathbf{U}]$ (that is for Pm, ApPm, and AmPm).
+Those results are similar to the one obtained in the deterministic setting of Table~\ref{tab:optim_scenar}.
+However, for $\mathbf{u}^t> \Ex_{\mathbf{U}}[\mathbf{U}]$ (Pp, ApPp, and AmPp), $\kmean$ is much closer to $\kest_{\mathrm{opt}}$, the optimal value without uncertainties.
+
+% Now for $\checkk_1$, while the estimates for scenarios Pp, ApPp and AmPp are similar to $\kmean$, the obtained values for the other scenarios are close to $\kest$.
+% Figures~\ref{fig:SWE_checkalpha} and~\ref{fig:SWE_profiles} show the contour plot and profiles of the cost function in centered conditions ($\Ex_{\mathbf{U}}[\mathbf{U}]$ scenario).
+Figures~\ref{fig:SWE_checkalphaApPp} and \ref{fig:SWE_profilesApPp} (resp.
+Figures~\ref{fig:SWE_checkalphaAmPm} and~\ref{fig:SWE_profilesAmPm}) show the contour plot and profiles of the cost function for the ApPp scenario (resp.
+AmPm scenario).
+
+% The concentration of $\checkkp$ close to $\kest_{\mathrm{opt}}$ is caused by the very small value of the cost function at its minimum over $\Kspace\times \Uspace$.
+Close to this minimum, the region of acceptable $\mathbf{k}$ will be growing slowly as $\alpha$ increases, weighing the estimation toward $\kest_{\mathrm{opt}}$.
+
+% The fact that we retrieved values close to the optimal one should not overlook that a robust estimate is not necessarily $\kest_{\mathrm{opt}}$, and that this result is specific to this problem.
+
+% \clearpage
+% \begin{figure*}[!h]
+% \includegraphics[width=8cm]{Figures/SWE_big3.pdf}
+% \caption{Top: Cost function of the SWE problem ($\Ex_{\mathbf{U}}[\mathbf{U}]$ scenario) and its conditional minimisers.
+The thick yellow lines represent the boundary of the region where $\phi_\alpha<0$.
+The red dashed line is the estimate $\checkk_{1}$.
+Bottom: $R_{\checka}$}
+% \label{fig:SWE_checkalpha}
+% \end{figure*}
+
+% \begin{figure*}[!h]
+%   \centering
+%   \includegraphics[width=8cm]{Figures/profile_swe.pdf}
+%   \caption{Profiles of different estimates of $\mathbf{k}$ for the $\Ex_{\mathbf{U}}[\mathbf{U}]$ scenario}
+%   \label{fig:SWE_profiles}
+% \end{figure*}
+
+% \begin{figure*}[!h]
+% \includegraphics[width=8cm]{Figures/SWE_ApPp3.pdf}
+% \caption{Top: Cost function of the SWE problem (ApPp scenario) and its conditional minimisers.
+The thick yellow lines represent the boundary of the region where $\phi_\alpha<0$.
+The red dashed line is the estimate $\checkk_{1}$.
+Bottom: $R_{\checka}$}
+% \label{fig:SWE_checkalphaApPp}
+% \end{figure*}
+
+% \begin{figure*}[!h]
+%   \centering
+%   \includegraphics[width=7cm]{Figures/SWE_ApPp_profile.pdf}
+%   \caption{Profiles of different estimates of $\mathbf{k}$ for the ApPp scenario}
+%   \label{fig:SWE_profilesApPp}
+% \end{figure*}
+
+% \begin{figure*}[!h]
+% \includegraphics[width=8cm]{Figures/SWE_AmPm3.pdf}
+% \caption{Top: Cost function of the SWE problem (AmPm scenario) and its conditional minimisers.
+The thick yellow lines represent the boundary of the region where $\phi_\alpha<0$.
+The red dashed line is the estimate $\checkk_{1}$.
+Bottom: $R_{\checka}$}
+% \label{fig:SWE_checkalphaAmPm}
+% \end{figure*}
+
+% \begin{figure*}[!h]
+%   \centering
+%   \includegraphics[width=8cm]{Figures/SWE_AmPm_profile.pdf}
+%   \caption{Profiles of different estimates of $\mathbf{k}$ for the AmPm scenario}
+%   \label{fig:SWE_profilesAmPm}
+% \end{figure*}
 
@@
 
+\codeavailability{TEXT} %% use this section when having only software code available
+
+% \dataavailability{TEXT} %% use this section when having only data sets available
+
+\codedataavailability{TEXT} %% use this section when having data sets and software code available
+
 % \sampleavailability{TEXT} %% use this section when having geoscientific samples available
@@
 
-%% If you have bibdatabase file and want bibtex to generate the
-%% bibitems, please use
+% \subsection{}     %% Appendix A1, A2, etc.
+
+% \noappendix       %% use this to mark the end of the appendix section
+
+%% Regarding figures and tables in appendices, the following two options are possible depending on your general handling of figures and tables in the manuscript environment:
+
+%% Option 1: If you sorted all figures and tables into the sections of the text, please also sort the appendix figures and appendix tables into the respective appendix sections.
+%% They will be correctly named automatically.
+
+%% Option 2: If you put all figures after the reference list, please insert appendix tables and figures after the normal tables and figures.
+%% To rename them correctly to A1, A2, etc., please add the following commands in front of them:
+
+\appendixfigures  %% needs to be added in front of appendix figures
+
+\appendixtables   %% needs to be added in front of appendix tables
+
+%% Please add \clearpage between each table and/or figure. Further guidelines on figures and tables can be found below.
+
+\authorcontribution{TEXT} %% it is strongly recommended to make use of this section
+
+\competinginterests{TEXT} %% this section is mandatory even if you declare that no competing interests are present
+
+\disclaimer{TEXT} %% optional section
+
+\begin{acknowledgements}
+TEXT
+\end{acknowledgements}
+
+%% REFERENCES
+
+%% The reference list is compiled as follows:
+
+% \begin{thebibliography}{}
+
+% \bibitem[AUTHOR(YEAR)]{LABEL1}
+% REFERENCE 1
+
+% \bibitem[AUTHOR(YEAR)]{LABEL2}
+% REFERENCE 2
+
+% \end{thebibliography}
+
+%% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
+%% authors experienced with BibTeX only have to include the following two lines:
 %%
-%%  \bibliographystyle{elsarticle-num-names} 
-%%  \bibliography{<your bibdatabase>}
-
-%% else use the following coding to input the bibitems directly in the
-%% TeX file.
-\bibliographystyle{elsarticle-num-names} 
+
+\bibliographystyle{copernicus}
 \bibliography{bibzotero}
 
+%%
+%% URLs and DOIs can be entered in your BibTeX file as:
+%%
+%% URL = {http://www.xyz.org/~jones/idx_g.htm}
+%% DOI = {10.5194/xyz}
+
+%% LITERATURE CITATIONS
+%%
+%% command                        & example result
+%% \citet{jones90}|               & Jones et al. (1990)
+%% \citep{jones90}|               & (Jones et al., 1990)
+%% \citep{jones90,jones93}|       & (Jones et al., 1990, 1993)
+%% \citep[p.~32]{jones90}|        & (Jones et al., 1990, p.~32)
+%% \citep[e.g.,][]{jones90}|      & (e.g., Jones et al., 1990)
+%% \citep[e.g.,][p.~32]{jones90}| & (e.g., Jones et al., 1990, p.~32)
+%% \citeauthor{jones90}|          & Jones et al.
+%% \citeyear{jones90}|            & 1990
+
+%% FIGURES
+
+%% When figures and tables are placed at the end of the MS (article in one-column style), please add \clearpage
+%% between bibliography and first table and/or figure as well as between each table and/or figure.
+
+%% ONE-COLUMN FIGURES
+
+%%f
+%\begin{figure}[t]
+%\includegraphics[width=8.3cm]{FILE NAME}
+%\caption{TEXT}
+%\end{figure}
+%
+%%% TWO-COLUMN FIGURES
+%
+%%f
+%\begin{figure*}[t]
+%\includegraphics[width=12cm]{FILE NAME}
+%\caption{TEXT}
+%\end{figure*}
+%
+%
+%%% TABLES
+%%%
+%%% The different columns must be seperated with a & command and should
+%%% end with \\ to identify the column brake.
+%
+%%% ONE-COLUMN TABLE
+%
+%%t
+%\begin{table}[t]
+%\caption{TEXT}
+%\begin{tabular}{column = lcr}
+%\tophline
+%
+%\middlehline
+%
+%\bottomhline
+%\end{tabular}
+%\belowtable{} % Table Footnotes
+%\end{table}
+%
+%%% TWO-COLUMN TABLE
+%
+%%t
+%\begin{table*}[t]
+%\caption{TEXT}
+%\begin{tabular}{column = lcr}
+%\tophline
+%
+%\middlehline
+%
+%\bottomhline
+%\end{tabular}
+%\belowtable{} % Table Footnotes
+%\end{table*}
+%
+%%% LANDSCAPE TABLE
+%
+%%t
+%\begin{sidewaystable*}[t]
+%\caption{TEXT}
+%\begin{tabular}{column = lcr}
+%\tophline
+%
+%\middlehline
+%
+%\bottomhline
+%\end{tabular}
+%\belowtable{} % Table Footnotes
+%\end{sidewaystable*}
+%
+%
+%%% MATHEMATICAL EXPRESSIONS
+%
+%%% All papers typeset by Copernicus Publications follow the math typesetting regulations
+%%% given by the IUPAC Green Book (IUPAC: Quantities, Units and Symbols in Physical Chemistry,
+%%% 2nd Edn., Blackwell Science, available at: http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf, 1993).
+%%%
+%%% Physical quantities/variables are typeset in italic font (t for time, T for Temperature)
+%%% Indices which are not defined are typeset in italic font (x, y, z, a, b, c)
+%%% Items/objects which are defined are typeset in roman font (Car A, Car B)
+%%% Descriptions/specifications which are defined by itself are typeset in roman font (abs, rel, ref, tot, net, ice)
+%%% Abbreviations from 2 letters are typeset in roman font (RH, LAI)
+%%% Vectors are identified in bold italic font using \vec{x}
+%%% Matrices are identified in bold roman font
+%%% Multiplication signs are typeset using the LaTeX commands \times (for vector products, grids, and exponential notations) or \cdot
+%%% The character * should not be applied as mutliplication sign
+%
+%
+%%% EQUATIONS
+%
+%%% Single-row equation
+%
+%\begin{equation}
+%
+%\end{equation}
+%
+%%% Multiline equation
+%
+%\begin{align}
+%& 3 + 5 = 8\\
+%& 3 + 5 = 8\\
+%& 3 + 5 = 8
+%\end{align}
+%
+%
+%%% MATRICES
+%
+%\begin{matrix}
+%x & y & z\\
+%x & y & z\\
+%x & y & z\\
+%\end{matrix}
+%
+%
+%%% ALGORITHM
+%
+%\begin{algorithm}
+%\caption{...}
+%\label{a1}
+%\begin{algorithmic}
+%...
+%\end{algorithmic}
+%\end{algorithm}
+%
+%
+%%% CHEMICAL FORMULAS AND REACTIONS
+%
+%%% For formulas embedded in the text, please use \chem{}
+%
+%%% The reaction environment creates labels including the letter R, i.e. (R1), (R2), etc.
+%
+%\begin{reaction}
+%%% \rightarrow should be used for normal (one-way) chemical reactions
+%%% \rightleftharpoons should be used for equilibria
+%%% \leftrightarrow should be used for resonance structures
+%\end{reaction}
+%
+%
+%%% PHYSICAL UNITS
+%%%
+%%% Please use \unit{} and apply the exponential notation
+
 \end{document}
-
-\endinput
-%%
-%% End of file `elsarticle-template-num-names.tex'.
 

### 2019-11-25 article.tex
fix merge issues

@@
 High-dimensional density estimation is a challenge in itself, but is necessary in order to tackle more realistic applications.
+
 %% The following commands are for the statements about the availability of data sets and/or software code corresponding to the manuscript.

### 2019-11-25 article.tex
remove part on weights of EM estimation, add k^*(u^i) with different u^i

--- 2019-11-22 article.tex
@@
 
-{\color{red} kmean ou kexpectation ?}
-
 Let us define $\mu(\mathbf{k})$ and $\sigma^2(\mathbf{k})$, the expected value and the variance of the cost variable  for a given $\mathbf{k}$ as 
@@
 One could instead consider how often a particular value $\mathbf{k}$ is a minimiser of the cost function, leading to the notion of most probable estimate, as explained in the next subsection.
-
-{\color{red} mean ou expectation ?}
 
@@
 Using Kernel density estimation (Gaussian), the estimation of $\kmpe$ is $\hatkmpe {}_{,\mathrm{KDE}} \approx 1.5$, while using the histogram and Gaussian mixture, $\hatkmpe {}_{,\mathrm{histogram}}=\hatkmpe {}_{,\mathrm{EM}}=3.8$.
-This difference is explained by the accumulation of minimisers at this point: this challenges the assumption that $\mathbf{K}^*$ is continuous.
+This difference in the estimation of the mode is explained by the accumulation of minimisers at this point: this challenges the assumption that $\mathbf{K}^*$ is continuous.
 As the density estimation techniques traditionally assume this continuity, the EM algorithm fits this using a normal distribution with a very small variance, while the KDE considers a sum of Gaussian kernels of constant bandwidth, located at the same point.
 This particular problem highlights the issue with $\kmpe$, as its estimation is highly sensitive to the density approximation procedure.
-
-Alternatively, we can consider the mixing coefficients of the EM
-density estimation. The Gaussian centered at $1.5$ has been attributed
-a weight of $0.608$, while the one centered at $3.8$ has a mixing
-weight of $0.226$. Ultimately, an optimiser would be more likely to be
-close to $1.5$, but we do not have information on its performance in
-this region around this value. \arthur{je ne comprends pas ce passage}
+% Alternatively, when considering the mixing coefficients of the EM estimation, the Gaussian centered at $1.5$ has the largest weight, of $0.608$.
+In other words, according to this estimated density, the optimal value $K^*$ has a probability of $0.608$ of being distributed normally around $1.5$.
+% Alternatively, we can consider the mixing coefficients of the EM
+% density estimation. The Gaussian centered at $1.5$ has been attributed
+% a weight of $0.608$, while the one centered at $3.8$ has a mixing
+% weight of $0.226$. Ultimately, an optimiser would be more likely to be
+% close to $1.5$, but we do not have information on its performance in
+% this region around this value. \arthur{je ne comprends pas ce passage}
 
 % as we can argue that both values may be a sensible choice for the MPE. This comes from the fact that the hypothesis that $\mathbf{K}^*$ is a continuous r.v.\ is violated.
+
 A way to avoid this issue is to introduce a bit of leeway for a value to be optimal, or at least ``acceptably not optimal''.
@@
 In the end, if the value $\hat{\checka}_p$ is too large, the relaxation needed to get acceptable values with probability $p$ is very high, so the resulting estimation $\hat{\checkk}_p$ may not be relevant for the future application.
-\victor{chapeau car ici je parle de l'estimation en pratique}
+% \victor{chapeau car ici je parle de l'estimation en pratique}
 
@@
 Those forecasts result from the integration of the numerical model between the time $T$ and a time $T_{\mathrm{pred}}$.
-
 Given the probabilistic nature of the environmental conditions $\mathbf{U}$, the forecasts will also be probabilistic.
 We will then compare $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{U})$, for a calibrated $\mathbf{k}$.
+The metric of comparison will be the squared forecast error, and the Continuous Ranked Probability Score (CRPS).
+The calibrated values that are compared are the minimiser of the expectation $\hatkmean$, the minimiser of the variance $\hatkvar$, the relative regret of level $p=1$: $\kest_1$ as described in the previous section, but also the global minimiser $\kest_{\mathrm{global}}$, and some conditional minimisers $\kest^*(\mathbf{u}^i)$ where the chosen environmental variables are $\{\mathbf{u}^i\}_{1\leq i \leq 4} = \{0.5, 0.55, 0.65, 0.7\}$.
+$\kest^*(0.6)$ has been omitted due to the fact that it result in a value very similar to the minimum of the expectation.
+These have been included in order to compare the different metrics obtained without using a robust approach.
+\todo{à revoir}
 
@@
 This can be done using a Monte-Carlo approximation: as $\mathbf{u}$ and $\mathbf{u}'$ are iid, let us assume that we have a set of samples $\{\mathbf{u}^i\}_{1\leq i \leq N_{\mathbf{u}}}$.
+The squared forecast error can then be approximated using this finite set of samples:
 \begin{equation}
@@
 We can see that $\kest_{\mathrm{global}}$ performs slightly better than $\kest_1$, itself performing slightly better than $\hatkmean$.
-Averaging $S(\mathbf{\kest}$ over only the time steps between $T$ and $T_{\mathrm{pred}}$, we have an indication on the quality of the forecast in the squared sense depending on the spatial position, as seen on the left plot of Figure~\ref{fig:forecast_squared_error}.
+Averaging $S(\mathbf{\kest})$ over the time steps between $T$ and $T_{\mathrm{pred}}$, we have an indication on the quality of the forecast in the squared sense depending on the spatial position, as seen on the left plot of Figure~\ref{fig:forecast_squared_error}.
 \begin{figure*}[!h]
 \centering
-\includegraphics[width=.9\textwidth]{Figures/forecast_error.pdf}
+\includegraphics[width=.9\textwidth]{Figures/L2_full.pdf}
 \caption{Quality of forecast, depending on the calibrated parameter.
@@
 We can see that the mean forecast error squared, on the right side, averaged over time and space is the smallest for $\kest_{\mathrm{global}}$, while $\kest_{1.0}$ performs slightly better $\hatkmean$.
-\begin{figure}[!h]
-  \centering
-  \includegraphics[width=.9\textwidth]{Figures/forecast_CRPS}
-  \caption{CRPS computed for different calibrated parameters}
-\label{fig:forecast_crps}
-\end{figure}
 
@@
 % \end{figure*}
-
+One issue with the squared forecast error is that it will penalize strongly a high sensitivity to the environmental conditions \todo{à conserver/changer ?}.
+A way to deal with this is to use another metric, that takes the probabilistic nature of the forecasts into account.
 \subsubsection{Continuous Ranked Probability Score}
@@
 \end{equation}
+
+\begin{figure}[!h]
+  \centering
+  \includegraphics[width=.9\textwidth]{Figures/CRPS_full}
+  \caption{CRPS computed for different calibrated parameters}
+\label{fig:forecast_crps}
+\end{figure}
 
@@
 High-dimensional density estimation is a challenge in itself, but is necessary in order to tackle more realistic applications.
-%% The following commands are for the statements about the availability of data sets and/or software code corresponding to the manuscript.
-%% It is strongly recommended to make use of these sections in case data sets and/or software code have been part of your research the article is based on.
-
-% \sampleavailability{TEXT} %% use this section when having geoscientific samples available
-
 % \appendix

### 2019-11-26 article.tex
fix typos, format of recap table, change subscript maxratio to ratio

@@
 Moreover, such uncertainties may be of different nature. 
-~\cite{walker_defining_2003} propose two to consider two categories of uncertainties.
+~\cite{walker_defining_2003} proposes to consider two categories of uncertainties.
 On the one hand aleatoric uncertainties,  coming from the inherent variability of a phenomenon, e.g.\ intrinsic randomness of some environmental variables.
@@
 We opted to model this compromise by the ratio $(p/\checkap)$, as it increases with respect to $p$ and decreases with respect to $\checka_p$.
-The level of confidence $p_{\mathrm{maxratio}}$ is then defined as the maximiser of $p\mapsto p / \checka_p$.
+The level of confidence $p_{\mathrm{ratio}}$ is then defined as the maximiser of $p\mapsto p / \checka_p$.
 
@@
   \centering
-\begin{tabular}{lrr}
+\begin{tabular}{lrp{5cm}}
   \toprule
@@
    $\argmax_{\mathbf{k}\in\Kspace} p_{\mathbf{K}^*}(\mathbf{k})$ & $\kmpe$ & Most probable minimiser\\
-    $\inf\left\{ \alpha \mid \exists \checkkp \in \Kspace,\, \Gamma_{\alpha}(\checkkp) \geq p \right\}$ & $(p, \checkkp,\checkap)$ & Acceptable values with fixed probability $p$ \\
-    $p_{\mathrm{maxratio}} = \argmax p/\checkap$ & $(p_{\mathrm{maxratio}}, \checkk_{\mathrm{maxratio}}, \checka_{\mathrm{maxratio}})$ & Maximal ratio of $p$ and $\checkap$ \\
+    $\inf\left\{ \alpha \mid \exists \checkkp \in \Kspace,\, \Gamma_{\alpha}(\checkkp) \geq p \right\}$ & $(p, \checkkp,\checkap)$ & Acceptable values\newline with fixed probability $p$ \\
+    $p_{\mathrm{ratio}} = \argmax p/\checkap$ & $(p_{\mathrm{ratio}}, \checkk_{\mathrm{ratio}}, \checka_{\mathrm{ratio}})$ & Maximal ratio of $p$ and $\checkap$ \\
   \bottomrule
@@
   $\hatkmpe$ & 1.628 \\
-  $\kest_{\mathrm{maxratio}},~\hat{p}_{\mathrm{maxratio}}=0.654$ & 1.637 \\
+  $\kest_{\mathrm{ratio}},~\hat{p}_{\mathrm{ratio}}=0.654$ & 1.637 \\
 $\kest_p,~p=0.95$ & 1.672 \\ \bottomrule
@@
 
-\begin{figure*}[t]
+\begin{figure*}[!h]
   \centering
@@
 Compared to the plots for $J_{\mathrm{BH}}$ in Figure~\ref{fig:ratio_BH}, $\hat{\checka}_p$ exhibits a smoother behaviour for the $J_{\mathrm{BHswap}}$ function as no change of slope is easily discernable.
-The computation of the ratio advocates for a level of confidence $p_{\mathrm{maxratio}}$ close to $0.75$.
+The computation of the ratio advocates for a level of confidence $p_{\mathrm{ratio}}$ close to $0.75$.
 The numerical values of the estimations $\hat{k}$ presented in Table~\ref{tab:recap_estimates_BHs} show that, contrary to the $J_{\mathrm{BH}}$ function, the objective are concurrent.
@@
 $\kest_{\mathrm{MPE}}$ & 0.606 \\ 
-$\kest_{\mathrm{maxratio}},~ \hat{p}_{\mathrm{maxratio}}=0.766$ & 1.537 \\ 
+$\kest_{\mathrm{ratio}},~ \hat{p}_{\mathrm{ratio}}=0.766$ & 1.537 \\ 
 $\hatkmean$ & 1.752 \\ 
@@
 
-In this case, $\hatkmpe$, $\hatkmean$ and $\hat{\checkk}_{\mathrm{maxratio}}$ present a similar behaviour.
+In this case, $\hatkmpe$, $\hatkmean$ and $\hat{\checkk}_{\mathrm{ratio}}$ present a similar behaviour.
 They perform very well for $\mathbf{u}>2$, especially for $\hatkmpe$ which is very close to the minimal value; However for $\mathbf{u}<2$, they produce high values of the function.
@@
 We are now going to compare how well three of those values compare in a forecast context: $\kest_1$, $\hatkmean$ and $\kest_{\mathrm{global}}$, as the first two refer quite naturally to the notion of robustness, and the latter is an example of an estimate that does not take into account the uncertainties.
-\clearpage
+
 \subsection{Assessing the quality of the forecast of the calibrated model}
@@
 \includegraphics[width=.9\textwidth]{Figures/L2_full.pdf}
-\caption{Quality of forecast, depending on the calibrated parameter.
+\caption{Squared forecast error, depending on the calibrated parameter.
 The left figures show the metric averaged over time, while the right figure show the mean forecast error, averaged over time and space}
@@
 
-% \begin{figure*}[!h]
-% \centering
-% \includegraphics[width=10cm]{Figures/distrib_L2norm.pdf}
-% \caption{Distribution of the forecast squared error, averaged over the different values of the uncertain parameter in the numerical simulations \victor{doublon avec fig.\ref{fig:forecast_squared_error} ?}}
-% \label{fig:forecast_squared_error_distrib}
-% \end{figure*}
 One issue with the squared forecast error is that it will penalize strongly a high sensitivity to the environmental conditions \todo{à conserver/changer ?}.
@@
 \end{equation}
+The left plot of Figure~\ref{fig:forecast_crps} shows the CRPS averaged over time, and the right plot shows the value of the CRPS averaged over time and space.
+The difference between the squared forecast error and the CRPS is apparent when comparing the general trends shared by the different calibrated parameters.
+According to the squared error, the region around $x=4$ is not well predicted, while around $x=8$, the prediction are better.
+On the other hand, according to the CRPS, the region around $x=8$ provide worse forecasts than the one at $x=4$ and $x=7$.
 
@@
 \end{figure}
+The numerical evaluations of the CRPS for different parameters show the same order of performances observed for the squared error.
+The calibrated parameters that present the best performances for forecasts according to those two metrics are $\kest^*(0.7)$, $\kest^*(0.65)$ which is very similar to $\kest_{\mathrm{global}}$.
 
 \clearpage
+
 \section*{Conclusion}  

### 2019-11-28 article.tex
add figures, continue forecast

@@
 Those forecasts result from the integration of the numerical model between the time $T$ and a time $T_{\mathrm{pred}}$.
+
 Given the probabilistic nature of the environmental conditions $\mathbf{U}$, the forecasts will also be probabilistic.
 We will then compare $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{U})$, for a calibrated $\mathbf{k}$.
-The metric of comparison will be the squared forecast error, and the Continuous Ranked Probability Score (CRPS).
-The calibrated values that are compared are the minimiser of the expectation $\hatkmean$, the minimiser of the variance $\hatkvar$, the relative regret of level $p=1$: $\kest_1$ as described in the previous section, but also the global minimiser $\kest_{\mathrm{global}}$, and some conditional minimisers $\kest^*(\mathbf{u}^i)$ where the chosen environmental variables are $\{\mathbf{u}^i\}_{1\leq i \leq 4} = \{0.5, 0.55, 0.65, 0.7\}$.
-$\kest^*(0.6)$ has been omitted due to the fact that it result in a value very similar to the minimum of the expectation.
-These have been included in order to compare the different metrics obtained without using a robust approach.
-\todo{à revoir}
+Two metrics of comparison will be computed: the squared forecast error, and the Continuous Ranked Probability Score (CRPS).
+The ``robust'' parameters that are compared are the minimiser of the expectation $\hatkmean$, the minimiser of the variance $\hatkvar$ and the relative regret of level $p=1$, $\kest_1$ as described in the previous section.
+
+We will also feature the global minimiser $\kest_{\mathrm{global}}$, and the conditional minimisers $\kest^*(\mathbf{u}^i)$ where the chosen environmental variables are $\{\mathbf{u}^i\}_{1\leq i \leq 4} = \{0.5, 0.55, 0.65, 0.7\}$.
+Those values are introduced in order to have a more precise idea on the possible performances of a deterministic version of the calibration problem.
+The conditional minimiser $\kest^*(0.6)$ has been omitted as it results in a value very similar to the minimum of the expectation.
 
@@
 \end{figure*}
-We can see that the mean forecast error squared, on the right side, averaged over time and space is the smallest for $\kest_{\mathrm{global}}$, while $\kest_{1.0}$ performs slightly better $\hatkmean$.
+We can see that the mean forecast error squared, on the right side, averaged over time and space is the smallest for the conditional minimisers $\kest^*(0.7)$ and $\kest^*(0.65)$, then $\kest_{\mathrm{global}}$, while $\kest_{1.0}$ performs slightly better $\hatkmean$.
+The range of those performance metrics carry also information on the limited impact of the choice of $\mathbf{k}$ in the calibration.
 
-One issue with the squared forecast error is that it will penalize strongly a high sensitivity to the environmental conditions \todo{à conserver/changer ?}.
+One issue with the squared forecast error is that it will penalize strongly the forecasts that present high variability with respect to the environmental conditions.
+
 A way to deal with this is to use another metric, that takes the probabilistic nature of the forecasts into account.
+
 \subsubsection{Continuous Ranked Probability Score}
@@
 \end{equation}
+
 The left plot of Figure~\ref{fig:forecast_crps} shows the CRPS averaged over time, and the right plot shows the value of the CRPS averaged over time and space.
@@
 The numerical evaluations of the CRPS for different parameters show the same order of performances observed for the squared error.
-The calibrated parameters that present the best performances for forecasts according to those two metrics are $\kest^*(0.7)$, $\kest^*(0.65)$ which is very similar to $\kest_{\mathrm{global}}$.
+The calibrated parameters that present the best performances for forecasts according to those two metrics are $\kest^*(0.7)$, $\kest^*(0.65)$ which is very similar to $\kest_{\mathrm{global}}$, and then $\kest_1$.
+
+It may seem surprising that the calibrated values chosen according to a robust objective perform worse than the ``deterministic'' objectives $\kest^*(0.7)$, $\kest^*(0.65)$ and $\kest_{\mathrm{global}}$.
 

### 2019-11-28 article.tex
continue forecasts aspects

@@
 \end{tabular}
+\caption{Robust estimators, based on a cost function $J$}
 \label{tab:RO_recap}
-  \caption{Robust estimators, based on a cost function $J$}
 \end{table}
@@
 On the bottom plots, the curves $\mathbf{k}\mapsto \hat{\Gamma}_{\alpha}(\mathbf{k})$ for $\alpha=\hat{\checka}_1$ and $\alpha=1.5$ along with the histogram of the minimisers are represented.
-One can notice that the relaxation does not present an issue with the accumulation of the minimisers of $\JBH$ at $3.8$, as opposed to the MPE and its dependence on the estimation procedure of the distribution.
+
+One can notice that the relaxation allows us to avoid the issue brought by the accumulation of the minimisers of $\JBH$ at $3.8$, as opposed to the MPE and its dependence on the estimation procedure of the distribution.
 
@@
 
- For the $J_{\mathrm{BH}}$ function, the numerical values can be found in Table~\ref{tab:recap_estimates_branin}. One can notice that the different estimates are close to each other for this problem.
+ For the $J_{\mathrm{BH}}$ function, the numerical values can be found in Table~\ref{tab:recap_estimates_branin}. For this particular problem, the different estimates are close to each other.
 
@@
 The computation of the ratio advocates for a level of confidence $p_{\mathrm{ratio}}$ close to $0.75$.
-The numerical values of the estimations $\hat{k}$ presented in Table~\ref{tab:recap_estimates_BHs} show that, contrary to the $J_{\mathrm{BH}}$ function, the objective are concurrent.
+The numerical values of the estimations $\kest$ presented in Table~\ref{tab:recap_estimates_BHs} show that contrary to the $J_{\mathrm{BH}}$ function, the calibrated values are more spread on $\Kspace$.
 
@@
  Calibration of a numerical model is usually based on the comparison between the numerical model and some observations in a fixed time interval $[0, T]$ called assimilation window.
-The physical system at stake is based on an input $\mathbf{u} \in \mathcal{U}$, that represents some operating conditions.
-This system can then be seen as a map from $\mathcal{U}$ to $\mathcal{Y}$, denoted as $\mathcal{M}^o : \mathbf{u}\mapsto \mathcal{M}^o(\mathbf{u})$.
+The physical system at stake is based on an input $\mathbf{u} \in \Uspace$, that represents some operating conditions.
+This system can then be seen as a map from $\Uspace$ to $\mathcal{Y}$, denoted as $\mathcal{M}^o : \mathbf{u}\mapsto \mathcal{M}^o(\mathbf{u})$.
 
-In addition to the operating conditions $\mathbf{u}$, the numerical model is also dependent on some other input $\mathbf{k}\in\mathcal{K}$.
+In addition to the operating conditions $\mathbf{u}$, the numerical model is also dependent on some other input $\mathbf{k}\in\Kspace$.
 This additional parametrization comes usually from the successive simplifications needed to implement a numerical model of the physical system observed, and from some unobserved physical parameters.
@@
 
-The true value taken by the physical system during this window is denoted by $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) \in \mathcal{Y}$, where $\mathbf{u}^{\mathrm{true}} \in \mathcal{U}$ is unknown.
+The true value taken by the physical system during this window is denoted by $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) \in \mathcal{Y}$, where $\mathbf{u}^{\mathrm{true}} \in \Uspace$ is unknown.
 The misfit $\mathcal{G}$ and the cost function $J$ defined Eq.\eqref{eq:def_cost_fun} can then be defined as
@@
 The environmental parameter $\mathbf{u}$ is the amplitude of a sine wave of period $1/\omega_0$.
-The domain of those two parameters are $\mathcal{K} = [0.0, 1.3]$ and $\mathcal{U} = [0.5, 0.7]$.
+The domain of those two parameters are $\Kspace = [0.0, 1.3]$ and $\Uspace = [0.5, 0.7]$.
 
@@
 The output of the computer code is the sea surface height $h$, on the center of all the volumes and at all the time-steps, that will be denoted $\mathcal{M}(\mathbf{k},\mathbf{u};\, \omega_0=1.0)$.
-In this setting, the variable input is uniformly distributed on $\mathcal{U}$.
+In this setting, the variable input is uniformly distributed on $\Uspace$.
 To generate the observations, we choose $\mathbf{u}^{\mathrm{true}}=2/3$, and define $\mathcal{M}^o$ based on the computer model $\mathcal{M}$, such that $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) = \mathcal{M}(\mathbf{k}^{\mathrm{true}}, \mathbf{u}^{\mathrm{true}}; \, \omega_0 = 0.999)$.
@@
 \subsubsection{Squared forecast error}
-Given two environmental conditions $\mathbf{u}$, used to run the computer simulation and $\mathbf{u}'$, used to generate the observations, the squared forecast error for the parameter $\mathbf{k}$ is
+Given two environmental conditions $\mathbf{u}$ and $\mathbf{u}'\in \Uspace$, the former used to run the computer simulation and the latter to generate the observations, the squared forecast error for the parameter $\mathbf{k}$ is
 \begin{equation}
@@
 \end{equation}
-Averaging over $\mathbf{u}$, $\mathbf{u}'$ defines the mean squared forecast error, defined on every point of the spatial domain, and at every time-steps.
-This can be done using a Monte-Carlo approximation: as $\mathbf{u}$ and $\mathbf{u}'$ are iid, let us assume that we have a set of samples $\{\mathbf{u}^i\}_{1\leq i \leq N_{\mathbf{u}}}$.
-The squared forecast error can then be approximated using this finite set of samples:
+Averaging over both $\mathbf{u}$ and $\mathbf{u}'$ defines the mean squared forecast error, defined on every point of the spatial domain, and at every time-steps.
+This can be done using a Monte-Carlo approximation.
+As $\mathbf{u}$ and $\mathbf{u}'$ are iid, assuming that we have a set of samples $\{\mathbf{u}^i\}_{1\leq i \leq N_{\mathbf{u}}}$, the squared forecast error can then be approximated using this finite set of samples:
 \begin{equation}

### 2019-11-28 article.tex
modif phrase/phrase avec arthur

@@
 
-For the $J_{\mathrm{BHswap}}$ function, we can observe that those three methods give coherent results, as $\hatkmpe {}_{,\mathrm{KDE}} =\hatkmpe {}_{,\mathrm{EM}}=\hatkmpe {}_{,\mathrm{histogram}}\approx 0.8$.
+For the $J_{\mathrm{BHswap}}$ function, we can observe that those three methods give consistent results, as $\hatkmpe {}_{,\mathrm{KDE}} =\hatkmpe {}_{,\mathrm{EM}}=\hatkmpe {}_{,\mathrm{histogram}}\approx 0.8$.
 This is not the case for the  $J_{\mathrm{BH}}$ function however.
 Using Kernel density estimation (Gaussian), the estimation of $\kmpe$ is $\hatkmpe {}_{,\mathrm{KDE}} \approx 1.5$, while using the histogram and Gaussian mixture, $\hatkmpe {}_{,\mathrm{histogram}}=\hatkmpe {}_{,\mathrm{EM}}=3.8$.
-This difference in the estimation of the mode is explained by the accumulation of minimisers at this point: this challenges the assumption that $\mathbf{K}^*$ is continuous.
+This difference is explained by the accumulation of minimisers at this point: this challenges the assumption that $\mathbf{K}^*$ is continuous.
 As the density estimation techniques traditionally assume this continuity, the EM algorithm fits this using a normal distribution with a very small variance, while the KDE considers a sum of Gaussian kernels of constant bandwidth, located at the same point.
-This particular problem highlights the issue with $\kmpe$, as its estimation is highly sensitive to the density approximation procedure.
+This particular problem highlights an issue with $\kmpe$, as its estimation is possibly sensitive to the density approximation procedure.
 % Alternatively, when considering the mixing coefficients of the EM estimation, the Gaussian centered at $1.5$ has the largest weight, of $0.608$.
@@
 
-% as we can argue that both values may be a sensible choice for the MPE. This comes from the fact that the hypothesis that $\mathbf{K}^*$ is a continuous r.v.\ is violated.
+% as we can argue that both values may be a sensible choice for the MPE. This comes from the fact that the hypothesis that $\mathbf{K}^*$ is a continuous r.v.\ is
 
-A way to avoid this issue is to introduce a bit of leeway for a value to be optimal, or at least ``acceptably not optimal''.
-This slackness takes the form of a relaxation coefficient, whose choice leads to a new family of robust estimators, along with a measure of their robustness via the coefficient.
+Instead of just considering the optimal minimisers, we introduce a bit of leeway, and look for ``acceptably not optimal'' parameters.
+ This slackness takes the form of a relaxation coefficient, whose choice leads to a new family of robust estimators, along with a measure of their robustness via the relaxation coefficient.
 %This leads us to the definition of a new family of estimators, for which one can attribute a {\it level of robustness} \elise{je me rend bien compte que cette phrase est un peu bizarre ...mais bon c'est l'idee}
@@
 The density of minimisers has been estimated by optimising $\mathbf{k}\mapsto J(\mathbf{k},\mathbf{u})$ over $\Kspace$ for different realisations of $\mathbf{u}$.
-Instead of only considering  optimal values, we propose to consider their {\it acceptable} neighbourhood in terms of performance of the cost function as well, as illustrated in Figure~\ref{fig:relax_tuto}.
-To do so, for each $\mathbf{u}$, we define as acceptable values of the cost function, the values that are below $\alpha J^*(\mathbf{u})$, with $\alpha > 1$.
+Instead of focusing on optimal values, we propose to consider their {\it acceptable} neighbourhood in terms of performance of the cost function as well.
+To do so, for each $\mathbf{u}$, $\mathbf{k}$ is deemed acceptable when  $J(\mathbf{k},\mathbf{u}) \leq \alpha J^*(\mathbf{u})$, with $\alpha > 1$.
 
-For each $\mathbf{u}$, we construct a region around the optimiser that produces acceptable values of the cost function, as seen on the bottom left plot.
-Looking at it the other way around, for a given $\mathbf{k}$, the set $R_{\alpha}(\mathbf{k}) \subset \Uspace$ is defined as the set of $\mathbf{u}$ verifying the condition of acceptability:
+In this context, for a given $\mathbf{k}$, the set $R_{\alpha}(\mathbf{k}) \subset \Uspace$ is defined as the set of $\mathbf{u}$, for which $\mathbf{k}$ is acceptable:
 \begin{equation}
@@
 \end{equation}
+In Figure~\ref{fig:relax_tuto} \victor{Mettre description}. 
 % This notion of acceptability will be introduced later.
-Finally, for each $\mathbf{k}$, we will measure (with respect to $\Prob_{\mathbf{U}}$) the set of $\mathbf{u}$ within this acceptable neighbourhood, as illustrated in the bottom right plot.
+% Finally, for each $\mathbf{k}$, we will measure (with respect to $\Prob_{\mathbf{U}}$) the set of $\mathbf{u}$ within this acceptable neighbourhood.
 
@@
 \includegraphics[width=12cm]{Figures/relaxation_tuto.pdf}
-\caption{Principle of the relaxation of the constraint on $J_{\mathrm{BHswap}}$, and illustration of $R_\alpha(\mathbf{k})$}
+\caption{Principle of the relaxation of the constraint on $J_{\mathrm{BHswap}}$, and illustration of $R_\alpha(\mathbf{k})$. Top plots: mieux décrire}
 \label{fig:relax_tuto}
@@
 %for a given $\mathbf{u}$, $\mathbf{k}$ is deemed acceptable if $J(\mathbf{k},\mathbf{u}) \leq \alpha J^*( \mathbf{u})$.
-Introducing the random nature of $\mathbf{U}$, $\Gamma_\alpha(\mathbf{k})$ is defined as the probability that $\mathbf{k}$ is acceptable given $\alpha$:
+Introducing the random nature of $\mathbf{U}$, one can define $\Gamma_\alpha(\mathbf{k})$ as the probability that $\mathbf{k}$ is acceptable given $\alpha$:
 \begin{equation}
@@
 \end{equation}
-In other words, $\Gamma_{\alpha}(\mathbf{k})$ is then the probability that $J(\mathbf{k},\mathbf{U})$ is between 
+In other words, $\Gamma_{\alpha}(\mathbf{k})$ is the probability that $J(\mathbf{k},\mathbf{U})$ is between 
 $J^*(\mathbf{U})$ and 
 $\alpha J^*(\mathbf{U})$.
-Without relaxation, i.e.\ when $\alpha$ is set to $1$, $\Gamma_1$ is non-zero if the set $\{\mathbf{u}\in\Uspace \mid J(\mathbf{k},\mathbf{u}) = J^*(\mathbf{u})\}$ has non-zero measure with respect to $\Prob_{\mathbf{U}}$, that is when the distribution of $\mathbf{K}^*$ presents atoms.
+
+Noting that without relaxation, \textit{i.e.} when $\alpha$ is set to $1$, $\Gamma_1$ is non-zero if the set $\{\mathbf{u}\in\Uspace \mid J(\mathbf{k},\mathbf{u}) = J^*(\mathbf{u})\}$ has non-zero measure with respect to $\Prob_{\mathbf{U}}$.
+It happens when the distribution of $\mathbf{K}^*$ presents atoms \victor{?}.
 This can be linked to the definition of the MPE from Eq.~\eqref{eq:MPE}.
@@
 For a given set of environmental conditions $\mathbf{u}$, if the function $\mathbf{k} \mapsto J(\mathbf{k},\mathbf{u})$ is flat around its minimum $\mathbf{k}^*(\mathbf{u})$, then choosing  $\mathbf{k}^*(\mathbf{u}) + \epsilon$ (for a small $\epsilon$) will produce a value closer to the minimum than when the function has a high curvature.
-In addition to that, relaxing the constraint using a multiplicative constant puts more weight (i.e.\ a slower increase of the acceptable region) on the values of $\mathbf{k}^*(\mathbf{u})$ when $J^*(\mathbf{u})$ is close to zero.
+In addition to that, relaxing the constraint using a multiplicative constant puts more weight on the values of $\mathbf{k}^*(\mathbf{u})$ when $J^*(\mathbf{u})$ is small.
 
-Given that $J>0$, $\Gamma_{\alpha}(\mathbf{k})$ is increasing with respect to $\alpha$ for any $\mathbf{k}\in\Kspace$.
+The choice of the relaxation constant $\alpha$ can be made to enforce some probability on the acceptability of the 
+For instance, given that $J>0$, $\Gamma_{\alpha}(\mathbf{k})$ is increasing with respect to $\alpha$ for any $\mathbf{k}\in\Kspace$.
 We can then focus on the smallest value of $\alpha$ such that $\Gamma_\alpha$ reaches a certain level of confidence $p\in[0,1]$.
@@
 
-This alternative definition of $\checka_1$ is useful to estimate quickly $\hat{\checka}_1$ whenever a grid over $\mathbb{K}\times\mathbb{U}$ has already been evaluated, thus avoiding multiple computations of $\Gamma_{\alpha}(\mathbf{k})$ until its maximum reaches $1$.
-By Eq.\eqref{eq:upper_bound_alpha_check}, choosing a level of confidence equal to $1$ is then equivalent to looking for the worst-case scenario of the ratio $\frac{J(\mathbf{k},\mathbf{u})}{J^*(\mathbf{u})}$, and therefore suffers from the same pitfall of the worst-case approach.
-As mentioned in the introduction, this returns over-conservative solution, and is not suited for random variable with unbounded support.
+This alternative definition of $\checka_1$ is useful to estimate it quickly whenever a grid over $\mathbb{K}\times\mathbb{U}$ has already been evaluated, thus avoiding multiple computations of $\Gamma_{\alpha}(\mathbf{k})$ until its maximum reaches $1$.
+From Eq.\eqref{eq:upper_bound_alpha_check}, choosing a level of confidence equal to $1$ is then equivalent to looking for the worst-case scenario of the ratio $\frac{J(\mathbf{k},\mathbf{u})}{J^*(\mathbf{u})}$.
+Therefore it may suffer from the same pitfall as the worst-case approach.
+As mentioned in the introduction, this is not suited for random variable with unbounded support as it may return over-conservative solution,
 
+$\checkap$ can be an indicator of the robustness of $\ckeckkp$.  
 A high value of $\checka_1$ corresponds to a high ratio $\frac{J(\mathbf{k},\mathbf{u})}{J^*(\mathbf{u})}$ for at least one particular $\mathbf{u}$.
 In that sense, $J(\checkk_1,\mathbf{u})$ may be possibly very high.
-More generally, for a level of confidence $p$ fixed, $\checkap$ is the slackness needed to be able to reach the probability $p$.
-So, in addition to the value of the estimate $\checkkp$, we have an indicator of the robustness associated.
-We can then see that it is sensible to study jointly $p$, $\checkap$ and $\checkkp$ in order to make a final decision.
+More generally, for a fixed level of confidence $p$, $\checkap$ is the slackness needed to be able to reach the probability $p$.
+% So, in addition to the value of the estimate $\checkkp$, we have an indicator of the robustness associated.
+We can then see that it is sensible to study jointly $p$, $\checkap$ and $\checkkp$.
 

### 2019-12-03 article.tex
continue corrections avec arthur, upd figures, rm unused figures

@@
 \newcommand{\kest}{\hat{\mathbf{k}}}
-
+\newcommand{\RRE}{RRE}
 \newcommand{\checkap}{{\alpha}_p}
@@
 \end{equation}
-In Figure~\ref{fig:relax_tuto} \victor{Mettre description}. 
+Figure~\ref{fig:relax_tuto} details the successive steps for the construction of the set $R_{\alpha}$.
+First, the conditional minimisers are computed, as shown on the top plots.
+Afterwards, for a level $\alpha=1.5$ and for all $\mathbf{u} \in \Uspace$, the acceptable $\mathbf{k}$ are identified, as shown on the bottom left plot.
+Finally, the region $R_{\alpha}(\mathbf{k})$ is the set of $\mathbf{u}$ for which $\mathbf{k}$ is acceptable, as represented with a vertical slice on the bottom right plot.
+
 % This notion of acceptability will be introduced later.
@@
 \includegraphics[width=12cm]{Figures/relaxation_tuto.pdf}
-\caption{Principle of the relaxation of the constraint on $J_{\mathrm{BHswap}}$, and illustration of $R_\alpha(\mathbf{k})$. Top plots: mieux décrire}
+\caption{Principle of the relaxation of the constraint on $J_{\mathrm{BHswap}}$, and illustration of $R_\alpha(\mathbf{k})$.
+Top plots: Computation of the conditional minimisers $\mathbf{k}^*(\mathbf{u})$.
+Top right plot: the set $(\mathbf{k}^*(\mathbf{u}),\mathbf{u})$ of conditional minimisers is represented in red.
+On the bottom left plot, for a relaxation $\alpha=1.5$, and $\mathbf{u}=3$, the acceptable $\mathbf{k}$ are in cyan, while the non-acceptable ones are in orange, while the frontier $\{(\mathbf{k}^*(\mathbf{u}),\mathbf{u}) \mid J^*(\mathbf{u}) = J(\mathbf{k},\mathbf{u})\}$ is in yellow.
+On the bottom right plot, the set $R_{\alpha}(\mathbf{k})$ for $\alpha=1.5$ and $\mathbf{k}=1.5$ is in green.}
 \label{fig:relax_tuto}
@@
 Noting that without relaxation, \textit{i.e.} when $\alpha$ is set to $1$, $\Gamma_1$ is non-zero if the set $\{\mathbf{u}\in\Uspace \mid J(\mathbf{k},\mathbf{u}) = J^*(\mathbf{u})\}$ has non-zero measure with respect to $\Prob_{\mathbf{U}}$.
-It happens when the distribution of $\mathbf{K}^*$ presents atoms \victor{?}.
-This can be linked to the definition of the MPE from Eq.~\eqref{eq:MPE}.
-In the more general case, the MPE can be seen as the limiting case when $\alpha$ tends to $1$.
+It happens when the distribution of $\mathbf{K}^*$ presents atoms.
+
+This can be linked to the definition of the distribution of the minimisers $\mathbf{K}^*$.
+For instance, if $\Kspace$ has a discrete support, we can rewrite $\Gamma_1$ as $\Gamma_1(\mathbf{k})=\Prob_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{u}) = J^*(\mathbf{U})\right] = \Prob_{\mathbf{U}}\left[\mathbf{k} = \mathbf{k}^*(\mathbf{U})\right]$ which is the probability mass function of $\mathbf{K}^*$.
 
@@
 that is the smallest $\alpha$, such that there exists a particular $\checkkp \in \Kspace$ for which $J(\checkkp,\mathbf{U}) \leq \checkap J^*(\mathbf{U})$ with probability $p$.
+$\{\mathbf{k}_p \text{ for } p \in [0;1] \}$ defines the relative-regret family of robust estimators (\RRE).
 This formulation can be linked to the quantiles and Value-at-Risk of the random variable $\max_{\mathbf{k}} \{ \frac{J(\mathbf{k},\mathbf{U})}{J^*(\mathbf{U})}\}$, that is a measure of risk usually applied in the financial sector (see~\cite{rockafellar_deviation_2002}).
@@
 \includegraphics[width = 8.3cm]{Figures/illu_alpha_p.pdf}
-\caption{Illustration of the influence of different levels $p$ on $\Gamma_{\alpha_p}$ and on $\mathbf{k}_p$ \victor{Pertinence ?}}
+\caption{Illustration of the influence of different levels $p$ on $\Gamma_{\alpha_p}$ and on $\mathbf{k}_p$}
 \label{fig:illu_alpha_p}
@@
 This alternative definition of $\checka_1$ is useful to estimate it quickly whenever a grid over $\mathbb{K}\times\mathbb{U}$ has already been evaluated, thus avoiding multiple computations of $\Gamma_{\alpha}(\mathbf{k})$ until its maximum reaches $1$.
-From Eq.\eqref{eq:upper_bound_alpha_check}, choosing a level of confidence equal to $1$ is then equivalent to looking for the worst-case scenario of the ratio $\frac{J(\mathbf{k},\mathbf{u})}{J^*(\mathbf{u})}$.
+From Eq.~\eqref{eq:upper_bound_alpha_check}, choosing a level of confidence equal to $1$ is then equivalent to looking for the worst-case scenario of the ratio $\frac{J(\mathbf{k},\mathbf{u})}{J^*(\mathbf{u})}$.
 Therefore it may suffer from the same pitfall as the worst-case approach.
@@
 
-$\checkap$ can be an indicator of the robustness of $\ckeckkp$.  
+$\checkap$ can be an indicator of the robustness of $\checkkp$.  
 A high value of $\checka_1$ corresponds to a high ratio $\frac{J(\mathbf{k},\mathbf{u})}{J^*(\mathbf{u})}$ for at least one particular $\mathbf{u}$.
@@
 
-\subsection{Concurrence between $p$ and $\alpha$}%Finding a balance between $p$ and $\checkap$}%Selection of a level of confidence}
+\subsection{Choosing the relaxation coefficient}%Finding a balance between $p$ and $\checkap$}%Selection of a level of confidence}
 \label{ssec:balance}
-For a practical purpose, we suppose that we have sampled $N$ values of $\mathbf{U}$, namely $\{\mathbf{u}^i\}_{1\leq i \leq N}$.
-In order to estimate the quantities introduced above, there are two starting points: either fixing $p$ or fixing the maximal threshold $\alpha$. 
-The most trivial way is to set $\alpha$, to find the couples of points $(\mathbf{k},\mathbf{u})$ verifying $J(\mathbf{k},\mathbf{u}) \leq \alpha J^*(\mathbf{u})$, and then to estimate the probability $\Gamma_{\alpha}(\mathbf{k})$ defined in Eq.~\eqref{eq:def_Ralpha} as
+
+In order to choose the quantities introduced above, there are three choices: either fixing $p$, either fixing the maximal threshold $\alpha$, or looking for a compromise between $p$ and $\alpha$.
+The most trivial way is to set $\alpha$, to find the couples of points $(\mathbf{k},\mathbf{u})$ verifying $J(\mathbf{k},\mathbf{u}) \leq \alpha J^*(\mathbf{u})$, and then to estimate the probability $\Gamma_{\alpha}(\mathbf{k})$ defined in Eq.~\eqref{eq:def_Ralpha}.
+For instance, when $N$ sampled values of $\mathbf{U}$: $\{\mathbf{u}^i\}_{1\leq i \leq N}$ are available, a possible estimator of $\Gamma_{\alpha}$ is
 \begin{equation}
@@
 \end{equation}
-If $\alpha$ is chosen too small, the resulting $\hat{p}=\max_{\mathbf{k}} \hat{\Gamma}_{\alpha}(\mathbf{k})$ will be also too small, meaning that the cost function will overshoot the value $\alpha J^*(\mathbf{U})$ with high probability.
-
-Similarly, if $p$ is fixed, the corresponding $\hat{\checka}_p$ is computed by searching for the smallest $\alpha$ such that $\max_{\mathbf{k}} \hat{\Gamma}_{\alpha}(\mathbf{k})$ is equal to the level $p$ fixed beforehand.
-In the end, if the value $\hat{\checka}_p$ is too large, the relaxation needed to get acceptable values with probability $p$ is very high, so the resulting estimation $\hat{\checkk}_p$ may not be relevant for the future application.
+However, this may be a risky approach.
+Indeed if $\alpha$ is chosen too small, the resulting $\hat{p}=\max_{\mathbf{k}} \hat{\Gamma}_{\alpha}(\mathbf{k})$ will be also small, meaning that the cost function will overshoot the value $\alpha J^*(\mathbf{U})$ with high probability.
+
+Similarly, if $p$ is fixed, the corresponding $\hat{\checka}_p$ is computed by searching for the smallest $\alpha$ satisfying $\max_{\mathbf{k}} \hat{\Gamma}_{\alpha}(\mathbf{k})=p$.
+Once again, if the value $\hat{\checka}_p$ is too large, the relaxation needed to get acceptable values with probability $p$ is very high, so the resulting estimation $\hat{\checkk}_p$ may not be relevant for the future application.
 % \victor{chapeau car ici je parle de l'estimation en pratique}
 
-Without posing any constraints on $p$ nor on $\alpha$, a compromise between $p$ and $\alpha$ would be preferable, and a rough idea of this balance can be obtained by studying $p \mapsto \checkap$, and particularly its slope.
+Looking for a compromise between $p$ and $\alpha$ would be preferable. This could be achieved by studying $p \mapsto \checkap$, and particularly its slope.
 If this curve presents a steep increase, the multiplicative constant $\checkap$ must be increased by a large amount in order to increase the probability $p$ by a small amount.
@@
 
-Another possibility is to combine directly $p$ and $\checkap$ in order to find a compromise.
-We opted to model this compromise by the ratio $(p/\checkap)$, as it increases with respect to $p$ and decreases with respect to $\checka_p$.
+Another possibility is to to model this compromise by the ratio $(p/\checkap)$, as it increases with respect to $p$ and decreases with respect to $\checka_p$.
 The level of confidence $p_{\mathrm{ratio}}$ is then defined as the maximiser of $p\mapsto p / \checka_p$.
 
-The different estimators introduced in this paper are summarised in Table~\ref{tab:RO_recap}.
+% We are now going to compute and compare those estimators on the $J_{\mathrm{BH}}$and $J_{\mathrm{BHswap}}$ function.
+
+% ----------------------------------------------------------------------------
+\subsection{Numerical Illustration}
+% Numerical application}
+\victor{Paragraphe introductif pour comparer, et renvoyer à Table1}
+In this Section, we will compare the different estimators introduced in this paper as summarised Table~\ref{tab:RO_recap}.
 
@@
 
-% We are now going to compute and compare those estimators on the $J_{\mathrm{BH}}$and $J_{\mathrm{BHswap}}$ function.
-
-% ----------------------------------------------------------------------------
-\subsection{Estimation of $\checkkp$ and $\checkap$ for the $J_{\mathrm{BH}}$ and $J_{\mathrm{BHswap}}$ functions}
-%Numerical application}
 As stated before, we chose to model the uncertainties as a random variable uniformly distributed on $\Uspace$.
-The bounded nature of $\Uspace$ allow us to consider the estimate introduced before up to a level of confidence $p=1$.
+The bounded nature of $\Uspace$ allows us to consider the estimators introduced before up to a level of confidence $p=1$.
 From now on, $\hatkmpe$ is estimated using KDE with Gaussian kernels.
@@
 The contour plots of those functions can be seen in the top plots of Figure~\ref{fig:contour_alpha}.
-The frontier corresponding to the couples of points $(\mathbf{k},\mathbf{u})$ verifying $\{J(\mathbf{k},\mathbf{u}) = \alpha J^*(\mathbf{u})\}$ has been drawn on top of these contour plots, for $\alpha=\hat{\checka}_1$ and an arbitrary $\alpha=1.5<\hat{\checka}_1$, to illustrate the effect of the acceptable region when the relaxation $\alpha$ increases.
-On the bottom plots, the curves $\mathbf{k}\mapsto \hat{\Gamma}_{\alpha}(\mathbf{k})$ for $\alpha=\hat{\checka}_1$ and $\alpha=1.5$ along with the histogram of the minimisers are represented.
+The frontier corresponding to the couples of points $(\mathbf{k},\mathbf{u})$ verifying $\{J(\mathbf{k},\mathbf{u}) = \alpha J^*(\mathbf{u})\}$ has been drawn on top of these contour plots, for $\alpha=\hat{\checka}_1$ and an arbitrary $\alpha=1.5<\hat{\checka}_1$, to illustrate the effect of the acceptable region when the relaxation $\alpha$ changes.
+On the bottom plots, the curves $\mathbf{k}\mapsto \hat{\Gamma}_{\alpha}(\mathbf{k})$ for $\alpha=\hat{\checka}_1$ and $\alpha=1.5$ along with the histograms of the minimisers are represented.
 
@@
 
-In order to choose a satisfying level of confidence $p$, we are going to study $p\mapsto \hat{\checka}_p$ and $p\mapsto p/\hat{\checka}_p$, as described in~\ref{ssec:balance}.
-
- The plot of $p\mapsto \hat{\checka}_p$ for the $J_{\mathrm{BH}}$ function on Figure~\ref{fig:ratio_BH} shows what seems to be a piecewise linear behaviour.
-The last change of slope, i.e.\ for $p\approx 0.9$ corresponds to a local maximum of the ratio, while the first change of slope corresponds to the global maximum of the ratio.
+In order to choose a satisfying level of confidence $p$, we are going to study $p\mapsto \hat{\checka}_p$ and $p\mapsto p/\hat{\checka}_p$, as described in Section~\ref{ssec:balance}.
+
+ The plot of $p\mapsto \hat{\checka}_p$ for $J_{\mathrm{BH}}$ on Figure~\ref{fig:ratio_BH} shows what seems to be a piecewise linear behaviour.
+The last change of slope, \textit{i.e.} for $p\approx 0.9$ corresponds to a local maximum of the ratio, while the first change of slope at $\hat{p}_{\mathrm{ratio}}=0.654$ corresponds to the global maximum of the ratio.
+The \RRE{} will then be evaluated for both these values, as well as $1$ for reference.
 
@@
 \includegraphics[width=10cm]{Figures/alpha_p_BH.pdf}
-\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for the $J_{\mathrm{BH}}$ function. The dashed line indicates the level $p$ associated with the highest ratio}
+\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $J_{\mathrm{BH}}$.
+The dashed line indicates the level $p$ associated with the highest ratio \victor{Mettre p=0.9}}
 \label{fig:ratio_BH}
@@
 
- For the $J_{\mathrm{BH}}$ function, the numerical values can be found in Table~\ref{tab:recap_estimates_branin}. For this particular problem, the different estimates are close to each other.
-
-\begin{table*}[!ht]
+ For $J_{\mathrm{BH}}$, the numerical values of the robust estimators can be found in Table~\ref{tab:recap_estimates_branin}. For this particular problem, different estimates are close to each other.
+
+% \begin{table*}[!ht]
+% \centering
+% \caption{Estimation performed for $J_{\mathrm{BH}}$, sorted by value}
+% \label{tab:recap_estimates_branin}
+% \begin{tabular}{lr}
+% \toprule
+% Estimate & Value \\ \midrule
+% $\hatkvar$ & 1.371 \\ 
+% $\kest_p,~p=1$ & 1.557 \\ 
+% $\hatkmean$ & 1.587 \\ 
+%   $\hatkmpe$ & 1.628 \\
+%   $\kest_{\mathrm{ratio}},~\hat{p}_{\mathrm{ratio}}=0.654$ & 1.637 \\
+% $\kest_p,~p=0.95$ & 1.672 \\ \bottomrule
+% \end{tabular}
+% \end{table*}
+\begin{table*}[!h]
   \centering
 \caption{Estimation performed for $J_{\mathrm{BH}}$, sorted by value}
-\label{tab:recap_estimates_branin}
 \begin{tabular}{lr}
   \toprule
-Estimate & Value \\ \midrule
+Estimator & Value \\ \midrule
 $\hatkvar$ & 1.371 \\ 
-$\kest_p,~p=1$ & 1.557 \\ 
+$\kest_{p},~p=1$ & 1.557 \\ 
 $\hatkmean$ & 1.587 \\ 
-  $\hatkmpe$ & 1.628 \\
+$\kest_{\mathrm{MPE}}$ & 1.628 \\ 
 $\kest_{\mathrm{ratio}},~\hat{p}_{\mathrm{ratio}}=0.654$ & 1.637 \\ 
-$\kest_p,~p=0.95$ & 1.672 \\ \bottomrule
+$\kest_p,~p=0.90$ & 1.797 \\  \bottomrule
 \end{tabular}
+\label{tab:recap_estimates_branin}
 \end{table*}
-
-Practically speaking, in order to compare the effective values taken by the objective function given an estimate $\kest$ we are going to consider the functions of the form $\mathbf{u} \mapsto J(\kest,\mathbf{u})$, that we will call ``profile of $\kest$''.
+Practically speaking, in order to compare the effective values taken by the objective function given an estimate $\kest$ we are going to consider the functions $\mathbf{u} \mapsto J(\kest,\mathbf{u})$, that we will call ``profile of $\kest$''.
 Those profiles are well suited for the representation of the cost function for an estimate $\kest$ fixed as the uncertain variable is modelled with a 1D uniform random variable.
 
-For the $J_{\mathrm{BH}}$ function, the curves are plotted in Figure~\ref{fig:profiles_branin}.
-Based on its definition, the profile of $\hat{\checkk}_1$ is always within the shaded region, corresponding to $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$.
-The profile of $\hatkmean$ in contrast, exceeds $\hat{\checka}_1 J^*(\mathbf{u})$ for $\mathbf{u}$ close to $5$, while the profile of $\hatkvar$ does for $\mathbf{u}$ close to $0$.
-As the different $\kest$ are very close for every criteria introduced in this paper, the profiles are almost undistinguishable.
+For $J_{\mathrm{BH}}$, the curves are plotted in Figure~\ref{fig:profiles_branin}.
+By construction, the profile of $\hat{\checkk}_1$ is always within the shaded region, corresponding to $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$.
+The profile of $\hatkmean$ in contrast, exceeds $\hat{\checka}_1 J^*(\mathbf{u})$ for $\mathbf{u}$ close to $5$, while the profile of $\hatkvar$ does it for $\mathbf{u}$ close to $0$.
+Except for $\hatkvar$, the different estimators give somewhat comparable results.
 
@@
   \centering
-\includegraphics[width=10cm]{Figures/profile_BH_all_estimates_noku.pdf}
-\caption{Profiles of the different estimates for the $J_{\mathrm{BH}}$ function, corresponding to the vertical cross sections of the contour.
+\includegraphics[width=10cm]{Figures/profile_BH.pdf}
+\caption{Profiles of the different estimates for $J_{\mathrm{BH}}$, corresponding to the vertical cross sections of the contour.
 The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$.
-The red dashed line, corresponding to the values taken by the cost function when the control variable is set to $\mathbf{k}_1$, is always between $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$ per design.}
+The profiles of $\kest_{\mathrm{MPE}}$ and $\kest_{\mathrm{ratio}}$ coincide in this case}
 \label{fig:profiles_branin}
 \end{figure*}
-
-We are now going to shift our focus on the $J_{\mathrm{BHswap}}$ function, as Figure~\ref{fig:ratio_BHs} provides the plots of $p\mapsto \hat{\checka}_p$ and $p\mapsto p/\hat{\checka}_p$.
+By contrast, $\JBHS$ will show a different behaviour as Figure~\ref{fig:ratio_BHs} provides the plots of $p\mapsto \hat{\checka}_p$ and $p\mapsto p/\hat{\checka}_p$.
+
 \begin{figure}[ht]
@@
 \includegraphics[width=10cm]{Figures/alpha_p_BHs.pdf}
-\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for the $J_{\mathrm{BHswap}}$ function. The dashed line indicates the level $p$ associated with the highest ratio}
+\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $J_{\mathrm{BHswap}}$. The dashed line indicates the level $p$ associated with the highest ratio}
 \label{fig:ratio_BHs}
@@
 
-Compared to the plots for $J_{\mathrm{BH}}$ in Figure~\ref{fig:ratio_BH}, $\hat{\checka}_p$ exhibits a smoother behaviour for the $J_{\mathrm{BHswap}}$ function as no change of slope is easily discernable.
-The computation of the ratio advocates for a level of confidence $p_{\mathrm{ratio}}$ close to $0.75$.
-The numerical values of the estimations $\kest$ presented in Table~\ref{tab:recap_estimates_BHs} show that contrary to the $J_{\mathrm{BH}}$ function, the calibrated values are more spread on $\Kspace$.
+Compared to the similar plots for $J_{\mathrm{BH}}$ in Figure~\ref{fig:ratio_BH}, $\hat{\checka}_p$ exhibits a smoother behaviour for $\JBHS$ as no abrupt change of slope is easily discernable and the ratio presents a unique maximum for $\hat{p}_{\mathrm{ratio}}=0.766$.
+The numerical values of the estimations $\kest$ presented in Table~\ref{tab:recap_estimates_BHs} show that contrary to $J_{\mathrm{BH}}$, the calibrated values are more spread over $\Kspace$.
 
@@
 $\hatkmean$ & 1.752 \\ 
-$\kest_p,~p=0.90$ & 2.112 \\ 
-$\kest_p,~p=0.95$ & 2.457 \\ 
 $\hatkvar$ & 2.638 \\ 
@@
 
-In a similar fashion, the profiles of the different estimates for the $J_{\mathrm{BHswap}}$ function are shown in Figure~\ref{fig:profiles_branin_switch}.
+Profiles of the different estimates of $J_{\mathrm{BHswap}}$ are shown in Figure~\ref{fig:profiles_branin_switch}.
 
@@
   \centering
-\includegraphics[width=10cm]{Figures/profile_BHs_all_estimates_noku.pdf}
-\caption{Profiles of the different estimates for the $J_{\mathrm{BHswap}}$ function.
+\includegraphics[width=10cm]{Figures/profile_BHs.pdf}
+\caption{Profiles of the different estimates for $J_{\mathrm{BHswap}}$.
 Those profiles are the vertical cross sections of the contours above.
-The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$.
-The red dashed line, corresponding to the values taken by the cost function when the control variable is set to $\mathbf{k}_1$, is always between $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$ per design.}
+The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$}
 \label{fig:profiles_branin_switch}
 \end{figure*}
+
+\victor{Rajouter cas U loi normale}
 

### 2019-12-09 article.tex
SWE application

@@
 Moreover, such uncertainties may be of different nature. 
-~\cite{walker_defining_2003} proposes to consider two categories of uncertainties.
+\cite{walker_defining_2003} proposes to consider two categories of uncertainties.
 On the one hand aleatoric uncertainties,  coming from the inherent variability of a phenomenon, e.g.\ intrinsic randomness of some environmental variables.
@@
 
-\victor{Rajouter cas U loi normale}
+Let us consider the following simple problem:
+\begin{equation}
+  \label{eq:Jinfinite}
+  J(\mathbf{k},\mathbf{u}) = u(\mathbf{k}-\mathbf{u})^2 + 1
+\end{equation}
 
@@
 \subsection{Calibration of a toy numerical model}
- We will follow \citeauthor{kennedy_bayesian_2001}'s approach in order to establish the function $\mathcal{G}$ described in the first section in Eq.~\eqref{eq:def_cost_fun}, and the resulting cost function $J$.
-
- Calibration of a numerical model is usually based on the comparison between the numerical model and some observations in a fixed time interval $[0, T]$ called assimilation window.
-The physical system at stake is based on an input $\mathbf{u} \in \Uspace$, that represents some operating conditions.
-This system can then be seen as a map from $\Uspace$ to $\mathcal{Y}$, denoted as $\mathcal{M}^o : \mathbf{u}\mapsto \mathcal{M}^o(\mathbf{u})$.
-
-In addition to the operating conditions $\mathbf{u}$, the numerical model is also dependent on some other input $\mathbf{k}\in\Kspace$.
-This additional parametrization comes usually from the successive simplifications needed to implement a numerical model of the physical system observed, and from some unobserved physical parameters.
+ We will follow the approach described in~\cite{kennedy_bayesian_2001} in order to establish the function $\mathcal{G}$ described in the first section in Eq.~\eqref{eq:def_cost_fun}, and the resulting cost function $J$.
+
+ The calibration of a numerical model is usually based on the comparison between the numerical model and some observations, during a fixed time interval $[0, T]$ called assimilation window.
+ The physical system modelled can be seen as a map from $\Uspace$ to $\mathcal{Y}$, denoted as $\mathcal{M}^o : \mathbf{u}\mapsto \mathcal{M}^o(\mathbf{u})$, where $\mathbf{u}\in\Uspace$ is an input representing some environmental conditions.
+The observation mentioned above is the output of the physical system during the time-window, and is denoted by $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) \in \mathcal{Y}$, where $\mathbf{u}^{\mathrm{true}} \in \Uspace$ is unknown.
+
+The numerical model is dependent on some other input $\mathbf{k}\in\Kspace$, in addition to $\mathbf{u}$.
+This additional parametrization comes usually from the successive simplifications and parametrizations needed to implement a numerical model of the physical system observed.
 These parameters need to be calibrated accordingly, so that the numerical model can be used to predict the behaviour of the physical system under different operating conditions.
 
-The true value taken by the physical system during this window is denoted by $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) \in \mathcal{Y}$, where $\mathbf{u}^{\mathrm{true}} \in \Uspace$ is unknown.
-The misfit $\mathcal{G}$ and the cost function $J$ defined Eq.\eqref{eq:def_cost_fun} can then be defined as
+The misfit $\mathcal{G}$ is defined as the difference between the numerical model and the observation. Choosing a squared norm, the cost function $J$ defined in Eq.~\eqref{eq:def_cost_fun} is
 \begin{equation}
@@
 
-The model we wish to calibrate is based on the Shallow Water equations, described Eq.~\eqref{eq:SWE_equations}.
-$h$ is the height of the water column, $q$ is the discharge, and $z$ is the bathymetry, while $g$ is the usual gravitation constant.
+The model to calibrate is an implementation of the Shallow Water equations, described Eq.~\eqref{eq:SWE_equations}, where $h$ is the height of the water column, $q$ is the discharge, and $z$ is the bathymetry, while $g$ is the usual gravitation constant.
 The parameter to calibrate, $\mathbf{k}$, is the quadratic friction term, proportional to the square of the inverse of Manning-Strickler coefficient.
@@
 In this setting, the variable input is uniformly distributed on $\Uspace$.
-To generate the observations, we choose $\mathbf{u}^{\mathrm{true}}=2/3$, and define $\mathcal{M}^o$ based on the computer model $\mathcal{M}$, such that $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) = \mathcal{M}(\mathbf{k}^{\mathrm{true}}, \mathbf{u}^{\mathrm{true}}; \, \omega_0 = 0.999)$.
+
+To generate the observation, we choose $\mathbf{u}^{\mathrm{true}}=2/3$, and define $\mathcal{M}^o$ based on the computer model $\mathcal{M}$, such that $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) = \mathcal{M}(\mathbf{k}^{\mathrm{true}}, \mathbf{u}^{\mathrm{true}}; \, \omega_0 = 0.999)$.
 $\omega_0$
 represents here the uncontrollable error between the observations and the numerical model and will now be omitted systematically in the notation.
+
 The true value of the bottom friction $\mathbf{k}^{\mathrm{true}} = (k_1^{\mathrm{true}}, k_2^{\mathrm{true}},\dots, k_{N_\mathrm{vol}}^{\mathrm{true}})$ is not constant over the whole domain, and is defined as
@@
 \end{equation*}
-where $x_i$ is the center of the $i$-th volume.
-The two sources of representativity errors are $\omega_0$, and the fact that we are looking to estimate $\mathbf{k}$ in a 1-dimensional space $\Kspace$.
-\subsection{Estimation}
-Given that the numerical model is expensive to evaluate, it has first been evaluated on a relatively small regular grid.
-A metamodel based on Gaussian process is constructed and the PEI criterion~\citep{ginsbourger_bayesian_2014,bossek_learning_2015} allow us to add point to evaluate and to better capture the locus of the conditional minimisers $\{(\mathbf{k}^*(\mathbf{u}), \mathbf{u}) \mid \mathbf{u} \in \Uspace \}$.
+where $x_i$ is the center of the $i$-th volume. The two sources of systematic errors are the one-dimensionality of $\Kspace$, and $\omega_0$..
+Given this setting, there exists no couple $(\mathbf{k},\mathbf{u})\in\Kspace \times \Uspace$ reproducing exactly the observations, thus the cost function will always be strictly positive.
+\subsection{Computation of the robust estimates}
+As the numerical model is expensive to evaluate, it has first been evaluated on a relatively small regular grid.
+A metamodel based on Gaussian process is constructed used the initial evaluations and the PEI criterion~\citep{ginsbourger_bayesian_2014,bossek_learning_2015} allows us to add points to the design, in order to better capture the locus of the conditional minimisers $\{(\mathbf{k}^*(\mathbf{u}), \mathbf{u}) \mid \mathbf{u} \in \Uspace \}$.
 A bigger regular grid is evaluated by the metamodel once the design space has been sufficiently explored.
-The different steps of the estimation are illustrated Figure~\ref{fig:estimation_swe}.
+The different steps of the estimation are illustrated Figure~\ref{fig:estimation_swe}: where the top plot shows the contour plot of $J$, with the conditional minimisers and the \RRE{} of level $p$.
+On the middle plot is shown the conditional moments, $\hatkmean$ and $\hatkvar$ and the estimated density of the minimisers.
+At the bottom of the Figure, $\hat{\Gamma}_{\alpha_p}$ are represented for different levels $p$.
+
 We can see that the estimation for this problem seems less problematic than the analytical examples shown above, as all derived quantites are unimodal.
@@
 As a basis for comparison, the global minimiser of $J$ over $\Kspace \times \Uspace$ has been computed, and $\kest_{\mathrm{global}}$ is then obtained by discarding the $\mathbf{u}$ value.
-
-As discussed earlier, the estimation of the MPE is dependent on the method used, and then its estimation using KDE in the middle plot of Figure~\ref{fig:estimation_swe} is here only for illustrative purposes.
 
@@
 \section*{Conclusion}  
-\victor{À faire à la fin}
-This paper deals with the problem of robust calibration of a computer code in the presence of uncertain inputs.
-
-Our contribution consists in introducing a new criterion of robustness, based on the distribution of the minimisers.
+% \victor{À faire à la fin}
+% This paper deals with the problem of robust calibration of a computer code in the presence of uncertain inputs.
+
+% Our contribution consists in introducing a new criterion of robustness, based on the distribution of the minimisers.
 More specifically, this estimate is bounding the ratio between the cost function and its conditional minimum.
-Experimental results show that this new estimate is able to make a compromise between the minimum of the expected value and the minimum of the variance, will also giving the range of the ratio evoked above.
-
-From a practical perspective, this estimation is very expensive: each evaluation of $\mathbf{k}^*$ requires an optimisation procedure.
+% Experimental results show that this new estimate is able to make a compromise between the minimum of the expected value and the minimum of the variance, will also giving the range of the ratio evoked above.
+
+% From a practical perspective, this estimation is very expensive: each evaluation of $\mathbf{k}^*$ requires an optimisation procedure.
 The distribution of the conditional minimisers is then very complicated to compute.
-In addition to that, in order to relax the constraint, the cost function must also be evaluated in the vicinity of the conditional minimisers.
+% In addition to that, in order to relax the constraint, the cost function must also be evaluated in the vicinity of the conditional minimisers.
 Computing precisely this estimate is then intractable if each run of the underlying model is expensive (longer than a couple of seconds).
 
-A solution to explore is the use of surrogate models. Based on an initial design of experiment, the (expensive) cost function is replaced by a function, that is cheap to evaluate.
-For instance,~\cite{ginsbourger_bayesian_2014}
-uses Gaussian Process regression and sequential methods to explore the conditional minimisers.
-
-Finally, the adaptibility of this method has to be studied in a higher dimensional setting.
+% A solution to explore is the use of surrogate models. Based on an initial design of experiment, the (expensive) cost function is replaced by a function, that is cheap to evaluate.
+% For instance,~\cite{ginsbourger_bayesian_2014}
+% uses Gaussian Process regression and sequential methods to explore the conditional minimisers.
+
+% Finally, the adaptibility of this method has to be studied in a higher dimensional setting.
 High-dimensional density estimation is a challenge in itself, but is necessary in order to tackle more realistic applications.

### 2019-12-10 article.tex
forecasts, alpha_p and ratio

@@
 The intention is that a robust estimate provides values of the cost function close enough to the attainable minimum for each configuration induced by $\mathbf{u}\in\Uspace$.
-Illustration of the various discribed methods are given on a numerical exemple in Section~\ref{sec:SWE_application}.
+Illustration of the various described methods are given on a numerical exemple in Section~\ref{sec:SWE_application}.
 
@@
  The calibration of a numerical model is usually based on the comparison between the numerical model and some observations, during a fixed time interval $[0, T]$ called assimilation window.
- The physical system modelled can be seen as a map from $\Uspace$ to $\mathcal{Y}$, denoted as $\mathcal{M}^o : \mathbf{u}\mapsto \mathcal{M}^o(\mathbf{u})$, where $\mathbf{u}\in\Uspace$ is an input representing some environmental conditions.
-The observation mentioned above is the output of the physical system during the time-window, and is denoted by $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) \in \mathcal{Y}$, where $\mathbf{u}^{\mathrm{true}} \in \Uspace$ is unknown.
-
-The numerical model is dependent on some other input $\mathbf{k}\in\Kspace$, in addition to $\mathbf{u}$.
+ The physical system modelled can be seen as a map from $\Uspace$ to $\mathbb{Y}$, the space of observations, denoted as $\mathcal{M}^o : \mathbf{u}\mapsto \mathcal{M}^o(\mathbf{u})$, where $\mathbf{u}\in\Uspace$ is an input representing some environmental conditions.
+The observation mentioned above is the output of the physical system during the time-window, and is denoted by $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) \in \mathbb{Y}$, where $\mathbf{u}^{\mathrm{true}} \in \Uspace$ is unknown.
+
+The numerical model $\mathcal{M}$ is dependent, in addition to $\mathbf{u}$ on some other input $\mathbf{k}\in\Kspace$.
 This additional parametrization comes usually from the successive simplifications and parametrizations needed to implement a numerical model of the physical system observed.
@@
 
-The model to calibrate is an implementation of the Shallow Water equations, described Eq.~\eqref{eq:SWE_equations}, where $h$ is the height of the water column, $q$ is the discharge, and $z$ is the bathymetry, while $g$ is the usual gravitation constant.
+The model to calibrate is an implementation of the Shallow Water equations, described in Eq.~\eqref{eq:SWE_equations}, where $h$ is the height of the water column, $q$ is the discharge, and $z$ is the bathymetry, while $g$ is the usual gravitation constant.
 The parameter to calibrate, $\mathbf{k}$, is the quadratic friction term, proportional to the square of the inverse of Manning-Strickler coefficient.
@@
 \end{equation*}
-where $x_i$ is the center of the $i$-th volume. The two sources of systematic errors are the one-dimensionality of $\Kspace$, and $\omega_0$..
+where $x_i$ is the center of the $i$-th volume. The two sources of systematic errors are the one-dimensionality of $\Kspace$, and $\omega_0$.
 Given this setting, there exists no couple $(\mathbf{k},\mathbf{u})\in\Kspace \times \Uspace$ reproducing exactly the observations, thus the cost function will always be strictly positive.
@@
 As the numerical model is expensive to evaluate, it has first been evaluated on a relatively small regular grid.
-A metamodel based on Gaussian process is constructed used the initial evaluations and the PEI criterion~\citep{ginsbourger_bayesian_2014,bossek_learning_2015} allows us to add points to the design, in order to better capture the locus of the conditional minimisers $\{(\mathbf{k}^*(\mathbf{u}), \mathbf{u}) \mid \mathbf{u} \in \Uspace \}$.
-A bigger regular grid is evaluated by the metamodel once the design space has been sufficiently explored.
-The different steps of the estimation are illustrated Figure~\ref{fig:estimation_swe}: where the top plot shows the contour plot of $J$, with the conditional minimisers and the \RRE{} of level $p$.
+A metamodel based on Gaussian processes is constructed using the initial evaluations and in order to better capture the locus of the conditional minimisers $\{(\mathbf{k}^*(\mathbf{u}), \mathbf{u}) \mid \mathbf{u} \in \Uspace \}$, the PEI criterion~\citep{ginsbourger_bayesian_2014,bossek_learning_2015} allows us to add points to the design.
+Afterwards, a bigger regular grid is evaluated by the metamodel once the design space has been sufficiently explored.
+The different steps of the estimation are illustrated Figure~\ref{fig:estimation_swe}, where the top plot shows the contour plot of $J$, with the conditional minimisers and the \RRE{} of level $p$.
 On the middle plot is shown the conditional moments, $\hatkmean$ and $\hatkvar$ and the estimated density of the minimisers.
 At the bottom of the Figure, $\hat{\Gamma}_{\alpha_p}$ are represented for different levels $p$.
-
-We can see that the estimation for this problem seems less problematic than the analytical examples shown above, as all derived quantites are unimodal.
-The different estimates however take a wide range of values, as seen on Table~\ref{tab:recap_estimates_metaSWE}.
-As a basis for comparison, the global minimiser of $J$ over $\Kspace \times \Uspace$ has been computed, and $\kest_{\mathrm{global}}$ is then obtained by discarding the $\mathbf{u}$ value.
 
@@
 \end{figure}
+
+We can see that the estimation for this problem seems less problematic than the analytical examples shown above.
+Looking at $p\mapsto \alpha_p$ and $p\mapsto p/\alpha_p$ on Figure~\ref{fig:alpha_p_SWE}, we can see that $\alpha_p$ evolves almost linearly for $p>0.5$, and that the ratio $p/\alpha_p$ is monotonically increasing, so that the maximal ratio is found for $p=1$.
+
+\begin{figure}[!h]
+  \centering
+  \includegraphics[scale=0.5]{Figures/alpha_SWE}
+  \caption{Evolution of $\alpha_p$ for different levels $p$, and ratio}
+\label{fig:alpha_p_SWE}
+\end{figure}
+
+The different estimates take a wide range of values, as seen on Table~\ref{tab:recap_estimates_metaSWE}, from $0.249$ to almost $1.0$, when $k_i^{\mathrm{true}} \in [0, 0.4]$ for $1\leq i \leq N_{\mathrm{vol}}$.
+As a basis for comparison, the global minimiser of $J$ over $\Kspace \times \Uspace$ has been computed, and $\kest_{\mathrm{global}}$ is then obtained by discarding the $\mathbf{u}$ value.
+
 \begin{table*}[!h]
@@
 We can see that the performances of $\kest_1$ and $\hatkmean$ are very similar, but $\kest_1$ has better performances when $\mathbf{u} > 0.6$.
-When comparing with the global optimiser $\kest_{\mathrm{global}}$, $\kest_1$ performs better when $\mathbf{u}<0.625$.
-As $\mathbf{U}$ is uniformly distributed on $\Uspace=[0.5,0.7]$, we can graphically estimate that the probability that $\kest_1$ outperforms $\kest_{\mathrm{global}}$ is greater than $0.5$, that is that $\Prob_\mathbf{U}\left[J(\kest_1,\mathbf{U})<J(\kest_{\mathrm{global}},\mathbf{U})\right] > 0.5$.
-
-The calibration of this numerical model is done in order to get a calibrated value $\kest$, that will be used for forecasts, using the same numerical model.
+When comparing with the global optimiser $\kest_{\mathrm{global}}$, $\kest_1$ performs better when $\mathbf{u}<0.625$, so more than half of the time.
+% As $\mathbf{U}$ is uniformly distributed on $\Uspace=[0.5,0.7]$, we can graphically estimate that the probability that $\kest_1$ outperforms $\kest_{\mathrm{global}}$ is greater than $0.5$, that is that $\Prob_\mathbf{U}\left[J(\kest_1,\mathbf{U})<J(\kest_{\mathrm{global}},\mathbf{U})\right] > 0.5$.
+
+% The calibration of this numerical model is done in order to get a calibrated value $\kest$, that will be used for forecasts, using the same numerical model.
 We are now going to compare how well three of those values compare in a forecast context: $\kest_1$, $\hatkmean$ and $\kest_{\mathrm{global}}$, as the first two refer quite naturally to the notion of robustness, and the latter is an example of an estimate that does not take into account the uncertainties.
@@
 We can see that the mean forecast error squared, on the right side, averaged over time and space is the smallest for the conditional minimisers $\kest^*(0.7)$ and $\kest^*(0.65)$, then $\kest_{\mathrm{global}}$, while $\kest_{1.0}$ performs slightly better $\hatkmean$.
-The range of those performance metrics carry also information on the limited impact of the choice of $\mathbf{k}$ in the calibration.
+
+It may seem surprising that some values calibrated without a robustness aspect perform better than $\kest_1$ and $\hatkmean$, but in fact, not all of those give better results.
+Choosing an arbitrary $\mathbf{u}$ and then taking the associated conditional minimiser can lead to good forecast (for $\mathbf{u}$ close to $0.7$), but also to bad ones (for $\mathbf{u}$ close to $0.5$).
 
@@
 The calibrated parameters that present the best performances for forecasts according to those two metrics are $\kest^*(0.7)$, $\kest^*(0.65)$ which is very similar to $\kest_{\mathrm{global}}$, and then $\kest_1$.
-
-It may seem surprising that the calibrated values chosen according to a robust objective perform worse than the ``deterministic'' objectives $\kest^*(0.7)$, $\kest^*(0.65)$ and $\kest_{\mathrm{global}}$.
+We can draw the same conclusions on the forecast performances of those calibrated values based on the CRPS than on the squared norm: taking an arbitrary $\mathbf{u}$ and using the conditional minimiser has some flaws.
 
@@
 %% TeX file.
+
 \bibliographystyle{elsarticle-num-names} 

### 2019-12-16 article.tex
explainations on forecasts, start ccl

@@
 % \victor{chapeau car ici je parle de l'estimation en pratique}
+Also, choosing $p=1$ is possible only if the sample space of $\mathbf{U}$ is bounded: let us consider the following simple problem
+\begin{align}
+  \label{eq:Jinfinite}
+  \Kspace &= \Uspace = [0,\,+\infty[ \\
+  J(\mathbf{k},\mathbf{u}) &= \mathbf{u}(\mathbf{k}-\mathbf{u})^2 + 1 \\
+  \mathbf{k}^*(\mathbf{u}) &= \mathbf{u} \\
+  J^*(\mathbf{u}) &= 1
+\end{align}
+In this case, for each $\mathbf{k}\in \Kspace$, $\lim_{\mathbf{u} \rightarrow + \infty} \frac{J(\mathbf{k},\mathbf{u})}{J^*(\mathbf{u})} = + \infty$, so there is no $\mathbf{k}$ such that the ratio $J/J *$ can be bounded, hence $\alpha_1$ does not exist in this case.
 
@@
 
-Another possibility is to to model this compromise by the ratio $(p/\checkap)$, as it increases with respect to $p$ and decreases with respect to $\checka_p$.
+Another possibility is to model this compromise by the ratio $(p/\checkap)$, as it increases with respect to $p$ and decreases with respect to $\checka_p$.
 The level of confidence $p_{\mathrm{ratio}}$ is then defined as the maximiser of $p\mapsto p / \checka_p$.
@@
 \includegraphics[width=10cm]{Figures/alpha_p_BH.pdf}
-\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $J_{\mathrm{BH}}$.
-The dashed line indicates the level $p$ associated with the highest ratio \victor{Mettre p=0.9}}
+\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $J_{\mathrm{BH}}$. The dashed line indicates the level $p$ associated with the highest ratio}
 \label{fig:ratio_BH}
@@
 
- For $J_{\mathrm{BH}}$, the numerical values of the robust estimators can be found in Table~\ref{tab:recap_estimates_branin}. For this particular problem, different estimates are close to each other.
+ For $J_{\mathrm{BH}}$, the numerical values of the robust estimators can be found in Table~\ref{tab:recap_estimates_branin}.
+For this particular problem, the different estimates are close to each other.
 
@@
 
-Let us consider the following simple problem:
-\begin{equation}
-  \label{eq:Jinfinite}
-  J(\mathbf{k},\mathbf{u}) = u(\mathbf{k}-\mathbf{u})^2 + 1
-\end{equation}
-
-% ----------------------------------------------------------------------------
+We have seen how some classical robust estimators and the \RRE{} behave on two different analytical problems.
+Apart from the usual levels of confidence: 95\%, 99\% \dots, one can also settle for a ad-hoc compromise, where $p$ maximizes the ratio $p/\alpha_p$.
+When the sample space of $\mathbf{U}$ is bounded, a conservative solution is to set $p=1$.
+We are now going to see how can robust minimisation is applied on the calibration of a numerical model.
 % ----------------------------------------------------------------------------
@@
 Given this setting, there exists no couple $(\mathbf{k},\mathbf{u})\in\Kspace \times \Uspace$ reproducing exactly the observations, thus the cost function will always be strictly positive.
+
 \subsection{Computation of the robust estimates}
@@
 At the bottom of the Figure, $\hat{\Gamma}_{\alpha_p}$ are represented for different levels $p$.
+As $\Uspace$ is bounded, $p=1$ is attainable, and $\kest_1$ is evaluated.
 
@@
 % The calibration of this numerical model is done in order to get a calibrated value $\kest$, that will be used for forecasts, using the same numerical model.
-We are now going to compare how well three of those values compare in a forecast context: $\kest_1$, $\hatkmean$ and $\kest_{\mathrm{global}}$, as the first two refer quite naturally to the notion of robustness, and the latter is an example of an estimate that does not take into account the uncertainties.
-
+We are now going to compare how well some of those calibrated values compare in a forecast context.
 \subsection{Assessing the quality of the forecast of the calibrated model}
@@
 \end{equation}
-The mean squared forecast error averaged over the whole space and over all the time-steps gives an indication on the overall prediction quality of the prediction given this metric, and are represented on the right plot of Figure~\ref{fig:forecast_squared_error}.
+The mean squared forecast error averaged over the whole space and over all the time-steps gives an indication on the overall prediction quality of the prediction given this metric, and are represented on the right of Figure~\ref{fig:forecast_squared_error}.
 We can see that $\kest_{\mathrm{global}}$ performs slightly better than $\kest_1$, itself performing slightly better than $\hatkmean$.
-Averaging $S(\mathbf{\kest})$ over the time steps between $T$ and $T_{\mathrm{pred}}$, we have an indication on the quality of the forecast in the squared sense depending on the spatial position, as seen on the left plot of Figure~\ref{fig:forecast_squared_error}.
+Averaging $S(\mathbf{\kest})$ over the time steps between $T$ and $T_{\mathrm{pred}}$, we have an indication on the quality of the forecast in the squared sense depending on the spatial position, as seen on the left of Figure~\ref{fig:forecast_squared_error}.
 \begin{figure*}[!h]
 \centering
-\includegraphics[width=.9\textwidth]{Figures/L2_full.pdf}
+\includegraphics[width=.9\textwidth]{Figures/L2_full_rel.pdf}
 \caption{Squared forecast error, depending on the calibrated parameter.
-The left figures show the metric averaged over time, while the right figure show the mean forecast error, averaged over time and space}
+The left figure shows the squared error averaged over time, while the right figure shows the mean forecast error, averaged over time and space}
 \label{fig:forecast_squared_error}
 \end{figure*}
-We can see that the mean forecast error squared, on the right side, averaged over time and space is the smallest for the conditional minimisers $\kest^*(0.7)$ and $\kest^*(0.65)$, then $\kest_{\mathrm{global}}$, while $\kest_{1.0}$ performs slightly better $\hatkmean$.
-
-It may seem surprising that some values calibrated without a robustness aspect perform better than $\kest_1$ and $\hatkmean$, but in fact, not all of those give better results.
-Choosing an arbitrary $\mathbf{u}$ and then taking the associated conditional minimiser can lead to good forecast (for $\mathbf{u}$ close to $0.7$), but also to bad ones (for $\mathbf{u}$ close to $0.5$).
-
+We can see that the mean forecast error squared, on the right side, averaged over time and space is the smallest for the conditional minimisers $\kest^*(0.7)$ and $\kest^*(0.65)$, then $\kest_{\mathrm{global}}$, while $\kest_{1.0}$ performs slightly better than $\hatkmean$.
+
+It may seem surprising that some parameters calibrated without a robustness aspect, so the conditional minimisers, perform better than $\kest_1$ and $\hatkmean$, but their performances are largely dependent on the choice of $\mathbf{u}$ and their associated conditional minimisers.
+This is shown for $\mathbf{u}=0.5$, that leads to bad forecasts.
 One issue with the squared forecast error is that it will penalize strongly the forecasts that present high variability with respect to the environmental conditions.
-
 A way to deal with this is to use another metric, that takes the probabilistic nature of the forecasts into account.
@@
 
+\begin{figure}[!h]
+  \centering
+  \includegraphics[width=.9\textwidth]{Figures/CRPS_full_rel}
+  \caption{CRPS computed for different calibrated parameters. The left figure show the CRPS averaged over time, and the right figure shows the CRPS, averaged over time and space}
+\label{fig:forecast_crps}
+\end{figure}
+
 The left plot of Figure~\ref{fig:forecast_crps} shows the CRPS averaged over time, and the right plot shows the value of the CRPS averaged over time and space.
 The difference between the squared forecast error and the CRPS is apparent when comparing the general trends shared by the different calibrated parameters.
-According to the squared error, the region around $x=4$ is not well predicted, while around $x=8$, the prediction are better.
+According to the squared error, the region around $x=4$ is not well predicted, while around $x=8$, the predictions are better.
 On the other hand, according to the CRPS, the region around $x=8$ provide worse forecasts than the one at $x=4$ and $x=7$.
-
-\begin{figure}[!h]
-  \centering
-  \includegraphics[width=.9\textwidth]{Figures/CRPS_full}
-  \caption{CRPS computed for different calibrated parameters}
-\label{fig:forecast_crps}
-\end{figure}
-The numerical evaluations of the CRPS for different parameters show the same order of performances observed for the squared error.
-The calibrated parameters that present the best performances for forecasts according to those two metrics are $\kest^*(0.7)$, $\kest^*(0.65)$ which is very similar to $\kest_{\mathrm{global}}$, and then $\kest_1$.
-We can draw the same conclusions on the forecast performances of those calibrated values based on the CRPS than on the squared norm: taking an arbitrary $\mathbf{u}$ and using the conditional minimiser has some flaws.
-
-\clearpage
+Given the properties of the two metrics,  we can conclude that the region around $x=4$ presents a lot of variability with respect to $\mathbf{u}$, for both the true model and the numerical one.
+However, for $x \approx 8$, there is a lot less variability, as the low squared error indicates, but probably a higher bias, due to the systematic errors between the truth and the numerical model.
+
+The numerical evaluations of the CRPS for different parameters show the same order of performances observed for the squared error: the calibrated parameters that present the best performances for forecasts according to those two metrics are $\kest^*(0.7)$, $\kest^*(0.65)$ which is very similar to $\kest_{\mathrm{global}}$, and then $\kest_1$, and $\hatkmean$.
+This presupposes to know which $\mathbf{u}$ to choose for the conditional minimisation, thus having a strong insight on the value of the parameters.
 
 \section*{Conclusion}
+In this paper, we dealt with a problem of robust calibration, or in other terms, the robust minimisation of a cost function.
+To adress this issue, we proposed a new set of robust estimators: the family of the \RRE{} (Relative-regret estimators), and compared it in a forecast context to some other robust estimators, for the calibration of the bottom friction of a shallow water model.
+Our approach is based on the will to be as close as possible to the conditional minimiser, with high probability.
+At a level $p$, in addition to the estimation, we have the relaxation coefficient $\alpha_p$ that bounds with probability $p$ the relative error of the cost function, that helps us assess the conservativeness of the proposed estimation.
+
+Except for simple analytical example, the exact evaluation of a member of the \RRE{} is very expensive computer-wise, not to say impossible.
+Some bottlenecks appear: the computations of the conditional minimisers $\mathbf{K}^*$, and the minimum $J^*$, that require very local exploration, and the computations of the probability of
+
+We have to rely on approximations for those estimations. Possible leads are
 % \victor{À faire à la fin}

### 2019-12-18 article.tex
typos and corrections

@@
 
-In this paper, we are going to present how to take into account those uncertainties by defining a notion of robustness based on the distribution of the conditional minimisers and compare it with the minimum in the mean sense, and the minimum of variance.
+In this paper, we are going to present how to take into account those uncertainties by defining a family of calibration objectives based on the notion of relative-regret with respect to the best attainable performance given the uncertainties and compare it with the minimum in the mean sense, and the minimum of variance.
 \end{abstract}
@@
 
-Numerical models are widely used to study or forecast natural phenomenon and improve industrial processes.
-However, by essence models only partially represents reality and sources of uncertainties are ubiquitous (discretisation errors, missing physical processes, poorly known boundary conditions).
+Numerical models are widely used to study or forecast natural phenomena and improve industrial processes.
+However, by essence models only partially represent reality and sources of uncertainties are ubiquitous (discretisation errors, missing physical processes, poorly known boundary conditions).
 %Many physical phenomena are modelled numerically in order to better understand and/or to predict their behaviour.
@@
 On the one hand aleatoric uncertainties,  coming from the inherent variability of a phenomenon, e.g.\ intrinsic randomness of some environmental variables.
-On the other hand, epistemic uncertainties coming from a lack of knowledge about the properties and conditions of the phenomena underlying the behaviour of the system under study.
+On the other hand, epistemic uncertainties coming from a lack of knowledge about the properties and conditions of the phenomenon underlying the behaviour of the system under study.
 The latter can be accounted for through the introduction of ad-hoc correcting terms in the numerical model, that need to be properly estimated.
@@
 is doomed to overfit the data, \emph{e.g} to artificially introduce errors in the controlled parameter to compensate for other sources.
-If such uncertainties are of aleatoric nature, then the parameter estimation is only optimal for the observed situation, and may be very poor in other configurations, phenomenon coined as \textit{localized optimization} in~\cite{huyse_free-form_2001}.
+If such uncertainties are of aleatoric nature, then the parameter estimation is only optimal for the observed situation, and may be very poor in other configurations, phenomenon coined as \textit{localized optimisation} in~\cite{huyse_free-form_2001}.
 %A methodology based on the Hessian matrix has been described in~\cite{ribaud_krigeage_2018-1}.
 %\arthur{L\`A AUSSI UNE REF SERAIT BIENVENUE}. 
-Taking into account aleatoric uncertainties in optimisation problems takes several names, including \textit{robust optimisation}, \textit{robust design} in~\cite{lelievre_consideration_2016}, or \textit{optimization under uncertainties} \citep{petrone_robustness_2011, seshadri_density-matching_2014,cook_horsetail_2018}.
+Taking into account aleatoric uncertainties in optimisation problems takes several names, including \textit{robust optimisation}, \textit{robust design} in~\cite{lelievre_consideration_2016}, or \textit{optimisation under uncertainties} \citep{petrone_robustness_2011, seshadri_density-matching_2014,cook_horsetail_2018}.
 
@@
 
-Let's denote $\mathbf{k} \in \Kspace$ the parameter set to be estimated, to reduce epistemic errors.
+Let's denote $\mathbf{k} \in \Kspace$ the parameter set to be estimated to reduce epistemic errors.
 The aleatoric uncertainties are modelled as a random vector $\mathbf{U}$ whose sample space is $\Uspace$.
@@
 %
-For a practical purpose, we assume that $\forall~ \mathbf{u}$ a realisation of $\mathbf{U}$, finding ${\mathbf{k}}_{\mathbf{u}}$ that minimises the cost function $J(\mathbf{k}, \mathbf{U}=\mathbf{u})$ is a well-posed problem, and that the optimum is unique.
-Additionally, the following assumption are made: the cost function is strictly positive, and $\forall~  \mathbf{k} \in \Kspace$, the random variable $J(\mathbf{k},\mathbf{U})$ has finite first- and second-order moments.
+For a practical purpose, we assume that for every realisation $\mathbf{u}\in\Uspace$ of $\mathbf{U}$, % $\forall~ \mathbf{u}$ a realisation of $\mathbf{U}$
+finding ${\mathbf{k}}_{\mathbf{u}}\in \Kspace$ that minimises the cost function $\mathbf{k}\mapsto J(\mathbf{k}, \mathbf{U}=\mathbf{u})$ is a well-posed problem, and that the optimum is unique.
+Additionally, the following assumptions are made: the cost function is strictly positive, and $\forall~  \mathbf{k} \in \Kspace$, the random variable $J(\mathbf{k},\mathbf{U})$ has finite first- and second-order moments.
 
@@
 As mentioned before, robustness can be understood as satisfactory for a broad range of $\mathbf{u}$, and/or as insensitive as possible to uncertainties encompassed in $\mathbf{U}$.
-Under this definition, one may design classical robust estimators, either by optimising the moments of the cost function; or based on the distribution of its minimisers.
+Under this definition, one may design robust estimators, either by using the moments of the cost function; or by exploiting the distribution of its minimisers.
 
@@
 Even though $\kmean$ is a reasonable choice, there is no guarantee that $J(\kmean, \mathbf{U}=\mathbf{u})$ will not reach catastrophic level for some  $\mathbf{u}$.
-On the other hand, using $\kvar$ will ensure stability of the cost function, but whithout any control of its level of quality.
+On the other hand, using $\kvar$ will ensure stability of the cost function, but without any control of its performance.
+%level of quality.
 %
@@
 %
-Ideally, one would want to have a small mean value, and a small variance as well.
+Ideally, one would want to have a small expectation and a small variance at the same time.
 Multi-objective optimisation is a proper tool to deal with these simultaneous and sometimes concurrent objectives, for exemple by computing the Pareto front of $\left(\mu(\mathbf{k}),\sigma^2(\mathbf{k})\right)$ as done in~\cite{baudoui_optimisation_2012}.
@@
 \subsection{Most probable estimate}
-Let us consider the minimal attainable cost in each configuration brought by $\mathbf{u}$.
-The resulting conditional minimum is denoted as $J^*$:
+Let us consider the minimal cost attainable in each configuration brought by $\mathbf{u}$.
+The resulting conditional minimum is denoted $J^*$:
 \begin{equation}
@@
 If the distribution $p_{\mathbf{K}^*}$ is heavily dominated by a single value, the MPE may be a good candidate for robust control. This is not so obvious in case of a multimodal distribution.
+
 In general, an analytical form of $p_{\mathbf{K}^*}$ is usually impossible to obtain, so an estimation $\hat{p}_{\mathbf{K}^*}$ must be used, and its maximum computed to get the MPE.
-
 Once again, a set of samples  $\{\mathbf{u}^i\}_{i=1\dots N}$ can be used to compute the set $\{\mathbf{k}_{\mathbf{u}^i}\}_{i=1\dots N}$, from which one can 
@@
 
-Despite the fact that those methods are well established, using them in a plug-in approach has some flaws.
+In practice, despite the fact that those methods are well established, using them in a plug-in approach has some flaws.
 One of the basic assumption of density estimation is to assume that $\mathbf{K}^*$ is a continuous random variable, hypothesis that may be violated.
@@
 Using Eq.~\eqref{eq:branin_hoo}, we define the two cost functions on $\Kspace \times \Uspace = [0,5] \times [0,5]$ as:
-\begin{align*} J_{\mathrm{BH}} : (\mathbf{k},\mathbf{u}) \mapsto \mathrm{BH}(\mathbf{k},\mathbf{u}) \\
-J_{\mathrm{BHswap}} : (\mathbf{k},\mathbf{u}) \mapsto \mathrm{BH}(\mathbf{u},\mathbf{k})
+\begin{align*} \JBH : (\mathbf{k},\mathbf{u}) \mapsto \mathrm{BH}(\mathbf{k},\mathbf{u}) \\
+\JBHS : (\mathbf{k},\mathbf{u}) \mapsto \mathrm{BH}(\mathbf{u},\mathbf{k})
 \end{align*}
 %We will continue to use $J$ as a generic notation for the cost function, when its use is not specific to the Branin-Hoo function.
-Even though the functions are quite similar, the asymmetric roles of $\mathbf{k}$ and $\mathbf{u}$ cause different behaviour.
+Even though the functions are quite similar, the asymmetric roles of $\mathbf{k}$ and $\mathbf{u}$ cause different behaviour in the estimations.
 
@@
   \centering
-  \includegraphics[width=12cm]{Figures/branin_side_moments_noscale.pdf}
-  \caption{The left column concerns the $J_{\mathrm{BH}}$ function, while the right one deals with $J_{\mathrm{BHswap}}$.
-Contours of both functions are plotted on the top, and curves of  $\mu(\mathbf{k})$ and $\sigma(\mathbf{k})$ are shown on the bottom (respective scales are note represented).
-Estimates $\hatkmean$ and $\hatkvar$ are plotted with the dashed line.
-} \label{fig:branin_moments}
+  \includegraphics[width=10cm]{Figures/branin_side_moments_noscale.pdf}
+  \caption{The left column concerns $\JBH$, while the right one deals with $\JBHS$.
+Contours of both functions are plotted on the top, and curves of  $\mu(\mathbf{k})$ and $\sigma(\mathbf{k})$ are shown on the bottom (respective scales are not displayed).
+Estimates $\hatkmean$ and $\hatkvar$ are plotted with the dashed line.}
+\label{fig:branin_moments}
 \end{figure*}
@@
 The estimations are %$\mathbf{k}\mapsto \mu(\mathbf{k})$ and $\mathbf{k}\mapsto\sigma(\mathbf{k})$ 
-based on a $1000 \times 1000$ regular grid over $\Kspace\times\Uspace$. Both cost functions are shown on~Figure~\ref{fig:branin_moments}, top row.
-
- The left, respectively right, column stands for $J_{\mathrm{BH}}$, respectively $J_{\mathrm{BHswap}}$ function.
-Functions $\mu(\mathbf{k})$ and $\sigma(\mathbf{k})$ are drawn on the bottom row, respectively in purple and green.
-The corresponding minimizers $\hatkmean$ and $\hatkvar$ are also plotted.
-On this figure, we can observe that $\hatkmean$ and $\hatkvar$ are close for the $J_{\mathrm{BH}}$ function, while being significantly different for the $J_{\mathrm{BHswap}}$ function.
+based on a $1000 \times 1000$ regular grid over $\Kspace\times\Uspace$. Both cost functions are shown on the top of~Figure~\ref{fig:branin_moments}.
+
+The left, (resp.\ right), column stands for $\JBH$ (resp.\ $\JBHS$).
+Functions $\mu(\mathbf{k})$ and $\sigma(\mathbf{k})$ are drawn on the bottom row, respectively in purple and green. The corresponding minimisers $\hatkmean$ and $\hatkvar$ are also plotted.
+On this figure, we can observe that $\hatkmean$ and $\hatkvar$ are close for $\JBH$, while being significantly different for $\JBHS$.
 %\clearpage
 
-Similarly $\hatkmpe$ estimations are depicted on Figure~\ref{fig:contours}.
-Top row shows the contour plot of both functions as well as the set of conditional minimisers $\{\mathbf{k}_{\mathbf{u}^i}\}_{1\leq i \leq N}$ in red, as defined in Eq.~\eqref{eq:conditional_minimiser}.
-The bottom rows presents three approximations of the density of minimisers: the histogram in grey (bin size selected using Freedman-Diaconis from~\cite{freedman_histogram_1981}), the result of a kernel density estimation (KDE) with Gaussian kernels in red (using Scott's rule from~\cite{scott_optimal_1979} for bandwidth selection), and the estimation by a Gaussian mixture.
-The latter has been calculated with the EM algorithm.
+Similarly, estimations of $\hatkmpe$ are depicted on Figure~\ref{fig:contours}.The top row shows the contours of both functions as well as the set of conditional minimisers $\{\mathbf{k}_{\mathbf{u}^i}\}_{1\leq i \leq N}$ in red, as defined in Eq.~\eqref{eq:conditional_minimiser}.
+The bottom row presents three approximations of the density of minimisers: the histogram in grey (bin size selected using Freedman-Diaconis from~\cite{freedman_histogram_1981}), the result of a kernel density estimation (KDE) with Gaussian kernels in red (using Scott's rule from~\cite{scott_optimal_1979} for bandwidth selection), and the estimation by a Gaussian mixture, calculated with the EM algorithm.
 The number of Gaussians has been fixed to 3, a guess based on the general shape of the histogram.
 Respective estimations of $\hatkmpe$ are also depicted using dashed lines.
-
-%The computation of the MPE is more problematic.
-Indeed, an analytical form of the distribution of the minimisers $p_{\mathbf{K}^*}$ is usually impossible to obtain, so an approximation must be used, and its maximum computed to get the MPE.
-%Computationally speaking, to compute a realisation of $\mathbf{K}^*$, a value $\mathbf{u}$ is sampled from $\mathbf{U}$, and a minimisation problem is solved to get $\mathbf{k}^*(\mathbf{u})$.
-Using the grid mentioned before, 1000 realisations of $\mathbf{K}^*$ have been obtained by direct search on grid.
-
-%In this paper, we used two different methods to estimate the distribution of the minimisers: KDE (kernel density estimation)~\citep{parzen_estimation_1962,bishop_pattern_2006} and the EM algorithm~\citep{dempster_maximum_1977,borman_expectation_2004} to fit a mixture of Gaussian distributions.
-This algorithm needing the number of densities to fit, we chose to fit three Gaussian, a guess based on the general shape of the histograms.
-%Figure~\ref{fig:contours} shows the contour plot, conditional mean and conditional minimisers of the $J_{\mathrm{BH}}$ function (left) and the $J_{\mathrm{BHswap}}$ function (right).
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=12cm]{Figures/branin_side_66.pdf}
-  \caption{Top Left:  $J_{\mathrm{BH}}$ function along with conditional minimisers in red.
-Bottom left: Estimated density using KDE and EM algorithm and conditional mean.
+\begin{figure}[!h]
+  \centering
+  \includegraphics[width=10cm]{Figures/branin_side_66.pdf}
+  \caption{Top Left:  $\JBH$ along with conditional minimisers in red.
+Bottom left: Estimated densities using KDE and EM algorithm and the histogram.
 The dashed lines indicate the MPE found using those methods.
-Right: Same quantities with $J_{\mathrm{BHswap}}$.}
+Right: Same quantities with $\JBHS$.}
 \label{fig:contours}
-\end{figure*}
-
-For the $J_{\mathrm{BHswap}}$ function, we can observe that those three methods give consistent results, as $\hatkmpe {}_{,\mathrm{KDE}} =\hatkmpe {}_{,\mathrm{EM}}=\hatkmpe {}_{,\mathrm{histogram}}\approx 0.8$.
-This is not the case for the  $J_{\mathrm{BH}}$ function however.
-Using Kernel density estimation (Gaussian), the estimation of $\kmpe$ is $\hatkmpe {}_{,\mathrm{KDE}} \approx 1.5$, while using the histogram and Gaussian mixture, $\hatkmpe {}_{,\mathrm{histogram}}=\hatkmpe {}_{,\mathrm{EM}}=3.8$.
+\end{figure}
+
+For $\JBHS$, we can observe that those three methods give consistent results, as $\hatkmpe {}_{,\mathrm{KDE}} =\hatkmpe {}_{,\mathrm{EM}}=\hatkmpe {}_{,\mathrm{histogram}}\approx 0.8$.
+This is not the case for $\JBH$: using Kernel density estimation (Gaussian), the estimation of $\kmpe$ is $\hatkmpe {}_{,\mathrm{KDE}} \approx 1.5$, while using the histogram and Gaussian mixture, $\hatkmpe {}_{,\mathrm{histogram}}=\hatkmpe {}_{,\mathrm{EM}}=3.8$.
+
 This difference is explained by the accumulation of minimisers at this point: this challenges the assumption that $\mathbf{K}^*$ is continuous.
@@
 This particular problem highlights an issue with $\kmpe$, as its estimation is possibly sensitive to the density approximation procedure.
-% Alternatively, when considering the mixing coefficients of the EM estimation, the Gaussian centered at $1.5$ has the largest weight, of $0.608$.
-In other words, according to this estimated density, the optimal value $K^*$ has a probability of $0.608$ of being distributed normally around $1.5$.
-% Alternatively, we can consider the mixing coefficients of the EM
-% density estimation. The Gaussian centered at $1.5$ has been attributed
-% a weight of $0.608$, while the one centered at $3.8$ has a mixing
-% weight of $0.226$. Ultimately, an optimiser would be more likely to be
-% close to $1.5$, but we do not have information on its performance in
-% this region around this value. \arthur{je ne comprends pas ce passage}
-
-% as we can argue that both values may be a sensible choice for the MPE. This comes from the fact that the hypothesis that $\mathbf{K}^*$ is a continuous r.v.\ is
 
 Instead of just considering the optimal minimisers, we introduce a bit of leeway, and look for ``acceptably not optimal'' parameters.
- This slackness takes the form of a relaxation coefficient, whose choice leads to a new family of robust estimators, along with a measure of their robustness via the relaxation coefficient.
+ This slackness takes the form of a relaxation coefficient and its choice defines a new family of robust estimators, where each one of its member carries information on its robustness through this coefficient.
 %This leads us to the definition of a new family of estimators, for which one can attribute a {\it level of robustness} \elise{je me rend bien compte que cette phrase est un peu bizarre ...mais bon c'est l'idee}
-
-%, by transforming the equality of Eq.~\eqref{eq:def_R1} into a inequality.
 
@@
 First, the conditional minimisers are computed, as shown on the top plots.
-Afterwards, for a level $\alpha=1.5$ and for all $\mathbf{u} \in \Uspace$, the acceptable $\mathbf{k}$ are identified, as shown on the bottom left plot.
+Afterwards, for a given level $\alpha=1.5$ and for all $\mathbf{u} \in \Uspace$, the acceptable $\mathbf{k}$ are identified, as shown on the bottom left plot.
 Finally, the region $R_{\alpha}(\mathbf{k})$ is the set of $\mathbf{u}$ for which $\mathbf{k}$ is acceptable, as represented with a vertical slice on the bottom right plot.
@@
 \centering
-\includegraphics[width=12cm]{Figures/relaxation_tuto.pdf}
-\caption{Principle of the relaxation of the constraint on $J_{\mathrm{BHswap}}$, and illustration of $R_\alpha(\mathbf{k})$.
+\includegraphics[width=10cm]{Figures/relaxation_tuto.pdf}
+\caption{Principle of the relaxation of the constraint on $\JBH$, and illustration of $R_\alpha(\mathbf{k})$.
 Top plots: Computation of the conditional minimisers $\mathbf{k}^*(\mathbf{u})$.
@@
 This can be linked to the definition of the distribution of the minimisers $\mathbf{K}^*$.
-For instance, if $\Kspace$ has a discrete support, we can rewrite $\Gamma_1$ as $\Gamma_1(\mathbf{k})=\Prob_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{u}) = J^*(\mathbf{U})\right] = \Prob_{\mathbf{U}}\left[\mathbf{k} = \mathbf{k}^*(\mathbf{U})\right]$ which is the probability mass function of $\mathbf{K}^*$.
+For instance, if $\Kspace$ is a discrete set, we can rewrite $\Gamma_1$ as $\Gamma_1(\mathbf{k})=\Prob_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{u}) = J^*(\mathbf{U})\right] = \Prob_{\mathbf{U}}\left[\mathbf{k} = \mathbf{k}^*(\mathbf{U})\right]$ which is the probability mass function of $\mathbf{K}^*$.
 
@@
 
-The choice of the relaxation constant $\alpha$ can be made to enforce some probability on the acceptability of the 
+The choice of the relaxation constant $\alpha$ can be made to ensure the existence of a parameter that is ``acceptable'' with a certain probability.
 For instance, given that $J>0$, $\Gamma_{\alpha}(\mathbf{k})$ is increasing with respect to $\alpha$ for any $\mathbf{k}\in\Kspace$.
@@
 \centering
-\includegraphics[width = 8.3cm]{Figures/illu_alpha_p.pdf}
+\includegraphics[width = 0.6\textwidth]{Figures/illu_alpha_p.pdf}
 \caption{Illustration of the influence of different levels $p$ on $\Gamma_{\alpha_p}$ and on $\mathbf{k}_p$}
@@
 Therefore it may suffer from the same pitfall as the worst-case approach.
-As mentioned in the introduction, this is not suited for random variable with unbounded support as it may return over-conservative solution,
+As mentioned in the introduction, this is not suited for random variable with unbounded support as it may return over-conservative solution, provided that a solution exists in the first place.
 
@@
 Similarly, if $p$ is fixed, the corresponding $\hat{\checka}_p$ is computed by searching for the smallest $\alpha$ satisfying $\max_{\mathbf{k}} \hat{\Gamma}_{\alpha}(\mathbf{k})=p$.
-Once again, if the value $\hat{\checka}_p$ is too large, the relaxation needed to get acceptable values with probability $p$ is very high, so the resulting estimation $\hat{\checkk}_p$ may not be relevant for the future application.
+Once again, if $\hat{\checka}_p$ is too large, the relaxation needed to get acceptable values with probability $p$ is very high, so the resulting estimation $\hat{\checkk}_p$ may not be relevant for the future application.
+
 % \victor{chapeau car ici je parle de l'estimation en pratique}
-Also, choosing $p=1$ is possible only if the sample space of $\mathbf{U}$ is bounded: let us consider the following simple problem
-\begin{align}
+Also, choosing $p=1$ is possible only if the sample space of $\mathbf{U}$ is bounded. An illustration of this flaw appears in the following simple problem:
+\begin{align*}
   \label{eq:Jinfinite}
@@
   J^*(\mathbf{u}) &= 1
-\end{align}
+\end{align*}
 In this case, for each $\mathbf{k}\in \Kspace$, $\lim_{\mathbf{u} \rightarrow + \infty} \frac{J(\mathbf{k},\mathbf{u})}{J^*(\mathbf{u})} = + \infty$, so there is no $\mathbf{k}$ such that the ratio $J/J *$ can be bounded, hence $\alpha_1$ does not exist in this case.
@@
 
-% We are now going to compute and compare those estimators on the $J_{\mathrm{BH}}$and $J_{\mathrm{BHswap}}$ function.
+% We are now going to compute and compare those estimators on the $\JBH$and $\JBHS$ function.
 
@@
 \subsection{Numerical Illustration}
+\label{ssec:numerical_illustration}
 % Numerical application}
-\victor{Paragraphe introductif pour comparer, et renvoyer à Table1}
-In this Section, we will compare the different estimators introduced in this paper as summarised Table~\ref{tab:RO_recap}.
-
-\begin{table}[t]
+
+In this Section, we will compare the different estimators introduced previously and summarised in Table~\ref{tab:RO_recap} on $\JBH$ and $\JBHS$.
+
+\begin{table}[!h]
   \centering
@@
 As stated before, we chose to model the uncertainties as a random variable uniformly distributed on $\Uspace$.
-The bounded nature of $\Uspace$ allows us to consider the estimators introduced before up to a level of confidence $p=1$.
+The bounded nature of $\Uspace$ allows us to consider members of the \RRE{} up to a level of confidence $p=1$.
 From now on, $\hatkmpe$ is estimated using KDE with Gaussian kernels.
-The smallest relaxation $\hat{\checka}_1$ and the corresponding $\hat{\checkk}_1$ has been computed for the $J_{\mathrm{BH}}$ and $J_{\mathrm{BHswap}}$ functions, using a regular grid of $1000 \times 1000$ points on $\Kspace\times\Uspace$.
+
+The smallest estimated relaxation $\hat{\checka}_1$ and the corresponding $\hat{\checkk}_1$ has been computed for $\JBH$ and $\JBHS$, using a regular grid of $1000 \times 1000$ points on $\Kspace\times\Uspace$.
 The contour plots of those functions can be seen in the top plots of Figure~\ref{fig:contour_alpha}.
-The frontier corresponding to the couples of points $(\mathbf{k},\mathbf{u})$ verifying $\{J(\mathbf{k},\mathbf{u}) = \alpha J^*(\mathbf{u})\}$ has been drawn on top of these contour plots, for $\alpha=\hat{\checka}_1$ and an arbitrary $\alpha=1.5<\hat{\checka}_1$, to illustrate the effect of the acceptable region when the relaxation $\alpha$ changes.
+The frontier corresponding to the couples of points $(\mathbf{k},\mathbf{u})$ verifying $\{J(\mathbf{k},\mathbf{u}) = \alpha J^*(\mathbf{u})\}$ has been drawn on top of these contour plots, for $\alpha=\hat{\checka}_1$ and an arbitrary $\alpha=1.5<\hat{\checka}_1$ to illustrate the effect of the acceptable region when the relaxation $\alpha$ changes.
 On the bottom plots, the curves $\mathbf{k}\mapsto \hat{\Gamma}_{\alpha}(\mathbf{k})$ for $\alpha=\hat{\checka}_1$ and $\alpha=1.5$ along with the histograms of the minimisers are represented.
@@
 \includegraphics[width=10cm]{Figures/branin_side_66_relax_gamma_both.pdf}
-\caption{Top: $J_{\mathrm{BH}}$ and $J_{\mathrm{BHswap}}$ contours.
+\caption{Top: $\JBH$ and $\JBHS$ contours.
 The thick yellow lines are the boundaries of the acceptable region defined for $\hat{\checka}_1$, the thick orange are for $\alpha=1.5$.
@@
 
-% For the $J_{\mathrm{BH}}$ function (left), the $\hat{\checka}_1$, $\hatkmean$ and $\hatkvar$ are quite close, so naturally we would expect a robust estimate to be significantly close to those values.
+% For the $\JBH$ function (left), the $\hat{\checka}_1$, $\hatkmean$ and $\hatkvar$ are quite close, so naturally we would expect a robust estimate to be significantly close to those values.
 $\hat{\checkk}_1$ supports this intuition, and appears to be very close to $\hatkmean$.
-%Concerning the $J_{\mathrm{BHswap}}$ function (right), $\hat{\checkk}_1$ appears to be closer to $\hatkvar$ this time.
+%Concerning the $\JBHS$ function (right), $\hat{\checkk}_1$ appears to be closer to $\hatkvar$ this time.s
 
@@
 
- The plot of $p\mapsto \hat{\checka}_p$ for $J_{\mathrm{BH}}$ on Figure~\ref{fig:ratio_BH} shows what seems to be a piecewise linear behaviour.
+ The plot of $p\mapsto \hat{\checka}_p$ for $\JBH$ on Figure~\ref{fig:ratio_BH} shows what seems to be a piecewise linear behaviour.
 The last change of slope, \textit{i.e.} for $p\approx 0.9$ corresponds to a local maximum of the ratio, while the first change of slope at $\hat{p}_{\mathrm{ratio}}=0.654$ corresponds to the global maximum of the ratio.
-The \RRE{} will then be evaluated for both these values, as well as $1$ for reference.
+The \RRE{} will then be evaluated for both of these values, as well as $1$ for reference.
 
@@
    \centering
-\includegraphics[width=10cm]{Figures/alpha_p_BH.pdf}
-\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $J_{\mathrm{BH}}$. The dashed line indicates the level $p$ associated with the highest ratio}
+\includegraphics[width=0.8\textwidth]{Figures/alpha_p_BH.pdf}
+\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $\JBH$. The dashed line indicates the level $p$ associated with the highest ratio}
 \label{fig:ratio_BH}
@@
 
- For $J_{\mathrm{BH}}$, the numerical values of the robust estimators can be found in Table~\ref{tab:recap_estimates_branin}.
-For this particular problem, the different estimates are close to each other.
+ For $\JBH$, the numerical values of the robust estimators can be found in Table~\ref{tab:recap_estimates_branin}. For this particular problem, the different estimates are close to each other.
 
@@
 % \centering
-% \caption{Estimation performed for $J_{\mathrm{BH}}$, sorted by value}
+% \caption{Estimation performed for $\JBH$, sorted by value}
 % \label{tab:recap_estimates_branin}
@@
   \centering
-\caption{Estimation performed for $J_{\mathrm{BH}}$, sorted by value}
+\caption{Estimation performed for $\JBH$, sorted by value}
 \begin{tabular}{lr}
   \toprule
-Estimator & Value \\ \midrule
+Estimate & Value \\ \midrule
 $\hatkvar$ & 1.371 \\ 
@@
 
-For $J_{\mathrm{BH}}$, the curves are plotted in Figure~\ref{fig:profiles_branin}.
-By construction, the profile of $\hat{\checkk}_1$ is always within the shaded region, corresponding to $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$.
-The profile of $\hatkmean$ in contrast, exceeds $\hat{\checka}_1 J^*(\mathbf{u})$ for $\mathbf{u}$ close to $5$, while the profile of $\hatkvar$ does it for $\mathbf{u}$ close to $0$.
-Except for $\hatkvar$, the different estimators give somewhat comparable results.
+For $\JBH$, the curves are plotted in Figure~\ref{fig:profiles_branin}.
 
@@
   \centering
-\includegraphics[width=10cm]{Figures/profile_BH.pdf}
-\caption{Profiles of the different estimates for $J_{\mathrm{BH}}$, corresponding to the vertical cross sections of the contour.
+\includegraphics[width=.8\textwidth]{Figures/profile_BH.pdf}
+\caption{Profiles of the different estimates for $\JBH$, corresponding to the vertical cross sections of the contour.
 The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$.
@@
 \end{figure*}
+
+By construction, the profile of $\hat{\checkk}_1$ is always within the shaded region, corresponding to $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$.
+The profile of $\hatkmean$ in contrast, exceeds $\hat{\checka}_1 J^*(\mathbf{u})$ for $\mathbf{u}$ close to $5$, while the profile of $\hatkvar$ does it for $\mathbf{u}$ close to $0$.
+Except for $\hatkvar$, the different estimators give somewhat comparable results.
+
 By contrast, $\JBHS$ will show a different behaviour as Figure~\ref{fig:ratio_BHs} provides the plots of $p\mapsto \hat{\checka}_p$ and $p\mapsto p/\hat{\checka}_p$.
 
-\begin{figure}[ht]
-  \centering
-\includegraphics[width=10cm]{Figures/alpha_p_BHs.pdf}
-\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $J_{\mathrm{BHswap}}$. The dashed line indicates the level $p$ associated with the highest ratio}
+\begin{figure}[!h]
+  \centering
+\includegraphics[width=0.8\textwidth]{Figures/alpha_p_BHs.pdf}
+\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $\JBHS$. The dashed line indicates the level $p$ associated with the highest ratio}
 \label{fig:ratio_BHs}
@@
 
-Compared to the similar plots for $J_{\mathrm{BH}}$ in Figure~\ref{fig:ratio_BH}, $\hat{\checka}_p$ exhibits a smoother behaviour for $\JBHS$ as no abrupt change of slope is easily discernable and the ratio presents a unique maximum for $\hat{p}_{\mathrm{ratio}}=0.766$.
-The numerical values of the estimations $\kest$ presented in Table~\ref{tab:recap_estimates_BHs} show that contrary to $J_{\mathrm{BH}}$, the calibrated values are more spread over $\Kspace$.
+Compared to the similar plots for $\JBH$ in Figure~\ref{fig:ratio_BH}, $\hat{\checka}_p$ exhibits a smoother behaviour for $\JBHS$ as no abrupt change of slope is easily discernable and the ratio presents a unique maximum for $\hat{p}_{\mathrm{ratio}}=0.766$.
+The numerical values of the estimations $\kest$ presented in Table~\ref{tab:recap_estimates_BHs} show that, contrary to $\JBH$, the calibrated values are more spread over $\Kspace$.
 
@@
 \centering
-\caption{Estimations performed for $J_{\mathrm{BHswap}}$, sorted by value}
+\caption{Estimations performed for $\JBHS$, sorted by value}
 \label{tab:recap_estimates_BHs}
@@
 
-Profiles of the different estimates of $J_{\mathrm{BHswap}}$ are shown in Figure~\ref{fig:profiles_branin_switch}.
-
-In this case, $\hatkmpe$, $\hatkmean$ and $\hat{\checkk}_{\mathrm{ratio}}$ present a similar behaviour.
-They perform very well for $\mathbf{u}>2$, especially for $\hatkmpe$ which is very close to the minimal value; However for $\mathbf{u}<2$, they produce high values of the function.
-
-The performances of $\hat{\checkk}_1$ are closer to the performances of $\hatkvar$ for this function, but it performs worse than $\hatkmean$ and $\hatkvar$ for $\mathbf{u}>2$, even though its range is designed to stay within the interval $[J^*(\mathbf{u}); \hat{\checka}_1 J^*(\mathbf{u})]$.
+Profiles of the different estimates of $\JBHS$ are shown in Figure~\ref{fig:profiles_branin_switch}.
 
@@
   \centering
-\includegraphics[width=10cm]{Figures/profile_BHs.pdf}
-\caption{Profiles of the different estimates for $J_{\mathrm{BHswap}}$.
+\includegraphics[width=0.8\textwidth]{Figures/profile_BHs.pdf}
+\caption{Profiles of the different estimates for $\JBHS$.
 Those profiles are the vertical cross sections of the contours above.
@@
 
+In this case, $\hatkmpe$, $\hatkmean$ and $\hat{\checkk}_{\mathrm{ratio}}$ present a similar behaviour.
+They perform very well for $\mathbf{u}>2$, especially for $\hatkmpe$ which is very close to the minimal value; however for $\mathbf{u}<2$, they produce high values of the function.
+The performances of $\hat{\checkk}_1$ are closer to the performances of $\hatkvar$ for this function, but it performs worse than $\hatkmean$ and $\hatkvar$ for $\mathbf{u}>2$, even though its range is designed to stay within the interval $[J^*(\mathbf{u}); \hat{\checka}_1 J^*(\mathbf{u})]$.
+
 We have seen how some classical robust estimators and the \RRE{} behave on two different analytical problems.
-Apart from the usual levels of confidence: 95\%, 99\% \dots, one can also settle for a ad-hoc compromise, where $p$ maximizes the ratio $p/\alpha_p$.
+In addition to the usual levels of confidence such as 90\% and 95\%, one can also settle for a ad-hoc compromise, where $p$ maximizes the ratio $p/\alpha_p$.
 When the sample space of $\mathbf{U}$ is bounded, a conservative solution is to set $p=1$.
@@
 % ----------------------------------------------------------------------------
-\clearpage
 
@@
 
-The numerical model $\mathcal{M}$ is dependent, in addition to $\mathbf{u}$ on some other input $\mathbf{k}\in\Kspace$.
-This additional parametrization comes usually from the successive simplifications and parametrizations needed to implement a numerical model of the physical system observed.
+In addition of $\mathbf{u}$, the numerical model $\mathcal{M}$ is dependent on some other input $\mathbf{k}\in\Kspace$.
+This additional parametrization comes usually from the successive simplifications needed to implement a numerical model of the physical system observed.
 These parameters need to be calibrated accordingly, so that the numerical model can be used to predict the behaviour of the physical system under different operating conditions.
@@
 
-The model to calibrate is an implementation of the Shallow Water equations, described in Eq.~\eqref{eq:SWE_equations}, where $h$ is the height of the water column, $q$ is the discharge, and $z$ is the bathymetry, while $g$ is the usual gravitation constant.
-The parameter to calibrate, $\mathbf{k}$, is the quadratic friction term, proportional to the square of the inverse of Manning-Strickler coefficient.
+The model to calibrate is an implementation of the 1D Shallow Water equations, described in Eq.~\eqref{eq:SWE_equations}, where $h$ is the height of the water column, $q$ is the discharge, and $z$ is the bathymetry, while $g$ is the usual gravitation constant.
+The parameter to calibrate $\mathbf{k}$ is the quadratic friction term, proportional to the square of the inverse of Manning-Strickler coefficient.
 The environmental parameter $\mathbf{u}$ is the amplitude of a sine wave of period $1/\omega_0$.
@@
 \end{align}
+
 These equations are integrated using a finite-volume scheme on a discretized domain $[0, L]$, up to a time $T$.
 The output of the computer code is the sea surface height $h$, on the center of all the volumes and at all the time-steps, that will be denoted $\mathcal{M}(\mathbf{k},\mathbf{u};\, \omega_0=1.0)$.
-In this setting, the variable input is uniformly distributed on $\Uspace$.
-
-To generate the observation, we choose $\mathbf{u}^{\mathrm{true}}=2/3$, and define $\mathcal{M}^o$ based on the computer model $\mathcal{M}$, such that $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) = \mathcal{M}(\mathbf{k}^{\mathrm{true}}, \mathbf{u}^{\mathrm{true}}; \, \omega_0 = 0.999)$.
+In this setting, the random variable $\mathbf{U}$ is uniformly distributed on $\Uspace$.
+
+To generate the observation, we set $\mathbf{u}^{\mathrm{true}}=2/3$, and define $\mathcal{M}^o$ based on the computer model $\mathcal{M}$, such that $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) = \mathcal{M}(\mathbf{k}^{\mathrm{true}}, \mathbf{u}^{\mathrm{true}}; \, \omega_0 = 0.999)$.
 $\omega_0$
@@
 \subsection{Computation of the robust estimates}
-As the numerical model is expensive to evaluate, it has first been evaluated on a relatively small regular grid.
-A metamodel based on Gaussian processes is constructed using the initial evaluations and in order to better capture the locus of the conditional minimisers $\{(\mathbf{k}^*(\mathbf{u}), \mathbf{u}) \mid \mathbf{u} \in \Uspace \}$, the PEI criterion~\citep{ginsbourger_bayesian_2014,bossek_learning_2015} allows us to add points to the design.
-Afterwards, a bigger regular grid is evaluated by the metamodel once the design space has been sufficiently explored.
-The different steps of the estimation are illustrated Figure~\ref{fig:estimation_swe}, where the top plot shows the contour plot of $J$, with the conditional minimisers and the \RRE{} of level $p$.
-On the middle plot is shown the conditional moments, $\hatkmean$ and $\hatkvar$ and the estimated density of the minimisers.
+As the numerical model is expensive to run, it has first been evaluated on a relatively small regular grid covering $\Kspace \times \Uspace$, and a metamodel based on Gaussian processes is constructed using those initial evaluations.
+In order to better capture the locus of the conditional minimisers $\{(\mathbf{k}^*(\mathbf{u}), \mathbf{u}) \mid \mathbf{u} \in \Uspace \}$, we select points maximising the PEI criterion~\citep{ginsbourger_bayesian_2014,bossek_learning_2015} in order to add points to the design that improve the metamodel accuracy close to the conditional minimisers.
+Afterwards, a bigger regular grid is evaluated by the metamodel once the design space has been sufficiently explored, and these computations are used to calibrate the model.
+
+The different steps of the estimation are illustrated Figure~\ref{fig:estimation_swe}, where the top plot shows the contour plot of $J$, with the conditional minimisers and the \RRE{} of level $p=1$.
+On the middle plot are shown the conditional moments, $\hatkmean$ and $\hatkvar$ and the estimated density of the minimisers.
 At the bottom of the Figure, $\hat{\Gamma}_{\alpha_p}$ are represented for different levels $p$.
@@
 
-We can see that the estimation for this problem seems less problematic than the analytical examples shown above.
+We can see that the different estimations seem less problematic for this problem than for the analytical examples shown in Section~\ref{ssec:numerical_illustration}, as everything appears to be very smooth and unimodal.
+
 Looking at $p\mapsto \alpha_p$ and $p\mapsto p/\alpha_p$ on Figure~\ref{fig:alpha_p_SWE}, we can see that $\alpha_p$ evolves almost linearly for $p>0.5$, and that the ratio $p/\alpha_p$ is monotonically increasing, so that the maximal ratio is found for $p=1$.
@@
   \centering
-  \includegraphics[scale=0.5]{Figures/alpha_SWE}
+  \includegraphics[width=0.8\textwidth]{Figures/alpha_SWE}
   \caption{Evolution of $\alpha_p$ for different levels $p$, and ratio}
@@
 
-The different estimates take a wide range of values, as seen on Table~\ref{tab:recap_estimates_metaSWE}, from $0.249$ to almost $1.0$, when $k_i^{\mathrm{true}} \in [0, 0.4]$ for $1\leq i \leq N_{\mathrm{vol}}$.
-As a basis for comparison, the global minimiser of $J$ over $\Kspace \times \Uspace$ has been computed, and $\kest_{\mathrm{global}}$ is then obtained by discarding the $\mathbf{u}$ value.
+The different estimates take a wide range of values, as seen on Table~\ref{tab:recap_estimates_metaSWE}, from $0.249$ to almost $1.0$, while $k_i^{\mathrm{true}} \in [0, 0.4]$ for $1\leq i \leq N_{\mathrm{vol}}$.
+It can be noted that the calibration may lead to values outside the range given by the true ones.
+This can be interpreted as the fact that the calibration look to compensate for errors on $\omega_0$.
+As a basis for comparison, the global minimiser of $J$ over $\Kspace \times \Uspace$ has also been computed, and $\kest_{\mathrm{global}}$ is then obtained by discarding the $\mathbf{u}$ value.
 
@@
 \begin{tabular}{lr} \toprule
-Estimator & Value \\ \midrule
+Estimate & Value \\ \midrule
 $\hatkmpe$ & 0.249 \\
@@
   \centering
-  \includegraphics[width=.8\textwidth]{Figures/profile_swe}
+  \includegraphics[width=.75\textwidth]{Figures/profile_swe}
   \caption{Profiles for the calibration problem}
@@
 \subsection{Assessing the quality of the forecast of the calibrated model}
-The calibration of the model has been performed using by integrating the model on a time-period $[0, T]$, called assimilation window. 
-We now want to compare the quality of the different forecasts, from different calibrated bottom friction.
-Those forecasts result from the integration of the numerical model between the time $T$ and a time $T_{\mathrm{pred}}$.
+For the calibration, the model has been integrated on a time-period $[0, T]$, called assimilation window, and have been compared with the observation of the sea water height on the same time-period.
+We now want to compare the quality of the different forecasts originating from different calibrated bottom frictions.
+Those forecasts result from the integration of the numerical model between the time $T$ and a time $T_{\mathrm{pred}}$: the forecast window.
 
 Given the probabilistic nature of the environmental conditions $\mathbf{U}$, the forecasts will also be probabilistic.
-We will then compare $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{U})$, for a calibrated $\mathbf{k}$.
-Two metrics of comparison will be computed: the squared forecast error, and the Continuous Ranked Probability Score (CRPS).
-The ``robust'' parameters that are compared are the minimiser of the expectation $\hatkmean$, the minimiser of the variance $\hatkvar$ and the relative regret of level $p=1$, $\kest_1$ as described in the previous section.
-
+We will then compare $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{U})$, that are the observation, and the numerical model on the forecast window for a calibrated $\mathbf{k}$.
+
+Two metrics will be computed: the squared forecast error, and the Continuous Ranked Probability Score (CRPS).
+The parameters satisfying a robust criterion that are compared are the minimiser of the expectation $\hatkmean$, the minimiser of the variance $\hatkvar$ and the relative regret of level $p=1$, $\kest_1$ as described in the previous section.
 We will also feature the global minimiser $\kest_{\mathrm{global}}$, and the conditional minimisers $\kest^*(\mathbf{u}^i)$ where the chosen environmental variables are $\{\mathbf{u}^i\}_{1\leq i \leq 4} = \{0.5, 0.55, 0.65, 0.7\}$.
-Those values are introduced in order to have a more precise idea on the possible performances of a deterministic version of the calibration problem.
+Those values, even though they do not meet a robustness criterion, are introduced in order to have a more precise idea on the possible performances of a deterministic version of the calibration problem.
 The conditional minimiser $\kest^*(0.6)$ has been omitted as it results in a value very similar to the minimum of the expectation.
@@
 \subsubsection{Squared forecast error}
+A first simple approach to measure the forecast quality is to take the squared difference between the numerical model and the observation for two samples of $\mathbf{U}$.
 Given two environmental conditions $\mathbf{u}$ and $\mathbf{u}'\in \Uspace$, the former used to run the computer simulation and the latter to generate the observations, the squared forecast error for the parameter $\mathbf{k}$ is
@@
 This can be done using a Monte-Carlo approximation.
-As $\mathbf{u}$ and $\mathbf{u}'$ are iid, assuming that we have a set of samples $\{\mathbf{u}^i\}_{1\leq i \leq N_{\mathbf{u}}}$, the squared forecast error can then be approximated using this finite set of samples:
+As $\mathbf{u}$ and $\mathbf{u}'$ are iid, assuming that we have a set of samples $\{\mathbf{u}^i\}_{1\leq i \leq N_{\mathbf{u}}}$, the squared forecast error can then be approximated:
 \begin{equation}
@@
 Averaging $S(\mathbf{\kest})$ over the time steps between $T$ and $T_{\mathrm{pred}}$, we have an indication on the quality of the forecast in the squared sense depending on the spatial position, as seen on the left of Figure~\ref{fig:forecast_squared_error}.
+
 \begin{figure*}[!h]
 \centering
-\includegraphics[width=.9\textwidth]{Figures/L2_full_rel.pdf}
+\includegraphics[width=.8\textwidth]{Figures/L2_full_rel.pdf}
 \caption{Squared forecast error, depending on the calibrated parameter.
-The left figure shows the squared error averaged over time, while the right figure shows the mean forecast error, averaged over time and space}
+The left figure shows the squared error averaged over time, while the right barplot shows the relative change of the mean forecast error, averaged over time and space, taken w.r.t.\ to the best attained performance for $\mathbf{k}^*(0.7)$}
 \label{fig:forecast_squared_error}
 \end{figure*}
+
 We can see that the mean forecast error squared, on the right side, averaged over time and space is the smallest for the conditional minimisers $\kest^*(0.7)$ and $\kest^*(0.65)$, then $\kest_{\mathrm{global}}$, while $\kest_{1.0}$ performs slightly better than $\hatkmean$.
 
-It may seem surprising that some parameters calibrated without a robustness aspect, so the conditional minimisers, perform better than $\kest_1$ and $\hatkmean$, but their performances are largely dependent on the choice of $\mathbf{u}$ and their associated conditional minimisers.
-This is shown for $\mathbf{u}=0.5$, that leads to bad forecasts.
+It may seem surprising that some parameters calibrated without a robustness aspect perform better than $\kest_1$ and $\hatkmean$, but their performances are largely dependent on the choice of $\mathbf{u}$ and their associated conditional minimisers.
+Good forecasts can be achieved as well as bad ones, as shown for $\mathbf{u}=0.5$, that leads to bad forecasts.
+
 One issue with the squared forecast error is that it will penalize strongly the forecasts that present high variability with respect to the environmental conditions.
@@
   \centering
-  \includegraphics[width=.9\textwidth]{Figures/CRPS_full_rel}
-  \caption{CRPS computed for different calibrated parameters. The left figure show the CRPS averaged over time, and the right figure shows the CRPS, averaged over time and space}
+  \includegraphics[width=.8\textwidth]{Figures/CRPS_full_rel}
+  \caption{CRPS computed for different calibrated parameters.
+The left figure show the CRPS averaged over time, and the right figure shows the relative change of the CRPS averaged over time and space, taken with respect to the best attained CRPS for $\mathbf{k}^*(0.7)$}
 \label{fig:forecast_crps}
@@
 According to the squared error, the region around $x=4$ is not well predicted, while around $x=8$, the predictions are better.
-On the other hand, according to the CRPS, the region around $x=8$ provide worse forecasts than the one at $x=4$ and $x=7$.
+On the other hand, according to the CRPS, the region around $x=8$ provide worse forecasts than when $x=4$ and $x=7$.
 Given the properties of the two metrics,  we can conclude that the region around $x=4$ presents a lot of variability with respect to $\mathbf{u}$, for both the true model and the numerical one.
@@
 The numerical evaluations of the CRPS for different parameters show the same order of performances observed for the squared error: the calibrated parameters that present the best performances for forecasts according to those two metrics are $\kest^*(0.7)$, $\kest^*(0.65)$ which is very similar to $\kest_{\mathrm{global}}$, and then $\kest_1$, and $\hatkmean$.
-This presupposes to know which $\mathbf{u}$ to choose for the conditional minimisation, thus having a strong insight on the value of the parameters.
+This presupposes to know which $\mathbf{u}$ to choose for the conditional minimisation, thus having a strong insight on the value of the parameters in the first place.
 
 \section*{Conclusion}
-In this paper, we dealt with a problem of robust calibration, or in other terms, the robust minimisation of a cost function.
+In this paper, we dealt with a problem of robust calibration, or in other terms, the robust minimisation of an objective function.
 To adress this issue, we proposed a new set of robust estimators: the family of the \RRE{} (Relative-regret estimators), and compared it in a forecast context to some other robust estimators, for the calibration of the bottom friction of a shallow water model.
+
 Our approach is based on the will to be as close as possible to the conditional minimiser, with high probability.
@@
 
-Except for simple analytical example, the exact evaluation of a member of the \RRE{} is very expensive computer-wise, not to say impossible.
-Some bottlenecks appear: the computations of the conditional minimisers $\mathbf{K}^*$, and the minimum $J^*$, that require very local exploration, and the computations of the probability of
-
-We have to rely on approximations for those estimations. Possible leads are
+Except for simple analytical examples, the exact evaluation of a member of the \RRE{} is very expensive computer-wise, not to say impossible.
+Some bottlenecks appear: the computations of the conditional minimisers $\mathbf{k}^*(\mathbf{u})$ and the minimum $J^*(\mathbf{u})$, that require very local exploration of $\Kspace$ for every $\mathbf{u}$; and the computations of the probability of overshooting a given bound that depends on $J^*(\mathbf{u})$ (analogous to a probability of failure), task that requires an efficient exploration of the whole sample space $\Uspace$.
+
+For the calibration of the shallow water model presented in Section~\ref{sec:SWE_application}, we chose to construct a response surface based on Gaussian processes, which is going to be used for the extensive computations.
+This construction is first based on an initial design, that is enriched to better capture the locus of the conditional minimisers using the PEI criterion introduced in~\cite{ginsbourger_bayesian_2014}.
+One lead that appears naturally to diminish the amount of computation is to find a sequential criterion that makes the balance between the minimisation of a probability of failure, and
+
+Comparing the performances of the different estimates, one can see that for the two metrics introduced in Section~\ref{sec:SWE_application}, $\kest_1$ performs better than $\hatkmean$, but is sometimes outperformed by ``non-robust'' solutions.
+
 % \victor{À faire à la fin}

### 2019-12-18 article.tex
ccl

@@
 %% keywords here, in the form: keyword \sep keyword
-
+Calibration \sep Robust optimisation \sep Relative-regret \sep shallow-water equations
 %% PACS codes here, in the form: \PACS code \sep code
@@
 
+% ----------------------------------------------------------------------
 \section*{Conclusion}
+
 In this paper, we dealt with a problem of robust calibration, or in other terms, the robust minimisation of an objective function.
@@
 This construction is first based on an initial design, that is enriched to better capture the locus of the conditional minimisers using the PEI criterion introduced in~\cite{ginsbourger_bayesian_2014}.
-One lead that appears naturally to diminish the amount of computation is to find a sequential criterion that makes the balance between the minimisation of a probability of failure, and
-
-Comparing the performances of the different estimates, one can see that for the two metrics introduced in Section~\ref{sec:SWE_application}, $\kest_1$ performs better than $\hatkmean$, but is sometimes outperformed by ``non-robust'' solutions.
-
+
+Comparing the performances of the different estimates in a forecast context, one can see that for the two metrics introduced in Section~\ref{sec:SWE_application}, $\kest_1$ performs better than $\hatkmean$, but is sometimes outperformed by ``non-robust'' solutions.
+Those require some additional knowledge about the environmental conditions, and did not present some robust properties during the calibration phase.
+
+Practically speaking, the estimation of those quantities is very crude, so the computational cost may be very expensive.
+As perspective, specific strategies have to be created, based for instance on sequential design of computer experiments using Gaussian processes, to diminish the amount of runs needed of the numerical model..
+Ideally, one would want to develop a acquisition criterion, that makes the balance between the minimisation of a well-chosen probability of failure, and the exploration around the conditional minimisers.
+Finally, the models upon which this calibration procedure have been applied are very simplistic.
+We plan in the future to apply this to the robust calibration of the bottom friction of a realistic model of the ocean.
 % \victor{À faire à la fin}

### 2019-12-19 article.tex
hat notation, biblio update

@@
 \section*{Introduction}
-\label{}
+\label{sec:intro}
 
@@
 Both approaches and related robust estimates are described in Section~\ref{robust formulations}.
-Section~\ref{sec:relax_constraint} introduces a new class of estimators, by relaxing the constraint of optimality and defining regions of acceptability, similarly as~\cite{buhmann_robust_2013} in discrete combinatorial problems.
+Section~\ref{sec:relax_constraint} introduces a new class of estimators, by relaxing the constraint of optimality and defining regions of acceptability, similarly as~\cite{buhmann_robust_2013} in discrete combinatorial problems, or~\cite{kouvelis_algorithms_1992,snyder_stochastic_2004} in operation research.
 The intention is that a robust estimate provides values of the cost function close enough to the attainable minimum for each configuration induced by $\mathbf{u}\in\Uspace$.
@@
 Then it would mean that this estimate is the minimiser of the cost function whatever the realisation of the uncertain variable, therefore optimal in all conditions.
-If the distribution $p_{\mathbf{K}^*}$ is heavily dominated by a single value, the MPE may be a good candidate for robust control. This is not so obvious in case of a multimodal distribution.
+If the distribution $p_{\mathbf{K}^*}$ is heavily dominated by a single value, the MPE may be a good candidate for robust control. This is not so obvious in the case of a multimodal distribution.
 
 In general, an analytical form of $p_{\mathbf{K}^*}$ is usually impossible to obtain, so an estimation $\hat{p}_{\mathbf{K}^*}$ must be used, and its maximum computed to get the MPE.
+In the rest of the paper, the hat notation will indicate an estimation using numerical values of the underlying theoretical quantity.
 Once again, a set of samples  $\{\mathbf{u}^i\}_{i=1\dots N}$ can be used to compute the set $\{\mathbf{k}_{\mathbf{u}^i}\}_{i=1\dots N}$, from which one can 
@@
 
-Our approach is based on the will to be as close as possible to the conditional minimiser, with high probability.
+Our approach is based on the will to be as close as possible to the conditional minimisers with high probability.
 At a level $p$, in addition to the estimation, we have the relaxation coefficient $\alpha_p$ that bounds with probability $p$ the relative error of the cost function, that helps us assess the conservativeness of the proposed estimation.
@@
 Practically speaking, the estimation of those quantities is very crude, so the computational cost may be very expensive.
-As perspective, specific strategies have to be created, based for instance on sequential design of computer experiments using Gaussian processes, to diminish the amount of runs needed of the numerical model..
+As perspective, specific strategies have to be created, based for instance on sequential design of computer experiments using Gaussian processes, to diminish the amount of runs needed of the numerical model.
 Ideally, one would want to develop a acquisition criterion, that makes the balance between the minimisation of a well-chosen probability of failure, and the exploration around the conditional minimisers.
@@
 \bibliographystyle{elsarticle-num-names} 
-\bibliography{bibzotero}
+\bibliography{biblio_file}
 

### 2020-01-20 article.tex
modifs Élise, et template JCP

@@
 %% please give \usepackage{epsfig}
-
+\usepackage{jcomp}
+\usepackage{framed,multirow}
 %% The amssymb package provides various useful mathematical symbols
@@
 %% \usepackage{lineno}
-\usepackage{easy-todo}
 \usepackage{graphicx}
@@
 \newcommand{\victor}[1]{{\itshape\color{green} ({#1})}}
+\usepackage{url}
+\usepackage{xcolor}
+\definecolor{newcolor}{rgb}{.8,.349,.1}
 
@@
 \begin{document}
-
-\begin{frontmatter}
 
@@
 
-\title{Robust calibration of numerical models based on relative regret}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
-
-\author[vt]{Victor Trappler}
+% \title{Robust calibration of numerical models based on relative regret}
+
+% %% use optional labels to link authors explicitly to addresses:
+% %% \author[label1,label2]{}
+% %% \address[label1]{}
+% %% \address[label2]{}
+
+% \author[vt]{Victor Trappler}
+% \ead{victor.trappler@univ-grenoble-alpes.fr}
+% \author[ea]{Élise Arnaud}
+% \author[av]{Arthur Vidard}
+% \author[ld]{Laurent Debreu}
+
+% \address[vt]{Univ. Grenoble Alpes, CNRS, Inria, Grenoble INP*, LJK, 38000 Grenoble, France}
+
+\verso{Victor Trappler \textit{etal}}
+
+\begin{frontmatter}
+
+\title{Robust calibration of numerical models based on relative regret}%
+
+\author[1]{Victor \snm{Trappler}\corref{cor1}}
+\cortext[cor1]{Corresponding author% : 
+  % Tel.: +0-000-000-0000;  
+  % fax: +0-000-000-0000
+  % ;
+}
 \ead{victor.trappler@univ-grenoble-alpes.fr}
-\author[ea]{Élise Arnaud}
-\author[av]{Arthur Vidard}
-\author[ld]{Laurent Debreu}
-
-\address[vt]{Univ. Grenoble Alpes, CNRS, Inria, Grenoble INP*, LJK, 38000 Grenoble, France}
+\author[1]{Élise \snm{Arnaud}}
+% \fntext[fn1]{This is author footnote for second author.}  
+\author[2]{Arthur \snm{Vidard}}
+%% Third author's email
+% \ead{author3@author.com}
+\author[2]{Laurent \snm{Debreu}}
+
+\address[1]{Univ. Grenoble Alpes, CNRS, Inria, Grenoble INP\fnref{fn1}, LJK, 38000 Grenoble, France}
+\fntext[fn1]{Institute of Engineering Univ. Grenoble Alpes}
+\address[2]{Univ. Grenoble Alpes, Inria, CNRS, Grenoble INP\fnref{fn1}, LJK, 38000 Grenoble, France}
+\received{}
+\finalform{}
+\accepted{}
+\availableonline{}
+\communicated{}
 
@@
 
-\begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
-Calibration \sep Robust optimisation \sep Relative-regret \sep shallow-water equations
-%% PACS codes here, in the form: \PACS code \sep code
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
-\end{keyword}
+% \begin{keyword}
+% %% keywords here, in the form: keyword \sep keyword
+% Calibration \sep Robust optimisation \sep Relative-regret \sep shallow-water equations
+% %% PACS codes here, in the form: \PACS code \sep code
+
+% %% MSC codes here, in the form: \MSC code \sep code
+% %% or \MSC[2008] code \sep code (2000 is the default)
+
+% \end{keyword}
 
@@
 %% main text
-\section*{Introduction}
+\section{Introduction}
 \label{sec:intro}
@@
 %----------------------------------------------------------------------------
-% \listoftodos{}
-
-%\arthur{Revoir les notations ($\hat{\bf k}$, ${\bf k}^*$ c'est la meme chose ou pas ? les u, U je ne suis pas sûr que c'est bon non plus)}
-%\victor{Pour moi, ce qui est en majuscule, c'est des v.a., et tous les inputs sont en gras (mais on peut laisser tomber le gras)}
-%% \introduction[modified heading if necessary]
-%\subsection{Motivation}
-
 Numerical models are widely used to study or forecast natural phenomena and improve industrial processes.
@@
 Under this definition, one may design robust estimators, either by using the moments of the cost function; or by exploiting the distribution of its minimisers.
-
-%
-%When robustness is defined as the ability of $\kest$ to perform reasonably well under different operating conditions (i.e.\ different $\mathbf{u}$), two classical  approaches can be used to define robust estimators:
-%\begin{itemize} 
-%\item Optimisation of the statistical moments of the random variable $J(\mathbf{k}, \mathbf{U})$: usually minimisation of the expected value, of the variance or a combination of them
-%\item Estimate based on the distribution of the minimisers $\mathbf{k}_{\mathbf{u}}$, assuming the inverse problem is well-posed to ensure the existence and the unicity of the minimiser for each $\mathbf{u}$.
-%\end{itemize}
-
-%\subsection{simple/classical estimators \arthur{TITRE \`A REVOIR}}
-
-%Broadly speaking, two different aspects can be used to define robust estimators:
-%\begin{itemize} 
-%\item Optimisation of the statistical moments of the random variable: usually minimisation of the expected value, of the variance or a combination of them
-%\item Estimate based on the distribution of the minimisers, assuming the inverse problem is well-posed to ensure the existence and the unicity of the minimiser for each $\mathbf{u}$. 
-%\end{itemize}
-
 % ----------------------------------------------------------------------------
 \subsection{Optimisation of the moments}
-
-%Statistical moments, especially  expectation and variance, are common tools used to describe and summarise a random variable.
-%A case in point are the Gaussian random variables, that are uniquely defined by their expected value and their variance.
-%It then makes sense that the statistical moments have a central role in robust optimisation.
-In practice, such ideas relies on the expected value as seen in \cite{shapiro_lectures_2009}, while looking at the same time mean and variance is the basis of Markowitz's portfolio selection theory in \cite{markowitz_portfolio_1952}.
-%
 
@@
 The resulting approximation and therefore its mode, is sensitive to the density estimation method.
-Main methods are KDE  (Kernel Density Estimation)~\cite{elise}, and EM (Expectation-Maximisation)~\citep{dempster_maximum_1977}.
+Main methods are KDE (Kernel Density Estimation)~\citep{silverman_density_2018}, and EM (Expectation-Maximisation)~\citep{dempster_maximum_1977}.
 
@@
   \centering
-  \includegraphics[width=10cm]{Figures/branin_side_moments_noscale.pdf}
+  \includegraphics[width=12cm]{Figures/branin_side_moments_noscale.pdf}
   \caption{The left column concerns $\JBH$, while the right one deals with $\JBHS$.
@@
 
-Similarly, estimations of $\hatkmpe$ are depicted on Figure~\ref{fig:contours}.The top row shows the contours of both functions as well as the set of conditional minimisers $\{\mathbf{k}_{\mathbf{u}^i}\}_{1\leq i \leq N}$ in red, as defined in Eq.~\eqref{eq:conditional_minimiser}.
+Similarly, estimations of $\hatkmpe$ are depicted on Figure~\ref{fig:contours}.
+The top row shows the contours of both functions as well as the set of conditional minimisers $\{\mathbf{k}_{\mathbf{u}^i}\}_{1\leq i \leq N}$ in red, as defined in Eq.~\eqref{eq:conditional_minimiser}.
 The bottom row presents three approximations of the density of minimisers: the histogram in grey (bin size selected using Freedman-Diaconis from~\cite{freedman_histogram_1981}), the result of a kernel density estimation (KDE) with Gaussian kernels in red (using Scott's rule from~\cite{scott_optimal_1979} for bandwidth selection), and the estimation by a Gaussian mixture, calculated with the EM algorithm.
@@
   \centering
-  \includegraphics[width=10cm]{Figures/branin_side_66.pdf}
+  \includegraphics[width=12cm]{Figures/branin_side_66.pdf}
   \caption{Top Left:  $\JBH$ along with conditional minimisers in red.
@@
 \subsection{Relaxing the optimality constraint}
-The density of minimisers has been estimated by optimising $\mathbf{k}\mapsto J(\mathbf{k},\mathbf{u})$ over $\Kspace$ for different realisations of $\mathbf{u}$.
+The density of minimisers has been estimated by optimising $\mathbf{k}\mapsto J(\mathbf{k},\mathbf{U}=\mathbf{u})$ over $\Kspace$ for different realisations of $\mathbf{u}$.
 Instead of focusing on optimal values, we propose to consider their {\it acceptable} neighbourhood in terms of performance of the cost function as well.
-To do so, for each $\mathbf{u}$, $\mathbf{k}$ is deemed acceptable when  $J(\mathbf{k},\mathbf{u}) \leq \alpha J^*(\mathbf{u})$, with $\alpha > 1$.
-
-In this context, for a given $\mathbf{k}$, the set $R_{\alpha}(\mathbf{k}) \subset \Uspace$ is defined as the set of $\mathbf{u}$, for which $\mathbf{k}$ is acceptable:
+To do so, for each $\mathbf{u}$, $\mathbf{k}$ is deemed acceptable when  $J(\mathbf{k},\mathbf{U}=\mathbf{u}) \leq \alpha J^*(\mathbf{u})$, with $\alpha > 1$. 
+%
+%
+In this context, for a given $\mathbf{k}$, the set $R_{\alpha}(\mathbf{k}) \subseteq \Uspace$ is defined as the set of $\mathbf{u}$, for which $\mathbf{k}$ is acceptable:
 \begin{equation}
 \label{eq:def_Ralpha}
-R_{\alpha}(\mathbf{k}) = \left\{ \mathbf{u} \in \Uspace \mid J(\mathbf{k},\mathbf{u}) \leq \alpha J^*(\mathbf{u}) \right\}
+R_{\alpha}(\mathbf{k}) = \left\{ \mathbf{u} \in \Uspace \mid J(\mathbf{k},\mathbf{U}=\mathbf{u}) \leq \alpha J^*(\mathbf{u}) \right\}
 \end{equation}
@@
 First, the conditional minimisers are computed, as shown on the top plots.
-Afterwards, for a given level $\alpha=1.5$ and for all $\mathbf{u} \in \Uspace$, the acceptable $\mathbf{k}$ are identified, as shown on the bottom left plot.
-Finally, the region $R_{\alpha}(\mathbf{k})$ is the set of $\mathbf{u}$ for which $\mathbf{k}$ is acceptable, as represented with a vertical slice on the bottom right plot.
+Afterwards, for a given level $\alpha=1.5$, the set of acceptable $\mathbf{k}$ can be identified for each $\mathbf{u} \in \Uspace$, as shown on the bottom left plot.
+Finally, the region $R_{\alpha}(\mathbf{k})$ is the subset of $\Uspace$ for which $\mathbf{k}$ is acceptable, as represented with a vertical slice on the bottom right plot.
 
@@
 \centering
-\includegraphics[width=10cm]{Figures/relaxation_tuto.pdf}
+\includegraphics[width=12cm]{Figures/relaxation_tuto.pdf}
 \caption{Principle of the relaxation of the constraint on $\JBH$, and illustration of $R_\alpha(\mathbf{k})$.
@@
 Top right plot: the set $(\mathbf{k}^*(\mathbf{u}),\mathbf{u})$ of conditional minimisers is represented in red.
-On the bottom left plot, for a relaxation $\alpha=1.5$, and $\mathbf{u}=3$, the acceptable $\mathbf{k}$ are in cyan, while the non-acceptable ones are in orange, while the frontier $\{(\mathbf{k}^*(\mathbf{u}),\mathbf{u}) \mid J^*(\mathbf{u}) = J(\mathbf{k},\mathbf{u})\}$ is in yellow.
+On the bottom left plot, for a relaxation $\alpha=1.5$, and $\mathbf{u}=3$, the acceptable $\mathbf{k}$ are in cyan, while the non-acceptable ones are in orange, while the frontier $\{(\mathbf{k}^*(\mathbf{u}),\mathbf{u}) \mid J^*(\mathbf{u}) = J(\mathbf{k},\mathbf{U}=\mathbf{u})\}$ is in yellow.
 On the bottom right plot, the set $R_{\alpha}(\mathbf{k})$ for $\alpha=1.5$ and $\mathbf{k}=1.5$ is in green.}
@@
 
-Noting that without relaxation, \textit{i.e.} when $\alpha$ is set to $1$, $\Gamma_1$ is non-zero if the set $\{\mathbf{u}\in\Uspace \mid J(\mathbf{k},\mathbf{u}) = J^*(\mathbf{u})\}$ has non-zero measure with respect to $\Prob_{\mathbf{U}}$.
+Noting that without relaxation, \textit{i.e.} when $\alpha$ is set to $1$, $\Gamma_1$ is non-zero if the set $\{\mathbf{u}\in\Uspace \mid J(\mathbf{k},\mathbf{U}=\mathbf{u}) = J^*(\mathbf{u})\}$ has non-zero measure with respect to $\Prob_{\mathbf{U}}$.
 It happens when the distribution of $\mathbf{K}^*$ presents atoms.
@@
 This can be linked to the definition of the distribution of the minimisers $\mathbf{K}^*$.
-For instance, if $\Kspace$ is a discrete set, we can rewrite $\Gamma_1$ as $\Gamma_1(\mathbf{k})=\Prob_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{u}) = J^*(\mathbf{U})\right] = \Prob_{\mathbf{U}}\left[\mathbf{k} = \mathbf{k}^*(\mathbf{U})\right]$ which is the probability mass function of $\mathbf{K}^*$.
+For instance, if $\Kspace$ is a discrete set, we can rewrite $\Gamma_1$ as $\Gamma_1(\mathbf{k})=\Prob_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U}=\mathbf{u}) = J^*(\mathbf{U})\right] = \Prob_{\mathbf{U}}\left[\mathbf{k} = \mathbf{k}^*(\mathbf{U})\right]$ which is the probability mass function of $\mathbf{K}^*$.
 
 The motivation behind this relaxation is to take into account the local behaviour of the function around the conditional minimisers.
-For a given set of environmental conditions $\mathbf{u}$, if the function $\mathbf{k} \mapsto J(\mathbf{k},\mathbf{u})$ is flat around its minimum $\mathbf{k}^*(\mathbf{u})$, then choosing  $\mathbf{k}^*(\mathbf{u}) + \epsilon$ (for a small $\epsilon$) will produce a value closer to the minimum than when the function has a high curvature.
+For a given set of environmental conditions $\mathbf{u}$, if the function $\mathbf{k} \mapsto J(\mathbf{k},\mathbf{U}=\mathbf{u})$ is flat around its minimum $\mathbf{k}^*(\mathbf{u})$, then choosing  $\mathbf{k}^*(\mathbf{u}) + \epsilon$ (for a small $\epsilon$) will produce a value closer to the minimum than when the function has a high curvature.
 In addition to that, relaxing the constraint using a multiplicative constant puts more weight on the values of $\mathbf{k}^*(\mathbf{u})$ when $J^*(\mathbf{u})$ is small.
@@
 This formulation can be linked to the quantiles and Value-at-Risk of the random variable $\max_{\mathbf{k}} \{ \frac{J(\mathbf{k},\mathbf{U})}{J^*(\mathbf{U})}\}$, that is a measure of risk usually applied in the financial sector (see~\cite{rockafellar_deviation_2002}).
-For different levels $p$, and thus different $\alpha_p$, Figure~\ref{fig:illu_alpha_p} shows examples of $\Gamma_{\alpha_p}$.
+For different levels $p$, and thus different $\alpha_p$, Figure~\ref{fig:illu_alpha_p} shows examples of $\Gamma_{\alpha_p}$ for $\JBHS$.
 By definition, the associated $\mathbf{k}_p$ is then the first value for which $\Gamma_{\alpha_p}$ reaches $p$.
@@
 \centering
-\includegraphics[width = 0.6\textwidth]{Figures/illu_alpha_p.pdf}
-\caption{Illustration of the influence of different levels $p$ on $\Gamma_{\alpha_p}$ and on $\mathbf{k}_p$}
+\includegraphics[width = 0.7\textwidth]{Figures/illu_alpha_p.pdf}
+\caption{Illustration of the influence of different levels $p$ on $\Gamma_{\alpha_p}$ and on $\mathbf{k}_p$ for $\JBHS$}
 \label{fig:illu_alpha_p}
@@
   \label{eq:upper_bound_alpha_check}
-  \checka_1 = \sup_{\mathbf{u}\in\Uspace} \frac{J(\mathbf{k}_1,\mathbf{u})}{J^*(\mathbf{u})} =  \inf_{\mathbf{k}\in\Kspace} \left\{ \sup_{\mathbf{u}\in\Uspace} \frac{J(\mathbf{k},\mathbf{u})}{J^*(\mathbf{u})} \right\}
+  \checka_1 = \sup_{\mathbf{u}\in\Uspace} \frac{J(\mathbf{k}_1,\mathbf{U}=\mathbf{u})}{J^*(\mathbf{u})} =  \inf_{\mathbf{k}\in\Kspace} \left\{ \sup_{\mathbf{u}\in\Uspace} \frac{J(\mathbf{k},\mathbf{U}=\mathbf{u})}{J^*(\mathbf{u})} \right\}
 \end{equation}
@@
 This alternative definition of $\checka_1$ is useful to estimate it quickly whenever a grid over $\mathbb{K}\times\mathbb{U}$ has already been evaluated, thus avoiding multiple computations of $\Gamma_{\alpha}(\mathbf{k})$ until its maximum reaches $1$.
-From Eq.~\eqref{eq:upper_bound_alpha_check}, choosing a level of confidence equal to $1$ is then equivalent to looking for the worst-case scenario of the ratio $\frac{J(\mathbf{k},\mathbf{u})}{J^*(\mathbf{u})}$.
+From Eq.~\eqref{eq:upper_bound_alpha_check}, choosing a level of confidence equal to $1$ is then equivalent to looking for the worst-case scenario of the ratio $\frac{J(\mathbf{k},\mathbf{U}=\mathbf{u})}{J^*(\mathbf{u})}$.
 Therefore it may suffer from the same pitfall as the worst-case approach.
@@
 $\checkap$ can be an indicator of the robustness of $\checkkp$.  
-A high value of $\checka_1$ corresponds to a high ratio $\frac{J(\mathbf{k},\mathbf{u})}{J^*(\mathbf{u})}$ for at least one particular $\mathbf{u}$.
-In that sense, $J(\checkk_1,\mathbf{u})$ may be possibly very high.
+A high value of $\checka_1$ corresponds to a high ratio $\frac{J(\mathbf{k},\mathbf{U}=\mathbf{u})}{J^*(\mathbf{u})}$ for at least one particular $\mathbf{u}$.
+In that sense, $J(\checkk_1,\mathbf{U}=\mathbf{u})$ may be possibly very high.
 More generally, for a fixed level of confidence $p$, $\checkap$ is the slackness needed to be able to reach the probability $p$.
@@
 In order to choose the quantities introduced above, there are three choices: either fixing $p$, either fixing the maximal threshold $\alpha$, or looking for a compromise between $p$ and $\alpha$.
-The most trivial way is to set $\alpha$, to find the couples of points $(\mathbf{k},\mathbf{u})$ verifying $J(\mathbf{k},\mathbf{u}) \leq \alpha J^*(\mathbf{u})$, and then to estimate the probability $\Gamma_{\alpha}(\mathbf{k})$ defined in Eq.~\eqref{eq:def_Ralpha}.
+The most trivial way is to set $\alpha$, to find the couples of points $(\mathbf{k},\mathbf{u})$ verifying $J(\mathbf{k},\mathbf{U}=\mathbf{u}) \leq \alpha J^*(\mathbf{u})$, and then to estimate the probability $\Gamma_{\alpha}(\mathbf{k})$ defined in Eq.~\eqref{eq:def_Ralpha}.
 For instance, when $N$ sampled values of $\mathbf{U}$: $\{\mathbf{u}^i\}_{1\leq i \leq N}$ are available, a possible estimator of $\Gamma_{\alpha}$ is
 \begin{equation}
-\hat{\Gamma}_{\alpha}(\mathbf{k}) = \frac{\# \left\{\mathbf{u}^i \mid J(\mathbf{k},\mathbf{u}^i) \leq \alpha J^*(\mathbf{u}^i)\right\}}{N}
+\hat{\Gamma}_{\alpha}(\mathbf{k}) = \frac{\mathrm{Card} \left\{\mathbf{u}^i \mid J(\mathbf{k},\mathbf{U}=\mathbf{u}^i) \leq \alpha J^*(\mathbf{u}^i)\right\}}{N}
 \end{equation}
 However, this may be a risky approach.
-Indeed if $\alpha$ is chosen too small, the resulting $\hat{p}=\max_{\mathbf{k}} \hat{\Gamma}_{\alpha}(\mathbf{k})$ will be also small, meaning that the cost function will overshoot the value $\alpha J^*(\mathbf{U})$ with high probability.
+Indeed if $\alpha$ is chosen too small, the resulting $\hat{p}=\max_{\mathbf{k}} \hat{\Gamma}_{\alpha}(\mathbf{k})$ will be also small, meaning that the cost function will have non acceptable values with high probability.
 
@@
   \Kspace &= \Uspace = [0,\,+\infty[ \\
-  J(\mathbf{k},\mathbf{u}) &= \mathbf{u}(\mathbf{k}-\mathbf{u})^2 + 1 \\
+  J(\mathbf{k},\mathbf{U}=\mathbf{u}) &= \mathbf{u}(\mathbf{k}-\mathbf{u})^2 + 1 \\
   \mathbf{k}^*(\mathbf{u}) &= \mathbf{u} \\
@@
 \end{align*}
-In this case, for each $\mathbf{k}\in \Kspace$, $\lim_{\mathbf{u} \rightarrow + \infty} \frac{J(\mathbf{k},\mathbf{u})}{J^*(\mathbf{u})} = + \infty$, so there is no $\mathbf{k}$ such that the ratio $J/J *$ can be bounded, hence $\alpha_1$ does not exist in this case.
+In this case, for each $\mathbf{k}\in \Kspace$, $\lim_{\mathbf{u} \rightarrow + \infty} \frac{J(\mathbf{k},\mathbf{U}=\mathbf{u})}{J^*(\mathbf{u})} = + \infty$, so there is no $\mathbf{k}$ such that the ratio $J/J *$ can be bounded, hence $\alpha_1$ does not exist in this case.
 
@@
 The contour plots of those functions can be seen in the top plots of Figure~\ref{fig:contour_alpha}.
-The frontier corresponding to the couples of points $(\mathbf{k},\mathbf{u})$ verifying $\{J(\mathbf{k},\mathbf{u}) = \alpha J^*(\mathbf{u})\}$ has been drawn on top of these contour plots, for $\alpha=\hat{\checka}_1$ and an arbitrary $\alpha=1.5<\hat{\checka}_1$ to illustrate the effect of the acceptable region when the relaxation $\alpha$ changes.
+The frontier corresponding to the couples of points $(\mathbf{k},\mathbf{u})$ verifying $\{J(\mathbf{k},\mathbf{U}=\mathbf{u}) = \alpha J^*(\mathbf{u})\}$ has been drawn on top of these contour plots, for $\alpha=\hat{\checka}_1$ and an arbitrary $\alpha=1.5<\hat{\checka}_1$ to illustrate the effect of the acceptable region when the relaxation $\alpha$ changes.
 On the bottom plots, the curves $\mathbf{k}\mapsto \hat{\Gamma}_{\alpha}(\mathbf{k})$ for $\alpha=\hat{\checka}_1$ and $\alpha=1.5$ along with the histograms of the minimisers are represented.
@@
   \centering
-\includegraphics[width=10cm]{Figures/branin_side_66_relax_gamma_both.pdf}
+\includegraphics[width=12cm]{Figures/branin_side_66_relax_gamma_both.pdf}
 \caption{Top: $\JBH$ and $\JBHS$ contours.
@@
 The last change of slope, \textit{i.e.} for $p\approx 0.9$ corresponds to a local maximum of the ratio, while the first change of slope at $\hat{p}_{\mathrm{ratio}}=0.654$ corresponds to the global maximum of the ratio.
-The \RRE{} will then be evaluated for both of these values, as well as $1$ for reference.
+The \RRE{} will then be evaluated for both of these values, as well as $p=1$ for reference.
 
@@
 \end{table*}
-Practically speaking, in order to compare the effective values taken by the objective function given an estimate $\kest$ we are going to consider the functions $\mathbf{u} \mapsto J(\kest,\mathbf{u})$, that we will call ``profile of $\kest$''.
+Practically speaking, in order to compare the effective values taken by the objective function given an estimate $\kest$ we are going to consider the functions $\mathbf{u} \mapsto J(\kest,\mathbf{U}=\mathbf{u})$, that we will call ``profiles of $\kest$''.
 Those profiles are well suited for the representation of the cost function for an estimate $\kest$ fixed as the uncertain variable is modelled with a 1D uniform random variable.
@@
 We have seen how some classical robust estimators and the \RRE{} behave on two different analytical problems.
-In addition to the usual levels of confidence such as 90\% and 95\%, one can also settle for a ad-hoc compromise, where $p$ maximizes the ratio $p/\alpha_p$.
+In addition to the usual levels of confidence such as 90\% and 95\%, one can also settle for an ad-hoc compromise, where $p$ maximizes the ratio $p/\alpha_p$.
 When the sample space of $\mathbf{U}$ is bounded, a conservative solution is to set $p=1$.
@@
  The calibration of a numerical model is usually based on the comparison between the numerical model and some observations, during a fixed time interval $[0, T]$ called assimilation window.
- The physical system modelled can be seen as a map from $\Uspace$ to $\mathbb{Y}$, the space of observations, denoted as $\mathcal{M}^o : \mathbf{u}\mapsto \mathcal{M}^o(\mathbf{u})$, where $\mathbf{u}\in\Uspace$ is an input representing some environmental conditions.
+ The modelled physical system can be seen as a map from $\Uspace$ to $\mathbb{Y}$, the space of observations, denoted as $\mathcal{M}^o : \mathbf{u}\mapsto \mathcal{M}^o(\mathbf{u})$, where $\mathbf{u}\in\Uspace$ is an input representing some environmental conditions.
 The observation mentioned above is the output of the physical system during the time-window, and is denoted by $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) \in \mathbb{Y}$, where $\mathbf{u}^{\mathrm{true}} \in \Uspace$ is unknown.
 
-In addition of $\mathbf{u}$, the numerical model $\mathcal{M}$ is dependent on some other input $\mathbf{k}\in\Kspace$.
-This additional parametrization comes usually from the successive simplifications needed to implement a numerical model of the physical system observed.
-These parameters need to be calibrated accordingly, so that the numerical model can be used to predict the behaviour of the physical system under different operating conditions.
+In addition of $\mathbf{u}$, the numerical model $\mathcal{M}$ depends on some other input $\mathbf{k}\in\Kspace$.
+This additional parametrization comes usually from the successive simplifications needed to implement a numerical model of the observed physical system.
+$\mathbf{k}$ needs to be calibrated accordingly, so that the numerical model can be used to predict the behaviour of the physical system under different operating conditions.
 
@@
 \begin{equation}
-J(\mathbf{k},\mathbf{u}) = \frac12 \| \mathcal{G}(\mathbf{k},\mathbf{u}) \|^2 = \frac12 \|\mathcal{M}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}(\mathbf{u}^{\mathrm{true}}) \|^2
+J(\mathbf{k},\mathbf{U}=\mathbf{u}) = \frac12 \| \mathcal{G}(\mathbf{k},\mathbf{u}) \|^2 = \frac12 \|\mathcal{M}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}(\mathbf{u}^{\mathrm{true}}) \|^2
 \end{equation}
@@
 
-The model to calibrate is an implementation of the 1D Shallow Water equations, described in Eq.~\eqref{eq:SWE_equations}, where $h$ is the height of the water column, $q$ is the discharge, and $z$ is the bathymetry, while $g$ is the usual gravitation constant.
+The model to calibrate is an implementation of the 1D Shallow Water equations, described in Eq.~\eqref{eq:SWE_equations}, where $h$ is the height of the water column, $q$ the discharge, and $z$ the bathymetry, while $g$ is the usual gravitation constant.
 The parameter to calibrate $\mathbf{k}$ is the quadratic friction term, proportional to the square of the inverse of Manning-Strickler coefficient.
@@
 \centering
-\includegraphics[width=.7\textwidth]{Figures/RobustSWEmis_plots.pdf}
+\includegraphics[width=.9\textwidth]{Figures/RobustSWEmis_plots.pdf}
 \caption{Procedure of robust calibration for the shallow water problem.
-Top: contours of $J$, conditional minimisers and $\{(\mathbf{k},\mathbf{u}) | J(\mathbf{k},\mathbf{u}) = \hat{\alpha}_1 J^*(\mathbf{u})\}$.
+Top: contours of $J$, conditional minimisers and $\{(\mathbf{k},\mathbf{U}=\mathbf{u}) | J(\mathbf{k},\mathbf{u}) = \hat{\alpha}_1 J^*(\mathbf{u})\}$.
 Middle: Conditional moments and histogram and KDE of the conditional minimisers.
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{Figures/alpha_SWE}
-  \caption{Evolution of $\alpha_p$ for different levels $p$, and ratio}
+  \includegraphics[width=0.9\textwidth]{Figures/alpha_SWE}
+  \caption{Evolution of $\alpha_p$ for different levels $p$, and ratio, for the shallow water problem}
 \label{fig:alpha_p_SWE}
@@
 \centering
-\caption{Calibrated values of $\mathbf{k}$ according to different criteria}
+\caption{Calibrated values of $\mathbf{k}$ according to different criteria, for the shallow water problem}
 \begin{tabular}{lr} \toprule
@@
   \centering
-  \includegraphics[width=.75\textwidth]{Figures/profile_swe}
-  \caption{Profiles for the calibration problem}
+  \includegraphics[width=.8\textwidth]{Figures/profile_swe}
+  \caption{Profiles for the calibration problem, for the shallow water case}
 \label{fig:profiles_swe}
@@
 
-Two metrics will be computed: the squared forecast error, and the Continuous Ranked Probability Score (CRPS).
+Two metrics will be computed: the squared forecast error, and the Continuous Ranked Probability Score (CRPS)~\citep{gneiting_probabilistic_2014}.
 The parameters satisfying a robust criterion that are compared are the minimiser of the expectation $\hatkmean$, the minimiser of the variance $\hatkvar$ and the relative regret of level $p=1$, $\kest_1$ as described in the previous section.
@@
 Given two environmental conditions $\mathbf{u}$ and $\mathbf{u}'\in \Uspace$, the former used to run the computer simulation and the latter to generate the observations, the squared forecast error for the parameter $\mathbf{k}$ is
+
 \begin{equation}
@@
 \end{equation}
+
 Averaging over both $\mathbf{u}$ and $\mathbf{u}'$ defines the mean squared forecast error, defined on every point of the spatial domain, and at every time-steps.
 This can be done using a Monte-Carlo approximation.
-As $\mathbf{u}$ and $\mathbf{u}'$ are iid, assuming that we have a set of samples $\{\mathbf{u}^i\}_{1\leq i \leq N_{\mathbf{u}}}$, the squared forecast error can then be approximated:
+As $\mathbf{u}$ and $\mathbf{u}'$ are i.i.d., assuming that we have a set of samples $\{\mathbf{u}^i\}_{1\leq i \leq N_{\mathbf{u}}}$, the squared forecast error can then be approximated:
+
 \begin{equation}
@@
 \end{equation}
+
 The mean squared forecast error averaged over the whole space and over all the time-steps gives an indication on the overall prediction quality of the prediction given this metric, and are represented on the right of Figure~\ref{fig:forecast_squared_error}.
 We can see that $\kest_{\mathrm{global}}$ performs slightly better than $\kest_1$, itself performing slightly better than $\hatkmean$.
-Averaging $S(\mathbf{\kest})$ over the time steps between $T$ and $T_{\mathrm{pred}}$, we have an indication on the quality of the forecast in the squared sense depending on the spatial position, as seen on the left of Figure~\ref{fig:forecast_squared_error}.
+Averaging $S(\mathbf{\kest})$ over the time steps between $T$ and $T_{\mathrm{pred}}$, we have an indication on the quality of the forecast in the squared sense depending on the spatial coordinate $x$, as seen on the left of Figure~\ref{fig:forecast_squared_error}.
 
@@
 \centering
-\includegraphics[width=.8\textwidth]{Figures/L2_full_rel.pdf}
-\caption{Squared forecast error, depending on the calibrated parameter.
-The left figure shows the squared error averaged over time, while the right barplot shows the relative change of the mean forecast error, averaged over time and space, taken w.r.t.\ to the best attained performance for $\mathbf{k}^*(0.7)$}
+\includegraphics[width=.9\textwidth]{Figures/L2_full_rel.pdf}
+\caption{Squared forecast error for the shallow water case, depending on the calibrated parameter.
+The left figure shows the squared error time-averaged as a function of the spatial coordinate $x$, while the right barplot shows the relative change of the mean forecast error, averaged over time and space, taken w.r.t.\ to the best attained performance for $\mathbf{k}^*(0.7)$}
 \label{fig:forecast_squared_error}
@@
 \label{eq:def_crps}
-\mathrm{CRPS}(\mathbf{k}) = \int_{\mathbb{R}} (F_{\mathrm{pred}}(x,\mathbf{k}) - F^o_{\mathrm{pred}}(x))^2 \,\mathrm{d}x
+\mathrm{CRPS}(\mathbf{k}) = \int_{\mathbb{R}} (F_{\mathrm{pred}}(\xi,\mathbf{k}) - F^o_{\mathrm{pred}}(x))^2 \,\mathrm{d}\xi
 \end{equation}
@@
   \centering
-  \includegraphics[width=.8\textwidth]{Figures/CRPS_full_rel}
-  \caption{CRPS computed for different calibrated parameters.
-The left figure show the CRPS averaged over time, and the right figure shows the relative change of the CRPS averaged over time and space, taken with respect to the best attained CRPS for $\mathbf{k}^*(0.7)$}
+  \includegraphics[width=.9\textwidth]{Figures/CRPS_full_rel}
+  \caption{CRPS computed for different calibrated parameters for the shallow water case.
+The left figure shows the CRPS time-averaged as a function of the spatial coordinate $x$, and the right figure shows the relative change of the CRPS averaged over time and space, taken with respect to the best attained CRPS for $\mathbf{k}^*(0.7)$}
 \label{fig:forecast_crps}
@@
 
-The left plot of Figure~\ref{fig:forecast_crps} shows the CRPS averaged over time, and the right plot shows the value of the CRPS averaged over time and space.
+The left plot of Figure~\ref{fig:forecast_crps} shows the CRPS averaged over time, where $x$ denotes the spatial coordinate and the right plot shows the value of the CRPS averaged over time and space.
 The difference between the squared forecast error and the CRPS is apparent when comparing the general trends shared by the different calibrated parameters.
-According to the squared error, the region around $x=4$ is not well predicted, while around $x=8$, the predictions are better.
+According to the squared error, the sea water height of the physical region $x=4$ is not well predicted, while around $x=8$, the predictions are better.
 On the other hand, according to the CRPS, the region around $x=8$ provide worse forecasts than when $x=4$ and $x=7$.
@@
 Our approach is based on the will to be as close as possible to the conditional minimisers with high probability.
-At a level $p$, in addition to the estimation, we have the relaxation coefficient $\alpha_p$ that bounds with probability $p$ the relative error of the cost function, that helps us assess the conservativeness of the proposed estimation.
+At a level $p$, in addition to the estimation, we have the relaxation coefficient $\alpha_p$ that bounds with probability $p$ the relative error of the cost function.
+This helps us to assess the robustness properties of the proposed estimation.
 
@@
 
-For the calibration of the shallow water model presented in Section~\ref{sec:SWE_application}, we chose to construct a response surface based on Gaussian processes, which is going to be used for the extensive computations.
+For the calibration of the shallow water model presented in Section~\ref{sec:SWE_application}, we chose to construct a response surface based on Gaussian processes, which is then used for the extensive computations.
 This construction is first based on an initial design, that is enriched to better capture the locus of the conditional minimisers using the PEI criterion introduced in~\cite{ginsbourger_bayesian_2014}.
@@
 As perspective, specific strategies have to be created, based for instance on sequential design of computer experiments using Gaussian processes, to diminish the amount of runs needed of the numerical model.
-Ideally, one would want to develop a acquisition criterion, that makes the balance between the minimisation of a well-chosen probability of failure, and the exploration around the conditional minimisers.
+Ideally, one would want to develop an acquisition criterion, that makes the balance between the minimisation of a well-chosen probability of failure, and the exploration around the conditional minimisers.
 Finally, the models upon which this calibration procedure have been applied are very simplistic.
@@
 
-\bibliographystyle{elsarticle-num-names} 
+\bibliographystyle{model1-num-names} 
 \bibliography{biblio_file}

### 2020-01-21 article.tex
Figures scaling

@@
 
+\newlength{\minisize}
+\setlength{\minisize}{3cm}
+\newlength{\singlecolumnsize}
+\setlength{\singlecolumnsize}{9cm}
+\newlength{\onehalfcolumn}
+\setlength{\onehalfcolumn}{14cm}
+\newlength{\fullwidth}
+\setlength{\fullwidth}{19cm}
+
 \journal{Journal of Computational Physics}
@@
   \centering
-  \includegraphics[width=12cm]{Figures/branin_side_moments_noscale.pdf}
+  \includegraphics[width=\singlecolumnsize]{Figures/branin_side_moments_noscale.pdf}
   \caption{The left column concerns $\JBH$, while the right one deals with $\JBHS$.
@@
   \centering
-  \includegraphics[width=12cm]{Figures/branin_side_66.pdf}
+  \includegraphics[width=\singlecolumnsize]{Figures/branin_side_66.pdf}
   \caption{Top Left:  $\JBH$ along with conditional minimisers in red.
@@
 \centering
-\includegraphics[width=12cm]{Figures/relaxation_tuto.pdf}
+\includegraphics[width=\onehalfcolumn]{Figures/relaxation_tuto.pdf}
 \caption{Principle of the relaxation of the constraint on $\JBH$, and illustration of $R_\alpha(\mathbf{k})$.
@@
 $\{\mathbf{k}_p \text{ for } p \in [0;1] \}$ defines the relative-regret family of robust estimators (\RRE).
-This formulation can be linked to the quantiles and Value-at-Risk of the random variable $\max_{\mathbf{k}} \{ \frac{J(\mathbf{k},\mathbf{U})}{J^*(\mathbf{U})}\}$, that is a measure of risk usually applied in the financial sector (see~\cite{rockafellar_deviation_2002}).
+This formulation can be linked to the quantiles and Value-at-Risk of the random variable $\max_{\mathbf{k}} \{ J(\mathbf{k},\mathbf{U}) / J^*(\mathbf{U})\}$, that is a measure of risk usually applied in the financial sector (see~\cite{rockafellar_deviation_2002}).
 For different levels $p$, and thus different $\alpha_p$, Figure~\ref{fig:illu_alpha_p} shows examples of $\Gamma_{\alpha_p}$ for $\JBHS$.
@@
 \centering
-\includegraphics[width = 0.7\textwidth]{Figures/illu_alpha_p.pdf}
+\includegraphics[width = \singlecolumnsize]{Figures/illu_alpha_p.pdf}
 \caption{Illustration of the influence of different levels $p$ on $\Gamma_{\alpha_p}$ and on $\mathbf{k}_p$ for $\JBHS$}
@@
 This alternative definition of $\checka_1$ is useful to estimate it quickly whenever a grid over $\mathbb{K}\times\mathbb{U}$ has already been evaluated, thus avoiding multiple computations of $\Gamma_{\alpha}(\mathbf{k})$ until its maximum reaches $1$.
-From Eq.~\eqref{eq:upper_bound_alpha_check}, choosing a level of confidence equal to $1$ is then equivalent to looking for the worst-case scenario of the ratio $\frac{J(\mathbf{k},\mathbf{U}=\mathbf{u})}{J^*(\mathbf{u})}$.
+From Eq.~\eqref{eq:upper_bound_alpha_check}, choosing a level of confidence equal to $1$ is then equivalent to looking for the worst-case scenario of the ratio ${J(\mathbf{k},\mathbf{U}=\mathbf{u})/J^*(\mathbf{u})}$.
 Therefore it may suffer from the same pitfall as the worst-case approach.
@@
 $\checkap$ can be an indicator of the robustness of $\checkkp$.  
-A high value of $\checka_1$ corresponds to a high ratio $\frac{J(\mathbf{k},\mathbf{U}=\mathbf{u})}{J^*(\mathbf{u})}$ for at least one particular $\mathbf{u}$.
+A high value of $\checka_1$ corresponds to a high ratio ${J(\mathbf{k},\mathbf{U}=\mathbf{u})/J^*(\mathbf{u})}$ for at least one particular $\mathbf{u}$.
 In that sense, $J(\checkk_1,\mathbf{U}=\mathbf{u})$ may be possibly very high.
@@
 \end{align*}
-In this case, for each $\mathbf{k}\in \Kspace$, $\lim_{\mathbf{u} \rightarrow + \infty} \frac{J(\mathbf{k},\mathbf{U}=\mathbf{u})}{J^*(\mathbf{u})} = + \infty$, so there is no $\mathbf{k}$ such that the ratio $J/J *$ can be bounded, hence $\alpha_1$ does not exist in this case.
+In this case, for each $\mathbf{k}\in \Kspace$, $\lim_{\mathbf{u} \rightarrow + \infty} {J(\mathbf{k},\mathbf{U}=\mathbf{u})/J^*(\mathbf{u})} = + \infty$, so there is no $\mathbf{k}$ such that the ratio $J/J *$ can be bounded, hence $\alpha_1$ does not exist in this case.
 
@@
   \centering
-\includegraphics[width=12cm]{Figures/branin_side_66_relax_gamma_both.pdf}
+\includegraphics[width=\onehalfcolumn]{Figures/branin_side_66_relax_gamma_both.pdf}
 \caption{Top: $\JBH$ and $\JBHS$ contours.
@@
    \centering
-\includegraphics[width=0.8\textwidth]{Figures/alpha_p_BH.pdf}
+\includegraphics[width=\onehalfcolumn]{Figures/alpha_p_BH.pdf}
 \caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $\JBH$. The dashed line indicates the level $p$ associated with the highest ratio}
@@
 % \end{table*}
-\begin{table*}[!h]
+\begin{table}[!h]
   \centering
@@
 \label{tab:recap_estimates_branin}
-\end{table*}
+\end{table}
 Practically speaking, in order to compare the effective values taken by the objective function given an estimate $\kest$ we are going to consider the functions $\mathbf{u} \mapsto J(\kest,\mathbf{U}=\mathbf{u})$, that we will call ``profiles of $\kest$''.
@@
   \centering
-\includegraphics[width=.8\textwidth]{Figures/profile_BH.pdf}
+\includegraphics[width=\onehalfcolumn]{Figures/profile_BH.pdf}
 \caption{Profiles of the different estimates for $\JBH$, corresponding to the vertical cross sections of the contour.
@@
   \centering
-\includegraphics[width=0.8\textwidth]{Figures/alpha_p_BHs.pdf}
+\includegraphics[width=\onehalfcolumn]{Figures/alpha_p_BHs.pdf}
 \caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $\JBHS$. The dashed line indicates the level $p$ associated with the highest ratio}
@@
 
-\begin{table*}[!h]
+\begin{table}[!h]
 \centering
@@
 \end{tabular}
-\end{table*}
+\end{table}
 
@@
   \centering
-\includegraphics[width=0.8\textwidth]{Figures/profile_BHs.pdf}
+\includegraphics[width=\onehalfcolumn]{Figures/profile_BHs.pdf}
 \caption{Profiles of the different estimates for $\JBHS$.
@@
 \centering
-\includegraphics[width=.9\textwidth]{Figures/RobustSWEmis_plots.pdf}
+\includegraphics[width=\singlecolumnsize]{Figures/RobustSWEmis_plots.pdf}
 \caption{Procedure of robust calibration for the shallow water problem.
@@
   \centering
-  \includegraphics[width=0.9\textwidth]{Figures/alpha_SWE}
+  \includegraphics[width=\onehalfcolumn]{Figures/alpha_SWE}
   \caption{Evolution of $\alpha_p$ for different levels $p$, and ratio, for the shallow water problem}
@@
 \label{tab:recap_estimates_metaSWE}
-\end{table*}
+\end{table}
+
 Similarly as for $\JBH$ and $\JBHS$, the profiles are depicted Figure~\ref{fig:profiles_swe}.
@@
   \centering
-  \includegraphics[width=.8\textwidth]{Figures/profile_swe}
+  \includegraphics[width=\onehalfcolumn]{Figures/profile_swe}
   \caption{Profiles for the calibration problem, for the shallow water case}
@@
 \end{figure}
+
 We can see that the performances of $\kest_1$ and $\hatkmean$ are very similar, but $\kest_1$ has better performances when $\mathbf{u} > 0.6$.
 When comparing with the global optimiser $\kest_{\mathrm{global}}$, $\kest_1$ performs better when $\mathbf{u}<0.625$, so more than half of the time.
-% As $\mathbf{U}$ is uniformly distributed on $\Uspace=[0.5,0.7]$, we can graphically estimate that the probability that $\kest_1$ outperforms $\kest_{\mathrm{global}}$ is greater than $0.5$, that is that $\Prob_\mathbf{U}\left[J(\kest_1,\mathbf{U})<J(\kest_{\mathrm{global}},\mathbf{U})\right] > 0.5$.
-
-% The calibration of this numerical model is done in order to get a calibrated value $\kest$, that will be used for forecasts, using the same numerical model.
 We are now going to compare how well some of those calibrated values compare in a forecast context.
+
 \subsection{Assessing the quality of the forecast of the calibrated model}
@@
 \centering
-\includegraphics[width=.9\textwidth]{Figures/L2_full_rel.pdf}
+\includegraphics[width=\onehalfcolumn]{Figures/L2_full_rel.pdf}
 \caption{Squared forecast error for the shallow water case, depending on the calibrated parameter.
@@
 \label{eq:def_crps}
-\mathrm{CRPS}(\mathbf{k}) = \int_{\mathbb{R}} (F_{\mathrm{pred}}(\xi,\mathbf{k}) - F^o_{\mathrm{pred}}(x))^2 \,\mathrm{d}\xi
+\mathrm{CRPS}(\mathbf{k}) = \int_{\mathbb{R}} (F_{\mathrm{pred}}(\xi,\mathbf{k}) - F^o_{\mathrm{pred}}(\xi))^2 \,\mathrm{d}\xi
 \end{equation}
@@
   \centering
-  \includegraphics[width=.9\textwidth]{Figures/CRPS_full_rel}
+  \includegraphics[width=\onehalfcolumn]{Figures/CRPS_full_rel}
   \caption{CRPS computed for different calibrated parameters for the shallow water case.

### 2020-01-27 article.tex
rename figures
back to preprint formatting
corresponding author
ordre auteurs et affiliation

@@
 %% please give \usepackage{epsfig}
-\usepackage{jcomp}
-\usepackage{framed,multirow}
+% \usepackage{jcomp}
+% \usepackage{framed,multirow}
 %% The amssymb package provides various useful mathematical symbols
@@
 
-\verso{Victor Trappler \textit{etal}}
+% \verso{Victor Trappler \textit{etal}}
 
@@
 
-\author[1]{Victor \snm{Trappler}\corref{cor1}}
-\cortext[cor1]{Corresponding author% : 
-  % Tel.: +0-000-000-0000;  
-  % fax: +0-000-000-0000
+\author[1]{Victor {Trappler}\corref{cor1}}
+\cortext[cor1]{Corresponding author
+  % Tel.: +0-000-000-
   % ;
@@
 \ead{victor.trappler@univ-grenoble-alpes.fr}
-\author[1]{Élise \snm{Arnaud}}
+\author[1]{Élise {Arnaud}}
 % \fntext[fn1]{This is author footnote for second author.}  
-\author[2]{Arthur \snm{Vidard}}
+\author[1]{Arthur {Vidard}}
+\author[1]{Laurent {Debreu}}
+
 %% Third author's email
 % \ead{author3@author.com}
-\author[2]{Laurent \snm{Debreu}}
-
-\address[1]{Univ. Grenoble Alpes, CNRS, Inria, Grenoble INP\fnref{fn1}, LJK, 38000 Grenoble, France}
+
+\address[1]{Univ. Grenoble Alpes, Inria, CNRS, Grenoble INP\textsuperscript{1}\fnref{fn1}, LJK, 38000 Grenoble, France}
 \fntext[fn1]{Institute of Engineering Univ. Grenoble Alpes}
-\address[2]{Univ. Grenoble Alpes, Inria, CNRS, Grenoble INP\fnref{fn1}, LJK, 38000 Grenoble, France}
-\received{}
-\finalform{}
-\accepted{}
-\availableonline{}
-\communicated{}
+% \address[2]{Univ. Grenoble Alpes, Inria, CNRS, Grenoble INP\fnref{fn1}, LJK, 38000 Grenoble, France}
+% \received{}
+% \finalform{}
+% \accepted{}
+% \availableonline{}
+% \communicated{}
 
@@
 
-% \begin{keyword}
-% %% keywords here, in the form: keyword \sep keyword
-% Calibration \sep Robust optimisation \sep Relative-regret \sep shallow-water equations
-% %% PACS codes here, in the form: \PACS code \sep code
-
-% %% MSC codes here, in the form: \MSC code \sep code
-% %% or \MSC[2008] code \sep code (2000 is the default)
-
-% \end{keyword}
+\begin{keyword}
+%% keywords here, in the form: keyword \sep keyword
+Calibration \sep Robust optimisation \sep Relative-regret \sep Shallow-water equations
+%% PACS codes here, in the form: \PACS code \sep code
+
+%% MSC codes here, in the form: \MSC code \sep code
+%% or \MSC[2008] code \sep code (2000 is the default)
+
+\end{keyword}
 
@@
   \centering
-  \includegraphics[width=\singlecolumnsize]{Figures/branin_side_moments_noscale.pdf}
+  \includegraphics[width=\singlecolumnsize]{Figures/FIG01.pdf}
   \caption{The left column concerns $\JBH$, while the right one deals with $\JBHS$.
@@
   \centering
-  \includegraphics[width=\singlecolumnsize]{Figures/branin_side_66.pdf}
+  \includegraphics[width=\singlecolumnsize]{Figures/FIG02.pdf}
   \caption{Top Left:  $\JBH$ along with conditional minimisers in red.
@@
 \centering
-\includegraphics[width=\onehalfcolumn]{Figures/relaxation_tuto.pdf}
+\includegraphics[width=\onehalfcolumn]{Figures/FIG03.pdf}
 \caption{Principle of the relaxation of the constraint on $\JBH$, and illustration of $R_\alpha(\mathbf{k})$.
@@
 \centering
-\includegraphics[width = \singlecolumnsize]{Figures/illu_alpha_p.pdf}
+\includegraphics[width = \singlecolumnsize]{Figures/FIG04.pdf}
 \caption{Illustration of the influence of different levels $p$ on $\Gamma_{\alpha_p}$ and on $\mathbf{k}_p$ for $\JBHS$}
@@
   \centering
-\includegraphics[width=\onehalfcolumn]{Figures/branin_side_66_relax_gamma_both.pdf}
+  \includegraphics[width=\onehalfcolumn]{Figures/FIG05.pdf}
 \caption{Top: $\JBH$ and $\JBHS$ contours.
@@
    \centering
-\includegraphics[width=\onehalfcolumn]{Figures/alpha_p_BH.pdf}
+\includegraphics[width=\onehalfcolumn]{Figures/FIG06.pdf}
 \caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $\JBH$. The dashed line indicates the level $p$ associated with the highest ratio}
@@
   \centering
-\includegraphics[width=\onehalfcolumn]{Figures/profile_BH.pdf}
+\includegraphics[width=\onehalfcolumn]{Figures/FIG07.pdf}
 \caption{Profiles of the different estimates for $\JBH$, corresponding to the vertical cross sections of the contour.
@@
   \centering
-\includegraphics[width=\onehalfcolumn]{Figures/alpha_p_BHs.pdf}
+\includegraphics[width=\onehalfcolumn]{Figures/FIG08.pdf}
 \caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $\JBHS$. The dashed line indicates the level $p$ associated with the highest ratio}
@@
   \centering
-\includegraphics[width=\onehalfcolumn]{Figures/profile_BHs.pdf}
+\includegraphics[width=\onehalfcolumn]{Figures/FIG09.pdf}
 \caption{Profiles of the different estimates for $\JBHS$.
@@
 \centering
-\includegraphics[width=\singlecolumnsize]{Figures/RobustSWEmis_plots.pdf}
+\includegraphics[width=\singlecolumnsize]{Figures/FIG10.pdf}
 \caption{Procedure of robust calibration for the shallow water problem.
@@
   \centering
-  \includegraphics[width=\onehalfcolumn]{Figures/alpha_SWE}
+  \includegraphics[width=\onehalfcolumn]{Figures/FIG11}
   \caption{Evolution of $\alpha_p$ for different levels $p$, and ratio, for the shallow water problem}
@@
   \centering
-  \includegraphics[width=\onehalfcolumn]{Figures/profile_swe}
+  \includegraphics[width=\onehalfcolumn]{Figures/FIG12}
   \caption{Profiles for the calibration problem, for the shallow water case}
@@
 \centering
-\includegraphics[width=\onehalfcolumn]{Figures/L2_full_rel.pdf}
+\includegraphics[width=\onehalfcolumn]{Figures/FIG13.pdf}
 \caption{Squared forecast error for the shallow water case, depending on the calibrated parameter.
@@
   \centering
-  \includegraphics[width=\onehalfcolumn]{Figures/CRPS_full_rel}
+  \includegraphics[width=\onehalfcolumn]{Figures/FIG14}
   \caption{CRPS computed for different calibrated parameters for the shallow water case.

### 2020-09-07 article.tex
add comments of revision july 2020

@@
 
-\documentclass[preprint, 1p]{elsarticle}
+\documentclass[preprint, review, 1p]{elsarticle}
 
@@
 The probability measure of $\mathbf{U}$ is $\Prob_{\mathbf{U}}$, and its density, if it exists, is $p_{\mathbf{U}}$.
-%Furthermore, $\mathbf{u}^t$ (used to generate $\mathbf{y}^{\mathrm{obs}}$) is sampled from $\mathbf{U}$.
+\victor{\#3: Did the authors implicitly assume that the aleatoric uncertainty is independent with the epistemic uncertainty?
+The authors should clarify this issue.}%Furthermore, $\mathbf{u}^t$ (used to generate $\mathbf{y}^{\mathrm{obs}}$) is sampled from $\mathbf{U}$.
 %
@@
 It is most often defined as the squared norm of a given function $\mathcal{G}(\mathbf{k}, \mathbf{U})$% involving the numerical model.
+\victor{\# 2: How should one choose and/or construct $U$ ?}
 \begin{align}
@@
 Illustration of the various described methods are given on a numerical exemple in Section~\ref{sec:SWE_application}.
+\victor{\# 1: In the existing literature, there are many robust estimation approaches, such as distributionally robust methods and the regularization strategy to improve robustness.
+What are the specific values of relative regret in case studies?
+Why this regret metric matter in real practice?
+The novelty should be highlighted in the revised manuscript by comparing with the above mentioned approaches.}
+
+\victor{\# 4: The literature review on optimization under uncertainties is relatively good.
+However, it still needs improvement to reflect the recent advances in this area.
+To help the reader get to know the state-of-the-art, the authors should add the work on "optimization under uncertainty in the era of big data and deep learning" in the revised manuscript}
 
@@
  \section{Relative regret-based family of estimators}%A new family of robust estimators \elise{titre a revoir}}
+ \victor{\# 5:For the proposed "relative regret-based family of estimators", the authors seem to know the probability distribution of u perfectly, this is impractical for real applications.
+Please consider some realistic applications where this distribution can be known and why it can be known perfectly.}
+\victor{\# 6: Why only consider relative regret?
+How about absolute regret (the difference between the estimated one and the optimal value)?
+Should the authors use the worst-case relative regret if only uncertainty set is known.
+The authors should carefully address this issue.}
 \label{sec:relax_constraint}
 \subsection{Relaxing the optimality constraint}
+
 The density of minimisers has been estimated by optimising $\mathbf{k}\mapsto J(\mathbf{k},\mathbf{U}=\mathbf{u})$ over $\Kspace$ for different realisations of $\mathbf{u}$.
@@
 \includegraphics[width = \singlecolumnsize]{Figures/FIG04.pdf}
-\caption{Illustration of the influence of different levels $p$ on $\Gamma_{\alpha_p}$ and on $\mathbf{k}_p$ for $\JBHS$}
+\caption{Illustration of the influence of different levels $p$ on $\Gamma_{\alpha_p}$ and on $\mathbf{k}_p$ for $\JBHS$ \victor{\# 7: difficult to identify the difference in color of the last two lines.
+The authors should revise the figure accordingly.}
+}
 \label{fig:illu_alpha_p}
@@
 
-By considering the particular case where $p=1$, a relation between $\checkk_1$ and $\checka_1$ can be derived, by using Eq.~\eqref{eq:def_alpha_check} and the strict positivity of the cost function:
+By considering the particular case where $p=1$, a relation between $\checkk_1$ and $\checka_1$ can be derived, by using Eq.~\eqref{eq:def_alpha_check} and the strict positivity of the cost function: \victor{\# 8: if the probability distribution Pu is perfectly known for the chance constraint, it seems to be trivial to the sample average approximation (SAA) method.
+How can the authors quantify the error of using this approximation method?
+Will it have an impact on the calibration results?
+The authors should explain it in detail}
 \begin{equation}
@@
 
+\victor{\# 9: The authors need to justify why their proposed approach is robust calibration based on a stochastic approach (using probability distribution and chance constraint)?}
 % ----------------------------------------------------------------------------

### 2020-10-25 response.tex
accepted version + zip of src

\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage[utf8]{inputenc}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{calc}
\usepackage{caption}
% \usepackage{zref-xr}
% \externaldocument{article}
\usepackage{easy-todo}
\usepackage{comment}
\usepackage{lipsum}
\usepackage{bbm}
\usepackage{fancyhdr}
\usepackage{tikz}
\usepackage{pdfpages}
\newcommand{\Var}{\mathbb{V}\text{ar}}
\newcommand{\Ex}{\mathbb{E}}
\newcommand{\Prob}{\mathbb{P}}
\DeclareMathOperator*{\argmin}{arg\,min \,}
\DeclareMathOperator*{\argmax}{arg\,max \,}
\usepackage{hyperref}
\usepackage{booktabs}

\begin{document}
\title{JCOMP-D-20-00132: Authors' response to reviewers:\\
  Robust calibration of numerical models based on relative regret
}

\maketitle
We would like to thank the reviewer for their review. Their comments helped us clarify and improve some points in the manuscript, and we got to study some aspects of the problem that we have not necessarily considered before.

In the revised manuscript, we adressed the concerns raised by the reviewer, and made some adjustements on the original text. The changes to the original text have been highlighted in {\color{teal}teal}.
\section{Reply to the reviewers}
\begin{enumerate}
\item\textit{In the existing literature, there are many robust estimation approaches, such as distributionally robust methods and the regularization strategy to improve robustness. What are the specific values of relative regret in case studies?} \textit{ Why this regret metric matter in real practice? The novelty should be highlighted in the revised manuscript by comparing with the above mentioned approaches.}

    In this work, as we assumed that $\mathbf{U}$ is perfectly known, so we did not consider distributional robustness, as now explained l~.84.
    In this work, we wanted to avoid an \emph{aggregation} approach, where the value of the cost function is integrated with respect to the environmental variable (such as moment optimisation).
    We wanted instead to consider separately each optimization problem corresponding to each $\mathbf{u}\in \mathbb{U}$, and measure the similarity of the cost function at a value $J(\mathbf{k},\mathbf{u})$ with $J^*(\mathbf{u})$. As now mentioned l.~282, this is linked to the optimisation of the Value-at-Risk, or equivalently, to the minimisation of a quantile, l.~345. This metric allows us to control the risk in terms of deviation from the optimal value.% . For a couple $(p=.90, \alpha_p=1.1)$, this approach allow us to make the following statement true: in 90\% percent of the cases, the objective function does not deviate more than $10\%$ from its optimal value.
 % l.~109 l.~233, l.~264

   % séparer questions, et valider
  % We 
\item \textit{For Equation (1), how do the authors choose the sample space U. How should one construct it?}

We assume that the aleatoric uncertainties, modelled as a random variable $\mathbf{U}$, come from expert knowledge, and then its distribution and its sample space is assumed to be known. This is now explicitely stated l.~62. If it is not known, we refer the reader as advised to the article mentioned in the comment \# 4
\item \textit{In Page 2, the authors mentioned that "set to be estimated to reduce epistemic errors. The aleatoric uncertainties are modelled as a random vector". Did the authors implicitly assume that the aleatoric uncertainty is independent with the epistemic uncertainty? The authors should clarify this issue.}

  We assume indeed that the epistemic and aleatoric uncertainties are independent, due to the fact that the aleatoric uncertainties come from some external forcings of models, and that the choice of our control parameter does not affect the aleatoric uncertainties. This is now explicitly addressed in the introduction (l.67).

\item \textit{The literature review on optimization under uncertainties is relatively good. However, it still needs improvement to reflect the recent advances in this area. To help the reader get to know the state-of-the-art, the authors should add the work on "optimization under uncertainty in the era of big data and deep learning" in the revised manuscript.
  }

  We indeed overlooked the problem of the possibly unknown distribution of $\mathbf{U}$. The paper is now cited in the literature review l.~64. In this section, we mention especially data-driven methods to model the aleatoric uncertainties, and mention now the case of distributional robustness.

\item \textit{For the proposed "relative regret-based family of estimators", the authors seem to know the probability distribution of u perfectly, this is impractical for real applications. Please consider some realistic applications where this distribution can be known and why it can be known perfectly.
  }

  We added a small discussion on the presumed knowledge of the distribution of $\mathbf{U}$ in the introduction l.~60. The  uncertainties are supposed to be known reasonably well, as they may come from empirical observations, or expert knowledge, in order to have relevant probabilistic description.

\item \textit{Why only consider relative regret? How about absolute regret (the difference between the estimated one and the optimal value)? Should the authors use the worst-case relative regret if only uncertainty set is known. The authors should carefully address this issue.}

  We added a comparison between relative and additive regret p.~13, l.~261, and motivated the choiceof the relative regret: choosing the relative regret allows the decider to put less weight on the region around $\mathbf{k}^*(\mathbf{u})$ when $\mathbf{u}$ corresponds to a bad situation (\textit{i.e.} when $J^*(\mathbf{u})$ is large). We hope this is clarified by the explanation l.~262.

\item \textit{In Figure 4, it is difficult to identify the difference in color of the last two lines. The authors should revise the figure accordingly.}

  The colors and linestyles in Figure 4 have been updated for more clarity.

\item \textit{ For Equation (19), if the probability distribution Pu is perfectly known for the chance constraint, it seems to be trivial to the sample average approximation (SAA) method. How can the authors quantify the error of using this approximation method? Will it have an impact on the calibration results? The authors should explain it in detail.}

  Eq.~(19) is now Eq.~(22) in the revised document. We introduced in Eq.~(25) the Sample Average Approximation of the Eq.~(20). Using SAA, the resulting $\hat{\alpha}_1$ is a lower bound on the true value. Furthermore, we can also use this estimated value to get a probabilistic upper bound on $\alpha_p$ for the prescribed level $p=(\eta/2)^{1/N}$, meaning that the approximated solution will be at least feasible at such a level with probability $1-\eta$.

\item \textit{The authors need to justify why their proposed approach is robust calibration based on a stochastic approach (using probability distribution and chance constraint)?}
From a random objective function $J(\mathbf{k}, \mathbf{U})$, we introduce the relative-regret which is a normalized quantity (l.~270). Our approach is then to introduce a chance-constraint on this relative-regret, as done Eq.~(20), in order to be able to control the deviations relative to the optimal value with some probability. In the case of almost-surely verified constraints (Eq.~(21) and (22)), this approach is quite similar to optimising in the worst-case the relative-regret, as highlighted Eq.~(24). Given $p$ and $\alpha_p$, our approach look then to minimise the relative-regret for the proportion $p$ of best-cases as now explained l.~286. We also highlighted the principle and novelty of our approach in the abstract l.11, and in the conclusion l.~557.

\end{enumerate}

\section{Summary of the changes}
\emph{Abstract (p.1)}
\begin{itemize}  
\item l.~5-8: clarified the distinction between control parameters, and uncontrollable random variables
\item l~.11-16: highlighted the role and novelty of the relative regret in this article
\end{itemize}
\emph{Introduction (p.1)}
\begin{itemize}
\item l.~34-37: added source of aleatoric uncertainties for ocean modelling
\item l.~38-48: added effect of omitting the uncertainties in problems
\item l.~48-51: added examples of the necessity of taking into account uncertainties, from a risk management perspective
\item l.~52-56: added different vocabulary found in the literature which convey the same idea
\item l.~57: fixed some typos and english mistakes.
\item l.~60: we explicit the knowledge of the distribution of $\mathbf{U}$.
\item l.~64: added state-of-the-art strategies to model aleatoric uncertainties and citation to Ning \& You.
\item l~.66-68: we clarify that the distributinto $\mathbf{U}$ is not dependent on the value of $\mathbf{k}$
\item l.~73: a reference to an exemple of such a cost function is added
\item l.~82: fixed typo
\item l.~84-85: added the mention of distributional robustness 
\item l.~92: added mention of overcalibration
\item l.~83: typo
\item l.~96,98,99: reformulation for clarity
\item l.~109: added rationale of the relative regret
\item l.~115: typo
\end{itemize}
\emph{Section 2 (p.5)}
\begin{itemize}
\item l.~119: change for clarification
\end{itemize}
\emph{Section 3.1 (p.11)}
\begin{itemize}
\item l.~232-238: clarification of the construction and definition of the relative-regret 
\item l.~253: added reminder that $\mathbf{K}^*$ is discrete.
\item l.~261-272: comparison between additive and relative regret, and justification of the use of relative-regret
\item l.~278-279: formulation of the problem in terms of chance-constraints in Eq.~(20)
\item l.~281-282: clarification of the link with the Value-at-Risk 
\item l.~283-286: interpretation of $\alpha_p$ in terms of bounding probabilistically the relative-error
\item l.~287-288: rewrote the definition of the RRE
\item l.~289-291: typo and english reformation
\item Figure 4 (p.14): changed linestyle, and added quick interpretation in the caption 
\item l.~293: added small synthesis on the properties of the RRE
\end{itemize}
\emph{Section 3.2 (p.14)}
  \begin{itemize}
\item l.~301: added subsection Almost-surely bounded relative-regret
\item l.~302-308: formulation of the a.s.\ bounded relative-regret in terms of chance constraint in Eq.~(21) and property verified by $\mathbf{k}_1$ and $\alpha_1$
\item l.~309-314: link with uncertain set and Savage's minimax approach for decision under uncertainty
\item l.~315-317: SAA formulation of the a.s. bounded constraint
\item l.~317-325: Probabilistic bounding of $\alpha_1$, and level $p=(\eta/2)^{1/N}$ guaranteed probabilistically
\item l.~330-333: clarify formulation of the general case $p \leq 1$
\item l~.336-337: estimation of $\Gamma_\alpha$ with indicator functions (Eq.~(27))
\item l~.339: possibility of unsatisfactory $(p, \alpha_p)$
\item l.~344: minimization of the quantile of order $p$ of the ratio $J / J^*$.
\end{itemize}
 \emph{Conclusion (p.31)}
\begin{itemize}
\item l~.557-564: summary of the robustness aspect of the RRE
\item l~.578-580: reformulation of the sequential design of experiment strategies.
\end{itemize}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2020-10-25 source_files/article.tex
accepted version + zip of src

--- 2020-09-07 article.tex
@@
 
-\documentclass[preprint, review, 1p]{elsarticle}
+\documentclass[preprint,review, 1p]{elsarticle}
 
@@
 \usepackage[utf8]{inputenc}
+\usepackage{soul}
+\usepackage{verbatim}
 %% The amsthm package provides extended theorem environments
@@
 %% for the whole article with \linenumbers.
-%% \usepackage{lineno}
+\usepackage[mathlines]{lineno}
+
 \usepackage{graphicx}
@@
 \newcommand{\JBHS}{J_{\mathrm{BHswap}}}
-
+\DeclareMathOperator*{\esssup}{ess\,sup}
 \newcommand{\arthur}[1]{{\itshape\color{cyan} ({#1})}}
 \newcommand{\elise}[1]{{\itshape\color{red} ({#1})}}
-\newcommand{\victor}[1]{{\itshape\color{green} ({#1})}}
+\newcommand{\victor}[1]{{\itshape\color{blue}}}
+\newcommand{\remove}[1]{{\color{red} {}}}
+\newcommand{\added}[1]{{\color{teal} #1}}
 \usepackage{url}
@@
 \definecolor{newcolor}{rgb}{.8,.349,.1}
-
+\usepackage{bbm}
 \newlength{\minisize}
@@
 \setlength{\fullwidth}{19cm}
+\usepackage{etoolbox}
 
@@
 
+\newcommand*\linenomathpatchAMS[1]{%
+  \expandafter\pretocmd\csname #1\endcsname {\linenomathAMS}{}{}%
+  \expandafter\pretocmd\csname #1*\endcsname{\linenomathAMS}{}{}%
+  \expandafter\apptocmd\csname end#1\endcsname {\endlinenomath}{}{}%
+  \expandafter\apptocmd\csname end#1*\endcsname{\endlinenomath}{}{}%
+}
+\expandafter\ifx\linenomath\linenomathWithnumbers
+  \let\linenomathAMS\linenomathWithnumbers
+  %% The following line gets rid of an extra line numbers at the bottom:
+  \patchcmd\linenomathAMS{\advance\postdisplaypenalty\linenopenalty}{}{}{}
+\else
+  \let\linenomathAMS\linenomathNonumbers
+\fi
+\linenomathpatchAMS{gather}
+\linenomathpatchAMS{multline}
+\linenomathpatchAMS{align}
+\linenomathpatchAMS{alignat}
+\linenomathpatchAMS{flalign}
 \begin{document}
-
+\linenumbers
 %% Title, authors and addresses
@@
 %% Text of abstract
-Classical methods of parameter estimation usually imply the minimisation of an objective function, that measures the error between some observations and the results obtained by a numerical model.
-In the presence of random inputs, the objective function becomes a random variable, and notions of robustness have to be introduced.
-
-In this paper, we are going to present how to take into account those uncertainties by defining a family of calibration objectives based on the notion of relative-regret with respect to the best attainable performance given the uncertainties and compare it with the minimum in the mean sense, and the minimum of variance.
+  Classical methods of \added{calibration}\remove{parameter estimation} usually imply the minimisation of an objective function \added{with respect to some control parameters.
+This function}\remove{, that} measures the error between some observations and the results obtained by a numerical model.
+In the presence of %uncontrollable/random nuisance
+  \added{uncontrollable additional parameters that we model as} random inputs, the objective function becomes a random variable, and notions of robustness have to be introduced \added{for such an optimisation problem.}
+
+  \remove{In this paper, we are going to present how to take into account those uncertainties by defining a family of calibration objectives based on the notion of relative-regret.
+with respect to the best attainable performance given the uncertainties and compare it with the minimum in the mean sense, and the minimum of variance.}
+
+  \added{In this paper, we are going to present how to take into account those uncertainties by defining the relative-regret.
+This quantity allow us to compare the value of the objective function to its best performance achievable  given a realisation of the random additional parameters.
+By controlling this relative-regret using a probabilistic constraint, we can then define a new family of estimators, whose robustness with respect to the random inputs can be adjusted.}
+
 \end{abstract}
@@
 %
-An application of such an approach, in the context of ocean circulation modeling, is the estimation of ocean bottom friction parameters in~\cite{das_estimation_1991} and~\cite{boutet_estimation_2015}.
-
-If parameters to be estimated are not the only source of uncertainties, their optimal control 
-%However, in the presence of other sources of uncertainties, parameter estimation 
+An application of such an approach, in the context of ocean circulation modelling, is the estimation of ocean bottom friction parameters, as done in~\cite{das_estimation_1991,das_variational_1992,boutet_estimation_2015}.
+\added{Moreover, as such studies are often performed at a coastal and regional scale, those models are often designed with open boundary conditions, and require external forcings, such as tidal and wind forcing.
+Those are then a source of aleatoric uncertainties, that should be taken into account as in~\cite{ten_brummelhuis_parameter_1990}.}
+\remove{If parameters to be estimated are not the only source of uncertainties, their optimal control 
   is doomed to overfit the data, \emph{e.g} to artificially introduce errors in the controlled parameter to compensate for other sources.
-If such uncertainties are of aleatoric nature, then the parameter estimation is only optimal for the observed situation, and may be very poor in other configurations, phenomenon coined as \textit{localized optimisation} in~\cite{huyse_free-form_2001}.
+If such uncertainties are of aleatoric nature, then the parameter estimation is only optimal for the observed situation, and may be very poor in other configurations, phenomenon coined as \textit{localized optimisation} in~%\cite{huyse_free-form_2001}.%
+}
+
+\added{If we overlook the aleatoric uncertainties by choosing a specific outcome, the optimal control of the parameters to be estimated can lead to \emph{localized optimisation} \citep{huyse_free-form_2001} and \emph{overcalibration}, that is choosing a value that is optimal for the given situation.
+This value does not carry the optimality to other situations.
+  In geophysics and especially in hydrological models, this overcalibration may lead to the appearance of abberations in the predictions as those uncertainties become prevalent sources of errors.
+In hydrology, uncertainties are the principal culprit of the existence of so called ``Hydrological monsters''~\citep{kuczera_there_2010}, that are calibrated models that perform really badly because some uncertainties in the modelling have been omitted, such as measurements errors.
+In flood modelling~\cite{wong_neglecting_2018}, the aleatoric uncertainty come from the structure of the model, and neglecting those uncertainties leads to underestimating hazard.
+In other domains as well, the aleatoric uncertainties can represent some manufacturing errors or environmental conditions such as wind direction and speed in wind turbine modelling~\cite{hu_robust_2011} or atmospheric conditions in aerospace vehicle design~\cite{brevault_contributions_2015}, thus they represent an important role in risk management.}
 %A methodology based on the Hessian matrix has been described in~\cite{ribaud_krigeage_2018-1}.
 %\arthur{L\`A AUSSI UNE REF SERAIT BIENVENUE}.
-Taking into account aleatoric uncertainties in optimisation problems takes several names, including \textit{robust optimisation}, \textit{robust design} in~\cite{lelievre_consideration_2016}, or \textit{optimisation under uncertainties} \citep{petrone_robustness_2011, seshadri_density-matching_2014,cook_horsetail_2018}.
+
+\added{It is then crucial to be able to take into account aleatoric uncertainties in optimisation problems.
+This consideration is called \textit{robust optimisation}, or also \textit{robust design} in~\cite{lelievre_consideration_2016}, or \textit{optimisation under uncertainties} \citep{petrone_robustness_2011,seshadri_density-matching_2014,cook_horsetail_2018}.
+Furthermore, the distinction is sometimes made between \emph{stochastic optimisation} and \emph{robust optimisation}, depending on the knowledge available on the aleatoric uncertainties.}% Présicer pbs + autres exemple avec unc aleatoric prises en compte -> flood
+% \remove{Taking into account aleatoric uncertainties in optimisation problems takes several names, including \textit{robust optimisation}, \textit{robust design} in~\cite{lelievre_consideration_2016}, or \textit{optimisation under uncertainties} \citep{petrone_robustness_2011,seshadri_density-matching_2014,cook_horsetail_2018}.}
 
@@
 
-%Taking into account aleatoric uncertainties while calibrating the model (reducing epistemic uncertainties) is often referred as {\it robust control problem} in the literature (see for instance, \arthur{REFs}), or optimization under uncertainties \citep{petrone_robustness_2011, seshadri_density-matching_2014,cook_horsetail_2018}.
-
-Let's denote $\mathbf{k} \in \Kspace$ the parameter set to be estimated to reduce epistemic errors.
-The aleatoric uncertainties are modelled as a random vector $\mathbf{U}$ whose sample space is $\Uspace$.
-The probability measure of $\mathbf{U}$ is $\Prob_{\mathbf{U}}$, and its density, if it exists, is $p_{\mathbf{U}}$.
-\victor{\#3: Did the authors implicitly assume that the aleatoric uncertainty is independent with the epistemic uncertainty?
+%Taking into account aleatoric uncertainties while calibrating the model (reducing epistemic uncertainties) is often referred as {\it robust control problem} in the literature (see for instance, \arthur{REFs}), or optimisation under uncertainties \citep{petrone_robustness_2011, seshadri_density-matching_2014,cook_horsetail_2018}.
+
+\remove{Let's} \added{Let us} denote $\mathbf{k} \in \Kspace$ the parameter \remove{set} to be estimated \added{in order} to reduce epistemic \remove{errors} \added{uncertainties}.
+\added{We assume that the aleatoric uncertainties can be modelled as a} random vector $\mathbf{U}$ whose sample space is $\Uspace$.
+The probability measure \added{associated with}\remove{of} $\mathbf{U}$ is $\Prob_{\mathbf{U}}$, and its density, if it exists, is $p_{\mathbf{U}}$.
+\added{This distribution is assumed to be known, and that it is possible to sample from it.
+This choice is motivated by the fact that in various applications, the aleatoric uncertainties come from expert knowledge, empirical observations, or the knowledge acquired using other models, for instance by ensemble assimilation.
+%  An example is functional uncertainties, where the random process can be decomposed on an orthogonal basis of random variables, which are uncorrelated and can be estimated.
+  However, if it is not the case,~\cite{ning_optimization_2019} provides a comprehensive review of optimisation under uncertainty, especially on the modelling and sampling of the aleatoric uncertainties.
+Since the source of the aleatoric uncertainties is considered external, the choice of $\mathbf{k}$ does not have any influence on the distribution of the random variable $\mathbf{U}$, and therefore the aleatoric and epistemic uncertainties are assumed independent.
+  %%%%
+
+}
+
+\victor{\#3 \checkmark: Did the authors implicitly assume that the aleatoric uncertainty is independent with the epistemic uncertainty?
 The authors should clarify this issue.}%Furthermore, $\mathbf{u}^t$ (used to generate $\mathbf{y}^{\mathrm{obs}}$) is sampled from $\mathbf{U}$.
@@
 \victor{\# 2: How should one choose and/or construct $U$ ?}
-\begin{align}
+\victor{
+  \begin{itemize}
+  \item Control on $\mathbf{k}$ but not on $\mathbf{u}$ + examples \checkmark
+  \item Misspecification and monsters \checkmark
+  \item Challenging examples
+  \item Give example of $J$, $\mathbf{k}$, $\mathbf{u}$
+  \end{itemize}
+}
+\begin{linenomath*}
+\begin{equation}
   \label{eq:def_cost_fun}
-  J(\mathbf{k},\mathbf{U}) & = \frac12\|\mathcal{G}(\mathbf{k}, \mathbf{U})\|^2
-  \end{align}
+  J(\mathbf{k},\mathbf{U}) = \frac12\|\mathcal{G}(\mathbf{k}, \mathbf{U})\|^2
+  \end{equation}
+\end{linenomath*}
+
 %$J$ is possibly complemented by a regularisation function that is omitted here for the sake of clarity. 
   For instance, in data assimilation, $J$ describes a distance between the output of the numerical model and given observed data, plus generally some regularization terms.
+\added{An example of such a function will be treated Section~\ref{sec:SWE_application}.}
+
 %Calibrating the numerical models consists in the computation of $\kest$ verifying
@@
 Indeed, one definition of the robustness of an estimate is a measure of the sensibility of said estimate to outliers~\citep{huber_robust_2011}.
-This lead to the introduction of robust norms in data assimilation \citep{rao_robust_2015}.
+This \remove{lead}\added{leads} to the introduction of robust norms in data assimilation \citep{rao_robust_2015}.
 %The point of this norm is to assume Gaussian distribution for small errors (the usual $L_2$ norm), while the large errors are assumed to be Laplace distributed (so the $L_1$ norm).
 In a Bayesian framework, robustness may refer to the sensitivity to a wrong specification of the priors~\citep{berger_overview_1994}.
-%
+\added{As the distribution of $\mathbf{U}$ is assumed known, we are not going to consider \emph{distributional robustness}, which deals with uncertainties on the distribution of $\mathbf{U}$~\cite{rahimian_distributionally_2019}.}
+
 Throughout this paper, 
@@
  In this case, $\kest$ is set to the optimum ${\mathbf{k}}_{\mathbf{u}^{b}} $ of $J(\mathbf{k}, \mathbf{U}=\mathbf{u}^b)$.
-There is no guarantee on the performance of $\kest$ if the calibrated model is used for predictions, as the estimated value will compensate the error made by a possibly wrong specification of $\mathbf{u}^b$.
-In a data assimilation context, this situation appears if $\mathbf{u}^b$ does not properly represent the conditions on which the observations have been obtained.
+There is no guarantee on the performance of $\kest$ if the calibrated model is used for predictions, as the estimated value will compensate the error made by a possibly wrong specification of $\mathbf{u}^b$\added{: this may be a case of \emph{overcalibration}}
+ In a data assimilation context, this situation appears if $\mathbf{u}^b$ does not properly represent the conditions \remove{on}\added{in} which the observations have been obtained.
+
 Another strategy, that consists in minimising $J$ over the joint space $\Kspace\times\Uspace$, is not always possible or relevant.
-The complexity of the optimisation is increased, and the computed estimation of $\kest$ has no reason to be robust in the end: this kind of method does not take into consideration the variability of the uncertain variable.
+\added{Indeed, joint optimisation increases} the complexity of the optimisation\remove{is increased}, and the computed estimation of $\kest$ has no reason to be robust in the end: this kind of method does not take into consideration the \added{intrinsic} variability of the \added{environmental}\remove{uncertain} variable.
 %
@@
 Both approaches and related robust estimates are described in Section~\ref{robust formulations}.
-Section~\ref{sec:relax_constraint} introduces a new class of estimators, by relaxing the constraint of optimality and defining regions of acceptability, similarly as~\cite{buhmann_robust_2013} in discrete combinatorial problems, or~\cite{kouvelis_algorithms_1992,snyder_stochastic_2004} in operation research.
-The intention is that a robust estimate provides values of the cost function close enough to the attainable minimum for each configuration induced by $\mathbf{u}\in\Uspace$.
-Illustration of the various described methods are given on a numerical exemple in Section~\ref{sec:SWE_application}.
+Section~\ref{sec:relax_constraint} introduces a new class of estimators, by relaxing the constraint of optimality and defining regions of acceptability, similarly as~\cite{buhmann_robust_2013} in discrete combinatorial problems, or~\cite{kouvelis_algorithms_1992,snyder_stochastic_2004} in operation\added{s} research.
+\added{The rationale behind this relaxation is to be able to construct an estimate $\kest$ which produces values of the cost function close enough from the minimal cost attainable given the configuration induced by $\mathbf{u} \in \Uspace$, with high enough probability.}\remove{The intention is that a robust estimate provides values of the cost function close enough to the attainable minimum for each configuration induced by $\mathbf{u}\in\Uspace$.} \added{This similarity will be measured using the relative regret.
+By adjusting either the relaxation or the confidence level, we can then define the \RRE{}, the relative-regret family estimators.
+}Illustration of the various described methods are given on a numerical \remove{exemple}\added{example} in Section~\ref{sec:SWE_application}.
 \victor{\# 1: In the existing literature, there are many robust estimation approaches, such as distributionally robust methods and the regularization strategy to improve robustness.
@@
 However, it still needs improvement to reflect the recent advances in this area.
-To help the reader get to know the state-of-the-art, the authors should add the work on "optimization under uncertainty in the era of big data and deep learning" in the revised manuscript}
+To help the reader get to know the state-of-the-art, the authors should add the work on "optimization under uncertainty in the era of big data and deep learning" in the revised manuscript;\checkmark}
 
@@
 As mentioned before, robustness can be understood as satisfactory for a broad range of $\mathbf{u}$, and/or as insensitive as possible to uncertainties encompassed in $\mathbf{U}$.
-Under this definition, one may design robust estimators, either by using the moments of the cost function; or by exploiting the distribution of its minimisers.
+Under this definition, one may design robust estimators \added{of $\mathbf{k}$}, either by using the moments of the cost function; or by exploiting the distribution of its minimisers.
 % ----------------------------------------------------------------------------
@@
 Let us define $\mu(\mathbf{k})$ and $\sigma^2(\mathbf{k})$, the expected value and the variance of the cost variable  for a given $\mathbf{k}$ as 
+\begin{linenomath*}
 \begin{align}
@@
 \end{align}
+\end{linenomath*}
+
 %
 Minimising the expectation leads to the estimate $\kmean$ defined by:
+\begin{linenomath*}
 \begin{equation}
@@
 \end{equation}
+\end{linenomath*}
+
 In order to take into account the spread around the mean value, one can choose to minimise the variance, leading to $\kvar$:
+\begin{linenomath*}
 \begin{equation}
@@
 \end{equation}
+\end{linenomath*}
 
@@
 The estimations at a given $\mathbf{k}$ are computed using standard Monte Carlo, resulting in the following optimisation problems:
+\begin{linenomath*}
 \begin{equation}
@@
 \end{equation}
+\end{linenomath*}
+
 and
+\begin{linenomath*}
 \begin{equation}
@@
 \end{equation}
+\end{linenomath*}
+
 %In the following, the hat notation will indicate an estimator. 
@@
 Some are based on a weighted sum of the objectives, as presented in~\cite{grodzevich_normalization_2006} and in~\cite{marler_weighted_2010}, while some others are based on the minimisation of one of the objectives under constraints on the others, as performed in~\cite{lehman_designing_2004}.
-Both of these methods are based on an \textit{delicate} choice of weights or of constraints before any computation.
+Both of these methods are based on an {delicate} choice of weights or of constraints before any computation.
 This choice relies heavily on a knowledge of the properties of the cost function.
@@
 The resulting conditional minimum is denoted $J^*$:
+\begin{linenomath*}
 \begin{equation}
@@
 \end{equation}
+\end{linenomath*}
+
 Similarly, the function of conditional minimisers can then defined by:
+\begin{linenomath*}
   \begin{equation}
@@
   \end{equation}
+\end{linenomath*}
+
 Using this function, we can define the corresponding random variable $\mathbf{K}^*$ as
+\begin{linenomath*}
   \begin{equation}
@@
   \end{equation}
+\end{linenomath*}
+
 and its associated density function $p_{\mathbf{K}^*}(\mathbf{k})$, that will be further referred as the density of minimisers.
 The mode of this density is called the Most Probable Estimate (MPE) and is noted  $\kmpe$:
+\begin{linenomath*}
 \begin{equation}
@@
 \end{equation}
+\end{linenomath*}
+
 To give some intuition on this estimate, let us imagine that the distribution of minimisers is a dirac centered on $\kmpe$.
@@
 
-In general, an analytical form of $p_{\mathbf{K}^*}$ is usually impossible to obtain, so an estimation $\hat{p}_{\mathbf{K}^*}$ must be used, and its maximum computed to get the MPE.
+In general, an analytical form of $p_{\mathbf{K}^*}$ is \remove{usually} impossible to obtain, so an estimation $\hat{p}_{\mathbf{K}^*}$ must be used, and its maximum computed to get the MPE.
 In the rest of the paper, the hat notation will indicate an estimation using numerical values of the underlying theoretical quantity.
@@
 KDE is a non-parametric estimation technique based on the use of a kernel function $f$. Assuming an isotropic kernel, the estimation has the following form:
+\begin{linenomath*}
 \begin{equation}
@@
 \end{equation}
+\end{linenomath*}
+
 where $h$ is the bandwidth.
@@
 The estimation has then the following form:
+\begin{linenomath*}
 \begin{equation}
@@
 \end{equation}
+\end{linenomath*}
+
 where $\phi( \cdot; \mathbf{m}, \mathbf{\Sigma})$ is the probability density function of the normal distribution of mean $\mathbf{m}$ and covariance matrix $\mathbf{\Sigma}$, and $\{\pi_i \}_{i=1 \dots \nu}$ are the mixing coefficients.
@@
 These functions are based on the Branin-Hoo's function, slightly modified to ensure strict positivity:
+\begin{linenomath*}
 \begin{align}
@@
  \mathrm{BH}(x_1,x_2) &= \frac{1}{51.95}\left[\left(\bar{x}_2 - \frac{5.1 \bar{x}_1^2}{4\pi^2} + \frac{5\bar{x}_1}{\pi} -6 \right)^2 + \left(10 - \frac{10}{8\pi}\right)\cos(\bar{x}_1)-44.81\right]+2\\
-&\text{with } \bar{x}_1 = 3x_1-5,\quad \bar{x}_2 = 3x_2
+&\text{with } \bar{x}_1 = 3x_1-5,\quad \bar{x}_2 = 3x_2 \nonumber
 \end{align}
+\end{linenomath*}
+
 %
 Using Eq.~\eqref{eq:branin_hoo}, we define the two cost functions on $\Kspace \times \Uspace = [0,5] \times [0,5]$ as:
-\begin{align*} \JBH : (\mathbf{k},\mathbf{u}) \mapsto \mathrm{BH}(\mathbf{k},\mathbf{u}) \\
+\begin{linenomath*}
+\begin{align} \JBH : (\mathbf{k},\mathbf{u}) \mapsto \mathrm{BH}(\mathbf{k},\mathbf{u}) \\
 \JBHS : (\mathbf{k},\mathbf{u}) \mapsto \mathrm{BH}(\mathbf{u},\mathbf{k})
-\end{align*}
+\end{align}
+\end{linenomath*}
+
 %We will continue to use $J$ as a generic notation for the cost function, when its use is not specific to the Branin-Hoo function.
@@
 
-The left, (resp.\ right), column stands for $\JBH$ (resp.\ $\JBHS$).
+The left\remove{,} (resp.\ right)\remove{,} column stands for $\JBH$ (resp.\ $\JBHS$).
 Functions $\mu(\mathbf{k})$ and $\sigma(\mathbf{k})$ are drawn on the bottom row, respectively in purple and green. The corresponding minimisers $\hatkmean$ and $\hatkvar$ are also plotted.
@@
 The density of minimisers has been estimated by optimising $\mathbf{k}\mapsto J(\mathbf{k},\mathbf{U}=\mathbf{u})$ over $\Kspace$ for different realisations of $\mathbf{u}$.
-Instead of focusing on optimal values, we propose to consider their {\it acceptable} neighbourhood in terms of performance of the cost function as well.
+Instead of focusing on optimal values, we propose
+\added{to construct an \textit{acceptable} {neighbourhood} in terms of performances of the cost function as well.
+In order to do so, we are going to introduce a relaxation coefficient $\alpha \geq 1$, and given $\mathbf{u}\in\Uspace$, we say that $\mathbf{k}\in \Kspace$ is acceptable when $J(\mathbf{k},\mathbf{U}=\mathbf{u}) \leq \alpha J^*(\mathbf{u})$.
+Using the strict positivity of the objective function, we can define the relative-regret as the ratio $J(\mathbf{k},\mathbf{U=u})/J^*(\mathbf{u})$, and the acceptability of $\mathbf{k}$ will then be tied to the maximal value taken by this ratio.}
+
+\remove{to consider their {\it acceptable} neighbourhood in terms of performance of the cost function as well.
 To do so, for each $\mathbf{u}$, $\mathbf{k}$ is deemed acceptable when  $J(\mathbf{k},\mathbf{U}=\mathbf{u}) \leq \alpha J^*(\mathbf{u})$, with $\alpha > 1$.
+\added{For $\mathbf{k}$, $\mathbf{u}$.
+The relative-regret is defined as the ratio $J(\mathbf{k},\mathbf{U=u})/J^*(\mathbf{u})$, for $\mathbf{u}\in \Uspace$, we say that $\mathbf{k}$ is acceptable at a level $\alpha$ if relative-regret is smaller than $\alpha$}}
 %
+
 %
 In this context, for a given $\mathbf{k}$, the set $R_{\alpha}(\mathbf{k}) \subseteq \Uspace$ is defined as the set of $\mathbf{u}$, for which $\mathbf{k}$ is acceptable:
+\begin{linenomath*}
 \begin{equation}
@@
 \end{equation}
+\end{linenomath*}
+
 Figure~\ref{fig:relax_tuto} details the successive steps for the construction of the set $R_{\alpha}$.
@@
 Introducing the random nature of $\mathbf{U}$, one can define $\Gamma_\alpha(\mathbf{k})$ as the probability that $\mathbf{k}$ is acceptable given $\alpha$:
+\begin{linenomath*}
 \begin{equation}
@@
 \end{equation}
+\end{linenomath*}
+
 In other words, $\Gamma_{\alpha}(\mathbf{k})$ is the probability that $J(\mathbf{k},\mathbf{U})$ is between 
@@
 
-This can be linked to the definition of the distribution of the minimisers $\mathbf{K}^*$.
-For instance, if $\Kspace$ is a discrete set, we can rewrite $\Gamma_1$ as $\Gamma_1(\mathbf{k})=\Prob_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U}=\mathbf{u}) = J^*(\mathbf{U})\right] = \Prob_{\mathbf{U}}\left[\mathbf{k} = \mathbf{k}^*(\mathbf{U})\right]$ which is the probability mass function of $\mathbf{K}^*$.
+This linked to the definition of the distribution of the minimisers $\mathbf{K}^*$.
+For instance, if $\Kspace$ is a discrete set, \added{$\mathbf{K}^*$ is a discrete random variable}, and we can rewrite $\Gamma_1$ as $\Gamma_1(\mathbf{k})=\Prob_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U}=\mathbf{u}) = J^*(\mathbf{U})\right] = \Prob_{\mathbf{U}}\left[\mathbf{k} = \mathbf{k}^*(\mathbf{U})\right]$ which is the probability mass function of $\mathbf{K}^*$.
 
@@
 For a given set of environmental conditions $\mathbf{u}$, if the function $\mathbf{k} \mapsto J(\mathbf{k},\mathbf{U}=\mathbf{u})$ is flat around its minimum $\mathbf{k}^*(\mathbf{u})$, then choosing  $\mathbf{k}^*(\mathbf{u}) + \epsilon$ (for a small $\epsilon$) will produce a value closer to the minimum than when the function has a high curvature.
-In addition to that, relaxing the constraint using a multiplicative constant puts more weight on the values of $\mathbf{k}^*(\mathbf{u})$ when $J^*(\mathbf{u})$ is small.
+
+\added{We consider in this work exclusively a multiplicative relaxation, instead of an additive one in the form $J(\mathbf{k},\mathbf{u}) \leq J^*(\mathbf{u}) + \beta$ for $\beta > 0$.
+Both formulations of the regret: the additive $J-J^*$ and the relative $J/J^*$, take into account the value of the conditional minimum $J^*(\mathbf{u})$, but relative regret allow us to scale the region of acceptable points with respect to the best situation available: if $J^*(\mathbf{u})$ is close to $0$, the region of acceptable points will grow slowly, so at a given $\alpha$, we put emphasis on $\mathbf{k}^*(\mathbf{u})$.
+On the other hand, if $J^*(\mathbf{u})$ is large, it means that tuning the parameter to $\mathbf{k}^*(\mathbf{u})$ will not lead to very good performances of the cost function anyway.
+We can then put less weight on this value $\mathbf{k}^*(\mathbf{u})$ in the estimation, hence the region of acceptability that grows quickly.
+Finally, the relative regret is a normalized quantity, in constrast to the additive regret, which shares the same unit as $J$.
+This normalization, as well as the direct relation to the relative error $\frac{J - J^*}{J^*}$ allows for an interpretation of the relaxation as a fraction of error.}
 
@@
 This leads to the definition of $\checkap$
+\begin{linenomath*}
 \begin{align}
@@
 \end{align}
+\end{linenomath*}
+
+\added{Rewriting the equation above, we can express $\alpha_p$ as the solution of the following chance constrained problem}
+% \added{\begin{equation}\label{eq:chance_constraint_formulation}
+%   \left\{
+%   \begin{array}{rl}
+%     \min  & q \\
+%     \text{such that}& \max_{\mathbf{k} \in \Kspace}\Prob_{\mathbf{U}}\left[\frac{J(\mathbf{k},\mathbf{U})}{J^*(\mathbf{U})} \leq q \right] \geq p
+%   \end{array}
+%   \right.
+% \end{equation}
+\added{
+  \begin{linenomath*}
+\begin{equation}\label{eq:chance_constraint_formulation}
+  \left\{
+  \begin{array}{rl}
+    \min & q \\
+    \text{s.t.} &% \max_{\mathbf{k}\in \Kspace}
+                  \max_{\mathbf{k}}\Prob_{\mathbf{U}}\left[\frac{J(\mathbf{k},\mathbf{U})}{J^*(\mathbf{U})} \leq q \right] \geq p% \quad \forall \mathbf{k}
+  \end{array}
+  \right.
+\end{equation}
+\end{linenomath*}
+
+}
+% \added{}
 that is the smallest $\alpha$, such that there exists a particular $\checkkp \in \Kspace$ for which $J(\checkkp,\mathbf{U}) \leq \checkap J^*(\mathbf{U})$ with probability $p$.
-$\{\mathbf{k}_p \text{ for } p \in [0;1] \}$ defines the relative-regret family of robust estimators (\RRE).
-This formulation can be linked to the quantiles and Value-at-Risk of the random variable $\max_{\mathbf{k}} \{ J(\mathbf{k},\mathbf{U}) / J^*(\mathbf{U})\}$, that is a measure of risk usually applied in the financial sector (see~\cite{rockafellar_deviation_2002}).
-For different levels $p$, and thus different $\alpha_p$, Figure~\ref{fig:illu_alpha_p} shows examples of $\Gamma_{\alpha_p}$ for $\JBHS$.
-By definition, the associated $\mathbf{k}_p$ is then the first value for which $\Gamma_{\alpha_p}$ reaches $p$.
-We can see that changing the level $p$ shifts the maximiser of $\Gamma_{\alpha_p}$, and that for small $\alpha$, $\Gamma_{\alpha}(\mathbf{k}_1)$ is also very small.
-This indicates that $\mathbf{k}_1$ is located quite far from the conditional minimisers, and arise as a compromise when the relaxation is large enough.
+\added{As highlighted by the formulation of Eq.~\eqref{eq:chance_constraint_formulation}, $\mathbf{k}_p$ and $\alpha_p$ are the result of the optimisation }of the Value-at-Risk of the random variable $J(\mathbf{k},\mathbf{U}) / J^*(\mathbf{U})$, \remove{that}\added{which} is a measure of risk usually applied in the financial sector (see~\cite{rockafellar_deviation_2002}).
+\added{In this spirit, when choosing $\mathbf{k}_p$, the relative error of the function $J$ will be less than $\alpha_p$ with probability $p$.
+The maximal relative regret of the function will be $\alpha_p$, except for the $100(1-p)\%$ least favourable cases.}
+
+\added{The set of maximisers of $\Gamma_{\alpha_p}$ for different $p$: $\{\mathbf{k}_p \text{ for } p \in [0;1] \}$ is what we are calling the relative-regret family of estimators \RRE.}
+\remove{$\{\mathbf{k}_p \text{ for } p \in [0;1] \}$ defines the relative-regret family of robust estimators (\RRE).}
+
+\remove{For different levels $p$, and thus different $\alpha_p$, }Figure~\ref{fig:illu_alpha_p} shows examples of $\Gamma_{\alpha_p}$ for $\JBHS$\added{, at different levels $p$, and the associated estimates of the \RRE.}
+\remove{By definition, the associated $\mathbf{k}_p$ is then the first value for which $\Gamma_{\alpha_p}$ reaches $p$.} We can see that changing the level $p$ shifts the maximiser of $\Gamma_{\alpha_p}$\remove{, and that for small $\alpha$, $\added{\max} \Gamma_{\alpha}\remove{(\mathbf{k}_1)}$ is also very small}.
+\added{Since} \remove{This indicates that }$\mathbf{k}_1$ is located quite far from the conditional minimisers, it arises as a compromise when the relaxation is large enough.
 
@@
 \includegraphics[width = \singlecolumnsize]{Figures/FIG04.pdf}
-\caption{Illustration of the influence of different levels $p$ on $\Gamma_{\alpha_p}$ and on $\mathbf{k}_p$ for $\JBHS$ \victor{\# 7: difficult to identify the difference in color of the last two lines.
-The authors should revise the figure accordingly.}
+\caption{Illustration of the influence of different levels $p$ on $\Gamma_{\alpha_p}$ and on $\mathbf{k}_p$ for $\JBHS$.
+\added{When $p$ increases, $\Gamma_{\alpha_p}$ increases as well.} \victor{\# 7: difficult to identify the difference in color of the last two lines.
+The authors should revise the figure accordingly.\checkmark}
 }
@@
 \end{figure}
+
+\victor{changed place}
+\remove{$\checkap$ can be \added{interpreted as} an indicator of the robustness of $\checkkp$.}%
+\remove{A high value of $\checka_1$ corresponds to a high ratio ${J(\mathbf{k},\mathbf{U}=\mathbf{u})/J^*(\mathbf{u})}$ for at least one particular $\mathbf{u}$.
+In that sense, $J(\checkk_1,\mathbf{U}=\mathbf{u})$ may be possibly very high.}%
+\remove{More generally, for a fixed level of confidence $p$, $\checkap$ is the slackness needed to be able to reach the probability $p$.
+% So, in addition to the value of the estimate $\checkkp$, we have an indicator of the robustness associated.
+We can then see that it is sensible to study jointly $p$, $\checkap$ and $\checkkp$.}
+\added{We have then introduced the \RRE, a family of estimators among which we can choose either large level of confidence $p$ \textit{i.e.} a large robustness as we are controlling the relative regret for a large fraction of possible configurations, or we can look for almost optimal performances albeit for a more reduced number of situations.
+Those quantities require the evaluation and optimisation of probabilities, so solving such a problem can be quite challenging.
+Moreover, the choice of a member of the \RRE, that is the choice of a level of confidence $p$ is also up to the modeller.}
 
@@
 
-By considering the particular case where $p=1$, a relation between $\checkk_1$ and $\checka_1$ can be derived, by using Eq.~\eqref{eq:def_alpha_check} and the strict positivity of the cost function: \victor{\# 8: if the probability distribution Pu is perfectly known for the chance constraint, it seems to be trivial to the sample average approximation (SAA) method.
+\subsection{\remove{Choosing the relaxation coefficient}\added{Choice and computation of the relaxation coefficient}}%Finding a balance between $p$ and $\checkap$}%Selection of a level of confidence}
+\label{ssec:balance}
+\added{\subsubsection{Almost-surely bounded relative-regret}}
+
+\added{Let us first consider that we want to satisfy the chance constraint of Eq.~\eqref{eq:chance_constraint_formulation} almost surely: this is the particular case}
+\remove{By considering the particular case}\remove{where}\added{of} $p=1$.
+\added{Given the strict positivity of $J$, the choice of such a level of confidence is possible only if there exists a $\mathbf{k}$ such that the ratio $J(\mathbf{k},\mathbf{U})/J^*(\mathbf{U})$ is bounded almost surely, and}
+\added{
+$\alpha_1$ is the solution of the (almost-surely) chance constrained problem:
+\begin{linenomath*}
+  \begin{equation}
+    \label{eq:chance_as}
+    \left\{
+    \begin{array}{rl}
+      \min & q \\
+      \text{s.t.} & % \max_{\mathbf{k} \in \Kspace}
+                    \min_{\mathbf{k}}\frac{J(\mathbf{k}, \mathbf{U})}{J^*(\mathbf{U})} \leq q \quad % \forall \mathbf{k} \in \Kspace 
+                    \text{ a.s.}
+    \end{array} \right.
+\end{equation}
+\end{linenomath*}
+}
+
+\remove{ and }\added{thus, $\mathbf{k}_1$ verifies}
+\begin{linenomath*}
+\begin{equation}
+  \label{eq:def_alpha1} % This is eq19 originally
+  \Prob_{\mathbf{U}}\left[\frac{J(\mathbf{k}_1,\mathbf{U})}{ J^*(\mathbf{U}) } \leq \checka_1\right]=1 \added{\iff \frac{J(\mathbf{k}_1,\mathbf{U})}{J^*(\mathbf{U})} \leq \alpha_1 \quad \text{a.s.}}
+\end{equation}
+\end{linenomath*}
+
+\remove{
+  \begin{linenomath*}
+{\begin{equation}
+  % \label{eq:upper_bound_alpha_check}
+  \checka_1 = \sup_{\mathbf{u}\in\Uspace} \frac{J(\mathbf{k}_1,\mathbf{U}=\mathbf{u})}{J^*(\mathbf{u})} =  \inf_{\mathbf{k}\in\Kspace} \left\{ \sup_{\mathbf{u}\in\Uspace} \frac{J(\mathbf{k},\mathbf{U}=\mathbf{u})}{J^*(\mathbf{u})} \right\}
+\end{equation}
+\end{linenomath*}
+}
+This alternative definition of $\checka_1$ is useful to estimate it quickly whenever a grid over $\mathbb{K}\times\mathbb{U}$ has already been evaluated, thus avoiding multiple computations of $\Gamma_{\alpha}(\mathbf{k})$ until its maximum reaches $1$.
+From Eq.~{\eqref{eq:upper_bound_alpha_check}}, choosing a level of confidence equal to $1$ is then equivalent to looking for the worst-case scenario of the ratio ${J(\mathbf{k},\mathbf{U}=\mathbf{u})/J^*(\mathbf{u})}$.
+}
+
+ \added{Under the assumption that $J(\mathbf{k},\cdot)$ is continuous for all $\mathbf{k}$, this is equivalent to approaching this problem using uncertain sets to model the uncertain nature of $\mathbf{U}$:
+   \begin{linenomath*}
+  \begin{equation}
+    \frac{J(\mathbf{k}_1,\mathbf{u})}{J^*(\mathbf{u})} \leq \alpha_1 \quad \forall \mathbf{u} \in \Uspace
+  \end{equation}
+\end{linenomath*}
+
+  it follows then that
+  \begin{linenomath*}
+\begin{equation}
+  \label{eq:upper_bound_alpha_check}
+  \checka_1 = \max_{\mathbf{u}\in\Uspace} \frac{J(\mathbf{k}_1,\mathbf{U}=\mathbf{u})}{J^*(\mathbf{u})} =  \min_{\mathbf{k}\in\Kspace} \left\{ \max_{\mathbf{u}\in\Uspace} \frac{J(\mathbf{k},\mathbf{U}=\mathbf{u})}{J^*(\mathbf{u})} \right\}
+\end{equation}
+\end{linenomath*}
+
+}
+
+\added{This can then be linked to Savage's minimax approach~\cite{savage_theory_1951}, which consists in a worst-case approach for the additive regret $J - J^*$, when in Eq.~\eqref{eq:upper_bound_alpha_check} we look to minimise the worst-case scenario in terms of the ratio.}
+
+\remove{An illustration of this flaw appears in the following simple problem:
+  \begin{linenomath*}
+\begin{align*}
+  \label{eq:Jinfinite}
+  \Kspace &= \Uspace = [0,\,+\infty) \\
+  J(\mathbf{k},\mathbf{U}=\mathbf{u}) &= \mathbf{u}(\mathbf{k}-\mathbf{u})^2 + 1 \\
+  \mathbf{k}^*(\mathbf{u}) &= \mathbf{u} \\
+  J^*(\mathbf{u}) &= 1
+\end{align*}
+\end{linenomath*}
+
+In this case, for each $\mathbf{k}\in \Kspace$, $\lim_{\mathbf{u} \rightarrow + \infty} {J(\mathbf{k},\mathbf{U}=\mathbf{u})/J^*(\mathbf{u})} = + \infty$, so there is no $\mathbf{k}$ such that the ratio $J/J^*$ can be bounded, hence $\alpha_1$ does not exist in this case.
+}
+
+% \remove{a relation between $\checkk_1$ and $\checka_1$ can be derived, by using Eq.~\eqref{eq:def_alpha_check} and the strict positivity of the cost function:}
+
+\victor{\# 8:  For Equation (19), if the probability distribution Pu is perfectly known for the chance constraint, it seems to be trivial to the sample average approximation (SAA) method.
 How can the authors quantify the error of using this approximation method?
 Will it have an impact on the calibration results?
-The authors should explain it in detail}
-\begin{equation}
-  \label{eq:def_alpha1}
-  \Prob_{\mathbf{U}}\left[\frac{J(\mathbf{k}_1,\mathbf{U})}{ J^*(\mathbf{U}) } \leq \checka_1\right]=1
-\end{equation}
-it follows then that 
-\begin{equation}
-  \label{eq:upper_bound_alpha_check}
-  \checka_1 = \sup_{\mathbf{u}\in\Uspace} \frac{J(\mathbf{k}_1,\mathbf{U}=\mathbf{u})}{J^*(\mathbf{u})} =  \inf_{\mathbf{k}\in\Kspace} \left\{ \sup_{\mathbf{u}\in\Uspace} \frac{J(\mathbf{k},\mathbf{U}=\mathbf{u})}{J^*(\mathbf{u})} \right\}
-\end{equation}
-
-This alternative definition of $\checka_1$ is useful to estimate it quickly whenever a grid over $\mathbb{K}\times\mathbb{U}$ has already been evaluated, thus avoiding multiple computations of $\Gamma_{\alpha}(\mathbf{k})$ until its maximum reaches $1$.
-From Eq.~\eqref{eq:upper_bound_alpha_check}, choosing a level of confidence equal to $1$ is then equivalent to looking for the worst-case scenario of the ratio ${J(\mathbf{k},\mathbf{U}=\mathbf{u})/J^*(\mathbf{u})}$.
-Therefore it may suffer from the same pitfall as the worst-case approach.
-As mentioned in the introduction, this is not suited for random variable with unbounded support as it may return over-conservative solution, provided that a solution exists in the first place.
-
-$\checkap$ can be an indicator of the robustness of $\checkkp$.  
+The authors should explain it in detail.}
+
+\added{
+ Using Sample Average Approximation (SAA), based on $N$ i.i.d.\ samples of $\mathbf{U}$: $\{\mathbf{u}^i\}_{1 \leq i \leq N}$, we can reformulate the problem Eq.~\eqref{eq:chance_as} as
+ \begin{linenomath*}
+  \begin{equation}
+    \label{eq:SAA_approx_as}
+    \left\{
+    \begin{array}{rl}
+      \min & q \\
+      \text{s.t.} & \min_{\mathbf{k}}\frac{J(\mathbf{k}, \mathbf{u^i})}{J^*(\mathbf{u^i})} \leq q \quad \text{ for }1\leq i \leq N 
+    \end{array} \right.
+  \end{equation}
+\end{linenomath*}
+
+  For a solution $\hat{\alpha}_1$ of Eq.~\eqref{eq:SAA_approx_as}, as SAA acts as a relaxation of the initial problem Eq.~\eqref{eq:chance_as}, the solution found acts as lower bound on the true value $\alpha_1$: $\hat{\alpha}_1 \leq \alpha_1$.
+
+  Moreover, this estimated value $\hat{\alpha}_1$ can be used for the estimation of the relaxation constant for a level $p$ close to $1$.
+Using Clopper-Pearson intervals~\cite{luedtke_sample_2008,thulin_cost_2014}, if $\hat{\alpha}_1$ is a solution of Eq.~\eqref{eq:SAA_approx_as}, it is also a feasible solution of Eq.~\eqref{eq:chance_constraint_formulation} at a level $p=\left(\frac{\eta}{2}\right)^{1/N}$ with probability $1-\eta$: $\hat{\alpha}_1$ is then a probabilistic upper bound on $\alpha_{\left(\frac{\eta}{2}\right)^\frac{1}{N}}$.
+  \begin{linenomath*}
+\begin{equation}
+  \label{eq:CPinterval_alpha1}
+  \hat{\alpha}_1 \in \left[\alpha_{\left(\frac{\eta}{2}\right)^{1/N}},  \alpha_1 \right]\text{ with probability }1-\eta
+\end{equation}
+\end{linenomath*}
+
+  % $\Prob_{\mathbf{U}}\left[J(\hat{\mathbf{k}}_1,\mathbf{u}) \leq J^*(\mathbf{u})\right] \geq \left(\eta /2 \right)^{1/N}$ with probability $\eta$, so
+  % $\Prob_{\mathbf{U}}\left[\left(\eta /2 \right)^{1/N} \leq \hat{\alpha}_1\right] = \eta$. $\hat{\alpha}_1 \in [\left(\eta /2 \right)^{1/N}, 1]$ with probability $\eta$.
+  % \begin{align}
+  %   \frac{1}{N}\log(\eta) -\frac{\log(2)}{N} \leq \log \hat{\alpha}_1 \\
+  %   N \geq \frac{\log \eta - \log 2}{\log \hat{\alpha}_1}
+  % \end{align}
+The estimated value $\hat{\alpha}_1$ will then be optimistic in the sense that it will underestimate the true value $\alpha_1$.
+We can however control this approximation using the probabilistic bound lower bound of Eq.~\eqref{eq:CPinterval_alpha1}}
+
+\added{Choosing a level of confidence $p=1$}\remove{Therefore it may} suffers from the same pitfall as the worst-case approach,\remove{As mentioned in the introduction, this is not suited for random variable with unbounded support} as it may return over-conservative solutions, provided that a solution exists in the first place.
+
+\remove{$\checkap$ can be \added{interpreted as} an indicator of the robustness of $\checkkp$.  
 A high value of $\checka_1$ corresponds to a high ratio ${J(\mathbf{k},\mathbf{U}=\mathbf{u})/J^*(\mathbf{u})}$ for at least one particular $\mathbf{u}$.
@@
 % So, in addition to the value of the estimate $\checkkp$, we have an indicator of the robustness associated.
-We can then see that it is sensible to study jointly $p$, $\checkap$ and $\checkkp$.
-
-\subsection{Choosing the relaxation coefficient}%Finding a balance between $p$ and $\checkap$}%Selection of a level of confidence}
-\label{ssec:balance}
-
-In order to choose the quantities introduced above, there are three choices: either fixing $p$, either fixing the maximal threshold $\alpha$, or looking for a compromise between $p$ and $\alpha$.
-The most trivial way is to set $\alpha$, to find the couples of points $(\mathbf{k},\mathbf{u})$ verifying $J(\mathbf{k},\mathbf{U}=\mathbf{u}) \leq \alpha J^*(\mathbf{u})$, and then to estimate the probability $\Gamma_{\alpha}(\mathbf{k})$ defined in Eq.~\eqref{eq:def_Ralpha}.
-For instance, when $N$ sampled values of $\mathbf{U}$: $\{\mathbf{u}^i\}_{1\leq i \leq N}$ are available, a possible estimator of $\Gamma_{\alpha}$ is
-\begin{equation}
-\hat{\Gamma}_{\alpha}(\mathbf{k}) = \frac{\mathrm{Card} \left\{\mathbf{u}^i \mid J(\mathbf{k},\mathbf{U}=\mathbf{u}^i) \leq \alpha J^*(\mathbf{u}^i)\right\}}{N}
-\end{equation}
-However, this may be a risky approach.
-Indeed if $\alpha$ is chosen too small, the resulting $\hat{p}=\max_{\mathbf{k}} \hat{\Gamma}_{\alpha}(\mathbf{k})$ will be also small, meaning that the cost function will have non acceptable values with high probability.
-
-Similarly, if $p$ is fixed, the corresponding $\hat{\checka}_p$ is computed by searching for the smallest $\alpha$ satisfying $\max_{\mathbf{k}} \hat{\Gamma}_{\alpha}(\mathbf{k})=p$.
-Once again, if $\hat{\checka}_p$ is too large, the relaxation needed to get acceptable values with probability $p$ is very high, so the resulting estimation $\hat{\checkk}_p$ may not be relevant for the future application.
+We can then see that it is sensible to study jointly $p$, $\checkap$ and $\checkkp$.}
+
+\added{\subsubsection{Estimation of \RRE}}
+\added{We are now going to focus on the more general case, where we can choose: to fix $p \leq 1$ and deduce $\alpha_p$, or to set a maximal threshold $\alpha$ and maximise the measure of the acceptable region, or finally to find a compromise $p$ and $\alpha_p$ in order to keep the latter not too large.}
+\remove{In order to choose the quantities introduced above, there are three choices: either fixing $p$, either fixing the maximal threshold $\alpha$, or looking for a compromise between $p$ and $\alpha$.}
+
+\added{A first approach}\remove{The most trivial way} is to set $\alpha$, \added{and then to estimate the function $\mathbf{k}\mapsto\Gamma_{\alpha}(\mathbf{k})$ % = \Prob_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U}) \leq \alpha J^*(\mathbf{U})\right]$
+  as} \remove{\added{and then }to find the couples of points $(\mathbf{k},\mathbf{u})$ verifying $J(\mathbf{k},\mathbf{U}=\mathbf{u}) \leq \alpha J^*(\mathbf{u})$, and \added{use these} to estimate the probability $\Gamma_{\alpha}(\mathbf{k})$} defined in Eq.~\eqref{eq:def_Ralpha}.
+For instance, when $N$ samples from $\mathbf{U}$ are available, namely $\{\mathbf{u}^i\}_{1\leq i \leq N}$, a possible estimate of $\Gamma_{\alpha}$ is
+\begin{linenomath*}
+\begin{equation}
+\hat{\Gamma}_{\alpha}(\mathbf{k}) = \frac{\mathrm{Card} \left\{\mathbf{u}^i \mid J(\mathbf{k},\mathbf{U}=\mathbf{u}^i) \leq \alpha J^*(\mathbf{u}^i)\right\}}{N} \added{ = \frac{1}{N} \sum_{i=1}^N \mathbbm{1}_{\{J(\mathbf{k},\mathbf{U}=\mathbf{u}^i) \leq \alpha J^*(\mathbf{u}^i)\}}}
+\end{equation}
+\end{linenomath*}
+
+\added{This expression is maximised with respect to $\mathbf{k}$, giving $\hat{p}=\max_{\mathbf{k}}\hat{\Gamma}_{\alpha}(\mathbf{k})$.
+We can also provide a confidence interval for the true value of $\Gamma_{\alpha}(\textbf{k})$ where $\textbf{k} = \argmax \hat{\Gamma}_{\alpha}$.}
+
+\added{However, unless the modeller has some precise idea of desired relaxation, doing so may lead to an unsatisfactory pairing of $\alpha$ and $p$.}\remove{However, this may be a risky approach.} Indeed if $\alpha$ is chosen too small, the resulting $\hat{p}=\max_{\mathbf{k}} \hat{\Gamma}_{\alpha}(\mathbf{k})$ will be also small, meaning that the cost function will have non acceptable values with high probability.
+
+Similarly, if $p$ is fixed, the corresponding $\hat{\checka}_p$ is computed by searching for the smallest $\alpha$ satisfying $\max_{\mathbf{k}} \hat{\Gamma}_{\alpha}(\mathbf{k})=p$\added{, or equivalently, by minimizing the quantile of order $p$ of the relative-regret, which is the ratio $J/J^*$}.
+Once again, if $\hat{\checka}_p$ is too large, \added{the cost function may not be controlled enough for the contemplated application.}\remove{ the relaxation needed to get acceptable values with probability $p$ is very high, so the resulting estimation $\hat{\checkk}_p$ may not be relevant for the future application.}
 
 % \victor{chapeau car ici je parle de l'estimation en pratique}
-Also, choosing $p=1$ is possible only if the sample space of $\mathbf{U}$ is bounded. An illustration of this flaw appears in the following simple problem:
-\begin{align*}
-  \label{eq:Jinfinite}
-  \Kspace &= \Uspace = [0,\,+\infty[ \\
-  J(\mathbf{k},\mathbf{U}=\mathbf{u}) &= \mathbf{u}(\mathbf{k}-\mathbf{u})^2 + 1 \\
-  \mathbf{k}^*(\mathbf{u}) &= \mathbf{u} \\
-  J^*(\mathbf{u}) &= 1
-\end{align*}
-In this case, for each $\mathbf{k}\in \Kspace$, $\lim_{\mathbf{u} \rightarrow + \infty} {J(\mathbf{k},\mathbf{U}=\mathbf{u})/J^*(\mathbf{u})} = + \infty$, so there is no $\mathbf{k}$ such that the ratio $J/J *$ can be bounded, hence $\alpha_1$ does not exist in this case.
+
+% \added{
+%   \begin{equation}\label{eq:SAAchance_constraint}
+%   \left\{
+%   \begin{array}{rl}
+%     \min_{\mathbf{k} \in \Kspace} & q \\
+%     \text{such that} &\frac{J(\mathbf{k},\mathbf{u}_i)}{J^*(\mathbf{u}_i)}  - q \leq M_i z_i \\
+%                                   & \sum_{i=1}^N z_i \leq \gamma N \\
+%                                   &z_i \in \{0, 1\}  \\
+%                                   & M_i \geq \max_{\mathbf{k}} J(\mathbf{k},\mathbf{u}_i)/J^*(\mathbf{u}_i)
+%   \end{array}
+%   \right.
+% \end{equation}}
 
@@
 We have seen how some classical robust estimators and the \RRE{} behave on two different analytical problems.
-In addition to the usual levels of confidence such as 90\% and 95\%, one can also settle for an ad-hoc compromise, where $p$ maximizes the ratio $p/\alpha_p$.
+In addition to the usual levels of confidence such as 90\% and 95\%, one can also settle for an ad-hoc compromise, where $p$ maximises the ratio $p/\alpha_p$.
 When the sample space of $\mathbf{U}$ is bounded, a conservative solution is to set $p=1$.
@@
 The misfit $\mathcal{G}$ is defined as the difference between the numerical model and the observation. Choosing a squared norm, the cost function $J$ defined in Eq.~\eqref{eq:def_cost_fun} is
+\begin{linenomath*}
 \begin{equation}
@@
 \end{equation}
+\end{linenomath*}
+
 \subsection{The Shallow Water equations}
@@
 
+\begin{linenomath*}
 \begin{align}
@@
 \end{align}
+\end{linenomath*}
 
@@
 The true value of the bottom friction $\mathbf{k}^{\mathrm{true}} = (k_1^{\mathrm{true}}, k_2^{\mathrm{true}},\dots, k_{N_\mathrm{vol}}^{\mathrm{true}})$ is not constant over the whole domain, and is defined as
-\begin{equation*}
+\begin{linenomath*}
+\begin{equation}
 {k}^{\mathrm{true}}_i = 0.2\cdot \left(1 + \sin\left(\frac{2 \pi x_i}{L}\right)\right)
-\end{equation*}
+\end{equation}
+\end{linenomath*}
+
 where $x_i$ is the center of the $i$-th volume. The two sources of systematic errors are the one-dimensionality of $\Kspace$, and $\omega_0$.
@@
 
+\begin{linenomath*}
 \begin{equation}
@@
 The Continuous ranked probability score (CRPS) measures the squared difference between the predicted CDF $F_{\mathrm{pred}}$ using a calibrated value, and the CDF of the observations $F_{\mathrm{pred}}^o$.
+\begin{linenomath*}
 \begin{equation}
@@
 
-Our approach is based on the will to be as close as possible to the conditional minimisers with high probability.
+\added{Our approach is based on the comparison of the objective function to the optimal value it can attain, given a realisation of the uncertain variable.
+By constraining this ratio in terms of probability, the modeller can then minimize the frequency at which the relative error of the objective function will exceed a prescribed threshold.
+Alternatively, at a level of confidence $p$, the associated threshold $\alpha_p$ bounds the relative deviation of the objective function for the proportion $p$ of the most favourable cases.
+The resulting estimate can then be assessed robust, as it corresponds to values of the objective function as close as possible to the optimal values.}
+
+\remove{Our approach is based on the will to be as close as possible to the conditional minimisers with high probability.
 At a level $p$, in addition to the estimation, we have the relaxation coefficient $\alpha_p$ that bounds with probability $p$ the relative error of the cost function.
-This helps us to assess the robustness properties of the proposed estimation.
-
+This helps us to assess the robustness properties of the proposed estimation.}
 Except for simple analytical examples, the exact evaluation of a member of the \RRE{} is very expensive computer-wise, not to say impossible.
@@
 
-Comparing the performances of the different estimates in a forecast context, one can see that for the two metrics introduced in Section~\ref{sec:SWE_application}, $\kest_1$ performs better than $\hatkmean$, but is sometimes outperformed by ``non-robust'' solutions.
-Those require some additional knowledge about the environmental conditions, and did not present some robust properties during the calibration phase.
+\remove{Comparing the performances of the different estimates in a forecast context, one can see that for the two metrics introduced in Section~\ref{sec:SWE_application}, $\kest_1$ performs better than $\hatkmean$, but is sometimes outperformed by ``non-robust'' solutions.
+Those require some additional knowledge about the environmental conditions, and did not present some robust properties during the calibration phase.}
 
 Practically speaking, the estimation of those quantities is very crude, so the computational cost may be very expensive.
-As perspective, specific strategies have to be created, based for instance on sequential design of computer experiments using Gaussian processes, to diminish the amount of runs needed of the numerical model.
-Ideally, one would want to develop an acquisition criterion, that makes the balance between the minimisation of a well-chosen probability of failure, and the exploration around the conditional minimisers.
+As perspective, specific strategies have to be created in order to \added{carefully select each additional point that will be evaluated, and thus reduce} the amount of \added{evaluations}\remove{runs} needed of the numerical model.
+\added{This selection can be} based for instance on sequential design of computer experiments using Gaussian processes\added{~\cite{ginsbourger_towards_2010}}.
+\remove{Ideally, one would want to develop an acquisition criterion, that makes the balance between the minimisation of a well-chosen probability of failure, and the exploration around the conditional minimisers.}
 Finally, the models upon which this calibration procedure have been applied are very simplistic.
@@
 \bibliographystyle{model1-num-names} 
-\bibliography{biblio_file}
+\bibliography{bibexport.bib}
 
@@
 
-\endinput
-%%
-%% End of file `elsarticle-template-num-names.tex'.
+% \endinput
+% %%
+% %% End of file `elsarticle-template-num-names.tex'.
 

### 2020-10-25 summary_of_changes.tex
accepted version + zip of src

\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage[utf8]{inputenc}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{calc}
\usepackage{caption}
% \usepackage{zref-xr}
% \externaldocument{article}
\usepackage{easy-todo}
\usepackage{comment}
\usepackage{lipsum}
\usepackage{bbm}
\usepackage{fancyhdr}
\usepackage{tikz}
\usepackage{pdfpages}
\newcommand{\Var}{\mathbb{V}\text{ar}}
\newcommand{\Ex}{\mathbb{E}}
\newcommand{\Prob}{\mathbb{P}}
\DeclareMathOperator*{\argmin}{arg\,min \,}
\DeclareMathOperator*{\argmax}{arg\,max \,}
\usepackage{hyperref}
\usepackage{booktabs}

\begin{document}
\title{JCOMP-D-20-00132: Summary of the changes:\\
  Robust calibration of numerical models based on relative regret
}

\maketitle
\emph{Abstract (p.1)}
\begin{itemize}  
\item l.~5-8: clarified the distinction between control parameters, and uncontrollable random variables
\item l~.11-16: highlighted the role and novelty of the relative regret in this article
\end{itemize}
\emph{Introduction (p.1)}
\begin{itemize}
\item l.~34-37: added source of aleatoric uncertainties for ocean modelling
\item l.~38-48: added effect of omitting the uncertainties in problems
\item l.~48-51: added examples of the necessity of taking into account uncertainties, from a risk management perspective
\item l.~52-56: added different vocabulary found in the literature which convey the same idea
\item l.~57: fixed some typos and english mistakes.
\item l.~60: we explicit the knowledge of the distribution of $\mathbf{U}$.
\item l.~64: added state-of-the-art strategies to model aleatoric uncertainties and citation to Ning \& You.
\item l~.66-68: we clarify that the distributinto $\mathbf{U}$ is not dependent on the value of $\mathbf{k}$
\item l.~73: a reference to an exemple of such a cost function is added
\item l.~82: fixed typo
\item l.~84-85: added the mention of distributional robustness 
\item l.~92: added mention of overcalibration
\item l.~83: typo
\item l.~96,98,99: reformulation for clarity
\item l.~109: added rationale of the relative regret
\item l.~115: typo
\end{itemize}
\emph{Section 2 (p.5)}
\begin{itemize}
\item l.~119: change for clarification
\end{itemize}
\emph{Section 3.1 (p.11)}
\begin{itemize}
\item l.~232-238: clarification of the construction and definition of the relative-regret 
\item l.~253: added reminder that $\mathbf{K}^*$ is discrete.
\item l.~261-272: comparison between additive and relative regret, and justification of the use of relative-regret
\item l.~278-279: formulation of the problem in terms of chance-constraints in Eq.~(20)
\item l.~281-282: clarification of the link with the Value-at-Risk 
\item l.~283-286: interpretation of $\alpha_p$ in terms of bounding probabilistically the relative-error
\item l.~287-288: rewrote the definition of the RRE
\item l.~289-291: typo and english reformation
\item Figure 4 (p.14): changed linestyle, and added quick interpretation in the caption 
\item l.~293: added small synthesis on the properties of the RRE
\end{itemize}
\emph{Section 3.2 (p.14)}
  \begin{itemize}
\item l.~301: added subsection Almost-surely bounded relative-regret
\item l.~302-308: formulation of the a.s.\ bounded relative-regret in terms of chance constraint in Eq.~(21) and property verified by $\mathbf{k}_1$ and $\alpha_1$
\item l.~309-314: link with uncertain set and Savage's minimax approach for decision under uncertainty
\item l.~315-317: SAA formulation of the a.s. bounded constraint
\item l.~317-325: Probabilistic bounding of $\alpha_1$, and level $p=(\eta/2)^{1/N}$ guaranteed probabilistically
\item l.~330-333: clarify formulation of the general case $p \leq 1$
\item l~.336-337: estimation of $\Gamma_\alpha$ with indicator functions (Eq.~(27))
\item l~.339: possibility of unsatisfactory $(p, \alpha_p)$
\item l.~344: minimization of the quantile of order $p$ of the ratio $J / J^*$.
\end{itemize}
 \emph{Conclusion (p.31)}
\begin{itemize}
\item l~.557-564: summary of the robustness aspect of the RRE
\item l~.578-580: reformulation of the sequential design of experiment strategies.
\end{itemize}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2021-09-16 robust_calibration_relative_regret/article.tex
folder structures

--- 2020-10-25 source_files/article.tex
@@
 
-\documentclass[preprint,review, 1p]{elsarticle}
+\documentclass[preprint, review, 1p]{elsarticle}
 
@@
 %% please give \usepackage{epsfig}
-% \usepackage{jcomp}
+%\usepackage{jcomp}
 % \usepackage{framed,multirow}
@@
 \newcommand{\remove}[1]{{\color{red} {}}}
-\newcommand{\added}[1]{{\color{teal} #1}}
+\newcommand{\added}[1]{% {\color{teal}
+    #1}
 \usepackage{url}
@@
 
-\newcommand*\linenomathpatchAMS[1]{%
-  \expandafter\pretocmd\csname #1\endcsname {\linenomathAMS}{}{}%
-  \expandafter\pretocmd\csname #1*\endcsname{\linenomathAMS}{}{}%
-  \expandafter\apptocmd\csname end#1\endcsname {\endlinenomath}{}{}%
-  \expandafter\apptocmd\csname end#1*\endcsname{\endlinenomath}{}{}%
-}
-\expandafter\ifx\linenomath\linenomathWithnumbers
-  \let\linenomathAMS\linenomathWithnumbers
-  %% The following line gets rid of an extra line numbers at the bottom:
-  \patchcmd\linenomathAMS{\advance\postdisplaypenalty\linenopenalty}{}{}{}
-\else
-  \let\linenomathAMS\linenomathNonumbers
-\fi
-\linenomathpatchAMS{gather}
-\linenomathpatchAMS{multline}
-\linenomathpatchAMS{align}
-\linenomathpatchAMS{alignat}
-\linenomathpatchAMS{flalign}
 \begin{document}
-\linenumbers
+% \linenumbers
 %% Title, authors and addresses
@@
 \label{eq:def_Ralpha}
-R_{\alpha}(\mathbf{k}) = \left\{ \mathbf{u} \in \Uspace \mid J(\mathbf{k},\mathbf{U}=\mathbf{u}) \leq \alpha J^*(\mathbf{u}) \right\}
+R_{\alpha}(\mathbf{k}) = \left\{ \mathbf{u} \in \Uspace \mid J(\mathbf{k},\mathbf{u}) \leq \alpha J^*(\mathbf{u}) \right\}
 \end{equation}
@@
 This linked to the definition of the distribution of the minimisers $\mathbf{K}^*$.
-For instance, if $\Kspace$ is a discrete set, \added{$\mathbf{K}^*$ is a discrete random variable}, and we can rewrite $\Gamma_1$ as $\Gamma_1(\mathbf{k})=\Prob_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U}=\mathbf{u}) = J^*(\mathbf{U})\right] = \Prob_{\mathbf{U}}\left[\mathbf{k} = \mathbf{k}^*(\mathbf{U})\right]$ which is the probability mass function of $\mathbf{K}^*$.
+For instance, if $\Kspace$ is a discrete set, \added{$\mathbf{K}^*$ is a discrete random variable}, and we can rewrite $\Gamma_1$ as $\Gamma_1(\mathbf{k})=\Prob_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U}) = J^*(\mathbf{U})\right] = \Prob_{\mathbf{U}}\left[\mathbf{k} = \mathbf{k}^*(\mathbf{U})\right]$ which is the probability mass function of $\mathbf{K}^*$.
 
@@
 \bibliographystyle{model1-num-names} 
-\bibliography{bibexport.bib}
+\bibliography{}
 
